### 2018-02-17 ionic_liquids.tex
added relevant files

%\documentclass[3p,preprint]{elsarticle}
\documentclass[3p,twocolumn]{elsarticle}
\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{commath}
\usepackage{amssymb}
\usepackage{scalerel}

\usepackage{adjustbox}   
\usepackage{threeparttable}
\usepackage{booktabs}
\usepackage{colortbl} 
\usepackage{xcolor}
\usepackage{float}
\usepackage{flafter}
\newcommand{\diff}[2]{\dfrac{\partial #1}{\partial #2}}

\biboptions{sort&compress}
\modulolinenumbers[5]

\journal{Journal of \LaTeX\ Templates}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%
%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{A molecular dynamics study of the solvation of CO\textsubscript{2}, water, and some organic compounds in the ionic liquids [emim][B(CN)\textsubscript{4}] and [emim][NTf\textsubscript{2}]}

%% Group authors per affiliation:
\author[rvt]{A.J.~Silveira}
\author[rvt]{S.~Pereda}
\author[focal,els]{F.W.~Tavares}
\author[focal]{C.R.A.~Abreu\corref{cor1}}
\ead{abreu@eq.ufrj.br}

\address[rvt]{Planta Piloto de Ingenier\'ia Qu\'imica, PLAPIQUI, Universidad Nacional del Sur,Camino La Carrindanga Km 7-CC: 717, Bah\'ia Blanca, Argentina}
\address[focal]{Chemical Engineering Department, Escola de Qu\'imica, Universidade Federal do Rio de Janeiro,Rio de Janeiro, RJ 21941-909, Brazil}
\address[els]{COPPE, Universidade Federal do Rio de Janeiro, Rio de Janeiro, RJ 21941-909, Brazil}

\cortext[cor1]{Corresponding author}

\begin{abstract}
In this paper we predict solvation in ionic liquids and macroscopic properties required in the design of chemical processes. Carbon dioxide produced in combustion processes is one of the main sources of anthropogenic generation of greenhouse gases. On the other hand, the potential of [emim][B(CN)\textsubscript{4}] for its capture has recently been reported. For comparison, the solvents [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N] were analyzed, both in the condition of infinite dilution and at high concentrations. The simulations confirmed what was observed experimentally, that is, a considerably lower pressure is required in [emim][B(CN)\textsubscript{4}] to obtain the same molality of CO\textsubscript{2}. The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in [emim][B(CN)\textsubscript{4}] were also calculated, and a comparison was made with experimental values recently reported in the literature.
\end{abstract}

\begin{keyword}
ionic liquids \sep solvation free energy \sep  CO\textsubscript{2} 
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}
State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results.

The CO\textsubscript{2} emissions from power generation plants are still sources of anthropogenic greenhouse gases~\cite{totalenergy} and the searching of solvents is an active field of research. Post combustion absorption technologies flue gas

Basically, the conventional process for CO\textsubscript{2} removal involves a chemical absorption followed by stripping at high temperatures. The solvents commonly used are volatile organic compounds, specially aqueous solutions of monoethanolamine (MEA). Despite its high absorption capability, the use of MEA suffers from a serious drawback in that there is considerable cost due to the energy consumption in the solvent recovery~\cite{Merkel_2010}. Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes with ambient pollution and generates extra costs for substituting the solvent.

The investigation of ionic liquids (ILs) as alternative solvents for CO\textsubscript{2} sequestration occupies a central place. The reasons in their well known properties, such as the negligible vapor pressure and high thermal stability. Furthermore, they are particularly attractive because they can be designed for specific applications, giving rise to the so-called task-specific ionic liquids~\cite{Seo_2014}. These remarkable properties makes ionic liquids suitable for a wide variety of applications in separation processes~\cite{Han_2010,Werner_2010}, catalysis~\cite{P_rvulescu_2007}, energy~\cite{MacFarlane_2014} and material science~\cite{Mecerreyes_2011,Tom_2015,Dupont_2010,Leones_2017,Kinik_2017}.

Recently, the potentiality of ionic liquids for CO\textsubscript{2} capture has been called into question by Carvalho~\textit{et al.}~\cite{Carvalho_2016}, who warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposed absorption capability of certain ionic liquids. While most thermodynamic models are developed based on molar fraction, the key factor to determine the absorption process efficiency is given by the amount of CO\textsubscript{2} that can be dissolved in a certain volume or mass of solvent. By expressing the solubility in terms of molality and performing an exhaustive comparison between various ionic liquids, Ref.~\cite{Carvalho_2016} shows that most systems which promote a physical absorption of CO\textsubscript{2} exhibit a CO\textsubscript{2} solubility similar or even lower than that observed for the heavy alkane eicosane. This is true for the ``popular'' [bmim][Tf\textsubscript{2}N], [bmim][PF\textsubscript{6}], [bmim][BF\textsubscript{4}], as well as for those synthesized from the fluorination of the cation or the anion, such as [(C\textsubscript{2}H\textsubscript{2}F\textsubscript{2})mim][NTf\textsubscript{2}] and [hmim][pFAP], the only exception being the family of ionic liquids containing the anion tetracyanoborate [B(CN)\textsubscript{4}]$^{-}$.

There is no obvious explanation accounting for the enhanced solubility promoted by the presence of the anion [B(CN)\textsubscript{4}]$^{-}$, whether special interactions with CO\textsubscript{2} are settled. In this sense, Molecular Simulation provides with a powerful tool for studying solvation processes. To our knowledge, only one study in the literature reports the free energy of solvation of CO\textsubscript{2} in [emim][B(CN)\textsubscript{4}] which, in addition, is overestimated. This motivated us to carry out a comparison of different force fields of [emim][B(CN)\textsubscript{4}] in terms of the free energy of solvation and, indeed,  it was possible to select a model that successfully predicts the value of the Henry constant of CO\textsubscript{2}. For comparison, the solvents [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N] were analyzed, both in the condition of infinite dilution and at high concentrations. The simulations confirmed what was observed experimentally, that is, a considerably lower pressure is required in [emim][B(CN)\textsubscript{4}] to obtain the same molality of CO\textsubscript{2}. The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in [emim][B(CN)\textsubscript{4}] were also calculated, and a comparison was made with experimental values recently reported in the literature.

This paper is organized as follows: in Section~\ref{sec:theory} we present some methodological details, including the mathematical relationships between free energy of simulated solvation and thermodynamic properties of diluted solutions. and a brief description of the force fields considered for [emim][B(CN)\textsubscript{4}], and the details of the simulations for free energy calculations are presented. The corresponding results are presented in the Section~\ref{sec:results}, where a comparison is made with the experimental data of Henry's constants, the results of the activity coefficients are shown at infinite dilution and, finally, a study of the CO\textsubscript{2} solvation is carried out in high concentrations.

\section{Theoretical background}
\label{sec:theory}

In this section, we present the formalism that allows a direct comparison between simulation results and the thermodynamic properties of dilute solutions: Henry constant and activity coefficient at infinite dilution. For this, we rely on the work of Shirts~\textit{et al.}~\cite{Shirts_2003}. Then, we reformulate the equations in order to carry out a study at concentrated conditions, which would be the more likely scenario in CO\textsubscript{2} capture processes.

\subsection*{Solvation free energy}
The solvation free energy, $\Delta G_{\text{solv}}$, is the reversible work needed to transfer a solute molecule from the gas phase to the solution. For dense systems, an efficient computation of solvation properties via molecular simulation is possible by means of the so-called alchemical methods, which employ non-physical pathways to connect the ``endpoint'' states, whose free energy difference is to be estimated. In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through a coupling parameter $\lambda$, which scales the intermolecular interactions taking values in the interval [0,1]: $\lambda$ = 1 corresponds to a fully interacting system, while for $\lambda$ = 0 the interactions between the solute and solvent molecules are completely turned-off.

In the following, the subscripts ``$s$'' and ``$\text{IL}$'' refer to the solute and the solvent (ionic liquid), respectively. For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is defined as
\begin{equation}
\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{LI},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{LI},P,T,\lambda = 0)}, 
\end{equation}
where $\bigtriangleup$ denotes the isobaric-isothermal partition function. Shirts~\textit{et al}.~\cite{Shirts_2003} presented a detailed mathematical derivation allowing to relate $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy and obtained the following expression: 
\begin{equation}
\begin{split}
\label{eq:free_solv}
 \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right) ,
\end{split}
\end{equation}
where $k_b$ is the Boltzmann's constant, $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid phase and $P_s$ is the partial pressure of the solute in the gas phase. It should be noted that in the derivation of Eq.~\ref{eq:free_solv}, the gas phase was treated as an ideal gas.

For small solutes, such as those considered in this work, the magnitude of the term $V^{\ast}/V_1$ is typically on the order of the free energy uncertainties~\cite{Shirts_2003}. Hence, that term could be neglected and will be omitted hereafter.

\subsection*{Henry constant}
If both $P_s$ and $c_s^{\ast}$ were not large, we can employ Eq.~\ref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is given by~\cite{Prausnitz}
\begin{equation}
\text{K}_s =\frac{P_s}{x_s}.
\end{equation}
Therefore, by simply expressing Eq.~\ref{eq:free_solv} in terms of the molar fraction $x_s$ and considering MW (molecular weight of the solution) = $\text{MW}_{\scaleto{LI}{4pt}}$ as well as $\rho$ (mass density of the solution) = $\rho_{\scaleto{LI}{4pt}}$, we obtain that
\begin{equation}
\label{eq:henry_eq}
K_s = \tilde{\rho}_{\scaleto{LI}{4pt}} R T \exp(\beta \, \Delta G_{\text{sim}}),
\end{equation}
where $R$ is the gas constant.

\subsection*{Infinite-dilution activity coefficient}

As will be shown below, the prediction of activity coefficients requires separate simulations in the pure solute, and in what follows we employ the superscript ``$0$'' to denote the pure solute properties.

Using standard thermodynamic relations~\cite{Tester}, we write the activity coefficient $\gamma_s$ in terms of residual chemical potentials, as follows
\begin{equation}
\label{eq:gamma}
\ln \gamma_s = \frac{1}{RT} (\mu_s^R - \mu_s^{R,0}),
\end{equation}
where $\mu_s^R$ and $\mu_s^{R,0}$ are the residual chemical potentials of the solute in the solution and in the pure solute, respectively. It is worth noting that we have used the definition $\mu_s^{R}$ (P,T) = $\mu_s$ (P,T) - $\mu_s^{ig}$ (P,T), where the superscript $ig$ refers to a solution of ideal gases. Also, recall that $\mu_s^{ig} (P,T)$ = $\mu_s^{ig,0} (P,T)$ + $RT \ln x_s$, so we have that
\begin{equation}
\mu_s^R = \mu_s^l(N_s^l,N_{LI},P,T) - \mu_s^{ig,0}(P,T) - k_b T \ln x_s. 
\end{equation}
Replacing $\mu_s^{l}$ and $\mu_s^{ig,0}$ by the corresponding expressions derived in Ref.~\cite{Shirts_2003} yields
\begin{equation}
\label{eq:mu_res}
\mu_s^R = \Delta G_{\text{sim}} - k_b T \ln \left( \frac{V^{\ast} P}{N_s^l k_b T} \right) -  k_b T \ln x_s.
\end{equation}
Of course, an analogous equation holds for $\mu_s^{R,0}$:
\begin{equation}
\label{eq:mu_res_0}
\mu_s^{R,0} = \Delta G_{\text{sim}}^{0} - k_b T \ln \left( \frac{V^{\ast,0} P}{N_s^{l,0} k_b T} \right).
\end{equation}

Considering $N_s^{l}$ = 1, which represents the infinite-dilute condition, and substituting Eqs.~\ref{eq:mu_res} and~\ref{eq:mu_res_0} into Eq.~\ref{eq:gamma}, we  obtain that
\begin{equation}
\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_{\text{sim}} - \Delta G_{\text{sim}}^{0} \right) + \frac{c_{\scaleto{LI}{4pt}}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
\end{equation}
where $c_{\scaleto{LI}{4pt}}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ correspond to the numerical densities of the solvent and the pure solute, respectively.

\subsection*{Partial pressure estimation}

For the ILs of interest to the present investigation, high concentrations of CO\textsubscript{2} are found at pressure values for which, in principle, the ideal gas assumption may be not valid. In this case, we shall correct the ideal gas contribution to the chemical potential, as follows
\begin{equation}
\label{eq:mu_gas_real}
\mu^{g}_s = \mu^{ig}_s + RT \ln \phi_s,
\end{equation}
where $\phi_s$ is the fugacity coefficient of the solute. This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate $\mu^{l}_s$ = $\mu^{g}_s$, which yields
\begin{equation}
\label{eq:fgas_d}
f^{g}_s = \exp  \left( \beta \Delta G_{\text{sim}} \right) +  k_b T c_s^{\ast}, 
\end{equation}
where $f^{g}_s$ is the fugacity of the solute in the gas phase. Having calculated $f^{g}_s$, $P_s$ could be predicted using the following equation
\begin{equation}
\label{eq:fgas}
f^{g}_s = P_s \exp\left[ \frac{B_s(T) P_s}{R T} \right],
\end{equation}
where $B_s$ corresponds to the second virial coefficient. Here we employ the correlation for CO\textsubscript{2} introduced by Holste~\textit{et al}~\cite{Holste_1987}, which is
\begin{equation}
B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
\end{equation}
where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = $-2.455297$ $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol). Actually, the prediction of $P_s$ should be iterative and in this work we propose the following scheme: (i) run an NPT simulation, (ii) calculate $\Delta G_{\text{sim}}$ and $f^{g}_s$ via Eq.~\ref{eq:fgas_d}, (iii) employ $f^{g}_s$ in Eq.~\ref{eq:fgas} to compute $P_s$ (iv) if $P_s$ $\neq$ P, repeat the above steps using $P_s$ as the specified pressure in a new NPT simulation. This is done until $P_s$ = P.

\section{Force fields}
\label{sec:force_field}
\subsection{Ionic liquids}
\label{sec:force_field_il}

The versatility of ILs for different applications is in part due to the fact that their physical properties strongly depend on the cation-anion combination. On the other hand, this characteristic also explains why the desirable transferability of force fields is particularly difficult to attain. Indeed, it is a common practice to extract the potential parameters corresponding to intramolecular (bond stretching, angle bending, torsion rotation) and Lennard-Jones interactions from a well established force field and then derive the partial atomic charges. This procedure is, however, inaccurate as in conventional force fields the determination of the atomic charges precedes the dihedrals parametrization. Another ad-hoc strategy, which intends to crudely incorporate polarization effects, is to scale the partial charges uniformly with a factor which normally takes values in the range 0.8-0.9. This practice has proven to be effective in improving the predictions of dynamic properties~\cite{Schr_der_2012}.

In this paper, we consider four models of [emim][B(CN)\textsubscript{4}]. Koller~\textit{et al.}~\cite{Koller_2012} were the first to introduce a specific non-polarizable force field of [emim][B(CN)\textsubscript{4}]. They tested three variations of a \textit{united-atoms} model, in which the alkyl groups $\text{CH}_3$ y $\text{CH}_2$ of [emim]$^{+}$ are replaced by pseudo-atoms. Among them, the ``FF-3'' model best reproduces the experimental values of density, self-diffusion coefficients and viscosity. In short, both the intramolecular and Lennard-Jones parameters of the cation were taken from the work of Liu~\textit{et al.}~\cite{Liu_2006}, which in turn is based on the AMBER~\cite{Cornell_1995} framework. The intramolecular parameters involving the boron atom were extracted from the DREIDING~\cite{Mayo_1990} force field and the anionic vdW parameters were refined based on the values reported by Price~\textit{et al.}~\cite{Price_2001}. The atomic partial charges were derived using the EA-RESP method~\cite{Basma_2001} from \textit{Post-Hartree-Fock ab-initio} calculations at MP2/6–31G$^\ast$+ level of theory, which automatically resulted in total charges on the ions of $\pm$0.8426e.

The potential parameters of [B(CN)\textsubscript{4}]$^{-}$ derived by Koller~\textit{et al.}~\cite{Koller_2012} were employed by Batista~\textit{et al.}~\cite{Batista_2015} to study aqueous solutions of [emim][B(CN)\textsubscript{4}]. In this case,  the authors considered the \textit{all-atom} model of [emim]$^{+}$ developed by Cadena and Maginn~\cite{Cadena_2006}. The atomic partial charges were obtained using the CHELP procedure~\cite{Breneman_1990}, resulting in net charges of $\pm$0.889$e$ on the ions. It should be noted that those force fields consider different scaling factors for 1-4 non-bonded interactions: Cadena and Maginn~\cite{Cadena_2006} use values of 1.0 y 0.4 for the Lennard-Jones and Coulombic interactions, respectively, while in Koller~\textit{et al.}~\cite{Koller_2012} the corresponding factors are 0.5 y 5/6, in accordance with AMBER force field. Batista~\textit{et al.}~\cite{Batista_2015} employ the same factors as Cadena and Maginn~\cite{Cadena_2006} (J.P. Coutinho, personal communication).

Another set of parameters for [emim][B(CN)\textsubscript{4}] was derived by Liu \textit{et al.}.~\cite{Liu_2014} in a study that investigates the dynamics of CO\textsubscript{2} and N\textsubscript{2} in that IL. Parameters corresponding to the intramolecular and Lennard-Jones interactions were extracted from GAFF~\cite{Wang_2004}, while the atomic partial charges were computed using the RESP method~\cite{Bayly_1993} from \textit{DFT}/B3LYP/6-311+G(d) calculations. The net charges of the ions were manually adjusted to a value of $\pm$0.8$e$.

We also consider the parametrization recently reported by Weber and Kirchner~\cite{Weber_2016}, which is based on the force field developed by P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}. The potential parameters for the anion are not specified in Refs.~\citenum{Weber_2016} and~\citenum{Canongia_Lopes_2006}, and we obtained them by a direct communication with the authors of Ref.~\citenum{Weber_2016}. The atomic partial charges were derived using the RESP procedure from \textit{Hartree-Fock} calculations at 6-31++G$^{\ast \ast}$ level of theory, resulting in net charges of $\pm$0.8$e$.

Finally, for [emim][Tf\textsubscript{2}N] we use the model of K\"{o}ddermann~\textit{et al}~\cite{K_ddermann_2007}, which result from ``refining'' the force field due to P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}. This ``refining'' was characterized by their authors as unusual, given that the LJ parameters were modified, while keeping the partial charges at their original values. This model was recently employed by Kerl~\textit{et al.}~\cite{Kerl__2017}, who were able to accurately predict Henry's constant for CO\textsubscript{2} at several temperatures.

\subsection{Solutes}
\label{sec:force_field_sol}

The solutes considered here are hexane, benzene, CO\textsubscript{2}, ethanol, cyclohexane and water. Hexane and benzene were modeled using the OPLS-AA force field~\cite{Jorgensen_1996}, while the TRAPPE potential~\cite{Chen_2001,Potoff_2001} was employed for ethanol and CO\textsubscript{2}. Cyclohexane was simulated using a rigid-body model~\cite{munoz2015lennard} whose sites only interact via the Lennard-Jones potential and for water we employ the TIP4P/2005 model~\cite{Abascal_2005,Vega_2011}.

\section{Computational details}
\label{sec:sim_details}

The gradual insertion/deletion of charged solutes involves scaling both the van der Waals (vdW) and the electrostatic intermolecular interaction. In order to avoid numerical instabilities associated to the vdW scaling, a standard approach is to employ a soft-core potential with a nonlinear coupling, and in this paper we use the modified Lennard-Jones potential due to Beutler~\textit{et al.}~\cite{Beutler_1994}. The electrostatic interactions, on the other hand, can be handled simply by a linear scaling~\cite{Naden_2015}. Furthermore, the contributions to $\Delta G$ originating at the different types of coupling can be taken into account separately, as follows
\begin{equation}
\begin{split}
\Delta G_{\text{sim}} =& \; \Delta G_{\,\text{vdW}} (\lambda_{\,\text{vdW}} = 0\rightarrow  1, \lambda_{\, \text{Coul}} = 0) \\
+ \; &\Delta G_{\,\text{Coul}} (\lambda_{\, \text{vdW}} = 1,\lambda_{\,\text{Coul}} = 0 \rightarrow 1),
\end{split}
\end{equation}
with $\lambda_{\,\text{vdW}}$ and $\lambda_{\,\text{Coul}}$ being the coupling parameters of the soft-core and electrostatic potentials, respectively. Note that in the process of coupling the vdW interactions, the Coulombic interactions are turned-off, while we set $\lambda_{\,\text{vdW}}$ = 1 when computing $\Delta G_{\,\text{Coul}}$.  This results in the ``end-point'' states given by ($\lambda_{\,\text{vdW}}$=0,$\lambda_{\,\text{Coul}}$=0) and ($\lambda_{\,\text{vdW}}$=1,$\lambda_{\,\text{Coul}}$=1), as expected. The complete sets of the coupling parameters we employ here are $\lambda_{\text{vdW}}$ = $\{0.0$, $0.05$, $0.1$, $0.2$, $0.25$, $0.3$, $0.35$, $0.4$, $0.45$, $0.5$, $0.6$, $0.7$, $0.8$, $0.9$, $1.0\}$ and $\lambda_{\text{Coul}}$ = $\{0.0$, $0.1$, $0.4$, $0.7$, $0.1\}$.

In this work, we perform independent simulation at each state of $\lambda_{\text{Coul}}$, while the expanded ensemble (EE) method~\cite{Lyubartsev_1992} is applied for sampling the states associated to the $\lambda_{\,\text{vdW}}$ set. In short, an EE is constructed as a weighted sum of subensembles, each assuming a different value of the variable chosen to explore the free energy landscape, which in our case is $\lambda_{\,\text{vdW}}$. This way, the sampling of the EE involves both sampling each subensamble with fixed variables (N,P,T,$\lambda_{\,\text{vdW}}$) and transitions in $\lambda_{\,\text{vdW}}$. Thus, the remarkable feature of the EE method is the possibility of exploring the whole alchemical route in a single simulation. In this work, we perform a sequential sampling of the EE \cite{Chodera_2011_2}, which consists in sampling each subensamble via NPT MD for a determined number of steps $N^{\text{EE}}$ followed with an attemp to change $\lambda_{\,\text{vdW}}$ using MC, and so on. In addition, the set of (arbitrary) weights $\eta$ of the subensambles enters in the acceptance criteria of MC, so it is possible to tune $\eta$ in order to enhance the sampling. If differences $\eta_i$ - $\eta_j$ were closed to $\Delta G_{ji}$, we expect an uniform sampling in $\lambda_{\,\text{vdW}}$~\cite{Lyubartsev_1992}. Of course, this can be achieved only iteratively. As demonstrated in Ref.~\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ generates more decorrelated configurations of the physical variables. Therefore, we employ $N^{EE}$ = 5. This value, together with the chosen $\lambda_{\, \text{vdW}}$ set resulted to be satisfactory, as up to three preliminar simulations of the EE were enough to determine the weights required for a uniform sampling of $\lambda_{\, \text{vdW}}$. Those simulations were about 10 ns. The time at each $\lambda_{\text{Coul}}$ was also 10 ns, while the final simulations of the EE were in the range of 20-40 ns, depending on the system. Finally, MBAR \cite{Shirts_2008} was applied form the sample of each $\lambda$ to estimate the free energy.

We implemented in LAMMPS~\cite{Plimpton1995} the expanded ensemble methodology, as well as the codes regarding the \textit{soft-core} and DSF potential with linear coupling. All of this is available in repository https://github.com/atoms-ufrj/USER-ALCHEMICAL. The electrostatic interactions were calculated using the damped shifted force (DSF) method~\cite{Fennell2006} with $\alpha$ = 0.2 {\AA}$^{-1}$, with the exception of hexane, for which we considered full Coulombic interactions. For the systems modelled as rigid molecules, we employ the NPT method of Kamberaj~\textit{et al.}~\cite{Kamberaj_2005} using $\Delta t$ = 1 fs. For flexible systems, we employ the scheme due to Shinoda~\textit{et al}.~\cite{Shinoda2004}. PLAYMOL

\section{Results and discussion}
\label{sec:results}

\subsection{Simulation strategies of ionic liquids}
\label{sec:prel_results}
In this section, we present results of preliminary simulations which to set the methodology employed in the simulations for free energy calculations. First, we considerd the ionic liquids as flexible ions.

\begin{table*}[htp]
\caption{Densidades de [emim][B(CN)\textsubscript{4}] calculadas a partir simulaciones de NPT DM 298.15 K y 1 atm. La densidad experimental corresponde a $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
\begin{threeparttable}
\begin{tabular}{ c  c  c  c  c}  
\hline \hline
$\text{[emim]}$[B(CN)\textsubscript{4}] & $T_{\text{sim}}$ & $ P_{\text{sim}} $ & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
model & (K) &  (atm) &  (g/cm$^{3}$) &  \\
			\hline
		 \multicolumn{5}{c}{Flexible ions/Ewald method}\\

Koller y col.~\cite{Koller_2012}  & 298.14 $\pm$  0.02 & 0 $\pm$ 2 & 1.046 & 1.0 \\
Batista y col.~\cite{Batista_2015} & 298.15 $\pm$ 0.01  & 1 $\pm$ 1 & 0.989 & 4.6  \\
Liu y col.~\cite{Liu_2014}  & 298.14 $\pm$ 0.01 & 0 $\pm$ 1 & 1.001 & 3.4  \\
Weber y Kirchner.~\cite{Weber_2016}  & 298.16  $\pm$ 0.01 & 1 $\pm$ 1 & 1.015 & 2.1  \\
	 \multicolumn{5}{c}{Rigid ions/DSF method}\\
Koller y col.~\cite{Koller_2012}   & 298.42  $\pm$ 0.03  & 1 $\pm$ 1 & 1.038 & 0.2 \\
Batista y col.~\cite{Batista_2015} & 298.43 $\pm$ 0.02  & 0.9 $\pm$ 0.7  & 0.988 & 4.7  \\
Liu y col.~\cite{Liu_2014}  & 298.46 $\pm$ 0.02 & 1.2  $\pm$ 0.8 & 0.991 &  4.4 \\
Weber y Kirchner.~\cite{Weber_2016} &  298.41 $\pm$ 0.03 & 1.1 $\pm$ 0.8 & 1.022 & 1.4  \\
 \hline \hline
\label{table:props_dsf} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$($\rho^{\text{exp}}$$ - $$\rho^{\text{sim}}$)/$\rho^{\text{exp}}$.
\end{tablenotes}
\end{threeparttable}
\end{table*}

\subsection{Henry constant of CO\textsubscript{2} in [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N]}
\label{sec:henry_results}

\begin{table*}[htp]
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Resultados de la energía libre de solvatación y de la constante de Henry de CO\textsubscript{2} en [emim][B(CN)\textsubscript{4}] y [emim][Tf\textsubscript{2}N] a T = 298.15 K y P = 1 atm. Los valores experimentales de la constante de Henry en [emim][B(CN)\textsubscript{4}] y [emim][Tf\textsubscript{2}N] corresponden a 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} y a 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}, respectivamente.}
\begin{tabular}{ c c c  c  c  c  c }  
\toprule
Modelo & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
			\hline
			\multicolumn{4}{c}{[emim][B(CN)\textsubscript{4}]} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
			\hline
Koller y col.~\cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
Batista y col.~\cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
Liu y col.~\cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
Weber y Kirchner~\cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
\hline
		\multicolumn{4}{c}{[emim][Tf\textsubscript{2}N]} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
		\hline
 K\"{o}ddermann y col.~\cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
 \bottomrule
\label{table:henry} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

\subsection{Inifinite-dilution activity coefficient in [emim] [B(CN)\textsubscript{4}]}
\label{sec:act_results}

\begin{table*}[htp]
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Resultados de la energía libre de solvatación a T = 298.15 K de las sustancias puras benceno, hexano, ciclohexano, etanol y agua.}
\begin{tabular}{ c c c c c c c c }
\toprule
Soluto & $\rho_{\text{sim}}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
 & (g/cm$^{3}$) &  & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   &  \\
\hline
benceno OPLS-AA   & 0.8611 $\pm$ 0.0002 & 1.4 & -3.75  $\pm$ 0.02 & -0.381 $\pm$ 0.007 & -4.14 $\pm$ 0.02 & -4.56 & 9.32  \\
hexano OPLS-AA    & 0.6513 $\pm$ 0.0003 & 0.5 & -3.67  $\pm$  0.03 & 0.011 $\pm$ 0 & -3.66 $\pm$ 0.03 & -4.06 & 9.90 \\
ciclohexano & 0.7692 $\pm$ 0.0007 & 0.6 & -4.39 $\pm$ 0.01 & 0 & -4.39 $\pm$ 0.01 & - & -  \\
etanol TRAPPE-UA   & 0.781 $\pm$ 0.008 & 1.01  &-0.93 $\pm$ 0.01 & -4.15 $\pm$ 0.02  & -5.08  $\pm$ 0.02  & -5.08 & 0 \\
agua TIP4P/2005   &  0.9948 $\pm$ 0.0003 & 0.2 & 2.015 $\pm$ 0.004 & -9.01 $\pm$ 0.02 & -6.99 $\pm$ 0.02 & -6.33  &10.43 \\
 \bottomrule
\label{table:mu_solutos} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(Z^{\text{exp}} - Z^{\text{sim}})/Z^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

\begin{table*}[htp]
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Coeficientes de actividad a dilución infinita en [emim][B(CN)\textsubscript{4}] a T = 298.15 K de los solutos benceno, hexano, ciclohexano, etanol y agua.}
\begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
\toprule
Soluto & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
 & (kcal/mol) & (kcal/mol) &  (kcal/mol)  &  & (298.15 K) \cite{Doma_ska_2011} & (303 K) \cite{Yan_2010} \\
\midrule % inserts single-line
hexano OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
ciclohexano& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
benceno OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
ethanol TRAPPE-UA& -0.73 $\pm$ 0.02 & -4.10 $\pm$ 0.04 & -4.83 $\pm$ 0.04 & 0.41 $\pm$ 0.03 & 1.58 & 1.64  \\
agua TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
 \bottomrule
\label{table:gamma} 
\end{tabular}
\end{threeparttable}
\end{adjustbox}
\end{table*}

\subsection{Study of concentrated solutions of CO\textsubscript{2} in [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N]}
\label{sec:prel_results}

\section{Concluding remarks}
\label{sec:conclusion}

\section*{Acknowledgments}
The authors acknowledge the financial support provided by Petrobras (project code CENPES 16113).

\section*{References}

\bibliography{mybibfile}
%\begin{equation}
%\begin{split}
%\Delta G_{\text{sim}} - k_b T \ln \left( \frac{V^{\ast}}{V_1} \right) &= k_b T \ln \left(\frac{P_s}{x_s} \frac{1}{\tilde{\rho}_{\scaleto{LI}{4pt}}} \right) \\
%&= k_b T \ln \left( \frac{K_s}{\tilde{\rho}_{\scaleto{LI}{4pt}} R T} \right),
%\end{split}
%\end{equation}
\end{document}

### 2018-02-19 ionic_liquids.tex
inclusion of gitignore
add figures

@@
 \usepackage{scalerel}
+\usepackage{natbib}
 
@@
 \usepackage{flafter}
+
 \newcommand{\diff}[2]{\dfrac{\partial #1}{\partial #2}}
+
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{commath}
+\usepackage{graphicx,bm}
+\usepackage[]{subfig}
+\usepackage{epstopdf}
 
@@
 We implemented in LAMMPS~\cite{Plimpton1995} the expanded ensemble methodology, as well as the codes regarding the \textit{soft-core} and DSF potential with linear coupling.
-All of this is available in repository https://github.com/atoms-ufrj/USER-ALCHEMICAL.
+All of this is available at https://github.com/atoms-ufrj/USER-ALCHEMICAL.
 The electrostatic interactions were calculated using the damped shifted force (DSF) method~\cite{Fennell2006} with $\alpha$ = 0.2 {\AA}$^{-1}$, with the exception of hexane, for which we considered full Coulombic interactions.
@@
 For flexible systems, we employ the scheme due to Shinoda~\textit{et al}.~\cite{Shinoda2004}.
-PLAYMOL
+Initial configurations were build using the PLAYMOL software available at https://github.com/atoms-ufrj/playmol.
 
@@
 \label{sec:prel_results}
-In this section, we present results of preliminary simulations which to set the methodology employed in the simulations for free energy calculations.
-First, we considerd the ionic liquids as flexible ions.
+
+In this section, we present results of preliminary simulations, which aimed at setting up a computational efficient protocol for the ionic liquids studied here.
+As alternatives to standard approaches, in this work we assess the possibility of modeling the ions as rigid bodies and employing the DSF method for calculating the electrostatic interactions.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=\linewidth]{ions_paper.pdf}
+\caption{[emim]$^{+}$ [B(CN)\textsubscript{4}]$^{-}$ [Tf\textsubscript{2}N]$^{-}$.}
+\label{fig:scheme}
+\end{figure}
+
+rigid-body configurations: We first carried out simulations of the isolated ion pairs in order to obtain the minimum energy configurations with respect to the corresponding (classical) model for each case.
 
@@
 \end{table*}
+
+\begin{figure*}
+\centering
+\subfloat[text for the first subfigure\label{sfig:testa}]{%
+  \includegraphics[width=.4\linewidth]{koller}%
+}
+\subfloat[text for the second subfigure\label{sfig:testa}]{%
+  \includegraphics[width=.4\linewidth]{batista}%
+}
+
+\subfloat[text for the second subfigure\label{sfig:testa}]{%
+  \includegraphics[width=.4\linewidth]{Liu}%
+}
+\subfloat[text for the second subfigure\label{sfig:testa}]{%
+  \includegraphics[width=.4\linewidth]{Weber}%
+}
+\caption{}
+\label{}
+\end{figure*}
+
+\begin{figure}
+\centering
+\subfloat[text for the first subfigure\label{sfig:testa}]{%
+  \includegraphics[width=\linewidth]{Ludwig}%
+}
+
+\subfloat[text for the second subfigure\label{sfig:testa}]{%
+  \includegraphics[width=\linewidth]{Ludwig_anion}%
+}
+\caption{}
+\label{}
+\end{figure}
 
@@
 \end{table*}
+
+\begin{figure}
+\centering
+\subfloat[text for the first subfigure\label{sfig:testa}]{%
+  \includegraphics[width=\linewidth]{kollerall.pdf}%
+}
+
+\subfloat[text for the second subfigure\label{sfig:testa}]{%
+  \includegraphics[width=\linewidth]{ludwigall.pdf}%
+}
+\caption{}
+\label{}
+\end{figure}
 

### 2018-02-19 ionic_liquids.tex
working version

@@
 \section{Introduction}
-State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results.
+State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results. foreseeable future
 
@@
 
+Among the force fields described in Sec.~\ref{sec:force_field_il}, only in Ref.~\citenum{Koller_2012} one can find the atomic coordinates of a minimum energy configuration obtained in an \textit{ab-initio} simulation.
+For the other models, we employ the tool \textit{build} of PLAYMOL, which enables to specify the geometric data of each model: bond and angle lengths and dihedral angles, from which PLAYMOL automatically determines the Cartesian coordinates.
+We first carried out simulations of the isolated ion pairs in order to obtain the minimum energy configurations with respect to the corresponding (classical) model for each case.
+Then, we obtain configurations of minimum energy with respect to the corresponding classical model.
+For this, we perform a series of MD simulations of each cation-anion pair.
+These simulations were performed in a cubic box of length L = 50 {\AA}.
+Initially, a short DM NVT with a time-step of 0.1 fs, followed by an equilibration using $\Delta t$ = 0.5 fs and, finally, we minimize the energy using 1 fs in a process of ``quenching'', in which the temperature is gradually reduce until reaching a value close to 0 K, for which we employ the Nos\'{e}-Hoover thermostat~\cite{Martyna1992}.
+
 \section{Results and discussion}
@@
 
-In this section, we present results of preliminary simulations, which aimed at setting up a computational efficient protocol for the ionic liquids studied here.
-As alternatives to standard approaches, in this work we assess the possibility of modeling the ions as rigid bodies and employing the DSF method for calculating the electrostatic interactions.
+In this section, we present results of preliminary simulations, which aimed at setting up a (more) computationally efficient protocol for the ionic liquids studied here.
+As alternatives to standard approaches, we assess the possibility of modeling the ions as rigid bodies and employing the DSF method~\cite{Fennell2006} for calculating the electrostatic interactions.
+For that, we compare the simulated properties of density and radial distribution functions to that obtained when considering the ions as flexible molecules and the Ewald method for the Coulombic interactions.
 
-\begin{figure}[H]
+For the determining the initial configuration to specify for the rigid bodies we performed a preliminary study of the dihedrals in the ethyl group of [emim]$^{+}$, as we consider that its flexibility  may introduce a more significant conformational change in the cation.
+Small anions are usually simulated as rigid bodies.
+The nomenclature of the atoms are shown in Fig.~\ref{fig:atoms_name}.
+In the \textit{united-atoms} version of [emim]$^{+}$,  the nomenclature is identical, but hydrogens ranging from H4 to H11 are eliminated.
+
+Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtain the combined distribution function for the angles of the dihedrals C1-N2-C5-C6 and C2-N2-C5-C6 sampled in NPT simulations of 250 ion pairs.
+We chose this analysis, in place of individual histograms, as it provides simultaneously rigidity of the ring.
+In Figure we present the results for each model, together withe the color scale associated to the histograms.
+
+A first inspection of Fig.~\ref{fig:dihedrals}, reveals a similar behavior of the models of Refs.~\cite{Koller_2012} and Liu.~\cite{Liu_2014}. This was previsible
+
+\begin{figure}
 \centering
@@
 \caption{[emim]$^{+}$ [B(CN)\textsubscript{4}]$^{-}$ [Tf\textsubscript{2}N]$^{-}$.}
-\label{fig:scheme}
+\label{fig:atoms_name}
 \end{figure}
 
-rigid-body configurations: We first carried out simulations of the isolated ion pairs in order to obtain the minimum energy configurations with respect to the corresponding (classical) model for each case.
+%\begin{figure*}
+%\centering
+%\subfloat[text for the first subfigure\label{sfig:testa}]{%
+%  \includegraphics[width=.4\linewidth]{koller}%
+%}
+%\subfloat[text for the second subfigure\label{sfig:testa}]{%
+%  \includegraphics[width=.4\linewidth]{batista}%
+%}
+%
+%\subfloat[text for the second subfigure\label{sfig:testa}]{%
+%  \includegraphics[width=.4\linewidth]{Liu}%
+%}
+%\subfloat[text for the second subfigure\label{sfig:testa}]{%
+%  \includegraphics[width=.4\linewidth]{Weber}%
+%}
+%\caption{ggggg}
+%\label{fig:dihedrals}
+%\end{figure*}
+
+%\begin{figure}
+%\centering
+%\subfloat[text for the first subfigure\label{sfig:testa}]{%
+%  \includegraphics[width=\linewidth]{Ludwig}%
+%}
+%
+%\subfloat[text for the second subfigure\label{sfig:testa}]{%
+%  \includegraphics[width=\linewidth]{Ludwig_anion}%
+%}
+%\caption{}
+%\label{}
+%\end{figure}
 
@@
 \end{table*}
-
-\begin{figure*}
-\centering
-\subfloat[text for the first subfigure\label{sfig:testa}]{%
-  \includegraphics[width=.4\linewidth]{koller}%
-}
-\subfloat[text for the second subfigure\label{sfig:testa}]{%
-  \includegraphics[width=.4\linewidth]{batista}%
-}
-
-\subfloat[text for the second subfigure\label{sfig:testa}]{%
-  \includegraphics[width=.4\linewidth]{Liu}%
-}
-\subfloat[text for the second subfigure\label{sfig:testa}]{%
-  \includegraphics[width=.4\linewidth]{Weber}%
-}
-\caption{}
-\label{}
-\end{figure*}
-
-\begin{figure}
-\centering
-\subfloat[text for the first subfigure\label{sfig:testa}]{%
-  \includegraphics[width=\linewidth]{Ludwig}%
-}
-
-\subfloat[text for the second subfigure\label{sfig:testa}]{%
-  \includegraphics[width=\linewidth]{Ludwig_anion}%
-}
-\caption{}
-\label{}
-\end{figure}
 
@@
 \bibliography{mybibfile}
+
+\end{document}
 %\begin{equation}
@@
 %\end{equation}
-\end{document}

### 2018-02-19 ionic_liquids.tex
begin discussion section

@@
 \documentclass[3p,twocolumn]{elsarticle}
-\usepackage{lineno,hyperref}
+\usepackage[hidelinks,colorlinks,citecolor=blue]{hyperref}
+\usepackage{lineno}
 \usepackage{amsmath}
@@
 \usepackage{xcolor}
-\usepackage{float}
-\usepackage{flafter}
 
@@
 \usepackage{epstopdf}
-
+\usepackage{float}
 \biboptions{sort&compress}
@@
 Small anions are usually simulated as rigid bodies.
-The nomenclature of the atoms are shown in Fig.~\ref{fig:atoms_name}.
+The nomenclature of the atoms are shown in Fig.
 In the \textit{united-atoms} version of [emim]$^{+}$,  the nomenclature is identical, but hydrogens ranging from H4 to H11 are eliminated.
@@
 
-A first inspection of Fig.~\ref{fig:dihedrals}, reveals a similar behavior of the models of Refs.~\cite{Koller_2012} and Liu.~\cite{Liu_2014}. This was previsible
+A first inspection of Fig.~\ref{fig:atoms_id} reveals a similar behavior of the models developed by Koller~\textit{et al.}~\cite{Koller_2012} and Liu~\textit{et al.}~\cite{Liu_2014}.
+This was expected as in both cases are based on AMBER.
+In addition, Figs are symmetric, which means that atoms C1-N2-C2 are coplanar.
 
-\begin{figure}
+In the case of , the most likely angles of 90 and 270
+
+\begin{figure}[H]
 \centering
@@
 \caption{[emim]$^{+}$ [B(CN)\textsubscript{4}]$^{-}$ [Tf\textsubscript{2}N]$^{-}$.}
-\label{fig:atoms_name}
+\label{fig:atoms_id}
 \end{figure}
 
-%\begin{figure*}
-%\centering
-%\subfloat[text for the first subfigure\label{sfig:testa}]{%
-%  \includegraphics[width=.4\linewidth]{koller}%
-%}
-%\subfloat[text for the second subfigure\label{sfig:testa}]{%
-%  \includegraphics[width=.4\linewidth]{batista}%
-%}
-%
-%\subfloat[text for the second subfigure\label{sfig:testa}]{%
-%  \includegraphics[width=.4\linewidth]{Liu}%
-%}
-%\subfloat[text for the second subfigure\label{sfig:testa}]{%
-%  \includegraphics[width=.4\linewidth]{Weber}%
-%}
-%\caption{ggggg}
-%\label{fig:dihedrals}
-%\end{figure*}
+\begin{figure*}
+\centering
+  \includegraphics[width=.4\linewidth]{koller.png}%
+  \includegraphics[width=.4\linewidth]{batista.png}%
 
-%\begin{figure}
-%\centering
-%\subfloat[text for the first subfigure\label{sfig:testa}]{%
-%  \includegraphics[width=\linewidth]{Ludwig}%
-%}
-%
-%\subfloat[text for the second subfigure\label{sfig:testa}]{%
-%  \includegraphics[width=\linewidth]{Ludwig_anion}%
-%}
-%\caption{}
-%\label{}
-%\end{figure}
+  \includegraphics[width=.4\linewidth]{Liu.png}%
+  \includegraphics[width=.4\linewidth]{Weber.png}%
+\caption{}
+\label{k}
+\end{figure*}
 
-\begin{table*}[htp]
+\begin{figure}[H]
+\centering
+  \includegraphics[width=\linewidth]{Ludwig.png}%
+
+  \includegraphics[width=\linewidth]{Ludwig_anion.png}%
+\caption{lala}
+\label{e}
+\end{figure}
+
+\begin{table*}
 \caption{Densidades de [emim][B(CN)\textsubscript{4}] calculadas a partir simulaciones de NPT DM 298.15 K y 1 atm.
@@
 
-\begin{table*}[htp]
+\begin{table*}
 \centering
@@
 \centering
-\subfloat[text for the first subfigure\label{sfig:testa}]{%
+\subfloat[text for the first subfigure]{%
   \includegraphics[width=\linewidth]{kollerall.pdf}%
@@
 
-\subfloat[text for the second subfigure\label{sfig:testa}]{%
+\subfloat[text for the second subfigure]{%
   \includegraphics[width=\linewidth]{ludwigall.pdf}%
@@
 \caption{}
-\label{}
+\label{f}
 \end{figure}

### 2018-02-21 ionic_liquids.tex
computational methods

@@
 
-\section{Computational details}
+\section{Computational methods}
 \label{sec:sim_details}
 
-The gradual insertion/deletion of charged solutes involves scaling both the van der Waals (vdW) and the electrostatic intermolecular interaction.
+With the aim of setting up a (more) computationally efficient protocol for the ILs, in this work we assess the possibility of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method~\cite{Fennell2006} for computing the electrostatic interactions.
+As an alternative to the Ewald schemes, McCann~\textit{et al.}~\cite{McCann_2013} tested the DSF method for various ILs modeled in the OPLS-AA framework.
+They concluded that using $\alpha$ = 0.2 {\AA}$^{-1}$ and a cutoff distance ($r_c$) of 15 {\AA} provides the best energetic agreement with Ewald.
+In this work, the comparisons are made in terms of the simulated densities and radial distribution functions for which, as will be shown in the next section, $\alpha$ = 0.2 {\AA}$^{-1}$ and $r_c$ = 12 {\AA} resulted in good agreement for the ILs studied here.
+Those values were also employed for the charged solutes, with the exception of hexane, for which we considered undamped Coulombic interactions.
+
+When it was possible to treat the ions as rigid bodies, the NPT algorithm of Kamberaj~\textit{et al.}~\cite{Kamberaj_2005} was employed to carry out the MD simulations.
+Otherwise, the scheme due to Shinoda~\textit{et al}.~\cite{Shinoda2004} was used along with the application of SHAKE~\cite{Ryckaert1977} to constrain the C-H bonds lengths.
+For both integrators, we employed $\Delta t$ = 1 fs.
+
+The gradual insertion/deletion of charged solutes involves scaling both the van der Waals (vdW) and the electrostatic intermolecular interactions.
 In order to avoid numerical instabilities associated to the vdW scaling, a standard approach is to employ a soft-core potential with a nonlinear coupling, and in this paper we use the modified Lennard-Jones potential due to Beutler~\textit{et al.}~\cite{Beutler_1994}.
-The electrostatic interactions, on the other hand, can be handled simply by a linear scaling~\cite{Naden_2015}.
+The electrostatic interactions, on the other hand, can be handled simply by a linear scaling~\cite{Naden_2015} of the potential, which in this work corresponds to the DSF method~\cite{Fennell2006}.
+
 Furthermore, the contributions to $\Delta G$ originating at the different types of coupling can be taken into account separately, as follows
@@
 
-In this work, we perform independent simulation at each state of $\lambda_{\text{Coul}}$, while the expanded ensemble (EE) method~\cite{Lyubartsev_1992} is applied for sampling the states associated to the $\lambda_{\,\text{vdW}}$ set.
+In this work, we performed independent simulation at each state of $\lambda_{\text{Coul}}$, while the expanded ensemble (EE) method~\cite{Lyubartsev_1992} was applied for sampling the states associated to the $\lambda_{\,\text{vdW}}$ set.
 In short, an EE is constructed as a weighted sum of subensembles, each assuming a different value of the variable chosen to explore the free energy landscape, which in our case is $\lambda_{\,\text{vdW}}$.
@@
 In this work, we perform a sequential sampling of the EE \cite{Chodera_2011_2}, which consists in sampling each subensamble via NPT MD for a determined number of steps $N^{\text{EE}}$ followed with an attemp to change $\lambda_{\,\text{vdW}}$ using MC, and so on.
+Independent sampling of $\lambda$~\cite{Chodera_2011_2}.
 In addition, the set of (arbitrary) weights $\eta$ of the subensambles enters in the acceptance criteria of MC, so it is possible to tune $\eta$ in order to enhance the sampling.
@@
 Of course, this can be achieved only iteratively.
-As demonstrated in Ref.~\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ generates more decorrelated configurations of the physical variables.
-Therefore, we employ $N^{EE}$ = 5.
-This value, together with the chosen $\lambda_{\, \text{vdW}}$ set resulted to be satisfactory, as up to three preliminar simulations of the EE were enough to determine the weights required for a uniform sampling of $\lambda_{\, \text{vdW}}$.
-Those simulations were about 10 ns.
-The time at each $\lambda_{\text{Coul}}$ was also 10 ns, while the final simulations of the EE were in the range of 20-40 ns, depending on the system.
-Finally, MBAR \cite{Shirts_2008} was applied form the sample of each $\lambda$ to estimate the free energy.
+The EE procedure, together with the \textit{soft-core} potential and the DSF method with linear coupling were all implemented in the LAMMPS software package~\cite{Plimpton1995}.
 
-We implemented in LAMMPS~\cite{Plimpton1995} the expanded ensemble methodology, as well as the codes regarding the \textit{soft-core} and DSF potential with linear coupling.
-All of this is available at https://github.com/atoms-ufrj/USER-ALCHEMICAL.
-The electrostatic interactions were calculated using the damped shifted force (DSF) method~\cite{Fennell2006} with $\alpha$ = 0.2 {\AA}$^{-1}$, with the exception of hexane, for which we considered full Coulombic interactions.
-For the systems modelled as rigid molecules, we employ the NPT method of Kamberaj~\textit{et al.}~\cite{Kamberaj_2005} using $\Delta t$ = 1 fs.
-For flexible systems, we employ the scheme due to Shinoda~\textit{et al}.~\cite{Shinoda2004}.
-Initial configurations were build using the PLAYMOL software available at https://github.com/atoms-ufrj/playmol.
+As demonstrated in Ref.~\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ generate more decorrelated samples in each subensemble.
+In this work, we employ $N^{EE}$ = 5 which, together with the specified $\lambda_{\, \text{vdW}}$ set, resulted to be satisfactory as up to 3 preliminary runs of the EE were enough to determine the weights $\eta$ that yielded, in a final simulation, a ``sufficient'' sampling of each subensamble.
+By ``sufficient'', we mean that the sampling provides an acceptable error in $\Delta G$.
+The simulation times for the preliminary and final EE runs were 10 and 40 ns, respectively, and each $\lambda_{\text{Coul}}$ state was simulated for 10 ns.
+Finally, the MBAR method~\cite{Shirts_2008}, as implemented by Klimovich~\textit{et al.}~\cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$ .
 
-Among the force fields described in Sec.~\ref{sec:force_field_il}, only in Ref.~\citenum{Koller_2012} one can find the atomic coordinates of a minimum energy configuration obtained in an \textit{ab-initio} simulation.
-For the other models, we employ the tool \textit{build} of PLAYMOL, which enables to specify the geometric data of each model: bond and angle lengths and dihedral angles, from which PLAYMOL automatically determines the Cartesian coordinates.
-We first carried out simulations of the isolated ion pairs in order to obtain the minimum energy configurations with respect to the corresponding (classical) model for each case.
-Then, we obtain configurations of minimum energy with respect to the corresponding classical model.
-For this, we perform a series of MD simulations of each cation-anion pair.
-These simulations were performed in a cubic box of length L = 50 {\AA}.
-Initially, a short DM NVT with a time-step of 0.1 fs, followed by an equilibration using $\Delta t$ = 0.5 fs and, finally, we minimize the energy using 1 fs in a process of ``quenching'', in which the temperature is gradually reduce until reaching a value close to 0 K, for which we employ the Nos\'{e}-Hoover thermostat~\cite{Martyna1992}.
+We end this section with a brief description of the procedure for generating the initial configurations.
+Only Ref.~\citenum{Liu_2014} provides the atomic coordinates of the cation-anion pair corresponding to a minimum energy configuration obtained in an \textit{ab-initio} simulation.
+For the other models, we employed the tool \textit{build} of PLAYMOL~\cite{playmol}, a software integrated with PACKMOL~\cite{Mart_nez_2009}, which enables to specify the following geometric data: bond and angle lengths and dihedral angles, from which PLAYMOL automatically determines the Cartesian coordinates.
+We first carried out NVT MD simulations of the isolated ion pairs in order to obtain a minimum energy conformation for the corresponding (classical) model of each pair.
+These simulations were performed using the the Nos\'{e}-Hoover thermostat~\cite{Martyna1992} and a cubic box of length L = 50 {\AA} with non-periodic boundary conditions.
+To relax the initial configurations, a short run with a small time step of 0.1 fs was performed, which was followed by an equilibration using $\Delta t$ = 0.5 fs.
+Finally, we carried out a ``quenching'' simulation with $\Delta t$ = 1 fs, in which the temperature is gradually reduced until reaching a value close to 0 K.
+The resulting coordinates were specified in PLAYMOL to build the initial configurations for simulating the liquid phases.
 
@@
 \label{sec:prel_results}
-
-In this section, we present results of preliminary simulations, which aimed at setting up a (more) computationally efficient protocol for the ionic liquids studied here.
-As alternatives to standard approaches, we assess the possibility of modeling the ions as rigid bodies and employing the DSF method~\cite{Fennell2006} for calculating the electrostatic interactions.
-For that, we compare the simulated properties of density and radial distribution functions to that obtained when considering the ions as flexible molecules and the Ewald method for the Coulombic interactions.
+In this section, we present results of preliminary simulations using the  alternatives to standard approaches of modeling the ions as rigid bodies and employing the DSF method~\cite{Fennell2006} For that, we compare the simulated properties of density and radial distribution functions to that obtained when considering the ions as flexible molecules and the Ewald method for the Coulombic interactions.
 

### 2018-02-21 convert_eps.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+for file in `ls *.eps`; do
+    echo "Converting $file"
+    convert -density 300 "$file" "$(basename "$file" .eps).png"
+done

### 2018-04-04 ionic_liquids.tex
discusionI

@@
 Koller~\textit{et al.}~\cite{Koller_2012} were the first to introduce a specific non-polarizable force field of [emim][B(CN)\textsubscript{4}].
-They tested three variations of a \textit{united-atoms} model, in which the alkyl groups $\text{CH}_3$ y $\text{CH}_2$ of [emim]$^{+}$ are replaced by pseudo-atoms.
+They tested three variations of a \textit{united-atoms} model, in which the alkyl groups $\text{CH}_3$ and $\text{CH}_2$ of [emim]$^{+}$ are replaced by pseudo-atoms.
 Among them, the ``FF-3'' model best reproduces the experimental values of density, self-diffusion coefficients and viscosity.
@@
 With the aim of setting up a (more) computationally efficient protocol for the ILs, in this work we assess the possibility of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method~\cite{Fennell2006} for computing the electrostatic interactions.
-As an alternative to the Ewald schemes, McCann~\textit{et al.}~\cite{McCann_2013} tested the DSF method for various ILs modeled in the OPLS-AA framework.
+As an alternative to the Ewald schemes~\cite{Ewald_1921,Darden_1993,Hockney_1988}, McCann~\textit{et al.}~\cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force fields.
 They concluded that using $\alpha$ = 0.2 {\AA}$^{-1}$ and a cutoff distance ($r_c$) of 15 {\AA} provides the best energetic agreement with Ewald.
@@
 Those values were also employed for the charged solutes, with the exception of hexane, for which we considered undamped Coulombic interactions.
+
+rigid treatment of the imidazolium ring~\cite{Kobrak_2004,Lynden_Bell_2006}
+\cite{Rey_Castro_2007}
 
@@
 Of course, this can be achieved only iteratively.
-The EE procedure, together with the \textit{soft-core} potential and the DSF method with linear coupling were all implemented in the LAMMPS software package~\cite{Plimpton1995}.
+The EE procedure, together with the \textit{soft-core} potential and the DSF method with linear coupling were all implemented in the LAMMPS software package~\cite{Plimpton1995}, which we employed for carrying out all the MD simulations.
 
@@
 Only Ref.~\citenum{Liu_2014} provides the atomic coordinates of the cation-anion pair corresponding to a minimum energy configuration obtained in an \textit{ab-initio} simulation.
-For the other models, we employed the tool \textit{build} of PLAYMOL~\cite{playmol}, a software integrated with PACKMOL~\cite{Mart_nez_2009}, which enables to specify the following geometric data: bond and angle lengths and dihedral angles, from which PLAYMOL automatically determines the Cartesian coordinates.
+For the other models, we employed the tool \textit{build} of PLAYMOL~\cite{playmol}, a software integrated with PACKMOL~\cite{Mart_nez_2009}, which enables to specify the following geometric data: bond and angle lengths and dihedral angles, from which PLAYMOL~\cite{playmol} automatically determines the Cartesian coordinates.
 We first carried out NVT MD simulations of the isolated ion pairs in order to obtain a minimum energy conformation for the corresponding (classical) model of each pair.
@@
 Finally, we carried out a ``quenching'' simulation with $\Delta t$ = 1 fs, in which the temperature is gradually reduced until reaching a value close to 0 K.
-The resulting coordinates were specified in PLAYMOL to build the initial configurations for simulating the liquid phases.
+The resulting coordinates were then specified in PLAYMOL~\cite{playmol} to build the initial configurations for simulating the liquid phases.
 
@@
 
-\subsection{Simulation strategies of ionic liquids}
+\subsection{Simulation strategies of ILs}
 \label{sec:prel_results}
-In this section, we present results of preliminary simulations using the  alternatives to standard approaches of modeling the ions as rigid bodies and employing the DSF method~\cite{Fennell2006} For that, we compare the simulated properties of density and radial distribution functions to that obtained when considering the ions as flexible molecules and the Ewald method for the Coulombic interactions.
 
-For the determining the initial configuration to specify for the rigid bodies we performed a preliminary study of the dihedrals in the ethyl group of [emim]$^{+}$, as we consider that its flexibility  may introduce a more significant conformational change in the cation.
-Small anions are usually simulated as rigid bodies.
-The nomenclature of the atoms are shown in Fig.
-In the \textit{united-atoms} version of [emim]$^{+}$,  the nomenclature is identical, but hydrogens ranging from H4 to H11 are eliminated.
+In this section, we present and compare the results obtained for the following two cases: (1) flexible ions and the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for the evaluation of the Ewald sums~\cite{Ewald_1921}, and (2) ions modeled as rigid bodies with the DSF method~\cite{Fennell2006} for calculating the Coulombic interactions.
 
-Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtain the combined distribution function for the angles of the dihedrals C1-N2-C5-C6 and C2-N2-C5-C6 sampled in NPT simulations of 250 ion pairs.
-We chose this analysis, in place of individual histograms, as it provides simultaneously rigidity of the ring.
-In Figure we present the results for each model, together withe the color scale associated to the histograms.
+First, we describe the approach for defining the rigid bodies.
+For that, we carried out an analysis of key dihedrals, particularly those whose flexibility could lead to significant conformational changes in [emim]$^{+}$ and [Tf\textsubscript{2}N]$^{-}$.
+On the other hand, small and highly symmetric anions, such as PF\textsubscript{6} and BF\textsubscript{4} are usually modeled as rigid bodies~\cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies that strategy in the case of [B(CN)\textsubscript{4}]$^{-}$.
+The atomic nomenclatureare adopted in this paper is shown in Fig~\ref{fig:atoms_id}.
+In the \textit{united-atoms} version of [emim]$^{+}$, the nomenclature is identical, but the hydrogens ranging from H4 to H11 are eliminated.
+
+Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtain the combined distribution function (CDF) of the dihedral angles containing the ehtyl chain atoms, which are C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs.
+The CDF, as an alternative of individual histograms, provides a way to  simultaneously analyse the rigidity of the ring.
+In Fig.~\ref{fig:dihedrals} we present the results of CDF for each model, together with the color scale associated to the histograms.
 
 A first inspection of Fig.~\ref{fig:atoms_id} reveals a similar behavior of the models developed by Koller~\textit{et al.}~\cite{Koller_2012} and Liu~\textit{et al.}~\cite{Liu_2014}.
-This was expected as in both cases are based on AMBER.
+This was expected as both were developed based on AMBER force field.
 In addition, Figs are symmetric, which means that atoms C1-N2-C2 are coplanar.
@@
 \caption{}
-\label{k}
+\label{fig:dihedrals}
 \end{figure*}

### 2018-04-05 ionic_liquids.tex
test hyperlinks

@@
 \documentclass[3p,twocolumn]{elsarticle}
-\usepackage[hidelinks,colorlinks,citecolor=blue]{hyperref}
+\usepackage[draft,unicode=true,hidelinks,colorlinks,citecolor=blue]{hyperref}
 \usepackage{lineno}
@@
 
-\usepackage{amssymb}
 \usepackage{amsmath}
@@
 \usepackage{graphicx,bm}
-\usepackage[]{subfig}
 \usepackage{epstopdf}
@@
 \modulolinenumbers[5]
+\usepackage{subfig}
+
+\usepackage[T1]{fontenc}
 
@@
 The potential parameters of [B(CN)\textsubscript{4}]$^{-}$ derived by Koller~\textit{et al.}~\cite{Koller_2012} were employed by Batista~\textit{et al.}~\cite{Batista_2015} to study aqueous solutions of [emim][B(CN)\textsubscript{4}].
-In this case,  the authors considered the \textit{all-atom} model of [emim]$^{+}$ developed by Cadena and Maginn~\cite{Cadena_2006}.
-The atomic partial charges were obtained using the CHELP procedure~\cite{Breneman_1990}, resulting in net charges of $\pm$0.889$e$ on the ions.
-It should be noted that those force fields consider different scaling factors for 1-4 non-bonded interactions: Cadena and Maginn~\cite{Cadena_2006} use values of 1.0 y 0.4 for the Lennard-Jones and Coulombic interactions, respectively, while in Koller~\textit{et al.}~\cite{Koller_2012} the corresponding factors are 0.5 y 5/6, in accordance with AMBER force field.
-Batista~\textit{et al.}~\cite{Batista_2015} employ the same factors as Cadena and Maginn~\cite{Cadena_2006} (J.P.
+In this case,  the authors considered the \textit{all-atom} model of [emim]$^{+}$ developed by Cadena and Maginn \cite{Cadena_2006}.
+The atomic partial charges were obtained using the CHELP procedure \cite{Breneman_1990}, resulting in net charges of $\pm$0.889$e$ on the ions.
+It should be noted that those force fields consider different scaling factors for 1-4 non-bonded interactions: Cadena and Maginn \cite{Cadena_2006} use values of 1.0 y 0.4 for the Lennard-Jones and Coulombic interactions, respectively, while in Koller \textit{et al.} \cite{Koller_2012} the corresponding factors are 0.5 y 5/6, in accordance with AMBER force field.
+Batista \textit{et al.} \cite{Batista_2015} employ the same factors as Cadena and Maginn \cite{Cadena_2006} (J.P.
 Coutinho, personal communication).
 
-Another set of parameters for [emim][B(CN)\textsubscript{4}] was derived by Liu \textit{et al.}.~\cite{Liu_2014} in a study that investigates the dynamics of CO\textsubscript{2} and N\textsubscript{2} in that IL.
+Another set of parameters for \mbox{[emim][B(CN)\textsubscript{4}]} was derived by Liu \textit{et al.}\cite{Liu_2014} in a study that investigates the dynamics of CO\textsubscript{2} and N\textsubscript{2} in that IL.
 Parameters corresponding to the intramolecular and Lennard-Jones interactions were extracted from GAFF~\cite{Wang_2004}, while the atomic partial charges were computed using the RESP method~\cite{Bayly_1993} from \textit{DFT}/B3LYP/6-311+G(d) calculations.
@@
 
-Finally, for [emim][Tf\textsubscript{2}N] we use the model of K\"{o}ddermann~\textit{et al}~\cite{K_ddermann_2007}, which result from ``refining'' the force field due to P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}.
-This ``refining'' was characterized by their authors as unusual, given that the LJ parameters were modified, while keeping the partial charges at their original values.
-This model was recently employed by Kerl~\textit{et al.}~\cite{Kerl__2017}, who were able to accurately predict Henry's constant for CO\textsubscript{2} at several temperatures.
+Finally, for [emim][Tf\textsubscript{2}N] we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which result from refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
+This refining was characterized by their authors as unusual, given that the LJ parameters were modified, while keeping the partial charges at their original values.
+This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry's constant for CO\textsubscript{2} at several temperatures.
 
@@
 Hexane and benzene were modeled using the OPLS-AA force field~\cite{Jorgensen_1996}, while the TRAPPE potential~\cite{Chen_2001,Potoff_2001} was employed for ethanol and CO\textsubscript{2}.
-Cyclohexane was simulated using a rigid-body model~\cite{munoz2015lennard} whose sites only interact via the Lennard-Jones potential and for water we employ the TIP4P/2005 model~\cite{Abascal_2005,Vega_2011}.
+Cyclohexane was simulated using a rigid-body model~\cite{munoz2015lennard} whose sites only interact via the Lennard-Jones potential and for water we employ the TIP4P/2005 model~\cite{Abascal_2005}, \cite{Vega_2011}.
 
@@
 
-Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtain the combined distribution function (CDF) of the dihedral angles containing the ehtyl chain atoms, which are C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs.
-The CDF, as an alternative of individual histograms, provides a way to  simultaneously analyse the rigidity of the ring.
-In Fig.~\ref{fig:dihedrals} we present the results of CDF for each model, together with the color scale associated to the histograms.
+Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtain the combined distribution function (CDF) of the dihedral angles corresponding to the torsions in C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs.
+The CDF, as an alternative of individual histograms, provides a way to  simultaneously analyze the rigidity of the ring.
+In Fig.~\ref{fig:dihedrals_emim} we present the results of the CDF for each model.
 
-A first inspection of Fig.~\ref{fig:atoms_id} reveals a similar behavior of the models developed by Koller~\textit{et al.}~\cite{Koller_2012} and Liu~\textit{et al.}~\cite{Liu_2014}.
-This was expected as both were developed based on AMBER force field.
-In addition, Figs are symmetric, which means that atoms C1-N2-C2 are coplanar.
-
-In the case of , the most likely angles of 90 and 270
+A first inspection of Fig.
+reveals a similar behavior of the models of [emim]$^{+}$ due to Koller~\textit{et al.}~\cite{Koller_2012} and Liu~\textit{et al.}~\cite{Liu_2014}.
+This was expected as both were developed based on the AMBER force field.
+In addition, Figs.(a) and(b) are symmetric, which means that atoms C1-N2-C2 are coplanar.
+Koller is the most rigid model, with The most likely angles in Fig.~(a) can be found in a narrow region around 90 and 270.
+Given that these angles correspond to the same configuration in the \textit{united-atom} version, we build all the rigid bodies specifying 90 for the dihedral angle of C5-C5-N2-C1.
+The other models present a larger flexibility of the ethyl chain, with high probability regions that extend  ina broad of angle values.
+However, in the case of Liu and Batista, it was possible to the following approach: we consider the most likely angles as obtained by the indificual histogram of the dihedral C5-C5-N2-C1, which were employed to construct two types of rigid bodies.
+In the case of Liu , 50 of the rigid bodies were build specifying the angle of 90 for the dihedral C6-C5-N2-C1 and -90 of the others.
+For Batista, we employed the angles 102.6  and -102.6 for buildign both types for rigid bodies in an equal proportion.
 
@@
 \centering
-  \includegraphics[width=.4\linewidth]{koller.png}%
-  \includegraphics[width=.4\linewidth]{batista.png}%
+\subfloat[Koller~\textit{et al.}~\cite{Koller_2012}]{%
+  \includegraphics[width=.4\linewidth]{koller.png}}%
+\subfloat[Batista~\textit{et al.}~\cite{Batista_2015}]{%  
+  \includegraphics[width=.4\linewidth]{batista.png}}%
 
-  \includegraphics[width=.4\linewidth]{Liu.png}%
-  \includegraphics[width=.4\linewidth]{Weber.png}%
-\caption{}
-\label{fig:dihedrals}
+\subfloat[Liu~\textit{et al.}~\cite{Liu_2014}]{%
+  \includegraphics[width=.4\linewidth]{Liu.png}}%
+\subfloat[Weber and Kirchner~\cite{Weber_2016}]{%
+  \includegraphics[width=.4\linewidth]{Weber.png}}%
+\caption{Combined distribution function (CDF) of [emim]}
+\label{fig:dihedrals_emim}
 \end{figure*}
@@
   \includegraphics[width=\linewidth]{Ludwig_anion.png}%
-\caption{lala}
-\label{e}
+\caption{Combined distribution function (CDF) of anion}
+\label{fig:dihedrals_anion}
 \end{figure}
@@
 \centering
-\subfloat[text for the first subfigure]{%
+\subfloat[[emim][BCN4]-CO\textsubscript{2}]{%
   \includegraphics[width=\linewidth]{kollerall.pdf}%
@@
 
-\subfloat[text for the second subfigure]{%
+\subfloat[[emim][BCN4]-CO\textsubscript{2}]{%
   \includegraphics[width=\linewidth]{ludwigall.pdf}%
 }
-\caption{}
-\label{f}
+\caption{Spatial distribution function}
+\label{fig:sdf}
 \end{figure}
@@
 \subsection{Study of concentrated solutions of CO\textsubscript{2} in [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N]}
-\label{sec:prel_results}
+\label{sec:results_conc}
 

### 2018-04-25 ionic_liquids.tex
henry

@@
 \documentclass[3p,twocolumn]{elsarticle}
-\usepackage[draft,unicode=true,hidelinks,colorlinks,citecolor=blue]{hyperref}
+\usepackage[draft,hidelinks,colorlinks,citecolor=blue]{hyperref}
 \usepackage{lineno}
@@
 \usepackage{xcolor}
+\usepackage{mhchem}
 
@@
 
-We also consider the parametrization recently reported by Weber and Kirchner~\cite{Weber_2016}, which is based on the force field developed by P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}.
+We also consider the parametrization recently reported by Weber and Kirchner \cite{Weber_2016}, which is based on the force field developed by P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}.
 The potential parameters for the anion are not specified in Refs.~\citenum{Weber_2016} and~\citenum{Canongia_Lopes_2006}, and we obtained them by a direct communication with the authors of Ref.~\citenum{Weber_2016}.
@@
 
-First, we describe the approach for defining the rigid bodies.
+First, we describe the approach for building the rigid bodies.
 For that, we carried out an analysis of key dihedrals, particularly those whose flexibility could lead to significant conformational changes in [emim]$^{+}$ and [Tf\textsubscript{2}N]$^{-}$.
 On the other hand, small and highly symmetric anions, such as PF\textsubscript{6} and BF\textsubscript{4} are usually modeled as rigid bodies~\cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies that strategy in the case of [B(CN)\textsubscript{4}]$^{-}$.
-The atomic nomenclatureare adopted in this paper is shown in Fig~\ref{fig:atoms_id}.
+The atomic nomenclature adopted in this paper is shown in Fig~\ref{fig:atoms_id}.
 In the \textit{united-atoms} version of [emim]$^{+}$, the nomenclature is identical, but the hydrogens ranging from H4 to H11 are eliminated.
-
-Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtain the combined distribution function (CDF) of the dihedral angles corresponding to the torsions in C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs.
-The CDF, as an alternative of individual histograms, provides a way to  simultaneously analyze the rigidity of the ring.
-In Fig.~\ref{fig:dihedrals_emim} we present the results of the CDF for each model.
-
-A first inspection of Fig.
-reveals a similar behavior of the models of [emim]$^{+}$ due to Koller~\textit{et al.}~\cite{Koller_2012} and Liu~\textit{et al.}~\cite{Liu_2014}.
-This was expected as both were developed based on the AMBER force field.
-In addition, Figs.(a) and(b) are symmetric, which means that atoms C1-N2-C2 are coplanar.
-Koller is the most rigid model, with The most likely angles in Fig.~(a) can be found in a narrow region around 90 and 270.
-Given that these angles correspond to the same configuration in the \textit{united-atom} version, we build all the rigid bodies specifying 90 for the dihedral angle of C5-C5-N2-C1.
-The other models present a larger flexibility of the ethyl chain, with high probability regions that extend  ina broad of angle values.
-However, in the case of Liu and Batista, it was possible to the following approach: we consider the most likely angles as obtained by the indificual histogram of the dihedral C5-C5-N2-C1, which were employed to construct two types of rigid bodies.
-In the case of Liu , 50 of the rigid bodies were build specifying the angle of 90 for the dihedral C6-C5-N2-C1 and -90 of the others.
-For Batista, we employed the angles 102.6  and -102.6 for buildign both types for rigid bodies in an equal proportion.
 
@@
 \end{figure}
+
+Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtain the combined distribution function (CDF) of the dihedral angles corresponding to the torsions in C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs.
+The CDF, as an alternative of individual histograms, provides a way to  simultaneously analyze the rigidity of the ring.
+In Fig.~\ref{fig:dihedrals_emim} we present the results for each model.
+
+A first inspection of Fig.~\ref{fig:dihedrals_emim} reveals a similar behavior of the models of [emim]$^{+}$ due to Koller \textit{et al.} \cite{Koller_2012} and Liu \textit{et al.} \cite{Liu_2014}.
+This was expected as both were developed based on the AMBER force field.
+In addition, Figs.~\ref{fig:dihedrals_emim}(a) and \ref{fig:dihedrals_emim}(b) are symmetric, which means that atoms C1, N2, and C2 are coplanar.
+The most likely angles in Fig.~\ref{fig:dihedrals_emim}(a) can be found in a narrow region around 90$^{\circ}$ and 270$^{\circ}$.
+Given that these angles correspond to the same configuration in the \textit{united-atom} representation, we build all the rigid bodies specifying the value of 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1.
+The other models showed a larger flexibility with high probability regions that extend in a broad range of angle values.
+Despite this, it was possible to build two types of rigid bodies, in equal proportion, by specifying the most probables dihedral angles of C6-C5-N2-C1.
+In the case of Liu \textit{et al.} \cite{Liu_2014}, those angles correspond to the values of  90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed the angles of 102.6$^{\circ}$ and -102.6$^{\circ}$.
+Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} presents a non negligible probability of sampling the angle value of 0$^{\circ}$, which notably differs from what was observed for the other models and we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of the rigid bodies, respectively; and for the remaining 15 \% we specified the angle of 0$^{\circ}$.
+
+In Table~\ref{table:props_dsf} we show the results of density for the strategies mentioned at the begining of this section considered to simulate [emim][B(CN)\textsubscript{4}].
+When comparing the cases (1) and (2) for each model, we observe that the density values practically do not differ.
+In addition, the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental density.
+The model due to Weber and Kirchner also presents a small deviation of 1 \%.
+
+For the simulation strategies (1) and (2) we have also compared the results of relevant radial distribution functions (rdfs).
+In the Appendix.
+The better agreement is found for the force fields due to Koller \textit{et al.} \cite{Koller_2012} and Batista \textit{et al.} \cite{Batista_2015}.
+The model of Liu \textit{et al.} \cite{Liu_2014} presents small deviations and the simulation with rigid bodies qualitatively reproduces the results obtained for flexible ions.
+Although not shown here, this conclusions are valid for other calculated rdfs:  N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion).
+The simulation with rigid bodies for the model of Weber y Kirchner\cite{Weber_2016} generates considerable discrepancies for the pairs of C5(catión)-N(anión), whose rdf present an anomaly at the distance of 4 {\AA}, and for C2(cation)-B(anion).
+That is why for this case, we have considered as rigid only the ring imidazolium, and let flexible the ethyl chain.
 
@@
 \end{figure*}
+
+For the system [emim][Tf\textsubscript{2}N] we carried out an analogous study of dihedrals.
+The CDF of dihedrals C1-N2-C5-C6 and C2-N2-C5-C6 is shown in Fig.~\ref{fig:die_ntf2}, which is similar to the one obtained for [emim]$^{+}$ modeled with the force field of Weber and Kirchner~\cite{Weber_2016}, but  the dihedral angle C1-N2-C5-C6 most likely corresponds to the value of 0$^{\circ}$.
+The similary was expected as both models are based on the force field of [emim]$^{+}$ developed by Canongia-Lopes and Pádua \cite{Canongia_Lopes_2006}.
+With regards to the anion [Tf\textsubscript{2}N]$^{-}$, Deetlefs \textit{et al.}~\cite{Deetlefs_2006} have determined the conformer population of the liquid phase employing neutron difraction.
+They observed that [Tf\textsubscript{2}N]$^{-}$ is mostly in \textit{trans} configuration (Fig.~\ref{fig:kdderman_a}).
+Fig.~\ref{fig:cddf_anion}, which corresponds to the CDF for the contiguous dihedrals: C1-S1-N1-S2 y S1-N1-S2-C2, verifies qualitatively what was observed by Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
+However, in this case we have not employed the strategy of rigid bodies, because the flexibility of the anion gives rise to highly different conformation and a more rigorous strategy for determinaning the proportion of rigid bodies is required.
+Thus, for the simulation of solvation of CO\textsubscript{2} in  [emim][Tf\textsubscript{2}N] will be carried out considering flexible ions and the DSF method with $\alpha$ = 0.2 {\AA}$^{-1}$.
+The simulated density for the pure ionic liquid was 1.495 $\pm$ 0.009 (g/cm$^3$), which has an error of 1.12\% with respect to the experimental density 1.513 g/cm$^3$)~\cite{Tokuda_2005}.
 
@@
 
+For each model of [emim][B(CN)\textsubscript{4}] described in Sec~\ref{sec:force_field_il}, in Table \ref{table:henry} we present the results of solvation free energy of CO\textsubscript{2} along with the Henry constant ($K_s$), as obtained from Eq.~\ref{eq:henry_eq}, which we compare with the experimental value reported by Mahurin \textit{et al.} \cite{Mahurin_2010}.
+Table \ref{table:henry} also includes the simulated results for [emim][Tf\textsubscript{2}N] and the experimental $K_s$ obtained by Finotello \textit{et al.}\cite{Finotello_2008}.
+The uncertainties were calculated using standard error propagation.
+
 \begin{table*}
@@
 
+It should be pointed out that the simulated $\Delta G$ of the model due to Liu \textit{et al.}~\cite{Liu_2014} is statistically identical to the value of -0.91 $\pm$ 0.03 kcal/mol reported by those authors, who applied the BAR method to independent simulations in $\lambda_{\text{LJ}}$ and $\lambda_{\, \text{Coul}}$.
+Moreove, the value of $\Delta G$ obtained for [emim][Tf\textsubscript{2}N] is very close -0.534 kcal/mol, which was obtained by Kerl \textit{et al.} \cite{Kerl__2017} using FEP method and no uncertainty is reported.
+
+In Table \ref{table:henry} we observe that the model of Koller y col.~\cite{Koller_2012} best reproduces the experimental value of $K_s$.
+Furthermore, the models with more errors in $K_s$, neither were able to reproduce the experimental density (Table \ref{table:props_dsf}).
+If we  look at the $\Delta G_{\, \text{LJ}}$ profiles in Fig.
+we can see that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014}, the maximum of free energy occur at lower values of energy.
+This indicates that those models subestimate the interatomic interactions, which explains the ``facility'' to inset the solute in those systems and explains the results relative to simulated densities.
+
+The $\Delta G_{\, \text{sim}}$ obtained for [emim][B(CN)\textsubscript{4}] suggest a more favorable solvation of CO\textsubscript{2} than in [emim][Tf\textsubscript{2}N].
+The contribution to $K_s$ from a more negative $\Delta G_{\, \text{sim}}$ is compensated with the higher molar density of [emim][B(CN)\textsubscript{4}], which tradues in almost equal values of $K_s$ for both ionic liquids.
+
+We now proceed to analyse the spatial distribution functions (SDFs)\cite{Svishchev_1993} corresponding to simulations of the systems CO\textsubscript{2}-[emim][B(CN)\textsubscript{4}] and CO\textsubscript{2}-[emim][Tf\textsubscript{2}N] for a molar fraction for the solute of 0.1.
+obtained using the software packages TRAVIS~\cite{Brehm_2011} and VMD~\cite{HUMP96}.
+In Fig.~\ref{fig:sdf_ions} we present the SDFs of the cation and the anion around a molecule of CO\textsubscript{2}.
+The isovalues were determined from a visual inspection in VDM, so as to obtain the probabilities corresponding to the first peak of the RDFs.
+In what follows, we refer to first solvation shell.
+Fig.~\ref{fig:ludwig_sdf} correspond to ions [emim]$^{+}$ and [Tf\textsubscript{2}N]$^{-}$, it can be seen that the region with low probability of finding an ion is larger than for [emim][B(CN)\textsubscript{4}].
+In Fig.~\ref{fig:anions} the SDFs involving the anions only, the first solvation shell regarding [B(CN)\textsubscript{4}]$^{-}$ occur at a sligthly shorter distance than for [Tf\textsubscript{2}N]$^{-}$.
+In accordance with the more favorable solvation indicated by the values of the solvation free energies.
+
 \begin{figure}
@@
 \label{sec:act_results}
+
+Having selected the model of [emim][B(CN)\textsubscript{4}] which best reproduces the experimental $K_s$ of CO\textsubscript{2}, we now proceed with the calculation of the infinite-dilution activity coefficient $\gamma^{\, \infty}$ for the solutes benzene, hexane, cyclohexane, ethanol and water; which were modeled with the force fields mentioned in Sec.~\ref{sec:force_field_sol}.
+We have chosen those solutes in order to compare with recent experimental data reported by Yan \textit{et al.}\cite{Yan_2010} and Doma{\'{n}}ska \textit{et al.} \cite{Doma_ska_2011}.
+
+The prediction of $\gamma^{\, \infty}$ we have the additional difficulty, given that the solute model has to be able to reproduce the pure solvation free energy, as well.
+In Table~\ref{table:mu_solutos} we present the simulated densities and the solvation free energies for the pure solutes $(\Delta G^{0}_{\text{sim}})$, which were compared to experimental data extracted from the work of Chang~\cite{Chang_2009}, which in turn has recomplied  En dicho trabajo se realiza una recopilación de $\Delta G^{0,\text{exp}}$ a partir de diversas fuentes bibliográficas.
+Cabe mencionar que no fue posible hallar en la literatura el valor correspondiente a ciclohexano.
+El único soluto para el cual se logra reproducir el valor de $\Delta G^{0,\text{exp}}$ corresponde a etanol.
+Para los otros solutos, el error en la predicción se encuentra en torno del 10\%.
+
+Los resultados de $\gamma^{\, \infty}$ en el líquido iónico [emim][B(CN)\textsubscript{4}] se presentan en la Tabla~\ref{table:gamma}.
+En los casos de benceno y agua las predicciones son excelentes, aunque existe una compensación de errores, dadas las divergencias observadas en la Tabla~\ref{table:mu_solutos}.
+Estas divergencias hacen necesaria una revisión más exhaustiva, tanto de los datos experimentales de la energía libre de solvatación, como de los campos de fuerza de los solutos.
+Nótese que los datos experimentales de $\gamma^{\, \infty}$ relativos al hexano difieren de forma considerable para las temperaturas próximas de 298.15 K y 303 K, con lo cual en este caso se hace más dificil aún determinar la calidad de los resultados de la simulación.
 

### 2018-05-04 ionic_liquids.tex
intro e abstract

--- 2018-04-05 ionic_liquids.tex
@@
 
-\title{A molecular dynamics study of the solvation of CO\textsubscript{2}, water, and some organic compounds in the ionic liquids [emim][B(CN)\textsubscript{4}] and [emim][NTf\textsubscript{2}]}
+\title{A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 
@@
 \begin{abstract}
-In this paper we predict solvation in ionic liquids and macroscopic properties required in the design of chemical processes.
+In this paper we calculate solvation free enegies in ionic liquids and predict macroscopic properties required in the design of chemical processes.
 Carbon dioxide produced in combustion processes is one of the main sources of anthropogenic generation of greenhouse gases.
-On the other hand, the potential of [emim][B(CN)\textsubscript{4}] for its capture has recently been reported.
-For comparison, the solvents [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N] were analyzed, both in the condition of infinite dilution and at high concentrations.
-The simulations confirmed what was observed experimentally, that is, a considerably lower pressure is required in [emim][B(CN)\textsubscript{4}] to obtain the same molality of CO\textsubscript{2}.
-The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in [emim][B(CN)\textsubscript{4}] were also calculated, and a comparison was made with experimental values recently reported in the literature.
+On the other hand, the potential of \ce{[emim][B(CN)_4]} for its capture has recently been reported.
+For comparison, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both in the condition of infinite dilution and at high concentrations.
+The simulations confirmed what was observed experimentally, namely the pressure required to obtain the same molality of \ce{CO_2} is notably lower in \ce{[emim][B(CN)_4]}.
+The infinite-dilution activity coefficients of hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} were also calculated, and a comparison was made with experimental values recently reported in literature.
 \end{abstract}
@@
 \begin{keyword}
-ionic liquids \sep solvation free energy \sep  CO\textsubscript{2} 
+ionic liquids \sep solvation free energy \sep  \ce{CO_2} 
 \end{keyword}
@@
 \section{Introduction}
-State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results. foreseeable future
 
-The CO\textsubscript{2} emissions from power generation plants are still sources of anthropogenic greenhouse gases~\cite{totalenergy} and the searching of solvents is an active field of research.
-Post combustion absorption technologies flue gas
+The \ce{CO_2} emissions from power generation plants are still an important source of anthropogenic greenhouse gases \cite{totalenergy}.
+International efforts aimed at regulating and reducing \ce{CO_2} emissions are increasing \cite{Tong_2018} and, in this context, the development of technologies for the capture and storage of \ce{CO_2} is essential.
+\cite{Markewitz_2014}.
 
-Basically, the conventional process for CO\textsubscript{2} removal involves a chemical absorption followed by stripping at high temperatures.
-The solvents commonly used are volatile organic compounds, specially aqueous solutions of monoethanolamine (MEA).
-Despite its high absorption capability, the use of MEA suffers from a serious drawback in that there is considerable cost due to the energy consumption in the solvent recovery~\cite{Merkel_2010}.
-Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes with ambient pollution and generates extra costs for substituting the solvent.
+The conventional process for \ce{CO_2} removal involves a chemical absorption followed by stripping at high temperatures.
+The solvents commonly employed are volatile organic compounds, specially aqueous solutions of monoethanolamine (MEA).
+Despite its high absorption capability, the use of MEA suffers from a serious drawback, namely a considerable cost due to the energy consumption of solvent recovery \cite{Merkel_2010}.
+Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes to increase the ambient pollution and generates extra costs to replace the solvent.
 
-The investigation of ionic liquids (ILs) as alternative solvents for CO\textsubscript{2} sequestration occupies a central place.
-The reasons in their well known properties, such as the negligible vapor pressure and high thermal stability.
-Furthermore, they are particularly attractive because they can be designed for specific applications, giving rise to the so-called task-specific ionic liquids~\cite{Seo_2014}.
-These remarkable properties makes ionic liquids suitable for a wide variety of applications in separation processes~\cite{Han_2010,Werner_2010}, catalysis~\cite{P_rvulescu_2007}, energy~\cite{MacFarlane_2014} and material science~\cite{Mecerreyes_2011,Tom_2015,Dupont_2010,Leones_2017,Kinik_2017}.
+The use of ionic liquids (ILs) as solvents for \ce{CO_2} sequestration occupies a central place in the investigation of alternative technologies.
+The reasons are their well known properties, such as the negligible vapor pressure and high thermal stability.
+Furthermore, they are particularly attractive because they can be designed for specific applications, giving rise to the so-called task-specific ILs \cite{Seo_2014}.
+These remarkable properties makes ILs suitable for a wide variety of applications in separation processes \cite{Han_2010,Werner_2010}, catalysis \cite{P_rvulescu_2007}, energy \cite{MacFarlane_2014} and material science \cite{Mecerreyes_2011,Tom_2015,Dupont_2010,Leones_2017,Kinik_2017}.
 
-Recently, the potentiality of ionic liquids for CO\textsubscript{2} capture has been called into question by Carvalho~\textit{et al.}~\cite{Carvalho_2016}, who warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposed absorption capability of certain ionic liquids.
-While most thermodynamic models are developed based on molar fraction, the key factor to determine the absorption process efficiency is given by the amount of CO\textsubscript{2} that can be dissolved in a certain volume or mass of solvent.
-By expressing the solubility in terms of molality and performing an exhaustive comparison between various ionic liquids, Ref.~\cite{Carvalho_2016} shows that most systems which promote a physical absorption of CO\textsubscript{2} exhibit a CO\textsubscript{2} solubility similar or even lower than that observed for the heavy alkane eicosane.
-This is true for the ``popular'' [bmim][Tf\textsubscript{2}N], [bmim][PF\textsubscript{6}], [bmim][BF\textsubscript{4}], as well as for those synthesized from the fluorination of the cation or the anion, such as [(C\textsubscript{2}H\textsubscript{2}F\textsubscript{2})mim][NTf\textsubscript{2}] and [hmim][pFAP], the only exception being the family of ionic liquids containing the anion tetracyanoborate [B(CN)\textsubscript{4}]$^{-}$.
+Recently, the potentiality of ILs for the \ce{CO_2} capture has been called into question by Carvalho \textit{et al.} \cite{Carvalho_2016}, who warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposed absorption capability of certain ILs.
+While most thermodynamic models were developed based on molar fraction, the key factor to determine the absorption process efficiency is given by the amount of \ce{CO_2} that can be dissolved in a certain volume or mass of solvent.
+By expressing the solubility in terms of molality and performing an exhaustive comparison between various ILs, Ref.
+\cite{Carvalho_2016} shows that most systems which promote a physical absorption of \ce{CO_2} exhibit a \ce{CO_2} solubility similar or even lower than that observed for the heavy alkane eicosane.
+This is true for the ``popular'' \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}, the only exception being the family of ILs containing the anion tetracyanoborate \ce{[B(CN)_4]^-]}.
 
-There is no obvious explanation accounting for the enhanced solubility promoted by the presence of the anion [B(CN)\textsubscript{4}]$^{-}$, whether special interactions with CO\textsubscript{2} are settled.
+There is no obvious explanation accounting for the enhanced solubility promoted by the presence of the anion \ce{[B(CN)_4]^-]}, whether special interactions with \ce{CO_2} are settled.
 In this sense, Molecular Simulation provides with a powerful tool for studying solvation processes.
-To our knowledge, only one study in the literature reports the free energy of solvation of CO\textsubscript{2} in [emim][B(CN)\textsubscript{4}] which, in addition, is overestimated.
-This motivated us to carry out a comparison of different force fields of [emim][B(CN)\textsubscript{4}] in terms of the free energy of solvation and, indeed,  it was possible to select a model that successfully predicts the value of the Henry constant of CO\textsubscript{2}.
-For comparison, the solvents [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N] were analyzed, both in the condition of infinite dilution and at high concentrations.
-The simulations confirmed what was observed experimentally, that is, a considerably lower pressure is required in [emim][B(CN)\textsubscript{4}] to obtain the same molality of CO\textsubscript{2}.
-The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in [emim][B(CN)\textsubscript{4}] were also calculated, and a comparison was made with experimental values recently reported in the literature.
+To our knowledge, only one study in the literature reports the free energy of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} \cite{Liu_2014_1} which, in addition, is overestimated.
+This motivated us to carry out a comparison of different force fields of \ce{[emim][B(CN)_4]} in terms of the free energy of solvation and, indeed,  it was possible to select a model that successfully predicts the value of the Henry constant of \ce{CO_2}.
+For comparison, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both in the condition of infinite dilution and at high concentrations.
+The simulations confirmed what was observed experimentally, that is, a considerably lower pressure is required in \ce{[emim][B(CN)_4]} to obtain the same molality of \ce{CO_2}.
+The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} were also calculated, and a comparison was made with experimental values recently reported in the literature.
 
-This paper is organized as follows: in Section~\ref{sec:theory} we present some methodological details, including the mathematical relationships between free energy of simulated solvation and thermodynamic properties of diluted solutions.
-and a brief description of the force fields considered for [emim][B(CN)\textsubscript{4}], and the details of the simulations for free energy calculations are presented.
-The corresponding results are presented in the Section~\ref{sec:results}, where a comparison is made with the experimental data of Henry's constants, the results of the activity coefficients are shown at infinite dilution and, finally, a study of the CO\textsubscript{2} solvation is carried out in high concentrations.
+This paper is organized as follows: in Sec.
+\ref{sec:theory} we present the mathematical relationships between the simulated solvation free energy and thermodynamic properties.
+This is followed by a brief description of the force fields considered for the ILs and the solutes.
+The methodological details are provided in Sec.
+\ref{sec:sim_details} and the numerical results are given in Sec.
+\ref{sec:results}.
+Finally, we present some concluding remarks in Sec.
+\ref{sec:conclusion}.
 
@@
 In this section, we present the formalism that allows a direct comparison between simulation results and the thermodynamic properties of dilute solutions: Henry constant and activity coefficient at infinite dilution.
-For this, we rely on the work of Shirts~\textit{et al.}~\cite{Shirts_2003}.
-Then, we reformulate the equations in order to carry out a study at concentrated conditions, which would be the more likely scenario in CO\textsubscript{2} capture processes.
+For this, we rely on the work of Shirts \textit{et al.} \cite{Shirts_2003}.
+Then, we reformulate the equations in order to carry out a study at concentrated conditions, which would be the more likely scenario in \ce{CO_2} capture processes.
 
@@
 \begin{equation}
+\label{eq:gamma_inf}
 \ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_{\text{sim}} - \Delta G_{\text{sim}}^{0} \right) + \frac{c_{\scaleto{LI}{4pt}}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
@@
 \subsection*{Partial pressure estimation}
+\label{sec:partial_pressure}
 
-For the ILs of interest to the present investigation, high concentrations of CO\textsubscript{2} are found at pressure values for which, in principle, the ideal gas assumption may be not valid.
+For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} are found at pressure values for which, in principle, the ideal gas assumption may be not valid.
 In this case, we shall correct the ideal gas contribution to the chemical potential, as follows
@@
 \end{equation}
-where $B_s$ corresponds to the second virial coefficient. Here we employ the correlation for CO\textsubscript{2} introduced by Holste~\textit{et al}~\cite{Holste_1987}, which is
+where $B_s$ corresponds to the second virial coefficient. Here we employ the correlation for \ce{CO_2} introduced by Holste~\textit{et al}~\cite{Holste_1987}, which is
 \begin{equation}
@@
 
-In this paper, we consider four models of [emim][B(CN)\textsubscript{4}].
-Koller~\textit{et al.}~\cite{Koller_2012} were the first to introduce a specific non-polarizable force field of [emim][B(CN)\textsubscript{4}].
-They tested three variations of a \textit{united-atoms} model, in which the alkyl groups $\text{CH}_3$ and $\text{CH}_2$ of [emim]$^{+}$ are replaced by pseudo-atoms.
+In this paper, we consider four models of \ce{[emim][B(CN)_4]}.
+Koller~\textit{et al.}~\cite{Koller_2012} were the first to introduce a specific non-polarizable force field of \ce{[emim][B(CN)_4]}.
+They tested three variations of a \textit{united-atoms} model, in which the alkyl groups $\text{CH}_3$ and $\text{CH}_2$ of \ce{[emim]^+} are replaced by pseudo-atoms.
 Among them, the ``FF-3'' model best reproduces the experimental values of density, self-diffusion coefficients and viscosity.
@@
 
-The potential parameters of [B(CN)\textsubscript{4}]$^{-}$ derived by Koller~\textit{et al.}~\cite{Koller_2012} were employed by Batista~\textit{et al.}~\cite{Batista_2015} to study aqueous solutions of [emim][B(CN)\textsubscript{4}].
-In this case,  the authors considered the \textit{all-atom} model of [emim]$^{+}$ developed by Cadena and Maginn \cite{Cadena_2006}.
+The potential parameters of [B(CN)\textsubscript{4}]$^{-}$ derived by Koller~\textit{et al.}~\cite{Koller_2012} were employed by Batista~\textit{et al.}~\cite{Batista_2015} to study aqueous solutions of \ce{[emim][B(CN)_4]}.
+In this case,  the authors considered the \textit{all-atom} model of \ce{[emim]^+} developed by Cadena and Maginn \cite{Cadena_2006}.
 The atomic partial charges were obtained using the CHELP procedure \cite{Breneman_1990}, resulting in net charges of $\pm$0.889$e$ on the ions.
@@
 
-Another set of parameters for \mbox{[emim][B(CN)\textsubscript{4}]} was derived by Liu \textit{et al.}\cite{Liu_2014} in a study that investigates the dynamics of CO\textsubscript{2} and N\textsubscript{2} in that IL.
+Another set of parameters for \mbox{\ce{[emim][B(CN)_4]}} was derived by Liu \textit{et al.} \cite{Liu_2014} in a study that investigates the dynamics of \ce{CO_2} and N\textsubscript{2} in that IL.
 Parameters corresponding to the intramolecular and Lennard-Jones interactions were extracted from GAFF~\cite{Wang_2004}, while the atomic partial charges were computed using the RESP method~\cite{Bayly_1993} from \textit{DFT}/B3LYP/6-311+G(d) calculations.
@@
 This refining was characterized by their authors as unusual, given that the LJ parameters were modified, while keeping the partial charges at their original values.
-This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry's constant for CO\textsubscript{2} at several temperatures.
+This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry's constant for \ce{CO_2} at several temperatures.
 
@@
 
-The solutes considered here are hexane, benzene, CO\textsubscript{2}, ethanol, cyclohexane and water.
-Hexane and benzene were modeled using the OPLS-AA force field~\cite{Jorgensen_1996}, while the TRAPPE potential~\cite{Chen_2001,Potoff_2001} was employed for ethanol and CO\textsubscript{2}.
+The solutes considered here are hexane, benzene, \ce{CO_2}, ethanol, cyclohexane and water.
+Hexane and benzene were modeled using the OPLS-AA force field~\cite{Jorgensen_1996}, while the TRAPPE potential~\cite{Chen_2001,Potoff_2001} was employed for ethanol and \ce{CO_2}.
 Cyclohexane was simulated using a rigid-body model~\cite{munoz2015lennard} whose sites only interact via the Lennard-Jones potential and for water we employ the TIP4P/2005 model~\cite{Abascal_2005}, \cite{Vega_2011}.
@@
 
-In this section, we present and compare the results obtained for the following two cases: (1) flexible ions and the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for the evaluation of the Ewald sums~\cite{Ewald_1921}, and (2) ions modeled as rigid bodies with the DSF method~\cite{Fennell2006} for calculating the Coulombic interactions.
+In this section, we present results for the following two cases: (1) flexible ions and the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for the evaluation of the Ewald sums~\cite{Ewald_1921}, and (2) ions modeled as rigid bodies with the DSF method~\cite{Fennell2006} ($\alpha$ = 0.2 {\AA}$^{-1}$) for calculating the Coulombic interactions.
+For both strategies we employed $r_c$ = 12 {\AA}.
 
-First, we describe the approach for defining the rigid bodies.
-For that, we carried out an analysis of key dihedrals, particularly those whose flexibility could lead to significant conformational changes in [emim]$^{+}$ and [Tf\textsubscript{2}N]$^{-}$.
-On the other hand, small and highly symmetric anions, such as PF\textsubscript{6} and BF\textsubscript{4} are usually modeled as rigid bodies~\cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies that strategy in the case of [B(CN)\textsubscript{4}]$^{-}$.
-The atomic nomenclatureare adopted in this paper is shown in Fig~\ref{fig:atoms_id}.
-In the \textit{united-atoms} version of [emim]$^{+}$, the nomenclature is identical, but the hydrogens ranging from H4 to H11 are eliminated.
-
-Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtain the combined distribution function (CDF) of the dihedral angles corresponding to the torsions in C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs.
-The CDF, as an alternative of individual histograms, provides a way to  simultaneously analyze the rigidity of the ring.
-In Fig.~\ref{fig:dihedrals_emim} we present the results of the CDF for each model.
-
-A first inspection of Fig.
-reveals a similar behavior of the models of [emim]$^{+}$ due to Koller~\textit{et al.}~\cite{Koller_2012} and Liu~\textit{et al.}~\cite{Liu_2014}.
-This was expected as both were developed based on the AMBER force field.
-In addition, Figs.(a) and(b) are symmetric, which means that atoms C1-N2-C2 are coplanar.
-Koller is the most rigid model, with The most likely angles in Fig.~(a) can be found in a narrow region around 90 and 270.
-Given that these angles correspond to the same configuration in the \textit{united-atom} version, we build all the rigid bodies specifying 90 for the dihedral angle of C5-C5-N2-C1.
-The other models present a larger flexibility of the ethyl chain, with high probability regions that extend  ina broad of angle values.
-However, in the case of Liu and Batista, it was possible to the following approach: we consider the most likely angles as obtained by the indificual histogram of the dihedral C5-C5-N2-C1, which were employed to construct two types of rigid bodies.
-In the case of Liu , 50 of the rigid bodies were build specifying the angle of 90 for the dihedral C6-C5-N2-C1 and -90 of the others.
-For Batista, we employed the angles 102.6  and -102.6 for buildign both types for rigid bodies in an equal proportion.
+First, we describe the approach for building the rigid bodies.
+For that, we carried out an analysis of key dihedrals, particularly those whose flexibility could lead to significant conformational changes in \ce{[emim]^+} and \ce{[Tf_2N]^-}.
+On the other hand, small and highly symmetric anions, such as \ce{PF_6} and \ce{BF_4} are usually modeled as rigid bodies~\cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies that strategy in the case of [B(CN)\ce{4}]$^{-}$.
+The atomic nomenclature adopted in this paper is shown in Fig~\ref{fig:atoms_id}.
+In the \textit{united-atoms} version of \ce{[emim]^+}, the nomenclature is identical, but the hydrogens ranging from H4 to H11 are eliminated.
 
@@
 \includegraphics[width=\linewidth]{ions_paper.pdf}
-\caption{[emim]$^{+}$ [B(CN)\textsubscript{4}]$^{-}$ [Tf\textsubscript{2}N]$^{-}$.}
+\caption{\ce{[emim]^+} [B(CN)\textsubscript{4}]$^{-}$ \ce{[NTf_2]^-}.}
 \label{fig:atoms_id}
 \end{figure}
+
+Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtained the combined distribution function (CDF) of the dihedral angles corresponding to the torsions in C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs.
+The CDF, as an alternative to individual histograms, provides a way to  simultaneously analyze the rigidity of the ring.
+In Fig.~\ref{fig:dihedrals_emim} we present the results for each model of \ce{[emim][B(CN)_4]}.
+
+A first inspection of Fig.~\ref{fig:dihedrals_emim} reveals a similar behavior of the models of \ce{[emim]^+} due to Koller \textit{et al.} \cite{Koller_2012} and Liu \textit{et al.} \cite{Liu_2014}.
+This was expected as both were developed based on the AMBER force field ~\cite{Cornell_1995}.
+In addition, Figs.~\ref{fig:dihedrals_emim}(a) and \ref{fig:dihedrals_emim}(b) are symmetric, which means that atoms C1, N2, and C2 are coplanar.
+In Fig.~\ref{fig:dihedrals_emim}(a), the most likely angles can be found in a narrow region around 90$^{\circ}$ and 270$^{\circ}$.
+Given that these angles correspond to the same configuration in the \textit{united-atom} representation of \ce{[emim]^+}, we built all the rigid bodies specifying the value of 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1.
+The other models showed a larger flexibility with high probability regions that extend in a broad range of angle values.
+Despite this, it was possible to build more than one type of rigid body by specifying the most probables angles for C6-C5-N2-C1.
+In the case of Liu \textit{et al.} \cite{Liu_2014}, those angles correspond to the values of  90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed the angles of 102.6$^{\circ}$ and -102.6$^{\circ}$.
+In these cases, two types of rigid bodies were built in equal proportion.
+Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} presents a non negligible probability of sampling the angle value of 0$^{\circ}$, which notably differs from what was observed for the other models.
+In this case we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of the rigid bodies, respectively; and for the remaining 15~\% we specified the angle of 0$^{\circ}$.
+
+In Table~\ref{table:props_dsf} we show the results of density for the strategies mentioned at the begining of this section.
+When comparing the cases (1) and (2) for each model, we observe that the density values practically do not differ.
+In addition, the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental density.
+The model due to Weber and Kirchner also presents a small deviation of 1\%.
+
+For the simulation strategies (1) and (2) we have also compared the results of relevant radial distribution functions (RDFs), which can be found in the Supplementary material.
+The better agreement was found for the force fields due to Koller \textit{et al.} \cite{Koller_2012} and Batista \textit{et al.} \cite{Batista_2015}.
+Even though the model of Liu \textit{et al.} \cite{Liu_2014} presented small deviations, the simulation with rigid bodies qualitatively reproduced the RDFs obtained for flexible ions.
+Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion).
+The model of Weber and Kirchner \cite{Weber_2016},
+on the other hand, presented important discrepancies in the RDFs for the pairs C5(cation)-N(anion) and C2(cation)-B(anion) when using rigid bodies.
+That is why in this case we have considered as being rigid only the imidazolium ring while letting  the ethyl chain flexible.
 
@@
 
+A study of dihedrals was also carried out for \ce{[emim][NTf_2]}.
+The CDF of dihedrals C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the behaviour of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 corresponds to 0$^{\circ}$.
+This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
+With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.}~\cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation (Fig.~\ref{fig:kdderman_a}).
+Fig.~\ref{fig:cddf_anion}, which corresponds to the CDF for the contiguous dihedrals C1-S1-N1-S2 and S1-N1-S2-C2, verifies qualitatively what was observed by Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
+Given that the flexibility of \ce{[NTf_2]^-} gives rise to highly different conformation, a more rigorous strategy for building rigid bodies would be required.
+Thus, for \ce{[emim][NTf_2]} we have considered flexible ions and the DSF method, which resulted in a simulated density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.
+
 \begin{figure}[H]
@@
 \begin{table*}
-\caption{Densidades de [emim][B(CN)\textsubscript{4}] calculadas a partir simulaciones de NPT DM 298.15 K y 1 atm.
-La densidad experimental corresponde a $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
+\caption{Densities of \ce{[emim][B(CN)_4]} predicted from MD NPT simulations at 298.15 K and 1 atm. The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
 \begin{threeparttable}
@@
 
-\subsection{Henry constant of CO\textsubscript{2} in [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N]}
+\subsection{Henry constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]}
 \label{sec:henry_results}
+
+For each model of \ce{[emim][B(CN)_4]} described in Sec~\ref{sec:force_field_il}, in Table \ref{table:henry} we present the results corresponding to the solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\ref{eq:henry_eq}, which we compare with the experimental value reported by Mahurin \textit{et al.} \cite{Mahurin_2010}.
+Table \ref{table:henry} also includes the results for [emim][Tf\textsubscript{2}N] and the experimental $K_s$ obtained by Finotello \textit{et al.} \cite{Finotello_2008}.
+The uncertainties were calculated using standard error propagation.
 
@@
 \begin{threeparttable}
-\caption{Resultados de la energía libre de solvatación y de la constante de Henry de CO\textsubscript{2} en [emim][B(CN)\textsubscript{4}] y [emim][Tf\textsubscript{2}N] a T = 298.15 K y P = 1 atm.
-Los valores experimentales de la constante de Henry en [emim][B(CN)\textsubscript{4}] y [emim][Tf\textsubscript{2}N] corresponden a 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} y a 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}, respectivamente.}
+\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at T = 298.15 K and P = 1 atm.
+The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}, respectively.}
 \begin{tabular}{ c c c  c  c  c  c }  
 \toprule
-Modelo & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
+Model & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
 & (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
 			\hline
-			\multicolumn{4}{c}{[emim][B(CN)\textsubscript{4}]} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
+			\multicolumn{4}{c}{\ce{[emim][B(CN)_4]}} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
 			\hline
-Koller y col.~\cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
-Batista y col.~\cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
-Liu y col.~\cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
-Weber y Kirchner~\cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
+Koller \textit{et al.} \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
+Batista \textit{et al.} \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
+Liu \textit{et al.} \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
+Weber y Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
 \hline
@@
 		\hline
- K\"{o}ddermann y col.~\cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
+ K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
  \bottomrule
@@
 
+First, it should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.}~\cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent simulations in $\lambda_{\text{LJ}}$ and $\lambda_{\, \text{Coul}}$.
+Moreover, the value of $\Delta G_{\text{sim}}$ corresponding to [emim][Tf\textsubscript{2}N] is very close to -0.534 kcal/mol, which was obtained by Kerl \textit{et al.} \cite{Kerl__2017} using the FEP method \cite{Zwanzig_1954} with no uncertainty reported.
+These consistencies serve for validating the methodological approaches we employed in each case.
+
+From Table \ref{table:henry} one can see that the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental value of $K_s$.
+If we look at the $\Delta G_{\, \text{LJ}}$ profiles in Fig.~\ref{fig:deltag} we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014}, the maximum of free energy occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which explains the ``facility'' to insert the solute molecule as well as their failure to reproduce the experimental densities.
+
+\begin{figure}[]
+\includegraphics[width=\linewidth]{free_energy_paper}
+\label{fig:deltag}
+\end{figure}
+
+The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in [emim][Tf\textsubscript{2}N].
+In order to have a graphical insight of solvation, we have also obtained the spatial distribution functions (SDFs) \cite{Svishchev_1993} using the software packages TRAVIS~\cite{Brehm_2011} and VMD~\cite{HUMP96}.
+For that, we carried out MD NPT simulations of the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] with a solute molar fraction of 0.1.
+In Fig.~\ref{fig:sdf_ions} we show the SDFs of the ions around a molecule of \ce{CO_2}.
+The isovalues were determined visually so as to observe the first solvation shell.
+From Fig.~\ref{fig:ludwig_sdf}(b), which correspond to the ions \ce{[emim]^+} and \ce{[NTf_2]^-}, it can be seen that the region with a low probability of finding an ion is larger than for \ce{[emim][B(CN)_4]}.
+In Fig.~\ref{fig:anions} we have plotted together the SDFs corresponding to the anions and we note that the first solvation shell for [B(CN)\textsubscript{4}]$^{-}$ occur at a sligthly shorter distance than for \ce{[NTf_2]^-}, in accordance with the more favorable solvation suggested by the free energy results.
+
 \begin{figure}
 \centering
-\subfloat[[emim][BCN4]-CO\textsubscript{2}]{%
+\subfloat[]{%
   \includegraphics[width=\linewidth]{kollerall.pdf}%
@@
 
-\subfloat[[emim][BCN4]-CO\textsubscript{2}]{%
+\subfloat[]{%
   \includegraphics[width=\linewidth]{ludwigall.pdf}%
@@
 \label{sec:act_results}
+
+Having selected the model of \ce{[emim][B(CN)_4]} which best reproduces the experimental $K_s$ of \ce{CO_2}, we now proceed to predict the infinite-dilution activity coefficient ($\gamma^{\, \infty}$) of benzene, hexane, cyclohexane, ethanol and water in \ce{[emim][B(CN)_4]}.
+These solutes were modeled as described in Sec.~\ref{sec:force_field_sol}.
+
+The task of accurately predicting $\gamma^{\, \infty}$ is more challenging given that, according to Eq.~\ref{eq:gamma_inf}, one should be able to reproduce the solvation free energies in both the pure solute and the solvent.
+In Table~\ref{table:mu_solutos} we present the simulated densities and the solvation free energies  $(\Delta G^{0}_{\text{sim}})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}.
+It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ of cyclohexane.
+Note that only in the case of ethanol we have reproduced $\Delta G^{0}_\text{exp}$ while the relative error for the other solutes is around 10\%.
+
+The results of $\gamma^{\, \infty}$ for the solutes in \ce{[emim][B(CN)_4]} are shown in Table~\ref{table:gamma}.
+For benzene and water, the predictions are very accurate, but thay are a result of error compensations given the divergences verified in Table~\ref{table:mu_solutos}.
+This makes necessary to review the force fields of the solutes.
+From Table \ref{table:gamma} one can also note that the experimental $\gamma^{\, \infty}$ for hexane at the close temperatures of 298.15 K and 303 K considerably differ.
+It is therefore difficult to assess the reliability of the simulated results in this case.
 
@@
 \begin{threeparttable}
-\caption{Coeficientes de actividad a dilución infinita en [emim][B(CN)\textsubscript{4}] a T = 298.15 K de los solutos benceno, hexano, ciclohexano, etanol y agua.}
+\caption{Coeficientes de actividad a dilución infinita en \ce{[emim][B(CN)_4]} a T = 298.15 K de los solutos benceno, hexano, ciclohexano, etanol y agua.}
 \begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
@@
 
-\subsection{Study of concentrated solutions of CO\textsubscript{2} in [emim][B(CN)\textsubscript{4}] and [emim][Tf\textsubscript{2}N]}
+\subsection{Study of concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]}
 \label{sec:results_conc}
+
+In Secs.~\ref{sec:henry_results} and \ref{sec:act_results} we obtained some solvation properties for diluted solutions.
+However, the corresponding derived conclusions cannot be extraploted to concentrated solutions, which are the more likely scenario in the \ce{CO_2} capture.
+Therefore, in this section we proceed to analyze the \ce{CO_2} solvation at the thermodynamic conditions specified in Table \ref{table:solv}.
+These conditions correspond to close values of molality of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N], which is the solubility measure employed by Carvalho \textit{et al.}~\cite{Carvalho_2016}.
+
+\begin{table*}
+\centering
+\begin{threeparttable}
+\caption{Thermodynamic conditions employed in the simulations of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]~\cite{Makino_2014,Schilderman_2007}}
+\begin{tabular}{ c  c  c  c  c  }  
+\toprule
+Ionic liquid & T (K)  & P (atm)  & molar fraction $x_s$ & molality $m_s$ \\
+\midrule		
+$\text{[emim]}$[B(CN)\textsubscript{4}]~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
+$\text{[emim]}$[Tf\textsubscript{2}N]~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
+ \bottomrule
+\label{table:solv} 
+\end{tabular}
+\end{threeparttable}
+\end{table*}
+
+In Fig.
+we present the results of each iteration according to the scheme proposed in Sec.
+\ref{sec:partial_pressure}.
+The predicted values of pressure ($P_s$) reproduce what is observed experimentaly, in the sense that $P_s$ for the system \ce{CO_2}-\ce{[emim][B(CN)_4]} is considerably smaller than the value obtained for \ce{CO_2}-[emim][Tf\textsubscript{2}N].% However, in this case we were not able to converge because an oscilatory behaviour was observed.
+
+\begin{table*}
+\centering
+\begin{adjustbox}{width=1\textwidth}
+\begin{threeparttable}
+\caption{Gaseous phase pressure, predicted from solvation free energies of \ce{CO_2} for the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N].}
+\begin{tabular}{ c c  c  c  c  c c }  
+\toprule
+\# & P &$\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $f^{g}_s$ (Ec.~\ref{eq:fgas_d}) & $P_s$ (Ec.~\ref{eq:fgas}) \\
+ &(atm) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm) & (atm) \\
+		\hline
+		\multicolumn{7}{c}{\ce{[emim][B(CN)_4]}~\cite{Koller_2012} } \\
+1 & 21.0 &  0.42 $\pm$ 0.01 & -1.176  $\pm$ 0.007  & -0.755 $\pm$ 0.01 & 16.96 $\pm$ 0.33 & 18.33 $\pm$ 0.4 \\
+2 & 18.33 &  0.39 $\pm$ 0.01 & -1.187  $\pm$ 0.008  & -0.794 $\pm$ 0.01 & 15.93 $\pm$ 0.33 & 17.14 $\pm$ 0.4 \\ 
+3 & 17.14 &  0.39 $\pm$ 0.01 & -1.164  $\pm$ 0.008  & -0.779 $\pm$ 0.01 & 16.32 $\pm$ 0.33 & 17.5 $\pm$ 0.4 \\
+		\hline
+       \multicolumn{7}{c}{[emim][Tf\textsubscript{2}N]~\cite{K_ddermann_2007} } \\
+1 & 37.0 &  0.314 $\pm$ 0.005  & -0.856 $\pm$ 0.005 & -0.542 $\pm$ 0.005 & 32.6 $\pm$ 0.37 & 38.4 $\pm$ 0.4 \\
+2 & 38.4 &  0.349 $\pm$ 0.005  & -0.840  $\pm$ 0.005 & -0.491 $\pm$ 0.005 & 35.35  & 42.47 \\
+ \bottomrule
+\label{table:deltaG_conc} 
+\end{tabular}
+\end{threeparttable}
+\end{adjustbox}
+\end{table*}
 

### 2018-05-04 ionic_liquids.tex
revision

@@
 On the other hand, the potential of \ce{[emim][B(CN)_4]} for its capture has recently been reported.
-For comparison, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both in the condition of infinite dilution and at high concentrations.
+For comparison purposes, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both in the condition of infinite dilution and at high concentrations.
 The simulations confirmed what was observed experimentally, namely the pressure required to obtain the same molality of \ce{CO_2} is notably lower in \ce{[emim][B(CN)_4]}.
@@
 In this sense, Molecular Simulation provides with a powerful tool for studying solvation processes.
-To our knowledge, only one study in the literature reports the free energy of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} \cite{Liu_2014_1} which, in addition, is overestimated.
+To the best of our knowledge, only one study in the literature reports the free energy of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} \cite{Liu_2014_1} which, in addition, is overestimated.
 This motivated us to carry out a comparison of different force fields of \ce{[emim][B(CN)_4]} in terms of the free energy of solvation and, indeed,  it was possible to select a model that successfully predicts the value of the Henry constant of \ce{CO_2}.
@@
 where $\bigtriangleup$ denotes the isobaric-isothermal partition function.
-Shirts~\textit{et al}.~\cite{Shirts_2003} presented a detailed mathematical derivation allowing to relate $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy and obtained the following expression:
+Shirts \textit{et al}.
+\cite{Shirts_2003} presented a detailed mathematical derivation allowing to relate $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy and obtained the following expression:
 \begin{equation}
@@
 
-For small solutes, such as those considered in this work, the magnitude of the term $V^{\ast}/V_1$ is typically on the order of the free energy uncertainties~\cite{Shirts_2003}.
+For small solutes, such as those considered in this work, the magnitude of the term $V^{\ast}/V_1$ is typically on the order of the free energy uncertainties \cite{Shirts_2003}.
 Hence, that term could be neglected and will be omitted hereafter.
@@
 \subsection*{Henry constant}
-If both $P_s$ and $c_s^{\ast}$ were not large, we can employ Eq.~\ref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is given by~\cite{Prausnitz}
+If both $P_s$ and $c_s^{\ast}$ were not large, we can employ Eq.~\ref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is given by \cite{Prausnitz}
 \begin{equation}
@@
 
-Using standard thermodynamic relations~\cite{Tester}, we write the activity coefficient $\gamma_s$ in terms of residual chemical potentials, as follows
+Using standard thermodynamic relations \cite{Tester}, we write the activity coefficient $\gamma_s$ in terms of residual chemical potentials, as follows
 \begin{equation}
@@
 \begin{equation}
-\mu_s^R = \mu_s^l(N_s^l,N_{LI},P,T) - \mu_s^{ig,0}(P,T) - k_b T \ln x_s. 
+\mu_s^R = \mu_s^l(N_s^l,N_{LI},P,T) - \mu_s^{ig,0}(P,T) - k_b T \ln x_s, 
 \end{equation}
-Replacing $\mu_s^{l}$ and $\mu_s^{ig,0}$ by the corresponding expressions derived in Ref.~\cite{Shirts_2003} yields
+where $\mu_s^l$ is the chemical potential of the solute in the liquid solution and $x_s$ is the molar fraction.
+Replacing $\mu_s^{l}$ and $\mu_s^{ig,0}$ by the corresponding expressions derived in Ref.
+\cite{Shirts_2003} yields
 \begin{equation}
@@
 \end{equation}
-where $B_s$ corresponds to the second virial coefficient. Here we employ the correlation for \ce{CO_2} introduced by Holste~\textit{et al}~\cite{Holste_1987}, which is
+where $B_s$ corresponds to the second virial coefficient. Here we employ the correlation for \ce{CO_2} introduced by Holste \textit{et al} \cite{Holste_1987}, which is
 \begin{equation}
@@
 
-The versatility of ILs for different applications is in part due to the fact that their physical properties strongly depend on the cation-anion combination.
+The versatility of ILs for different applications is in part due to the fact that their physical properties strongly vary with the particular cation-anion combination.
 On the other hand, this characteristic also explains why the desirable transferability of force fields is particularly difficult to attain.
-Indeed, it is a common practice to extract the potential parameters corresponding to intramolecular (bond stretching, angle bending, torsion rotation) and Lennard-Jones interactions from a well established force field and then derive the partial atomic charges.
+Indeed, it is a common practice to extract the potential parameters corresponding to intramolecular (bond stretching, angle bending, torsion rotation) and Lennard-Jones (LJ) interactions from a well established force field and then derive the partial atomic charges.
 This procedure is, however, inaccurate as in conventional force fields the determination of the atomic charges precedes the dihedrals parametrization.
 Another ad-hoc strategy, which intends to crudely incorporate polarization effects, is to scale the partial charges uniformly with a factor which normally takes values in the range 0.8-0.9.
-This practice has proven to be effective in improving the predictions of dynamic properties~\cite{Schr_der_2012}.
+This practice has proven to be effective in improving the predictions of dynamic properties \cite{Schr_der_2012}.
 
 In this paper, we consider four models of \ce{[emim][B(CN)_4]}.
-Koller~\textit{et al.}~\cite{Koller_2012} were the first to introduce a specific non-polarizable force field of \ce{[emim][B(CN)_4]}.
-They tested three variations of a \textit{united-atoms} model, in which the alkyl groups $\text{CH}_3$ and $\text{CH}_2$ of \ce{[emim]^+} are replaced by pseudo-atoms.
+Koller \textit{et al.} \cite{Koller_2012} were the first to introduce a specific non-polarizable force field of \ce{[emim][B(CN)_4]}.
+They tested three variations of a \textit{united-atoms} model, in which the alkyl groups \ce{CH_3} and \ce{CH_2} of \ce{[emim]^+} are replaced by pseudo-atoms.
 Among them, the ``FF-3'' model best reproduces the experimental values of density, self-diffusion coefficients and viscosity.
-In short, both the intramolecular and Lennard-Jones parameters of the cation were taken from the work of Liu~\textit{et al.}~\cite{Liu_2006}, which in turn is based on the AMBER~\cite{Cornell_1995} framework.
-The intramolecular parameters involving the boron atom were extracted from the DREIDING~\cite{Mayo_1990} force field and the anionic vdW parameters were refined based on the values reported by Price~\textit{et al.}~\cite{Price_2001}.
-The atomic partial charges were derived using the EA-RESP method~\cite{Basma_2001} from \textit{Post-Hartree-Fock ab-initio} calculations at MP2/6–31G$^\ast$+ level of theory, which automatically resulted in total charges on the ions of $\pm$0.8426e.
+In short, both the intramolecular and LJ parameters of the cation were taken from the work of Liu \textit{et al.} \cite{Liu_2006}, which in turn is based on the AMBER \cite{Cornell_1995} framework.
+The intramolecular parameters involving the boron atom were extracted from the DREIDING \cite{Mayo_1990} force field and the anionic vdW parameters were refined based on the values reported by Price \textit{et al.} \cite{Price_2001}.
+The atomic partial charges were derived using the EA-RESP method \cite{Basma_2001} from \textit{Post-Hartree-Fock ab-initio} calculations at MP2/6-31G$^\ast$+ level of theory, which automatically resulted in total charges on the ions of $\pm$0.8426$e$.
 
-The potential parameters of [B(CN)\textsubscript{4}]$^{-}$ derived by Koller~\textit{et al.}~\cite{Koller_2012} were employed by Batista~\textit{et al.}~\cite{Batista_2015} to study aqueous solutions of \ce{[emim][B(CN)_4]}.
+The potential parameters of \ce{[B(CN)_4]^-} derived by Koller \textit{et al.} \cite{Koller_2012} were then employed by Batista \textit{et al.} \cite{Batista_2015} to study aqueous solutions of \ce{[emim][B(CN)_4]}.
 In this case, the authors considered the \textit{all-atom} model of \ce{[emim]^+} developed by Cadena and Maginn \cite{Cadena_2006}.
 The atomic partial charges were obtained using the CHELP procedure \cite{Breneman_1990}, resulting in net charges of $\pm$0.889$e$ on the ions.
-It should be noted that those force fields consider different scaling factors for 1-4 non-bonded interactions: Cadena and Maginn \cite{Cadena_2006} use values of 1.0 y 0.4 for the Lennard-Jones and Coulombic interactions, respectively, while in Koller \textit{et al.} \cite{Koller_2012} the corresponding factors are 0.5 y 5/6, in accordance with AMBER force field.
+It should be noted that those force fields consider different scaling factors for the 1-4 non-bonded interactions: Cadena and Maginn \cite{Cadena_2006} use values of 1.0 y 0.4 for the LJ and Coulombic interactions, respectively; while in Koller \textit{et al.} \cite{Koller_2012} the corresponding factors are 0.5 y 5/6, in accordance with the AMBER force field.
 Batista \textit{et al.} \cite{Batista_2015} employ the same factors as Cadena and Maginn \cite{Cadena_2006} (J.P.
@@
 
-Another set of parameters for \mbox{\ce{[emim][B(CN)_4]}} was derived by Liu \textit{et al.} \cite{Liu_2014} in a study that investigates the dynamics of \ce{CO_2} and N\textsubscript{2} in that IL.
-Parameters corresponding to the intramolecular and Lennard-Jones interactions were extracted from GAFF~\cite{Wang_2004}, while the atomic partial charges were computed using the RESP method~\cite{Bayly_1993} from \textit{DFT}/B3LYP/6-311+G(d) calculations.
+Another set of parameters for \ce{[emim][B(CN)_4]} was derived by Liu \textit{et al.} \cite{Liu_2014} in a study that investigates the dynamics of \ce{CO_2} and \ce{N_2} in that IL.
+Parameters corresponding to the intramolecular and LJ interactions were extracted from GAFF \cite{Wang_2004}, while the atomic partial charges were computed using the RESP method \cite{Bayly_1993} from \textit{DFT}/B3LYP/6-311+G(d) calculations.
 The net charges of the ions were manually adjusted to a value of $\pm$0.8$e$.
@@
 
-Finally, for [emim][Tf\textsubscript{2}N] we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which result from refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
-This refining was characterized by their authors as unusual, given that the LJ parameters were modified, while keeping the partial charges at their original values.
-This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry's constant for \ce{CO_2} at several temperatures.
+Finally, for [emim][Tf\textsubscript{2}N] we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which was derived by refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
+This refining was characterized by their authors as ``unusual'', given that the LJ parameters were modified, while keeping the partial charges at their original values.
+This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry's constant of \ce{CO_2} at several temperatures.
 
@@
 The solutes considered here are hexane, benzene, \ce{CO_2}, ethanol, cyclohexane and water.
-Hexane and benzene were modeled using the OPLS-AA force field~\cite{Jorgensen_1996}, while the TRAPPE potential~\cite{Chen_2001,Potoff_2001} was employed for ethanol and \ce{CO_2}.
-Cyclohexane was simulated using a rigid-body model~\cite{munoz2015lennard} whose sites only interact via the Lennard-Jones potential and for water we employ the TIP4P/2005 model~\cite{Abascal_2005}, \cite{Vega_2011}.
+Hexane and benzene were modeled using the OPLS-AA force field \cite{Jorgensen_1996}, while the TRAPPE potential \cite{Chen_2001,Potoff_2001} was employed for ethanol and \ce{CO_2}.
+Cyclohexane was simulated using a rigid-body model \cite{munoz2015lennard} whose sites only interact via the LJ potential and for water we employ the TIP4P/2005 model \cite{Abascal_2005,Vega_2011}.
 
@@
 
-With the aim of setting up a (more) computationally efficient protocol for the ILs, in this work we assess the possibility of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method~\cite{Fennell2006} for computing the electrostatic interactions.
-As an alternative to the Ewald schemes~\cite{Ewald_1921,Darden_1993,Hockney_1988}, McCann~\textit{et al.}~\cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force fields.
-They concluded that using $\alpha$ = 0.2 {\AA}$^{-1}$ and a cutoff distance ($r_c$) of 15 {\AA} provides the best energetic agreement with Ewald.
+With the aim of setting up a (more) computationally efficient protocol for the ILs, in this work we assess the possibility of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method \cite{Fennell2006} for computing the electrostatic interactions.
+As an alternative to the Ewald schemes \cite{Ewald_1921,Darden_1993,Hockney_1988}, McCann \textit{et al.} \cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force fields.
+They concluded that using $\alpha$ = 0.2 {\AA}$^{-1}$ together with a cutoff distance ($r_c$) of 15 {\AA} provide the best energetic agreement with the Ewald method.
 In this work, the comparisons are made in terms of the simulated densities and radial distribution functions for which, as will be shown in the next section, $\alpha$ = 0.2 {\AA}$^{-1}$ and $r_c$ = 12 {\AA} resulted in good agreement for the ILs studied here.
-Those values were also employed for the charged solutes, with the exception of hexane, for which we considered undamped Coulombic interactions.
+These values were also employed for the charged solutes, with the exception of hexane, for which we considered undamped Coulombic interactions.
+The reason for this exception is that we were able to improve the agreement with the experimental solvation free energy of that pure substance.
 
-rigid treatment of the imidazolium ring~\cite{Kobrak_2004,Lynden_Bell_2006}
-\cite{Rey_Castro_2007}
-
-When it was possible to treat the ions as rigid bodies, the NPT algorithm of Kamberaj~\textit{et al.}~\cite{Kamberaj_2005} was employed to carry out the MD simulations.
-Otherwise, the scheme due to Shinoda~\textit{et al}.~\cite{Shinoda2004} was used along with the application of SHAKE~\cite{Ryckaert1977} to constrain the C-H bonds lengths.
+When it was possible to treat the ions as rigid bodies, the NPT algorithm of Kamberaj \textit{et al.} \cite{Kamberaj_2005} was employed to carry out the MD simulations.
+Otherwise, the scheme due to Shinoda \textit{et al}.
+\cite{Shinoda2004} was used along with the application of SHAKE \cite{Ryckaert1977} to constrain the C-H bonds lengths.
 For both integrators, we employed $\Delta t$ = 1 fs.
@@
 The gradual insertion/deletion of charged solutes involves scaling both the van der Waals (vdW) and the electrostatic intermolecular interactions.
-In order to avoid numerical instabilities associated to the vdW scaling, a standard approach is to employ a soft-core potential with a nonlinear coupling, and in this paper we use the modified Lennard-Jones potential due to Beutler~\textit{et al.}~\cite{Beutler_1994}.
-The electrostatic interactions, on the other hand, can be handled simply by a linear scaling~\cite{Naden_2015} of the potential, which in this work corresponds to the DSF method~\cite{Fennell2006}.
+In order to avoid numerical instabilities associated to the vdW scaling, a standard approach is to employ a soft-core potential with a nonlinear coupling.
+In this paper we use the modified LJ potential due to Beutler \textit{et al.} \cite{Beutler_1994}.
+The electrostatic interactions, on the other hand, can be handled simply by a linear scaling of the potential \cite{Naden_2015}.
 
@@
 
-In this work, we performed independent simulation at each state of $\lambda_{\text{Coul}}$, while the expanded ensemble (EE) method~\cite{Lyubartsev_1992} was applied for sampling the states associated to the $\lambda_{\,\text{vdW}}$ set.
+In this work, we carried out independent simulation at each state of $\lambda_{\text{Coul}}$, while the expanded ensemble (EE) method~\cite{Lyubartsev_1992} was applied for sampling the states associated to the $\lambda_{\,\text{vdW}}$ set.
 In short, an EE is constructed as a weighted sum of subensembles, each assuming a different value of the variable chosen to explore the free energy landscape, which in our case is $\lambda_{\,\text{vdW}}$.
 This way, the sampling of the EE involves both sampling each subensamble with fixed variables (N,P,T,$\lambda_{\,\text{vdW}}$) and transitions in $\lambda_{\,\text{vdW}}$.
-Thus, the remarkable feature of the EE method is the possibility of exploring the whole alchemical route in a single simulation.
-In this work, we perform a sequential sampling of the EE \cite{Chodera_2011_2}, which consists in sampling each subensamble via NPT MD for a determined number of steps $N^{\text{EE}}$ followed with an attemp to change $\lambda_{\,\text{vdW}}$ using MC, and so on.
-Independent sampling of $\lambda$~\cite{Chodera_2011_2}.
+Thus, a remarkable feature of the EE method is the possibility of exploring the whole alchemical route in a single simulation.
+In this work, we perform a sequential sampling of the EE \cite{Chodera_2011_2}, which consists in sampling each subensamble via NPT MD for a determined number of steps $N^{\text{EE}}$ followed by an attemp to change $\lambda_{\,\text{vdW}}$ using MC, and so on.
+That change in $\lambda_{\,\text{vdW}}$ is randomly proposed according to an independent sampling scheme \cite{Chodera_2011_2}.
 In addition, the set of (arbitrary) weights $\eta$ of the subensambles enters in the acceptance criteria of MC, so it is possible to tune $\eta$ in order to enhance the sampling.
-If differences $\eta_i$ - $\eta_j$ were closed to $\Delta G_{ji}$, we expect an uniform sampling in $\lambda_{\,\text{vdW}}$~\cite{Lyubartsev_1992}.
+If differences $\eta_i$ - $\eta_j$ were closed to $\Delta G_{ji}$, we expect an uniform sampling in $\lambda_{\,\text{vdW}}$ \cite{Lyubartsev_1992}.
 Of course, this can be achieved only iteratively.
-The EE procedure, together with the \textit{soft-core} potential and the DSF method with linear coupling were all implemented in the LAMMPS software package~\cite{Plimpton1995}, which we employed for carrying out all the MD simulations.
+The EE procedure, together with the \textit{soft-core} potential and the DSF method with linear coupling were all implemented in the LAMMPS software package \cite{Plimpton1995}, which we employed for carrying out all the MD simulations.
 
-As demonstrated in Ref.~\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ generate more decorrelated samples in each subensemble.
+As demonstrated in Ref.
+\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ generate more decorrelated samples in each subensemble.
 In this work, we employ $N^{EE}$ = 5 which, together with the specified $\lambda_{\, \text{vdW}}$ set, resulted to be satisfactory as up to 3 preliminary runs of the EE were enough to determine the weights $\eta$ that yielded, in a final simulation, a ``sufficient'' sampling of each subensamble.
 By ``sufficient'', we mean that the sampling provides an acceptable error in $\Delta G$.
-The simulation times for the preliminary and final EE runs were 10 and 40 ns, respectively, and each $\lambda_{\text{Coul}}$ state was simulated for 10 ns.
-Finally, the MBAR method~\cite{Shirts_2008}, as implemented by Klimovich~\textit{et al.}~\cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$ .
+The simulation times for the preliminary and final EE runs were 10 and 40 ns, respectively; and each $\lambda_{\text{Coul}}$ state was simulated for 10 ns.
+Finally, the MBAR method \cite{Shirts_2008}, as implemented by Klimovich \textit{et al.} \cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$ .
 
 We end this section with a brief description of the procedure for generating the initial configurations.
-Only Ref.~\citenum{Liu_2014} provides the atomic coordinates of the cation-anion pair corresponding to a minimum energy configuration obtained in an \textit{ab-initio} simulation.
-For the other models, we employed the tool \textit{build} of PLAYMOL~\cite{playmol}, a software integrated with PACKMOL~\cite{Mart_nez_2009}, which enables to specify the following geometric data: bond and angle lengths and dihedral angles, from which PLAYMOL~\cite{playmol} automatically determines the Cartesian coordinates.
+Only Ref.
+\citenum{Liu_2014} provides the atomic coordinates of the cation-anion pair corresponding to a minimum energy configuration obtained in an \textit{ab-initio} simulation.
+For the other models, we employed the tool \textit{build} of PLAYMOL \cite{playmol}, a software integrated with PACKMOL \cite{Mart_nez_2009}, which enables to specify the following geometric data: bond and angle lengths and dihedral angles, from which PLAYMOL~\cite{playmol} automatically determines the Cartesian coordinates.
 We first carried out NVT MD simulations of the isolated ion pairs in order to obtain a minimum energy conformation for the corresponding (classical) model of each pair.
-These simulations were performed using the the Nos\'{e}-Hoover thermostat~\cite{Martyna1992} and a cubic box of length L = 50 {\AA} with non-periodic boundary conditions.
+These simulations were performed using the the Nos\'{e}-Hoover thermostat \cite{Martyna1992} and a cubic box of length L = 50 {\AA} with non-periodic boundary conditions.
 To relax the initial configurations, a short run with a small time step of 0.1 fs was performed, which was followed by an equilibration using $\Delta t$ = 0.5 fs.
 Finally, we carried out a ``quenching'' simulation with $\Delta t$ = 1 fs, in which the temperature is gradually reduced until reaching a value close to 0 K.
-The resulting coordinates were then specified in PLAYMOL~\cite{playmol} to build the initial configurations for simulating the liquid phases.
+The resulting coordinates were then specified in PLAYMOL \cite{playmol} to build the initial configurations for simulating the liquid phases.
 
@@
 
-In this section, we present results for the following two cases: (1) flexible ions and the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for the evaluation of the Ewald sums~\cite{Ewald_1921}, and (2) ions modeled as rigid bodies with the DSF method~\cite{Fennell2006} ($\alpha$ = 0.2 {\AA}$^{-1}$) for calculating the Coulombic interactions.
+In this section, we present results for the following two cases: (1) flexible ions and the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for the evaluation of the Ewald sums \cite{Ewald_1921}, and (2) ions modeled as rigid bodies with the DSF method \cite{Fennell2006} ($\alpha$ = 0.2 {\AA}$^{-1}$) for calculating the Coulombic interactions.
 For both strategies we employed $r_c$ = 12 {\AA}.
@@
 For that, we carried out an analysis of key dihedrals, particularly those whose flexibility could lead to significant conformational changes in \ce{[emim]^+} and \ce{[Tf_2N]^-}.
-On the other hand, small and highly symmetric anions, such as \ce{PF_6} and \ce{BF_4} are usually modeled as rigid bodies~\cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies that strategy in the case of [B(CN)\ce{4}]$^{-}$.
+On the other hand, small and highly symmetric anions, such as \ce{PF_6} and \ce{BF_4} are usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies that strategy in the case of \ce{[B(CN)_4]^-}.
 The atomic nomenclature adopted in this paper is shown in Fig~\ref{fig:atoms_id}.
@@
 \includegraphics[width=\linewidth]{ions_paper.pdf}
-\caption{\ce{[emim]^+} [B(CN)\textsubscript{4}]$^{-}$ \ce{[NTf_2]^-}.}
+\caption{\ce{[emim]^+} \ce{[B(CN)_4]^-} \ce{[NTf_2]^-}.}
 \label{fig:atoms_id}
@@
 
-Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtained the combined distribution function (CDF) of the dihedral angles corresponding to the torsions in C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs.
+Using the software TRAVIS \cite{Brehm_2011}, for each model we obtained the combined distribution function (CDF) of the dihedral angles corresponding to the torsions in C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs.
 The CDF, as an alternative to individual histograms, provides a way to  simultaneously analyze the rigidity of the ring.
@@
 In the case of Liu \textit{et al.} \cite{Liu_2014}, those angles correspond to the values of  90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed the angles of 102.6$^{\circ}$ and -102.6$^{\circ}$.
-In these cases, two types of rigid bodies were built in equal proportion.
+For those cases, two types of rigid bodies were built in equal proportion.
 Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} presents a non negligible probability of sampling the angle value of 0$^{\circ}$, which notably differs from what was observed for the other models.
-In this case we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of the rigid bodies, respectively; and for the remaining 15~\% we specified the angle of 0$^{\circ}$.
+In this case, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of the rigid bodies, respectively; and for the remaining 15~\% we specified the angle of 0$^{\circ}$.
 
@@
 \end{document}
+%rigid treatment of the imidazolium ring \cite{Kobrak_2004,Lynden_Bell_2006}\cite{Rey_Castro_2007}
+
 %\begin{equation}

### 2018-05-07 ionic_liquids.tex
revision I

@@
 The other models showed a larger flexibility with high probability regions that extend in a broad range of angle values.
-Despite this, it was possible to build more than one type of rigid body by specifying the most probables angles for C6-C5-N2-C1.
+Despite this, it was possible to build more than one type of rigid body by specifying the most probables angles of C6-C5-N2-C1.
 In the case of Liu \textit{et al.} \cite{Liu_2014}, those angles correspond to the values of  90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed the angles of 102.6$^{\circ}$ and -102.6$^{\circ}$.
 For those cases, two types of rigid bodies were built in equal proportion.
-Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} presents a non negligible probability of sampling the angle value of 0$^{\circ}$, which notably differs from what was observed for the other models.
+Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} presents a non-negligible probability of sampling the angle value of 0$^{\circ}$, which notably differs from what was observed for the other models.
 In this case, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of the rigid bodies, respectively; and for the remaining 15~\% we specified the angle of 0$^{\circ}$.
@@
 The model of Weber and Kirchner \cite{Weber_2016},
-on the other hand, presented important discrepancies in the RDFs for the pairs C5(cation)-N(anion) and C2(cation)-B(anion) when using rigid bodies.
-That is why in this case we have considered as being rigid only the imidazolium ring while letting  the ethyl chain flexible.
+on the other hand, presented important discrepancies in the RDFs of the pairs C5(cation)-N(anion) and C2(cation)-B(anion) when using rigid bodies.
+That is why, in this case only the imidazolium ring was considered rigid while the ethyl chain was left unconstrained.
 
@@
 A study of dihedrals was also carried out for \ce{[emim][NTf_2]}.
-The CDF of dihedrals C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the behaviour of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 corresponds to 0$^{\circ}$.
+The CDF of dihedrals angles corresponding to torsions in C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the behaviour of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 corresponds to 0$^{\circ}$.
 This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
-With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.}~\cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation (Fig.~\ref{fig:kdderman_a}).
-Fig.~\ref{fig:cddf_anion}, which corresponds to the CDF for the contiguous dihedrals C1-S1-N1-S2 and S1-N1-S2-C2, verifies qualitatively what was observed by Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
+With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.} \cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
+Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2, verifies qualitatively what was observed by Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
 Given that the flexibility of \ce{[NTf_2]^-} gives rise to highly different conformation, a more rigorous strategy for building rigid bodies would be required.
@@
 \caption{Combined distribution function (CDF) of anion}
-\label{fig:dihedrals_anion}
+\label{fig:die_ntf2}
 \end{figure}
@@
 \begin{table*}
+\begin{threeparttable}
 \caption{Densities of \ce{[emim][B(CN)_4]} predicted from MD NPT simulations at 298.15 K and 1 atm. The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
-\begin{threeparttable}
 \begin{tabular}{ c  c  c  c  c}  
@@
 
-Koller y col.~\cite{Koller_2012}  & 298.14 $\pm$  0.02 & 0 $\pm$ 2 & 1.046 & 1.0 \\
-Batista y col.~\cite{Batista_2015} & 298.15 $\pm$ 0.01  & 1 $\pm$ 1 & 0.989 & 4.6  \\
-Liu y col.~\cite{Liu_2014}  & 298.14 $\pm$ 0.01 & 0 $\pm$ 1 & 1.001 & 3.4  \\
-Weber y Kirchner.~\cite{Weber_2016}  & 298.16  $\pm$ 0.01 & 1 $\pm$ 1 & 1.015 & 2.1  \\
+Koller y col. \cite{Koller_2012}  & 298.14 $\pm$  0.02 & 0 $\pm$ 2 & 1.046 & 1.0 \\
+Batista y col. \cite{Batista_2015} & 298.15 $\pm$ 0.01  & 1 $\pm$ 1 & 0.989 & 4.6  \\
+Liu y col. \cite{Liu_2014}  & 298.14 $\pm$ 0.01 & 0 $\pm$ 1 & 1.001 & 3.4  \\
+Weber y Kirchner. \cite{Weber_2016}  & 298.16  $\pm$ 0.01 & 1 $\pm$ 1 & 1.015 & 2.1  \\
 	 \multicolumn{5}{c}{Rigid ions/DSF method}\\
-Koller y col.~\cite{Koller_2012}   & 298.42  $\pm$ 0.03  & 1 $\pm$ 1 & 1.038 & 0.2 \\
-Batista y col.~\cite{Batista_2015} & 298.43 $\pm$ 0.02  & 0.9 $\pm$ 0.7  & 0.988 & 4.7  \\
-Liu y col.~\cite{Liu_2014}  & 298.46 $\pm$ 0.02 & 1.2  $\pm$ 0.8 & 0.991 &  4.4 \\
-Weber y Kirchner.~\cite{Weber_2016} &  298.41 $\pm$ 0.03 & 1.1 $\pm$ 0.8 & 1.022 & 1.4  \\
+Koller y col. \cite{Koller_2012}   & 298.42  $\pm$ 0.03  & 1 $\pm$ 1 & 1.038 & 0.2 \\
+Batista y col. \cite{Batista_2015} & 298.43 $\pm$ 0.02  & 0.9 $\pm$ 0.7  & 0.988 & 4.7  \\
+Liu y col. \cite{Liu_2014}  & 298.46 $\pm$ 0.02 & 1.2  $\pm$ 0.8 & 0.991 &  4.4 \\
+Weber y Kirchner \cite{Weber_2016} &  298.41 $\pm$ 0.03 & 1.1 $\pm$ 0.8 & 1.022 & 1.4  \\
  \hline \hline
@@
 
-For each model of \ce{[emim][B(CN)_4]} described in Sec~\ref{sec:force_field_il}, in Table \ref{table:henry} we present the results corresponding to the solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\ref{eq:henry_eq}, which we compare with the experimental value reported by Mahurin \textit{et al.} \cite{Mahurin_2010}.
+For each model of \ce{[emim][B(CN)_4]} described in Sec~\ref{sec:force_field_il}, in Table \ref{table:henry} we present the results of solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\ref{eq:henry_eq}, which we compare with the experimental value reported by Mahurin \textit{et al.} \cite{Mahurin_2010}.
 Table \ref{table:henry} also includes the results for [emim][Tf\textsubscript{2}N] and the experimental $K_s$ obtained by Finotello \textit{et al.} \cite{Finotello_2008}.
-The uncertainties were calculated using standard error propagation.
+The uncertainties in $K_s$ were calculated using standard error propagation.
 
@@
 \caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at T = 298.15 K and P = 1 atm.
-The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}, respectively.}
+The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
 \begin{tabular}{ c c c  c  c  c  c }  
@@
 
-First, it should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.}~\cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent simulations in $\lambda_{\text{LJ}}$ and $\lambda_{\, \text{Coul}}$.
-Moreover, the value of $\Delta G_{\text{sim}}$ corresponding to [emim][Tf\textsubscript{2}N] is very close to -0.534 kcal/mol, which was obtained by Kerl \textit{et al.} \cite{Kerl__2017} using the FEP method \cite{Zwanzig_1954} with no uncertainty reported.
+First, it should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent simulations in $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
+Moreover, the $\Delta G_{\text{sim}}$ of [emim][Tf\textsubscript{2}N] is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
 These consistencies serve for validating the methodological approaches we employed in each case.
@@
 From Table \ref{table:henry} one can see that the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental value of $K_s$.
-If we look at the $\Delta G_{\, \text{LJ}}$ profiles in Fig.~\ref{fig:deltag} we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014}, the maximum of free energy occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which explains the ``facility'' to insert the solute molecule as well as their failure to reproduce the experimental densities.
+If we look at the $\Delta G_{\lambda_{\,\text{vdW}}}$ profiles in Fig.~\ref{fig:deltag} we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014}, the maximum of the profiles occurs at lower values of free energies, suggesting that those models underestimate the interatomic interactions, which explains the ``facility'' to insert a \ce{CO_2} molecule as well as their failure to reproduce the experimental densities.
 
@@
 \includegraphics[width=\linewidth]{free_energy_paper}
+\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles of \ce{[emim][B(CN)_4]}.}
 \label{fig:deltag}
@@
 The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in [emim][Tf\textsubscript{2}N].
-In order to have a graphical insight of solvation, we have also obtained the spatial distribution functions (SDFs) \cite{Svishchev_1993} using the software packages TRAVIS~\cite{Brehm_2011} and VMD~\cite{HUMP96}.
+
+We have also obtained the spatial distribution functions (SDFs) \cite{Svishchev_1993} using the software packages TRAVIS~\cite{Brehm_2011} and VMD~\cite{HUMP96}.
 For that, we carried out MD NPT simulations of the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] with a solute molar fraction of 0.1.
@@
 From Fig.~\ref{fig:ludwig_sdf}(b), which correspond to the ions \ce{[emim]^+} and \ce{[NTf_2]^-}, it can be seen that the region with a low probability of finding an ion is larger than for \ce{[emim][B(CN)_4]}.
-In Fig.~\ref{fig:anions} we have plotted together the SDFs corresponding to the anions and we note that the first solvation shell for [B(CN)\textsubscript{4}]$^{-}$ occur at a sligthly shorter distance than for \ce{[NTf_2]^-}, in accordance with the more favorable solvation suggested by the free energy results.
+In Fig.~\ref{fig:anions} we have plotted together the SDFs corresponding to the anions and we note that the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a sligthly shorter distance than for \ce{[NTf_2]^-}, in accordance with the more favorable solvation suggested by the free energy results.
 
@@
 It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ of cyclohexane.
-Note that only in the case of ethanol we have reproduced $\Delta G^{0}_\text{exp}$ while the relative error for the other solutes is around 10\%.
+Note that only in the case of ethanol we have reproduced $\Delta G^{0}_\text{exp}$, while the relative error for the other solutes is around 10\%.
 
 The results of $\gamma^{\, \infty}$ for the solutes in \ce{[emim][B(CN)_4]} are shown in Table~\ref{table:gamma}.
-For benzene and water, the predictions are very accurate, but thay are a result of error compensations given the divergences verified in Table~\ref{table:mu_solutos}.
+For benzene and water, the predictions are very accurate, but they are a result of error compensations given the divergences verified in Table~\ref{table:mu_solutos}.
 This makes necessary to review the force fields of the solutes.

### 2018-07-23 ionic_liquids.tex
intro small corrections

@@
 \begin{abstract}
-In this paper we calculate solvation free enegies in ionic liquids and predict macroscopic properties required in the design of chemical processes.
+In this paper, we calculate solvation free enegies in ionic liquids and predict macroscopic properties required in the design of chemical processes.
 Carbon dioxide produced in combustion processes is one of the main sources of anthropogenic generation of greenhouse gases.
@@
 \section{Introduction}
+\ce{CO_2} emissions from fossil-fuel power generation plants account for a large portion of the anthropogenic greenhouse gases \cite{totalenergy}.
+International efforts aimed at regulating and reducing \ce{CO_2} emissions are increasing \cite{Tong_2018} and, in this context, the development of technologies for the capture and storage of \ce{CO_2} plays an essential role \cite{Markewitz_2014}.
 
-The \ce{CO_2} emissions from power generation plants are still an important source of anthropogenic greenhouse gases \cite{totalenergy}.
-International efforts aimed at regulating and reducing \ce{CO_2} emissions are increasing \cite{Tong_2018} and, in this context, the development of technologies for the capture and storage of \ce{CO_2} is essential.
-\cite{Markewitz_2014}.
-
-The conventional process for \ce{CO_2} removal involves a chemical absorption followed by stripping at high temperatures.
-The solvents commonly employed are volatile organic compounds, specially aqueous solutions of monoethanolamine (MEA).
-Despite its high absorption capability, the use of MEA suffers from a serious drawback, namely a considerable cost due to the energy consumption of solvent recovery \cite{Merkel_2010}.
-Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes to increase the ambient pollution and generates extra costs to replace the solvent.
+The conventional process for \ce{CO_2} removal comprises a chemical absorption followed by stripping at high temperatures.
+The most commonly used solvents are volatile organic compounds, specially aqueous solutions of monoethanolamine (MEA).
+Despite its high absorption capability, the use of MEA suffers from a serious drawback due to the high cost of solvent recovery \cite{Merkel_2010}.
+Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes to increase the environment pollution and generates extra costs for replacing the solvent.
 
 The use of ionic liquids (ILs) as solvents for \ce{CO_2} sequestration occupies a central place in the investigation of alternative technologies.
-The reasons are their well known properties, such as the negligible vapor pressure and high thermal stability.
-Furthermore, they are particularly attractive because they can be designed for specific applications, giving rise to the so-called task-specific ILs \cite{Seo_2014}.
-These remarkable properties makes ILs suitable for a wide variety of applications in separation processes \cite{Han_2010,Werner_2010}, catalysis \cite{P_rvulescu_2007}, energy \cite{MacFarlane_2014} and material science \cite{Mecerreyes_2011,Tom_2015,Dupont_2010,Leones_2017,Kinik_2017}.
+The reasons are their well known properties, such as their almost negligible vapor pressure and high thermal stability.
+Furthermore, they are particularly attractive since they can be designed for specific applications, giving rise to the so-called task-specific ILs \cite{Seo_2014}.
+These remarkable properties makes ILs suitable for a wide variety of applications in separation processes \cite{Han_2010,Werner_2010}, catalysis \cite{P_rvulescu_2007}, energy \cite{MacFarlane_2014}, and material science \cite{Mecerreyes_2011,Tom_2015,Dupont_2010,Leones_2017,Kinik_2017}.
 
-Recently, the potentiality of ILs for the \ce{CO_2} capture has been called into question by Carvalho \textit{et al.} \cite{Carvalho_2016}, who warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposed absorption capability of certain ILs.
-While most thermodynamic models were developed based on molar fraction, the key factor to determine the absorption process efficiency is given by the amount of \ce{CO_2} that can be dissolved in a certain volume or mass of solvent.
-By expressing the solubility in terms of molality and performing an exhaustive comparison between various ILs, Ref.
-\cite{Carvalho_2016} shows that most systems which promote a physical absorption of \ce{CO_2} exhibit a \ce{CO_2} solubility similar or even lower than that observed for the heavy alkane eicosane.
-This is true for the ``popular'' \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}, the only exception being the family of ILs containing the anion tetracyanoborate \ce{[B(CN)_4]^-]}.
+Recently, the potentiality of ILs for \ce{CO_2} capture has been called into question by Carvalho \textit{et al.} \cite{Carvalho_2016}, who warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposed absorption capability of certain ILs.
+Although most thermodynamic models are formulated in terms of molar fractions, a key factor that dictates the absorption process efficiency is given by the amount of \ce{CO_2} that can be dissolved in a certain \textit{volume} or \textit{mass} of solvent.
+By expressing the solubility values in terms of molality and performing an exhaustive comparison between various ILs, Ref.
+\cite{Carvalho_2016} shows that most systems which promote a physical absorption of \ce{CO_2} exhibit a solubility similar or even lower than that observed for the heavy alkane eicosane.
+This is true for the ``popular'' \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}; the only exception being the family of ILs containing the anion tetracyanoborate \ce{[B(CN)_4]^-}.
 
-There is no obvious explanation accounting for the enhanced solubility promoted by the presence of the anion \ce{[B(CN)_4]^-]}, whether special interactions with \ce{CO_2} are settled.
+There is no obvious explanation accounting for the enhanced solubility promoted by the presence of the anion \ce{[B(CN)_4]^-}.
 In this sense, Molecular Simulation provides with a powerful tool for studying solvation processes.
-To the best of our knowledge, only one study in the literature reports the free energy of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} \cite{Liu_2014_1} which, in addition, is overestimated.
-This motivated us to carry out a comparison of different force fields of \ce{[emim][B(CN)_4]} in terms of the free energy of solvation and, indeed,  it was possible to select a model that successfully predicts the value of the Henry constant of \ce{CO_2}.
-For comparison, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both in the condition of infinite dilution and at high concentrations.
-The simulations confirmed what was observed experimentally, that is, a considerably lower pressure is required in \ce{[emim][B(CN)_4]} to obtain the same molality of \ce{CO_2}.
-The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} were also calculated, and a comparison was made with experimental values recently reported in the literature.
+To the best of our knowledge, only one study in literature reports the free energy of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} \cite{Liu_2014_1} which, in addition, is overestimated.
+This motivated us to evaluate different force fields of \ce{[emim][B(CN)_4]} and, as we will show below, it was possible to select a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2}.
+For comparison, \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both in the condition of infinite dilution and at high concentrations.
+The simulations confirmed what is observed in experiments: for \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}.
+The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} were also calculated, and a comparison was made with experimental values recently reported in literature.
 
-This paper is organized as follows: in Sec.
-\ref{sec:theory} we present the mathematical relationships between the simulated solvation free energy and thermodynamic properties.
-This is followed by a brief description of the force fields considered for the ILs and the solutes.
-The methodological details are provided in Sec.
-\ref{sec:sim_details} and the numerical results are given in Sec.
-\ref{sec:results}.
-Finally, we present some concluding remarks in Sec.
-\ref{sec:conclusion}.
+This paper is organized as follows: in Sec.~\ref{sec:theory} we present the theoretical background, which is followed by a brief description of the force fields used in this work.
+The methodological details are provided in Sec.~\ref{sec:sim_details} and the corresponding numerical results are given in Sec.~\ref{sec:results}.
+Finally, we present some concluding remarks in Sec.~\ref{sec:conclusion}.
 
@@
 
-In this section, we present the formalism that allows a direct comparison between simulation results and the thermodynamic properties of dilute solutions: Henry constant and activity coefficient at infinite dilution.
+In this section, we present the formalism that allows us to compute the Henry constant and activity coefficient, both at infinite dilution, from the simulated free energy.
 For this, we rely on the work of Shirts \textit{et al.} \cite{Shirts_2003}.
-Then, we reformulate the equations in order to carry out a study at concentrated conditions, which would be the more likely scenario in \ce{CO_2} capture processes.
+Then, we reformulate the equations in order to study concentrated solutions, which would be the more likely scenario in \ce{CO_2} capture processes.
 

### 2018-07-24 ionic_liquids.tex
small changes in theory

@@
 There is no obvious explanation accounting for the enhanced solubility promoted by the presence of the anion \ce{[B(CN)_4]^-}.
-In this sense, Molecular Simulation provides with a powerful tool for studying solvation processes.
+In this sense, molecular simulation provides with a powerful tool for studying solvation processes.
 To the best of our knowledge, only one study in literature reports the free energy of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} \cite{Liu_2014_1} which, in addition, is overestimated.
@@
 \subsection*{Solvation free energy}
-The solvation free energy, $\Delta G_{\text{solv}}$, is the reversible work needed to transfer a solute molecule from the gas phase to the solution.
+The solvation free energy, $\Delta G_{\text{solv}}$, is defined as the reversible work needed to transfer a solute molecule from the gas phase to the solution.
 For dense systems, an efficient computation of solvation properties via molecular simulation is possible by means of the so-called alchemical methods, which employ non-physical pathways to connect the ``endpoint'' states, whose free energy difference is to be estimated.
-In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through a coupling parameter $\lambda$, which scales the intermolecular interactions taking values in the interval [0,1]: $\lambda$ = 1 corresponds to a fully interacting system, while for $\lambda$ = 0 the interactions between the solute and solvent molecules are completely turned-off.
+In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through the use of a coupling parameter $\lambda$, which scales the intermolecular interactions taking values in the interval [0,1]: $\lambda$ = 1 corresponds to a fully interacting system, while for $\lambda$ = 0 the interactions between the solute and solvent molecules are completely turned-off.
 
 In the following, the subscripts ``$s$'' and ``$\text{IL}$'' refer to the solute and the solvent (ionic liquid), respectively.
-For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is defined as
+For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
 \begin{equation}
-\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{LI},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{LI},P,T,\lambda = 0)}, 
+\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 0)}, 
 \end{equation}
-where $\bigtriangleup$ denotes the isobaric-isothermal partition function.
-Shirts \textit{et al}.
-\cite{Shirts_2003} presented a detailed mathematical derivation allowing to relate $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy and obtained the following expression:
+where superscript ``$l$'' refers to the liquid solution, $\bigtriangleup$ denotes the isobaric-isothermal partition function, and $k_b$ is the Boltzmann's constant.
+Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy.
+They found out that
 \begin{equation}
@@
 \end{equation}
-where $k_b$ is the Boltzmann's constant, $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid phase and $P_s$ is the partial pressure of the solute in the gas phase.
+where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid phase and $P_s$ is the partial pressure of the solute in the gas phase.
 It should be noted that in the derivation of Eq.~\ref{eq:free_solv}, the gas phase was treated as an ideal gas.
@@
 For small solutes, such as those considered in this work, the magnitude of the term $V^{\ast}/V_1$ is typically on the order of the free energy uncertainties \cite{Shirts_2003}.
-Hence, that term could be neglected and will be omitted hereafter.
+Hence, that term can be neglected and will be omitted hereafter.
 
 \subsection*{Henry constant}
-If both $P_s$ and $c_s^{\ast}$ were not large, we can employ Eq.~\ref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is given by \cite{Prausnitz}
+If both $P_s$ and $c_s^{\ast}$ were not large, we can resort to Eq.~\ref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
 \begin{equation}
@@
 \end{equation}
-Therefore, by simply expressing Eq.~\ref{eq:free_solv} in terms of the molar fraction $x_s$ and considering MW (molecular weight of the solution) = $\text{MW}_{\scaleto{LI}{4pt}}$ as well as $\rho$ (mass density of the solution) = $\rho_{\scaleto{LI}{4pt}}$, we obtain that
+Therefore, by simply expressing Eq.~\ref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that MW (molecular weight of the solution) = $\text{MW}_{\scaleto{IL}{4pt}}$, as well as $\rho$ (mass density of the solution) = $\rho_{\scaleto{IL}{4pt}}$, we obtain that
 \begin{equation}
 \label{eq:henry_eq}
-K_s = \tilde{\rho}_{\scaleto{LI}{4pt}} R T \exp(\beta \, \Delta G_{\text{sim}}),
+K_s = \tilde{\rho}_{\scaleto{IL}{4pt}} R \, T \exp(\beta \, \Delta G_{\text{sim}}),
 \end{equation}
-where $R$ is the gas constant.
+where $\tilde{\rho}_{\scaleto{IL}{4pt}}$ is the molar density of the solvent and $R$ is the gas constant.
 
@@
 
-As will be shown below, the prediction of activity coefficients requires separate simulations in the pure solute, and in what follows we employ the superscript ``$0$'' to denote the pure solute properties.
+As will be shown below, the prediction of activity coefficients requires extra simulations involving the pure solute.
+In what follows, we use the superscript ``$0$'' to denote the pure solute properties.
 
-Using standard thermodynamic relations \cite{Tester}, we write the activity coefficient $\gamma_s$ in terms of residual chemical potentials, as follows
+Using standard thermodynamic relations \cite{Tester}, we write the activity coefficient $\gamma_s$ in terms of residual chemical potentials, as follows:
 \begin{equation}
@@
 \begin{equation}
-\mu_s^R = \mu_s^l(N_s^l,N_{LI},P,T) - \mu_s^{ig,0}(P,T) - k_b T \ln x_s, 
+\mu_s^R = \mu_s^l(N_s^l,N_{LI},P,T) - \mu_s^{ig,0}(P,T) - k_b T \ln x_s.
 \end{equation}
-where $\mu_s^l$ is the chemical potential of the solute in the liquid solution and $x_s$ is the molar fraction.
-Replacing $\mu_s^{l}$ and $\mu_s^{ig,0}$ by the corresponding expressions derived in Ref.
-\cite{Shirts_2003} yields
+Replacing $\mu_s^{l}$ and $\mu_s^{ig,0}$ by the corresponding expressions derived in Ref.~\cite{Shirts_2003} yields
 \begin{equation}
@@
 
-Considering $N_s^{l}$ = 1, which represents the infinite-dilute condition, and substituting Eqs.~\ref{eq:mu_res} and~\ref{eq:mu_res_0} into Eq.~\ref{eq:gamma}, we  obtain that
+If one makes $N_s^{l}$ = 1, and substitute Eqs.~\ref{eq:mu_res} and~\ref{eq:mu_res_0} into Eq.~\ref{eq:gamma}, the infinite-dilution activity coefficient, $\gamma^{\infty}_s$, can be predicted according to the following equation:
 \begin{equation}
@@
 \end{equation}
-where $c_{\scaleto{LI}{4pt}}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ correspond to the numerical densities of the solvent and the pure solute, respectively.
+where $c_{\scaleto{IL}{4pt}}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ are the numerical densities of the solvent and the pure solute, respectively.
 
@@
 \end{equation}
-where $f^{g}_s$ is the fugacity of the solute in the gas phase. Having calculated $f^{g}_s$, $P_s$ could be predicted using the following equation
+where $f^{g}_s$ is the fugacity of the solute in the gas phase. Having calculated $f^{g}_s$, $P_s$ can be predicted using the following equation
 \begin{equation}
@@
 \end{equation}
-where $B_s$ corresponds to the second virial coefficient. Here we employ the correlation for \ce{CO_2} introduced by Holste \textit{et al} \cite{Holste_1987}, which is
+where $B_s$ corresponds to the second virial coefficient.
+
+Here we employ the correlation of $B_s$ for \ce{CO_2} introduced by Holste \textit{et al.} \cite{Holste_1987}, which is
 \begin{equation}
@@
 where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = $-2.455297$ $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol).
+At equilibrium, $P_s$ = $P$.
+However, 
+equilibrium pressure
+We have found from preliminaries simulations that $\Delta G_{\text{sim}}$
+
  Actually, the prediction of $P_s$ should be iterative and in this work we propose the following scheme: (i) run an NPT simulation, (ii) calculate $\Delta G_{\text{sim}}$ and $f^{g}_s$ via Eq.~\ref{eq:fgas_d}, (iii) employ $f^{g}_s$ in Eq.~\ref{eq:fgas} to compute $P_s$ (iv) if $P_s$ $\neq$ P, repeat the above steps using $P_s$ as the specified pressure in a new NPT simulation.

### 2018-07-25 ionic_liquids.tex
strategies of IL revised

@@
 \documentclass[3p,twocolumn]{elsarticle}
-\usepackage[draft,hidelinks,colorlinks,citecolor=blue]{hyperref}
+\usepackage[colorlinks,citecolor=blue]{hyperref}
 \usepackage{lineno}
@@
 %% Numbered without titles
-\bibliographystyle{model1a-num-names}
+%\bibliographystyle{model1a-num-names}
 
@@
 %% `Elsevier LaTeX' style
-%\bibliographystyle{elsarticle-num}
+\bibliographystyle{elsarticle-num}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 Recently, the potentiality of ILs for \ce{CO_2} capture has been called into question by Carvalho \textit{et al.} \cite{Carvalho_2016}, who warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposed absorption capability of certain ILs.
-Although most thermodynamic models are formulated in terms of molar fractions, a key factor that dictates the absorption process efficiency is given by the amount of \ce{CO_2} that can be dissolved in a certain \textit{volume} or \textit{mass} of solvent.
+Although most thermodynamic models are formulated in terms of molar fraction, a key factor that dictates the absorption process efficiency is given by the amount of \ce{CO_2} that can be dissolved in a certain \textit{volume} or \textit{mass} of solvent.
 By expressing the solubility values in terms of molality and performing an exhaustive comparison between various ILs, Ref.
@@
 where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid phase and $P_s$ is the partial pressure of the solute in the gas phase.
-It should be noted that in the derivation of Eq.~\ref{eq:free_solv}, the gas phase was treated as an ideal gas.
+It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase was treated as an ideal gas.
 
@@
 \subsection*{Henry constant}
-If both $P_s$ and $c_s^{\ast}$ were not large, we can resort to Eq.~\ref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
+If both $P_s$ and $c_s^{\ast}$ were not large, we can resort to Eq.~\eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
 \begin{equation}
@@
 \end{equation}
-Therefore, by simply expressing Eq.~\ref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that MW (molecular weight of the solution) = $\text{MW}_{\scaleto{IL}{4pt}}$, as well as $\rho$ (mass density of the solution) = $\rho_{\scaleto{IL}{4pt}}$, we obtain that
+Therefore, by simply expressing Eq.~\eqref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that MW (molecular weight of the solution) = $\text{MW}_{\scaleto{IL}{4pt}}$, as well as $\rho$ (mass density of the solution) = $\rho_{\scaleto{IL}{4pt}}$, we obtain that
 \begin{equation}
@@
 
-If one makes $N_s^{l}$ = 1, and substitute Eqs.~\ref{eq:mu_res} and~\ref{eq:mu_res_0} into Eq.~\ref{eq:gamma}, the infinite-dilution activity coefficient, $\gamma^{\infty}_s$, can be predicted according to the following equation:
+If one makes $N_s^{l}$ = 1, and substitute Eqs.~\eqref{eq:mu_res} and~\eqref{eq:mu_res_0} into Eq.~\eqref{eq:gamma}, the infinite-dilution activity coefficient, $\gamma^{\infty}_s$, can be predicted according to the following equation:
 \begin{equation}
@@
 \end{equation}
-where $B_s$ corresponds to the second virial coefficient.
-
-Here we employ the correlation of $B_s$ for \ce{CO_2} introduced by Holste \textit{et al.} \cite{Holste_1987}, which is
+where $B_s$ corresponds to the second virial coefficient. Here we employ the correlation of $B_s$ for \ce{CO_2} introduced by Holste \textit{et al.} \cite{Holste_1987}, which is
 \begin{equation}
@@
 where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = $-2.455297$ $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol).
-At equilibrium, $P_s$ = $P$.
-However, 
-equilibrium pressure
-We have found from preliminaries simulations that $\Delta G_{\text{sim}}$
 
- Actually, the prediction of $P_s$ should be iterative and in this work we propose the following scheme: (i) run an NPT simulation, (ii) calculate $\Delta G_{\text{sim}}$ and $f^{g}_s$ via Eq.~\ref{eq:fgas_d}, (iii) employ $f^{g}_s$ in Eq.~\ref{eq:fgas} to compute $P_s$ (iv) if $P_s$ $\neq$ P, repeat the above steps using $P_s$ as the specified pressure in a new NPT simulation.
-This is done until $P_s$ = P.
+As supported by preliminary simulations, it is reasonable to assume $\Delta G_{\text{sim}}$ as independent of pressure over the range of experimental data considered in this work.
+Then, the equilibrium pressure is determined by solving Eq.~\eqref{eq:fgas} for $P_s$.
 
@@
 
-The versatility of ILs for different applications is in part due to the fact that their physical properties strongly vary with the particular cation-anion combination.
-On the other hand, this characteristic also explains why the desirable transferability of force fields is particularly difficult to attain.
-Indeed, it is a common practice to extract the potential parameters corresponding to intramolecular (bond stretching, angle bending, torsion rotation) and Lennard-Jones (LJ) interactions from a well established force field and then derive the partial atomic charges.
+The versatility of ILs for different applications is in part due to the fact that their physical properties strongly depend on the particular cation-anion combination.
+On the other hand, this feature also explains why the desirable transferability of force fields is particularly difficult to attain.
+Indeed, it is a common practice to extract the potential parameters of the intramolecular (bond stretching, angle bending, torsion rotation) and Lennard-Jones (LJ) interactions from a well established force field and, then, only derive the partial atomic charges with the aim of ``adjusting'' the model for a specific pair of ions.
 This procedure is, however, inaccurate as in conventional force fields the determination of the atomic charges precedes the dihedrals parametrization.
 Another ad-hoc strategy, which intends to crudely incorporate polarization effects, is to scale the partial charges uniformly with a factor which normally takes values in the range 0.8-0.9.
-This practice has proven to be effective in improving the predictions of dynamic properties \cite{Schr_der_2012}.
+This has proven to be effective for predicting dynamic properties \cite{Schr_der_2012}.
 
 In this paper, we consider four models of \ce{[emim][B(CN)_4]}.
-Koller \textit{et al.} \cite{Koller_2012} were the first to introduce a specific non-polarizable force field of \ce{[emim][B(CN)_4]}.
+Koller \textit{et al.} \cite{Koller_2012} were the first to introduce a specific non-polarizable force field for that IL.
 They tested three variations of a \textit{united-atoms} model, in which the alkyl groups \ce{CH_3} and \ce{CH_2} of \ce{[emim]^+} are replaced by pseudo-atoms.
@@
 
-The potential parameters of \ce{[B(CN)_4]^-} derived by Koller \textit{et al.} \cite{Koller_2012} were then employed by Batista \textit{et al.} \cite{Batista_2015} to study aqueous solutions of \ce{[emim][B(CN)_4]}.
+The potential parameters of \ce{[B(CN)_4]^-} derived by Koller \textit{et al.} \cite{Koller_2012} were then used by Batista \textit{et al.} \cite{Batista_2015} to study aqueous solutions of \ce{[emim][B(CN)_4]}.
 In this case, the authors considered the \textit{all-atom} model of \ce{[emim]^+} developed by Cadena and Maginn \cite{Cadena_2006}.
 The atomic partial charges were obtained using the CHELP procedure \cite{Breneman_1990}, resulting in net charges of $\pm$0.889$e$ on the ions.
-It should be noted that those force fields consider different scaling factors for the 1-4 non-bonded interactions: Cadena and Maginn \cite{Cadena_2006} use values of 1.0 y 0.4 for the LJ and Coulombic interactions, respectively; while in Koller \textit{et al.} \cite{Koller_2012} the corresponding factors are 0.5 y 5/6, in accordance with the AMBER force field.
-Batista \textit{et al.} \cite{Batista_2015} employ the same factors as Cadena and Maginn \cite{Cadena_2006} (J.P.
+It should be noted that the factors for scaling the 1-4 non-bonded interactions are different for these force fields: Cadena and Maginn \cite{Cadena_2006} apply factors of 1.0 and 0.4 for the LJ and Coulombic interactions, respectively; while in Koller \textit{et al.} \cite{Koller_2012} the corresponding values are 0.5 and 5/6, in accordance with the AMBER force field.
+Batista \textit{et al.} \cite{Batista_2015} used the first ones (J.P.
 Coutinho, personal communication).
@@
 
-We also consider the parametrization recently reported by Weber and Kirchner \cite{Weber_2016}, which is based on the force field developed by P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}.
+We also consider the parametrization reported by Weber and Kirchner \cite{Weber_2016}, which is based on the force field developed by P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}.
 The potential parameters for the anion are not specified in Refs.~\citenum{Weber_2016} and~\citenum{Canongia_Lopes_2006}, and we obtained them by a direct communication with the authors of Ref.~\citenum{Weber_2016}.
@@
 This refining was characterized by their authors as ``unusual'', given that the LJ parameters were modified, while keeping the partial charges at their original values.
-This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry's constant of \ce{CO_2} at several temperatures.
+This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry constants of \ce{CO_2} at several temperatures.
 
@@
 
-The solutes considered here are hexane, benzene, \ce{CO_2}, ethanol, cyclohexane and water.
+The solutes considered in this work are hexane, benzene, \ce{CO_2}, ethanol, cyclohexane and water.
 Hexane and benzene were modeled using the OPLS-AA force field \cite{Jorgensen_1996}, while the TRAPPE potential \cite{Chen_2001,Potoff_2001} was employed for ethanol and \ce{CO_2}.
-Cyclohexane was simulated using a rigid-body model \cite{munoz2015lennard} whose sites only interact via the LJ potential and for water we employ the TIP4P/2005 model \cite{Abascal_2005,Vega_2011}.
+Cyclohexane was simulated using a rigid-body model \cite{munoz2015lennard} whose sites only interact via a LJ potential.
+For water, we employ the TIP4P/2005 model \cite{Abascal_2005,Vega_2011}.
 
@@
 
-With the aim of setting up a (more) computationally efficient protocol for the ILs, in this work we assess the possibility of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method \cite{Fennell2006} for computing the electrostatic interactions.
+With the aim of setting up a computationally efficient protocol for the ILs, in this work we assess the possibility of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method \cite{Fennell2006} for computing the electrostatic interactions.
 As an alternative to the Ewald schemes \cite{Ewald_1921,Darden_1993,Hockney_1988}, McCann \textit{et al.} \cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force fields.
-They concluded that using $\alpha$ = 0.2 {\AA}$^{-1}$ together with a cutoff distance ($r_c$) of 15 {\AA} provide the best energetic agreement with the Ewald method.
-In this work, the comparisons are made in terms of the simulated densities and radial distribution functions for which, as will be shown in the next section, $\alpha$ = 0.2 {\AA}$^{-1}$ and $r_c$ = 12 {\AA} resulted in good agreement for the ILs studied here.
-These values were also employed for the charged solutes, with the exception of hexane, for which we considered undamped Coulombic interactions.
-The reason for this exception is that we were able to improve the agreement with the experimental solvation free energy of that pure substance.
+They concluded that using $\alpha$ = 0.2 {\AA}$^{-1}$ and a cutoff distance ($r_c$) of 15 {\AA} provide the best energetic agreement with the Ewald method.
+In this work, the comparisons are made in terms of the simulated densities and radial distribution functions for which, as will be shown in the next section, $\alpha$ = 0.2 {\AA}$^{-1}$ and $r_c$ = 12 {\AA} resulted in a good agreement.
+These values were also employed for the charged solutes, with the exception of hexane, for which we applied undamped Coulombic interactions improving the prediction of the chemical potential.
 
-When it was possible to treat the ions as rigid bodies, the NPT algorithm of Kamberaj \textit{et al.} \cite{Kamberaj_2005} was employed to carry out the MD simulations.
-Otherwise, the scheme due to Shinoda \textit{et al}.
-\cite{Shinoda2004} was used along with the application of SHAKE \cite{Ryckaert1977} to constrain the C-H bonds lengths.
-For both integrators, we employed $\Delta t$ = 1 fs.
+The NPT algorithm of Kamberaj \textit{et al.} \cite{Kamberaj_2005} was used to perform the simulations with rigid bodies.
+For flexible molecules, we applied the scheme due to Shinoda \textit{et al.} \cite{Shinoda2004} C-H bonds were constrained by the SHAKE method \cite{Ryckaert1977}.
+For both integrators, we used a time-step size ($\Delta t$) of 1 fs.
 
@@
 In this paper we use the modified LJ potential due to Beutler \textit{et al.} \cite{Beutler_1994}.
-The electrostatic interactions, on the other hand, can be handled simply by a linear scaling of the potential \cite{Naden_2015}.
-
-Furthermore, the contributions to $\Delta G$ originating at the different types of coupling can be taken into account separately, as follows
+The electrostatic interactions, on the other hand, can be handled by a linear scaling \cite{Naden_2015}.
+Furthermore, the contributions to $\Delta G$ originating at the different couplings are taken into account separately, as follows:
 \begin{equation}
@@
 \end{equation}
-with $\lambda_{\,\text{vdW}}$ and $\lambda_{\,\text{Coul}}$ being the coupling parameters of the soft-core and electrostatic potentials, respectively.
+where $\lambda_{\,\text{vdW}}$ and $\lambda_{\,\text{Coul}}$ are the coupling parameters of the soft-core and electrostatic potentials, respectively.
 Note that in the process of coupling the vdW interactions, the Coulombic interactions are turned-off, while we set $\lambda_{\,\text{vdW}}$ = 1 when computing $\Delta G_{\,\text{Coul}}$.
 This results in the ``end-point'' states given by ($\lambda_{\,\text{vdW}}$=0,$\lambda_{\,\text{Coul}}$=0) and ($\lambda_{\,\text{vdW}}$=1,$\lambda_{\,\text{Coul}}$=1), as expected.
-The complete sets of the coupling parameters we employ here are $\lambda_{\text{vdW}}$ = $\{0.0$, $0.05$, $0.1$, $0.2$, $0.25$, $0.3$, $0.35$, $0.4$, $0.45$, $0.5$, $0.6$, $0.7$, $0.8$, $0.9$, $1.0\}$ and $\lambda_{\text{Coul}}$ = $\{0.0$, $0.1$, $0.4$, $0.7$, $0.1\}$.
+The complete sets of the coupling parameters we use here are $\lambda_{\text{vdW}}$ = $\{0.0$, $0.05$, $0.1$, $0.2$, $0.25$, $0.3$, $0.35$, $0.4$, $0.45$, $0.5$, $0.6$, $0.7$, $0.8$, $0.9$, $1.0\}$ and $\lambda_{\text{Coul}}$ = $\{0.0$, $0.1$, $0.4$, $0.7$, $0.1\}$.
 
-In this work, we carried out independent simulation at each state of $\lambda_{\text{Coul}}$, while the expanded ensemble (EE) method~\cite{Lyubartsev_1992} was applied for sampling the states associated to the $\lambda_{\,\text{vdW}}$ set.
+In this work, we carried out independent simulation at each state of $\lambda_{\text{Coul}}$, while the expanded ensemble (EE) method~\cite{Lyubartsev_1992} was applied for sampling the $\lambda_{\,\text{vdW}}$ set.
 In short, an EE is constructed as a weighted sum of subensembles, each assuming a different value of the variable chosen to explore the free energy landscape, which in our case is $\lambda_{\,\text{vdW}}$.
-This way, the sampling of the EE involves both sampling each subensamble with fixed variables (N,P,T,$\lambda_{\,\text{vdW}}$) and transitions in $\lambda_{\,\text{vdW}}$.
+This way, the sampling of an EE comprises both sampling each subensamble with fixed variables (N,P,T,$\lambda_{\,\text{vdW}}$) and transitions in $\lambda_{\,\text{vdW}}$.
 Thus, a remarkable feature of the EE method is the possibility of exploring the whole alchemical route in a single simulation.
-In this work, we perform a sequential sampling of the EE \cite{Chodera_2011_2}, which consists in sampling each subensamble via NPT MD for a determined number of steps $N^{\text{EE}}$ followed by an attemp to change $\lambda_{\,\text{vdW}}$ using MC, and so on.
-That change in $\lambda_{\,\text{vdW}}$ is randomly proposed according to an independent sampling scheme \cite{Chodera_2011_2}.
+In this work, we perform a sequential sampling of the EE \cite{Chodera_2011_2}, which consists in sampling each subensamble via NPT molecular dynamics (MD) for a determined number of steps $N^{\text{EE}}$ followed by an attemp to change $\lambda_{\,\text{vdW}}$ using MC, and so on.
+This change in $\lambda_{\,\text{vdW}}$ is randomly proposed according to an independent sampling scheme \cite{Chodera_2011_2}.
 In addition, the set of (arbitrary) weights $\eta$ of the subensambles enters in the acceptance criteria of MC, so it is possible to tune $\eta$ in order to enhance the sampling.
@@
 Of course, this can be achieved only iteratively.
-The EE procedure, together with the \textit{soft-core} potential and the DSF method with linear coupling were all implemented in the LAMMPS software package \cite{Plimpton1995}, which we employed for carrying out all the MD simulations.
+The EE procedure, together with the \textit{soft-core} potential and the DSF method with linear coupling were implemented in the LAMMPS software package \cite{Plimpton1995}, which we used for carrying out all the simulations.
 
-As demonstrated in Ref.
-\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ generate more decorrelated samples in each subensemble.
+As demonstrated in Ref.~\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ yield more decorrelated samples in each subensemble.
 In this work, we employ $N^{EE}$ = 5 which, together with the specified $\lambda_{\, \text{vdW}}$ set, resulted to be satisfactory as up to 3 preliminary runs of the EE were enough to determine the weights $\eta$ that yielded, in a final simulation, a ``sufficient'' sampling of each subensamble.
-By ``sufficient'', we mean that the sampling provides an acceptable error in $\Delta G$.
+By ``sufficient'', we mean that the sampling provides an acceptable uncertainty in $\Delta G$.
 The simulation times for the preliminary and final EE runs were 10 and 40 ns, respectively; and each $\lambda_{\text{Coul}}$ state was simulated for 10 ns.
-Finally, the MBAR method \cite{Shirts_2008}, as implemented by Klimovich \textit{et al.} \cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$ .
+Finally, the MBAR method \cite{Shirts_2008}, as implemented by Klimovich \textit{et al.} \cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$.
 
-We end this section with a brief description of the procedure for generating the initial configurations.
-Only Ref.
-\citenum{Liu_2014} provides the atomic coordinates of the cation-anion pair corresponding to a minimum energy configuration obtained in an \textit{ab-initio} simulation.
-For the other models, we employed the tool \textit{build} of PLAYMOL \cite{playmol}, a software integrated with PACKMOL \cite{Mart_nez_2009}, which enables to specify the following geometric data: bond and angle lengths and dihedral angles, from which PLAYMOL~\cite{playmol} automatically determines the Cartesian coordinates.
-We first carried out NVT MD simulations of the isolated ion pairs in order to obtain a minimum energy conformation for the corresponding (classical) model of each pair.
-These simulations were performed using the the Nos\'{e}-Hoover thermostat \cite{Martyna1992} and a cubic box of length L = 50 {\AA} with non-periodic boundary conditions.
-To relax the initial configurations, a short run with a small time step of 0.1 fs was performed, which was followed by an equilibration using $\Delta t$ = 0.5 fs.
-Finally, we carried out a ``quenching'' simulation with $\Delta t$ = 1 fs, in which the temperature is gradually reduced until reaching a value close to 0 K.
-The resulting coordinates were then specified in PLAYMOL \cite{playmol} to build the initial configurations for simulating the liquid phases.
+The initial configurations were obtained with PLAYMOL \cite{playmol}, a software integrated with PACKMOL \cite{Mart_nez_2009}, using the tool \textit{build} to specify geometric data (bond and angle lengths, and dihedral angles), from which PLAYMOL automatically determines the Cartesian coordinates.
+We first carried out NVT MD simulations of the isolated ion pairs in order to obtain a minimum energy conformation.
+For this, we used the Nos\'{e}-Hoover thermostat \cite{Martyna1992} and a cubic box of length L = 50 {\AA} with non-periodic boundary conditions.
+After a short run with $\Delta t$ = 0.5 fs, we carried out a ``quenching'' simulation with $\Delta t$ = 1 fs, in which the temperature is gradually reduced until reaching a value close to 0 K.
+The resulting coordinates were then specified in PLAYMOL \cite{playmol} to build the configurations of the liquid phases.
 
@@
 
-In this section, we present results for the following two cases: (1) flexible ions and the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for the evaluation of the Ewald sums \cite{Ewald_1921}, and (2) ions modeled as rigid bodies with the DSF method \cite{Fennell2006} ($\alpha$ = 0.2 {\AA}$^{-1}$) for calculating the Coulombic interactions.
-For both strategies we employed $r_c$ = 12 {\AA}.
+In this section, we present results for the following two cases: (1) flexible ions and the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$, and (2) ions modeled as rigid bodies with the DSF method \cite{Fennell2006} ($\alpha$ = 0.2 {\AA}$^{-1}$) for calculating the Coulombic interactions.
+In both cases, $r_c$ = 12 {\AA}.
 
-First, we describe the approach for building the rigid bodies.
-For that, we carried out an analysis of key dihedrals, particularly those whose flexibility could lead to significant conformational changes in \ce{[emim]^+} and \ce{[Tf_2N]^-}.
-On the other hand, small and highly symmetric anions, such as \ce{PF_6} and \ce{BF_4} are usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies that strategy in the case of \ce{[B(CN)_4]^-}.
-The atomic nomenclature adopted in this paper is shown in Fig~\ref{fig:atoms_id}.
-In the \textit{united-atoms} version of \ce{[emim]^+}, the nomenclature is identical, but the hydrogens ranging from H4 to H11 are eliminated.
+The configurations of rigid bodies were obtained after carrying out an analysis of key dihedrals, whose flexibility could lead to significant conformational changes in \ce{[emim]^+} and \ce{[NTf_2]^-}.
+On the other hand, small and highly symmetric anions, such as \ce{PF_6} and \ce{BF_4} are usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies the strategy in the case of \ce{[B(CN)_4]^-}.
+The nomenclature used in this paper is shown in Fig~\ref{fig:atoms_id}.
+In the \textit{united-atoms} version of \ce{[emim]^+}, the hydrogens ranging from H4 to H11 are eliminated.
 
@@
 \centering
-\includegraphics[width=\linewidth]{ions_paper.pdf}
-\caption{\ce{[emim]^+} \ce{[B(CN)_4]^-} \ce{[NTf_2]^-}.}
+\includegraphics[width=\linewidth]{ions_paper_test.pdf}
+\caption{Adopted nomenclature for 1-ethyl-3-methylimidazolium  (\ce{[emim]^+}), tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
 \label{fig:atoms_id}
@@
 
-Using the software TRAVIS \cite{Brehm_2011}, for each model we obtained the combined distribution function (CDF) of the dihedral angles corresponding to the torsions in C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT simulations of 250 ion pairs.
-The CDF, as an alternative to individual histograms, provides a way to  simultaneously analyze the rigidity of the ring.
-In Fig.~\ref{fig:dihedrals_emim} we present the results for each model of \ce{[emim][B(CN)_4]}.
-
-A first inspection of Fig.~\ref{fig:dihedrals_emim} reveals a similar behavior of the models of \ce{[emim]^+} due to Koller \textit{et al.} \cite{Koller_2012} and Liu \textit{et al.} \cite{Liu_2014}.
-This was expected as both were developed based on the AMBER force field ~\cite{Cornell_1995}.
+Using the software TRAVIS \cite{Brehm_2011}, we obtained the combined distribution functions (CDFs) of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs at $T = 298.0~\text{K}$ and $P = 1.0~\text{bar}$.
+In Fig.~\ref{fig:dihedrals_emim} we show the CDFs for each force field of \ce{[emim][B(CN)_4]}.
+A first inspection of this figure reveals a similar behavior of the models due to Koller \textit{et al.} \cite{Koller_2012} and Liu \textit{et al.} \cite{Liu_2014}.
+This was expected as both are based on the AMBER framework \cite{Cornell_1995}.
 In addition, Figs.~\ref{fig:dihedrals_emim}(a) and \ref{fig:dihedrals_emim}(b) are symmetric, which means that atoms C1, N2, and C2 are coplanar.
 In Fig.~\ref{fig:dihedrals_emim}(a), the most likely angles can be found in a narrow region around 90$^{\circ}$ and 270$^{\circ}$.
-Given that these angles correspond to the same configuration in the \textit{united-atom} representation of \ce{[emim]^+}, we built all the rigid bodies specifying the value of 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1.
-The other models showed a larger flexibility with high probability regions that extend in a broad range of angle values.
+Since these angles correspond to an equivalent configuration in the \textit{united-atom} \ce{[emim]^+}, we built all the rigid bodies specifying 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1.
+The other models show a larger flexibility with high probability regions that extend in a broad range of angle values.
 Despite this, it was possible to build more than one type of rigid body by specifying the most probables angles of C6-C5-N2-C1.
-In the case of Liu \textit{et al.} \cite{Liu_2014}, those angles correspond to the values of  90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed the angles of 102.6$^{\circ}$ and -102.6$^{\circ}$.
-For those cases, two types of rigid bodies were built in equal proportion.
-Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} presents a non-negligible probability of sampling the angle value of 0$^{\circ}$, which notably differs from what was observed for the other models.
+In the case of Liu \textit{et al.} \cite{Liu_2014}, these angles correspond to 90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed 102.6$^{\circ}$ and -102.6$^{\circ}$.
+In these cases, two types of rigid bodies were built in equal proportion.
+Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} there is a non-negligible probability of sampling the angle of 0$^{\circ}$.
 In this case, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of the rigid bodies, respectively; and for the remaining 15~\% we specified the angle of 0$^{\circ}$.
 
-In Table~\ref{table:props_dsf} we show the results of density for the strategies mentioned at the begining of this section.
-When comparing the cases (1) and (2) for each model, we observe that the density values practically do not differ.
-In addition, the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental density.
+In Table~\ref{table:props_dsf} we present the results of density for the strategies mentioned at the beginning of this section.
+When comparing cases (1) and (2) for each model, we note that the density values practically do not differ.
+In addition, the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental value.
 The model due to Weber and Kirchner also presents a small deviation of 1\%.
-
-For the simulation strategies (1) and (2) we have also compared the results of relevant radial distribution functions (RDFs), which can be found in the Supplementary material.
-The better agreement was found for the force fields due to Koller \textit{et al.} \cite{Koller_2012} and Batista \textit{et al.} \cite{Batista_2015}.
-Even though the model of Liu \textit{et al.} \cite{Liu_2014} presented small deviations, the simulation with rigid bodies qualitatively reproduced the RDFs obtained for flexible ions.
+We have also computed relevant radial distribution functions (RDFs), which can be found in the Supplementary material.
+The better agreement is found for the models of Koller \textit{et al.} \cite{Koller_2012} and Batista \textit{et al.} \cite{Batista_2015}.
+Despite the small deviations observed for the model of Liu \textit{et al.} \cite{Liu_2014}, the simulation with rigid bodies qualitatively reproduces the RDFs obtained for the flexible ions.
 Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion).
-The model of Weber and Kirchner \cite{Weber_2016},
-on the other hand, presented important discrepancies in the RDFs of the pairs C5(cation)-N(anion) and C2(cation)-B(anion) when using rigid bodies.
-That is why, in this case only the imidazolium ring was considered rigid while the ethyl chain was left unconstrained.
+The model of Weber and Kirchner \cite{Weber_2016}, on the other hand, presents important discrepancies in the RDFs of the pairs C5(cation)-N(anion) and C2(cation)-B(anion) when using rigid bodies.
+That is why, in this case only the imidazolium ring was considered rigid and the ethyl chain was left unconstrained.
 
@@
   \includegraphics[width=.4\linewidth]{Weber.png}}%
-\caption{Combined distribution function (CDF) of [emim]}
+\caption{Combined distribution function of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs for each model of \ce{[emim][B(CN)_4]}.}
 \label{fig:dihedrals_emim}
@@
 A study of dihedrals was also carried out for \ce{[emim][NTf_2]}.
-The CDF of dihedrals angles corresponding to torsions in C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the behaviour of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 corresponds to 0$^{\circ}$.
+The CDF of dihedrals angles of C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the results of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 is 0$^{\circ}$.
 This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
 With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.} \cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
-Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2, verifies qualitatively what was observed by Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
-Given that the flexibility of \ce{[NTf_2]^-} gives rise to highly different conformation, a more rigorous strategy for building rigid bodies would be required.
-Thus, for \ce{[emim][NTf_2]} we have considered flexible ions and the DSF method, which resulted in a simulated density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.
+Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
+Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy is required for building the rigid bodies.
+Thus, the simulations of \ce{[emim][NTf_2]} were performed with flexible ions and the DSF method, which results in a computed density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.
 
-\begin{figure}[H]
+\begin{figure}[]
 \centering
@@
   \includegraphics[width=\linewidth]{Ludwig_anion.png}%
-\caption{Combined distribution function (CDF) of anion}
+\caption{Combined distribution function of (a) the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, and (b) of the dihedral angles of the contiguous  C1-S1-N1-S2 and S1-N1-S2-C2 chains, obtained from NPT-MD simulations of 250 molecules of \ce{[emim][NTf_2]}.}
 \label{fig:die_ntf2}
@@
 \begin{threeparttable}
-\caption{Densities of \ce{[emim][B(CN)_4]} predicted from MD NPT simulations at 298.15 K and 1 atm. The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
+\caption{Comparison of predicted and experimental densities for differents models of \ce{[emim][B(CN)_4]} via NPT-MD simulations at $T = 298.0~\text{K}$ and $P = 1.0~\text{atm}$.
+The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
 \begin{tabular}{ c  c  c  c  c}  
 \hline \hline
-$\text{[emim]}$[B(CN)\textsubscript{4}] & $T_{\text{sim}}$ & $ P_{\text{sim}} $ & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
-model & (K) &  (atm) &  (g/cm$^{3}$) &  \\
+$\text{[emim]}$[B(CN)\textsubscript{4}] &  $\rho_{\text{sim}}$ & error (\%)\tnote{a}  & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
+model & (g/cm$^{3}$) &  &  (g/cm$^{3}$) &  \\
 			\hline
-		 \multicolumn{5}{c}{Flexible ions/Ewald method}\\
-
-Koller y col. \cite{Koller_2012}  & 298.14 $\pm$  0.02 & 0 $\pm$ 2 & 1.046 & 1.0 \\
-Batista y col. \cite{Batista_2015} & 298.15 $\pm$ 0.01  & 1 $\pm$ 1 & 0.989 & 4.6  \\
-Liu y col. \cite{Liu_2014}  & 298.14 $\pm$ 0.01 & 0 $\pm$ 1 & 1.001 & 3.4  \\
-Weber y Kirchner. \cite{Weber_2016}  & 298.16  $\pm$ 0.01 & 1 $\pm$ 1 & 1.015 & 2.1  \\
-	 \multicolumn{5}{c}{Rigid ions/DSF method}\\
-Koller y col. \cite{Koller_2012}   & 298.42  $\pm$ 0.03  & 1 $\pm$ 1 & 1.038 & 0.2 \\
-Batista y col. \cite{Batista_2015} & 298.43 $\pm$ 0.02  & 0.9 $\pm$ 0.7  & 0.988 & 4.7  \\
-Liu y col. \cite{Liu_2014}  & 298.46 $\pm$ 0.02 & 1.2  $\pm$ 0.8 & 0.991 &  4.4 \\
-Weber y Kirchner \cite{Weber_2016} &  298.41 $\pm$ 0.03 & 1.1 $\pm$ 0.8 & 1.022 & 1.4  \\
+& \multicolumn{2}{c}{Flexible ions/Ewald method} & \multicolumn{2}{c}{Rigid ions/DSF method} \\
+Koller y col. \cite{Koller_2012}    & 1.046 & 1.0 & 1.038 & 0.2 \\
+Batista y col. \cite{Batista_2015}  & 0.989 & 4.6 & 0.988 & 4.7 \\
+Liu y col. \cite{Liu_2014}          & 1.001 & 3.4 & 0.991 & 4.4 \\
+Weber y Kirchner. \cite{Weber_2016} & 1.015 & 2.1 & 1.022 & 1.4  \\
  \hline \hline
@@
 
-For each model of \ce{[emim][B(CN)_4]} described in Sec~\ref{sec:force_field_il}, in Table \ref{table:henry} we present the results of solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\ref{eq:henry_eq}, which we compare with the experimental value reported by Mahurin \textit{et al.} \cite{Mahurin_2010}.
+For each model of \ce{[emim][B(CN)_4]} described in Sec~\ref{sec:force_field_il}, in Table \ref{table:henry} we present the results of solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}, which we compare with the experimental value reported by Mahurin \textit{et al.} \cite{Mahurin_2010}.
 Table \ref{table:henry} also includes the results for [emim][Tf\textsubscript{2}N] and the experimental $K_s$ obtained by Finotello \textit{et al.} \cite{Finotello_2008}.
@@
 We have also obtained the spatial distribution functions (SDFs) \cite{Svishchev_1993} using the software packages TRAVIS~\cite{Brehm_2011} and VMD~\cite{HUMP96}.
-For that, we carried out MD NPT simulations of the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] with a solute molar fraction of 0.1.
+For that, we carried out NPT-MD simulations of the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] with a solute molar fraction of 0.1.
 In Fig.~\ref{fig:sdf_ions} we show the SDFs of the ions around a molecule of \ce{CO_2}.
@@
 
-The task of accurately predicting $\gamma^{\, \infty}$ is more challenging given that, according to Eq.~\ref{eq:gamma_inf}, one should be able to reproduce the solvation free energies in both the pure solute and the solvent.
+The task of accurately predicting $\gamma^{\, \infty}$ is more challenging given that, according to Eq.~\eqref{eq:gamma_inf}, one should be able to reproduce the solvation free energies in both the pure solute and the solvent.
 In Table~\ref{table:mu_solutos} we present the simulated densities and the solvation free energies  $(\Delta G^{0}_{\text{sim}})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}.
@@
 \toprule
-\# & P &$\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $f^{g}_s$ (Ec.~\ref{eq:fgas_d}) & $P_s$ (Ec.~\ref{eq:fgas}) \\
+\# & P &$\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $f^{g}_s$ (Eq.~\eqref{eq:fgas_d}) & $P_s$ (Ec.~\eqref{eq:fgas}) \\
  &(atm) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm) & (atm) \\

### 2018-08-02 ionic_liquids.tex

@@
 \usepackage{natbib}
+\usepackage[version=4]{mhchem}
 
@@
 \begin{abstract}
-In this paper, we calculate solvation free enegies in ionic liquids and predict macroscopic properties required in the design of chemical processes.
-Carbon dioxide produced in combustion processes is one of the main sources of anthropogenic generation of greenhouse gases.
+In this paper, we calculate solvation free energies in ionic liquids and predict macroscopic properties required in the design of chemical processes.
+Carbon dioxide from combustion processes is one of the main sources of anthropogenic generation of greenhouse gases.
 On the other hand, the potential of \ce{[emim][B(CN)_4]} for its capture has recently been reported.
-For comparison purposes, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both in the condition of infinite dilution and at high concentrations.
-The simulations confirmed what was observed experimentally, namely the pressure required to obtain the same molality of \ce{CO_2} is notably lower in \ce{[emim][B(CN)_4]}.
-The infinite-dilution activity coefficients of hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} were also calculated, and a comparison was made with experimental values recently reported in literature.
+For comparison, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} are analyzed, both at infinite dilution and at high concentrations of \ce{CO_2}.
+Our results confirm what is experimentally observed, namely a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}.
+The infinite-dilution activity coefficients of hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} are also calculated, and a comparison is made with experimental values recently reported in literature.
 \end{abstract}
@@
 \begin{keyword}
-ionic liquids \sep solvation free energy \sep  \ce{CO_2} 
+ionic liquids \sep solvation free energy \sep  \ce{CO_2} Henry constant \sep infinite-dilution activity coefficient 
 \end{keyword}
@@
 Despite its high absorption capability, the use of MEA suffers from a serious drawback due to the high cost of solvent recovery \cite{Merkel_2010}.
-Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes to increase the environment pollution and generates extra costs for replacing the solvent.
+Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes to increase the environmental pollution and generates extra costs for replacing the solvent.
 
@@
 By expressing the solubility values in terms of molality and performing an exhaustive comparison between various ILs, Ref.
-\cite{Carvalho_2016} shows that most systems which promote a physical absorption of \ce{CO_2} exhibit a solubility similar or even lower than that observed for the heavy alkane eicosane.
+\cite{Carvalho_2016} shows that most systems which promote a physical absorption of \ce{CO_2} exhibit a solubility similar, or even lower, than that observed for the heavy alkane eicosane.
 This is true for the ``popular'' \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}; the only exception being the family of ILs containing the anion tetracyanoborate \ce{[B(CN)_4]^-}.
 
-There is no obvious explanation accounting for the enhanced solubility promoted by the presence of the anion \ce{[B(CN)_4]^-}.
-In this sense, molecular simulation provides with a powerful tool for studying solvation processes.
+There is no obvious explanation accounting for the enhanced solubility promoted by the presence of \ce{[B(CN)_4]^-}.
+In this context, molecular simulation provides with a powerful tool for studying solvation processes.
 To the best of our knowledge, only one study in literature reports the free energy of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} \cite{Liu_2014_1} which, in addition, is overestimated.
-This motivated us to evaluate different force fields of \ce{[emim][B(CN)_4]} and, as we will show below, it was possible to select a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2}.
-For comparison, \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both in the condition of infinite dilution and at high concentrations.
+This motivated us to evaluate different force fields of \ce{[emim][B(CN)_4]} and, as we will show below, it was possible to find a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2}.
+For comparison, \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both at infinite dilution and at high concentrations of \ce{CO_2}.
 The simulations confirmed what is observed in experiments: for \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}.
@@
 \label{eq:free_solv}
- \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right) ,
+ \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
 \end{split}
@@
 where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid phase and $P_s$ is the partial pressure of the solute in the gas phase.
-It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase was treated as an ideal gas.
+It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.
 
@@
 \end{equation}
-where $\phi_s$ is the fugacity coefficient of the solute. This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate $\mu^{l}_s$ = $\mu^{g}_s$, which yields
+where $\phi_s$ is the fugacity coefficient of the solute.
+This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate $\mu^{l}_s$ = $\mu^{g}_s$, which yields
 \begin{equation}
@@
 \end{equation}
-where $f^{g}_s$ is the fugacity of the solute in the gas phase. Having calculated $f^{g}_s$, $P_s$ can be predicted using the following equation
+where $f^{g}_s$ is the fugacity of the solute in the gas phase.
+Having calculated $f^{g}_s$, $P_s$ can be predicted using the following equation
 \begin{equation}
@@
 \end{equation}
-where $B_s$ corresponds to the second virial coefficient. Here we employ the correlation of $B_s$ for \ce{CO_2} introduced by Holste \textit{et al.} \cite{Holste_1987}, which is
+where $B_s$ corresponds to the second virial coefficient.
+Here, we employ the correlation of $B_s$ for \ce{CO_2} introduced by Holste \textit{et al.} \cite{Holste_1987}, which is
 \begin{equation}
@@
 \end{equation}
-where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = $-2.455297$ $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol).
+where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = -2.455297 $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol).
 
-As supported by preliminary simulations, it is reasonable to assume $\Delta G_{\text{sim}}$ as independent of pressure over the range of experimental data considered in this work.
-Then, the equilibrium pressure is determined by solving Eq.~\eqref{eq:fgas} for $P_s$.
+As supported by preliminary simulations, it seems reasonable to assume $\Delta G_{\text{sim}}$ as independent of pressure over the range of experimental data considered in this work.
+Then, the equilibrium pressure is determined by directly solving Eq.~\eqref{eq:fgas} for $P_s$.
 
@@
 It should be noted that the factors for scaling the 1-4 non-bonded interactions are different for these force fields: Cadena and Maginn \cite{Cadena_2006} apply factors of 1.0 and 0.4 for the LJ and Coulombic interactions, respectively; while in Koller \textit{et al.} \cite{Koller_2012} the corresponding values are 0.5 and 5/6, in accordance with the AMBER force field.
-Batista \textit{et al.} \cite{Batista_2015} used the first ones (J.P.
-Coutinho, personal communication).
+Batista \textit{et al.} \cite{Batista_2015} used the first ones (J.P. Coutinho, personal communication).
 
@@
 Hexane and benzene were modeled using the OPLS-AA force field \cite{Jorgensen_1996}, while the TRAPPE potential \cite{Chen_2001,Potoff_2001} was employed for ethanol and \ce{CO_2}.
-Cyclohexane was simulated using a rigid-body model \cite{munoz2015lennard} whose sites only interact via a LJ potential.
+Cyclohexane was simulated using a rigid-body model \cite{munoz2015lennard} whose sites only interact via a LJ potential
 For water, we employ the TIP4P/2005 model \cite{Abascal_2005,Vega_2011}.
@@
 They concluded that using $\alpha$ = 0.2 {\AA}$^{-1}$ and a cutoff distance ($r_c$) of 15 {\AA} provide the best energetic agreement with the Ewald method.
-In this work, the comparisons are made in terms of the simulated densities and radial distribution functions for which, as will be shown in the next section, $\alpha$ = 0.2 {\AA}$^{-1}$ and $r_c$ = 12 {\AA} resulted in a good agreement.
+In this work, comparisons are made in terms of the simulated densities and radial distribution functions for which, as will be shown in the next section, $\alpha$ = 0.2 {\AA}$^{-1}$ and $r_c$ = 12 {\AA} resulted in a good agreement.
 These values were also employed for the charged solutes, with the exception of hexane, for which we applied undamped Coulombic interactions improving the prediction of the chemical potential.
@@
 The NPT algorithm of Kamberaj \textit{et al.} \cite{Kamberaj_2005} was used to perform the simulations with rigid bodies.
-For flexible molecules, we applied the scheme due to Shinoda \textit{et al.} \cite{Shinoda2004} C-H bonds were constrained by the SHAKE method \cite{Ryckaert1977}.
+For flexible molecules, we applied the scheme due to Shinoda \textit{et al.} \cite{Shinoda2004} and C-H bonds were constrained by the SHAKE method \cite{Ryckaert1977}.
 For both integrators, we used a time-step size ($\Delta t$) of 1 fs.
@@
 Thus, a remarkable feature of the EE method is the possibility of exploring the whole alchemical route in a single simulation.
-In this work, we perform a sequential sampling of the EE \cite{Chodera_2011_2}, which consists in sampling each subensamble via NPT molecular dynamics (MD) for a determined number of steps $N^{\text{EE}}$ followed by an attemp to change $\lambda_{\,\text{vdW}}$ using MC, and so on.
-This change in $\lambda_{\,\text{vdW}}$ is randomly proposed according to an independent sampling scheme \cite{Chodera_2011_2}.
+In this work, we perform a sequential sampling of the EE \cite{Chodera_2011_2}, which consists in sampling each subensamble via NPT molecular dynamics (MD) for a determined number of steps $N^{\text{EE}}$ followed by an attempt to change $\lambda_{\,\text{vdW}}$ using MC, and so on.
+The $\lambda_{\,\text{vdW}}$ transitions are performed according to an independent sampling scheme \cite{Chodera_2011_2}.
 In addition, the set of (arbitrary) weights $\eta$ of the subensambles enters in the acceptance criteria of MC, so it is possible to tune $\eta$ in order to enhance the sampling.
@@
 For this, we used the Nos\'{e}-Hoover thermostat \cite{Martyna1992} and a cubic box of length L = 50 {\AA} with non-periodic boundary conditions.
-After a short run with $\Delta t$ = 0.5 fs, we carried out a ``quenching'' simulation with $\Delta t$ = 1 fs, in which the temperature is gradually reduced until reaching a value close to 0 K.
+After a short run with $\Delta t$ = $0.5~/text{fs}$, we carried out a ``quenching'' simulation with $\Delta t$ = $1 ~/text{fs}$, in which the temperature is gradually reduced until reaching a value close to $0~/text{K}$.
 The resulting coordinates were then specified in PLAYMOL \cite{playmol} to build the configurations of the liquid phases.
@@
 
-In this section, we present results for the following two cases: (1) flexible ions and the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$, and (2) ions modeled as rigid bodies with the DSF method \cite{Fennell2006} ($\alpha$ = 0.2 {\AA}$^{-1}$) for calculating the Coulombic interactions.
+In this section, we present results for the following two cases: (1) flexible ions together with the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for calculating the Coulombic interactions, and (2) ions modeled as rigid bodies with the DSF method \cite{Fennell2006} ($\alpha$ = 0.2 {\AA}$^{-1}$) as the alternative to the PPPM scheme.
 In both cases, $r_c$ = 12 {\AA}.
+The nomenclature used in this paper is shown in Fig~\ref{fig:atoms_id}.
+In the \textit{united-atoms} version of \ce{[emim]^+}, hydrogens ranging from H4 to H11 are eliminated.
 
-The configurations of rigid bodies were obtained after carrying out an analysis of key dihedrals, whose flexibility could lead to significant conformational changes in \ce{[emim]^+} and \ce{[NTf_2]^-}.
+The rigid bodies were built after carrying out an analysis of key dihedrals, whose flexibility could lead to significant conformational changes in \ce{[emim]^+} and \ce{[NTf_2]^-}.
 On the other hand, small and highly symmetric anions, such as \ce{PF_6} and \ce{BF_4} are usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies the strategy in the case of \ce{[B(CN)_4]^-}.
-The nomenclature used in this paper is shown in Fig~\ref{fig:atoms_id}.
-In the \textit{united-atoms} version of \ce{[emim]^+}, the hydrogens ranging from H4 to H11 are eliminated.
 
-\begin{figure}[H]
+\begin{figure}[ht]
 \centering
-\includegraphics[width=\linewidth]{ions_paper_test.pdf}
+\includegraphics[width=\linewidth]{ions_paper.pdf}
 \caption{Adopted nomenclature for 1-ethyl-3-methylimidazolium  (\ce{[emim]^+}), tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
@@
 In Fig.~\ref{fig:dihedrals_emim}(a), the most likely angles can be found in a narrow region around 90$^{\circ}$ and 270$^{\circ}$.
-Since these angles correspond to an equivalent configuration in the \textit{united-atom} \ce{[emim]^+}, we built all the rigid bodies specifying 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1.
+Since these angles correspond to an equivalent configuration in the \textit{united-atom} \ce{[emim]^+}, in the case of Koller \textit{et al.} \cite{Koller_2012} we built all the rigid bodies by specifying 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1.
 The other models show a larger flexibility with high probability regions that extend in a broad range of angle values.
@@
 In the case of Liu \textit{et al.} \cite{Liu_2014}, these angles correspond to 90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed 102.6$^{\circ}$ and -102.6$^{\circ}$.
-In these cases, two types of rigid bodies were built in equal proportion.
-Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} there is a non-negligible probability of sampling the angle of 0$^{\circ}$.
-In this case, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of the rigid bodies, respectively; and for the remaining 15~\% we specified the angle of 0$^{\circ}$.
+These two types of rigid bodies were built in equal proportion.
+In Fig.~\ref{fig:dihedrals_emim}(d), which corresponds to Weber and Kirchner \cite{Weber_2016}, one sees that the angle As this is the most flexible model, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of them, respectively; and 0$^{\circ}$ for the remaining 15~\%.
 
@@
 A study of dihedrals was also carried out for \ce{[emim][NTf_2]}.
-The CDF of dihedrals angles of C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the results of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 is 0$^{\circ}$.
+The CDF of the dihedrals angles of C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the results of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 is 0$^{\circ}$.
 This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
@@
 Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy is required for building the rigid bodies.
-Thus, the simulations of \ce{[emim][NTf_2]} were performed with flexible ions and the DSF method, which results in a computed density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.
+Thus, the simulations of \ce{[emim][NTf_2]} were performed considering flexible ions and the DSF method, which results in a computed density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.
 
-\begin{figure}[]
+\begin{figure}[ht]
 \centering
@@
 
-\subsection{Henry constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]}
+\subsection{Henry constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 \label{sec:henry_results}
 
-For each model of \ce{[emim][B(CN)_4]} described in Sec~\ref{sec:force_field_il}, in Table \ref{table:henry} we present the results of solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}, which we compare with the experimental value reported by Mahurin \textit{et al.} \cite{Mahurin_2010}.
-Table \ref{table:henry} also includes the results for [emim][Tf\textsubscript{2}N] and the experimental $K_s$ obtained by Finotello \textit{et al.} \cite{Finotello_2008}.
+In Table \ref{table:henry} we present the results of solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}.
+Table \ref{table:henry} also includes the results for [emim][Tf\textsubscript{2}N] as well as the experimental $K_s$ reported by Mahurin \textit{et al.} \cite{Mahurin_2010} and Finotello \textit{et al.} \cite{Finotello_2008}.
 The uncertainties in $K_s$ were calculated using standard error propagation.
@@
 
-First, it should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent simulations in $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
-Moreover, the $\Delta G_{\text{sim}}$ of [emim][Tf\textsubscript{2}N] is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
-These consistencies serve for validating the methodological approaches we employed in each case.
+It should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent sampling of $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
+Moreover, the $\Delta G_{\text{sim}}$ in [emim][Tf\textsubscript{2}N] is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
+These consistencies have served for validating the methodological approaches of this work.
 
 From Table \ref{table:henry} one can see that the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental value of $K_s$.
-If we look at the $\Delta G_{\lambda_{\,\text{vdW}}}$ profiles in Fig.~\ref{fig:deltag} we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014}, the maximum of the profiles occurs at lower values of free energies, suggesting that those models underestimate the interatomic interactions, which explains the ``facility'' to insert a \ce{CO_2} molecule as well as their failure to reproduce the experimental densities.
+If we look at the $\Delta G_{\lambda_{\,\text{vdW}}}$ profiles in Fig.~\ref{fig:deltag}, we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014} the maximum occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which may also explains their failure to reproduce the experimental densities.
 
-\begin{figure}[]
+\begin{figure}[ht]
 \includegraphics[width=\linewidth]{free_energy_paper}
-\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles of \ce{[emim][B(CN)_4]}.}
+\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, which was modeled according to the force fields of (circles) Koller \textit{et al.} \cite{Koller_2012}, (squares) Batista \textit{et al.} \cite{Batista_2015}, (up triangles) Liu \textit{et al.} \cite{Liu_2014}, and (x) Weber y Kirchner \cite{Weber_2016}.}
 \label{fig:deltag}
@@
 
-The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in [emim][Tf\textsubscript{2}N].
-
-We have also obtained the spatial distribution functions (SDFs) \cite{Svishchev_1993} using the software packages TRAVIS~\cite{Brehm_2011} and VMD~\cite{HUMP96}.
+The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf\textsubscript{2}]}.
+The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm these results.
+The SDFs of the ions around a \ce{CO_2} molecule were obtained by using the software packages TRAVIS \cite{Brehm_2011} and VMD \cite{HUMP96}.
 For that, we carried out NPT-MD simulations of the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] with a solute molar fraction of 0.1.
-In Fig.~\ref{fig:sdf_ions} we show the SDFs of the ions around a molecule of \ce{CO_2}.
-The isovalues were determined visually so as to observe the first solvation shell.
-From Fig.~\ref{fig:ludwig_sdf}(b), which correspond to the ions \ce{[emim]^+} and \ce{[NTf_2]^-}, it can be seen that the region with a low probability of finding an ion is larger than for \ce{[emim][B(CN)_4]}.
-In Fig.~\ref{fig:anions} we have plotted together the SDFs corresponding to the anions and we note that the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a sligthly shorter distance than for \ce{[NTf_2]^-}, in accordance with the more favorable solvation suggested by the free energy results.
-
-\begin{figure}
+The isovalues were visually determined so as to observe the first solvation shell.
+From Fig.~\ref{fig:sdf_ions}(b), which correspond to the ions \ce{[emim]^+} and \ce{[NTf_2]^-}, it can be seen that the region with a low probability of finding an ion is larger than for \ce{[emim][B(CN)_4]}.
+Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a sligthly shorter distance than for \ce{[NTf_2]^-}, as one can note from Fig.
+\begin{figure}[ht]
 \centering
@@
 }
-\caption{Spatial distribution function}
-\label{fig:sdf}
+\caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[NTf_2]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
+Fig. (c) corresponds to the SDFs of the anions, only.}
+\label{fig:sdf_ions}
 \end{figure}
 
-\subsection{Inifinite-dilution activity coefficient in [emim] [B(CN)\textsubscript{4}]}
+\subsection{Inifinite-dilution activity coefficient in \ce{[emim][B(CN)_4]}}
 \label{sec:act_results}
 
-Having selected the model of \ce{[emim][B(CN)_4]} which best reproduces the experimental $K_s$ of \ce{CO_2}, we now proceed to predict the infinite-dilution activity coefficient ($\gamma^{\, \infty}$) of benzene, hexane, cyclohexane, ethanol and water in \ce{[emim][B(CN)_4]}.
+Having selected the model of \ce{[emim][B(CN)_4]} that best reproduces the experimental $K_s$ of \ce{CO_2}, we carried out the calculation of infinite-dilution activity coefficients ($\gamma^{\, \infty}$) of benzene, hexane, cyclohexane, ethanol and water in \ce{[emim][B(CN)_4]}.
 These solutes were modeled as described in Sec.~\ref{sec:force_field_sol}.
 
-The task of accurately predicting $\gamma^{\, \infty}$ is more challenging given that, according to Eq.~\eqref{eq:gamma_inf}, one should be able to reproduce the solvation free energies in both the pure solute and the solvent.
-In Table~\ref{table:mu_solutos} we present the simulated densities and the solvation free energies  $(\Delta G^{0}_{\text{sim}})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}.
-It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ of cyclohexane.
-Note that only in the case of ethanol we have reproduced $\Delta G^{0}_\text{exp}$, while the relative error for the other solutes is around 10\%.
+The task of accurately predicting $\gamma^{\, \infty}$ is challenging since, according to Eq.~\eqref{eq:gamma_inf}, one should reproduce the solvation free energies in both the pure solute and the solvent.
+In Table~\ref{table:mu_solutes} we show the simulated densities and the solvation free energies $(\Delta G^{0}_{\text{sim}})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}.
+It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ for cyclohexane.
+Note that only in the case of ethanol we successfully predicted the $\Delta G^{0}_\text{exp}$.
+The relative errors for the other solutes is around 10\%.
 
-The results of $\gamma^{\, \infty}$ for the solutes in \ce{[emim][B(CN)_4]} are shown in Table~\ref{table:gamma}.
-For benzene and water, the predictions are very accurate, but they are a result of error compensations given the divergences verified in Table~\ref{table:mu_solutos}.
-This makes necessary to review the force fields of the solutes.
-From Table \ref{table:gamma} one can also note that the experimental $\gamma^{\, \infty}$ for hexane at the close temperatures of 298.15 K and 303 K considerably differ.
-It is therefore difficult to assess the reliability of the simulated results in this case.
+The results of $\gamma^{\, \infty}$ are presented in Table~\ref{table:gamma}.
+For benzene and water, the predictions are very accurate, but this may be due to fortuitous error compensations given the divergences shown in Table~\ref{table:mu_solutes}.
+From Table \ref{table:gamma}, one sees that the experimental $\gamma^{\, \infty}$ for hexane at $298.15~\text{K}$ and $303~\text{K}$ considerably differ.
+It is therefore difficult to assess the reliability of our results in this case.
 
@@
 \begin{threeparttable}
-\caption{Resultados de la energía libre de solvatación a T = 298.15 K de las sustancias puras benceno, hexano, ciclohexano, etanol y agua.}
+\caption{Solvation free energy at $T = 298.15~/text{K}$ for the pure solutes benzene, hexane, cyclohexane, ethanol and water.}
 \begin{tabular}{ c c c c c c c c }
 \toprule
-Soluto & $\rho_{\text{sim}}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
+Solute & $\rho_{\text{sim}}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
  & (g/cm$^{3}$) &  & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   &  \\
 \hline
-benceno OPLS-AA   & 0.8611 $\pm$ 0.0002 & 1.4 & -3.75  $\pm$ 0.02 & -0.381 $\pm$ 0.007 & -4.14 $\pm$ 0.02 & -4.56 & 9.32  \\
-hexano OPLS-AA    & 0.6513 $\pm$ 0.0003 & 0.5 & -3.67  $\pm$  0.03 & 0.011 $\pm$ 0 & -3.66 $\pm$ 0.03 & -4.06 & 9.90 \\
-ciclohexano & 0.7692 $\pm$ 0.0007 & 0.6 & -4.39 $\pm$ 0.01 & 0 & -4.39 $\pm$ 0.01 & - & -  \\
-etanol TRAPPE-UA   & 0.781 $\pm$ 0.008 & 1.01  &-0.93 $\pm$ 0.01 & -4.15 $\pm$ 0.02  & -5.08  $\pm$ 0.02  & -5.08 & 0 \\
-agua TIP4P/2005   &  0.9948 $\pm$ 0.0003 & 0.2 & 2.015 $\pm$ 0.004 & -9.01 $\pm$ 0.02 & -6.99 $\pm$ 0.02 & -6.33  &10.43 \\
+benzene OPLS-AA   & 0.8611 $\pm$ 0.0002 & 1.4 & -3.75  $\pm$ 0.02 & -0.381 $\pm$ 0.007 & -4.14 $\pm$ 0.02 & -4.56 & 9.32  \\
+hexane OPLS-AA    & 0.6513 $\pm$ 0.0003 & 0.5 & -3.67  $\pm$  0.03 & 0.011 $\pm$ 0 & -3.66 $\pm$ 0.03 & -4.06 & 9.90 \\
+cyclohexane & 0.7692 $\pm$ 0.0007 & 0.6 & -4.39 $\pm$ 0.01 & 0 & -4.39 $\pm$ 0.01 & - & -  \\
+ethanol TRAPPE-UA   & 0.781 $\pm$ 0.008 & 1.01  &-0.93 $\pm$ 0.01 & -4.15 $\pm$ 0.02  & -5.08  $\pm$ 0.02  & -5.08 & 0 \\
+water TIP4P/2005   &  0.9948 $\pm$ 0.0003 & 0.2 & 2.015 $\pm$ 0.004 & -9.01 $\pm$ 0.02 & -6.99 $\pm$ 0.02 & -6.33  &10.43 \\
  \bottomrule
-\label{table:mu_solutos} 
+\label{table:mu_solutes} 
 \end{tabular}
@@
 \begin{threeparttable}
-\caption{Coeficientes de actividad a dilución infinita en \ce{[emim][B(CN)_4]} a T = 298.15 K de los solutos benceno, hexano, ciclohexano, etanol y agua.}
+\caption{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]} at $T = 298.15~/text{K}$ of the pure solutes benzene, hexane, cyclohexane, ethanol, and water.}
 \begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
 \toprule
-Soluto & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
+Solute & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
  & (kcal/mol) & (kcal/mol) &  (kcal/mol)  &  & (298.15 K) \cite{Doma_ska_2011} & (303 K) \cite{Yan_2010} \\
 \midrule % inserts single-line
-hexano OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
-ciclohexano& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
-benceno OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
+hexane OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
+cyclohexane& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
+benzene OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
 ethanol TRAPPE-UA& -0.73 $\pm$ 0.02 & -4.10 $\pm$ 0.04 & -4.83 $\pm$ 0.04 & 0.41 $\pm$ 0.03 & 1.58 & 1.64  \\
-agua TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
+water TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
  \bottomrule

### 2018-08-03 ionic_liquids.tex
add pressure figure

@@
 For this, we used the Nos\'{e}-Hoover thermostat \cite{Martyna1992} and a cubic box of length L = 50 {\AA} with non-periodic boundary conditions.
-After a short run with $\Delta t$ = $0.5~/text{fs}$, we carried out a ``quenching'' simulation with $\Delta t$ = $1 ~/text{fs}$, in which the temperature is gradually reduced until reaching a value close to $0~/text{K}$.
+After a short run with $\Delta t$ = $0.5~\text{fs}$, we carried out a ``quenching'' simulation with $\Delta t$ = $1 ~\text{fs}$, in which the temperature is gradually reduced until reaching a value close to $0~\text{K}$.
 The resulting coordinates were then specified in PLAYMOL \cite{playmol} to build the configurations of the liquid phases.
@@
 These two types of rigid bodies were built in equal proportion.
-In Fig.~\ref{fig:dihedrals_emim}(d), which corresponds to Weber and Kirchner \cite{Weber_2016}, one sees that the angle As this is the most flexible model, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of them, respectively; and 0$^{\circ}$ for the remaining 15~\%.
+Fig.~\ref{fig:dihedrals_emim}(d) corresponds to Weber and Kirchner \cite{Weber_2016}. 
+Given the wide range of sampled angles, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of them, respectively; and 0$^{\circ}$ for the remaining 15~\%.
 
 In Table~\ref{table:props_dsf} we present the results of density for the strategies mentioned at the beginning of this section.
-When comparing cases (1) and (2) for each model, we note that the density values practically do not differ.
-In addition, the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental value.
-The model due to Weber and Kirchner also presents a small deviation of 1\%.
-We have also computed relevant radial distribution functions (RDFs), which can be found in the Supplementary material.
+When comparing cases (1) and (2) for each model, we note that the simulated densities practically do not differ.
+In addition, the models of Koller \textit{et al.} \cite{Koller_2012} and Weber and Kirchner \cite{Weber_2016} best reproduce the experimental value.
+We have also computed radial distribution functions (RDFs), which can be found in the Supplementary material.
 The better agreement is found for the models of Koller \textit{et al.} \cite{Koller_2012} and Batista \textit{et al.} \cite{Batista_2015}.
@@
 Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
-Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy is required for building the rigid bodies.
+Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy for building the rigid bodies is required.
 Thus, the simulations of \ce{[emim][NTf_2]} were performed considering flexible ions and the DSF method, which results in a computed density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.
@@
 In Table \ref{table:henry} we present the results of solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}.
-Table \ref{table:henry} also includes the results for [emim][Tf\textsubscript{2}N] as well as the experimental $K_s$ reported by Mahurin \textit{et al.} \cite{Mahurin_2010} and Finotello \textit{et al.} \cite{Finotello_2008}.
+Table~\ref{table:henry} also contains the experimental $K_s$ reported by Mahurin \textit{et al.} \cite{Mahurin_2010} and Finotello \textit{et al.} \cite{Finotello_2008}.
 The uncertainties in $K_s$ were calculated using standard error propagation.
@@
 From Table \ref{table:henry} one can see that the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental value of $K_s$.
-If we look at the $\Delta G_{\lambda_{\,\text{vdW}}}$ profiles in Fig.~\ref{fig:deltag}, we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014} the maximum occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which may also explains their failure to reproduce the experimental densities.
+If we look at the $\Delta G_{\lambda_{\,\text{vdW}}}$ profiles in Fig.~\ref{fig:deltag}, we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014} the maximum occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which may also explain their failure to reproduce the experimental density.
 
@@
 The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf\textsubscript{2}]}.
-The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm these results.
+The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm this result.
 The SDFs of the ions around a \ce{CO_2} molecule were obtained by using the software packages TRAVIS \cite{Brehm_2011} and VMD \cite{HUMP96}.
-For that, we carried out NPT-MD simulations of the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] with a solute molar fraction of 0.1.
+For that, we carried out NPT-MD simulations of \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] systems with a \ce{CO_2} molar fraction of 0.1.
 The isovalues were visually determined so as to observe the first solvation shell.
-From Fig.~\ref{fig:sdf_ions}(b), which correspond to the ions \ce{[emim]^+} and \ce{[NTf_2]^-}, it can be seen that the region with a low probability of finding an ion is larger than for \ce{[emim][B(CN)_4]}.
-Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a sligthly shorter distance than for \ce{[NTf_2]^-}, as one can note from Fig.
+If we compare Figs.~\ref{fig:sdf_ions} (a) and (b), one notes that the region with a low probability of finding an ion is larger for \ce{[emim][NTf_2]}.
+Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.
 \begin{figure}[ht]
@@
 
-Having selected the model of \ce{[emim][B(CN)_4]} that best reproduces the experimental $K_s$ of \ce{CO_2}, we carried out the calculation of infinite-dilution activity coefficients ($\gamma^{\, \infty}$) of benzene, hexane, cyclohexane, ethanol and water in \ce{[emim][B(CN)_4]}.
-These solutes were modeled as described in Sec.~\ref{sec:force_field_sol}.
+Having selected the model of \ce{[emim][B(CN)_4]} that best reproduces the experimental $K_s$ of \ce{CO_2}, we next calculate the infinite-dilution activity coefficients ($\gamma^{\, \infty}$) of benzene, hexane, cyclohexane, ethanol and water in \ce{[emim][B(CN)_4]}.
 
@@
 
-In Secs.~\ref{sec:henry_results} and \ref{sec:act_results} we obtained some solvation properties for diluted solutions.
-However, the corresponding derived conclusions cannot be extraploted to concentrated solutions, which are the more likely scenario in the \ce{CO_2} capture.
-Therefore, in this section we proceed to analyze the \ce{CO_2} solvation at the thermodynamic conditions specified in Table \ref{table:solv}.
-These conditions correspond to close values of molality of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N], which is the solubility measure employed by Carvalho \textit{et al.}~\cite{Carvalho_2016}.
+Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].
 
@@
 \ref{sec:partial_pressure}.
-The predicted values of pressure ($P_s$) reproduce what is observed experimentaly, in the sense that $P_s$ for the system \ce{CO_2}-\ce{[emim][B(CN)_4]} is considerably smaller than the value obtained for \ce{CO_2}-[emim][Tf\textsubscript{2}N].% However, in this case we were not able to converge because an oscilatory behaviour was observed.
+The predicted values of pressure ($P_s$) reproduce what is observed experimentaly, in the sense that $P_s$ for the system \ce{CO_2}-\ce{[emim][B(CN)_4]} is considerably smaller than the value obtained for \ce{CO_2}-[emim][Tf\textsubscript{2}N].
 
-\begin{table*}
-\centering
-\begin{adjustbox}{width=1\textwidth}
-\begin{threeparttable}
-\caption{Gaseous phase pressure, predicted from solvation free energies of \ce{CO_2} for the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N].}
-\begin{tabular}{ c c  c  c  c  c c }  
-\toprule
-\# & P &$\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $f^{g}_s$ (Eq.~\eqref{eq:fgas_d}) & $P_s$ (Ec.~\eqref{eq:fgas}) \\
- &(atm) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm) & (atm) \\
-		\hline
-		\multicolumn{7}{c}{\ce{[emim][B(CN)_4]}~\cite{Koller_2012} } \\
-1 & 21.0 &  0.42 $\pm$ 0.01 & -1.176  $\pm$ 0.007  & -0.755 $\pm$ 0.01 & 16.96 $\pm$ 0.33 & 18.33 $\pm$ 0.4 \\
-2 & 18.33 &  0.39 $\pm$ 0.01 & -1.187  $\pm$ 0.008  & -0.794 $\pm$ 0.01 & 15.93 $\pm$ 0.33 & 17.14 $\pm$ 0.4 \\ 
-3 & 17.14 &  0.39 $\pm$ 0.01 & -1.164  $\pm$ 0.008  & -0.779 $\pm$ 0.01 & 16.32 $\pm$ 0.33 & 17.5 $\pm$ 0.4 \\
-		\hline
-       \multicolumn{7}{c}{[emim][Tf\textsubscript{2}N]~\cite{K_ddermann_2007} } \\
-1 & 37.0 &  0.314 $\pm$ 0.005  & -0.856 $\pm$ 0.005 & -0.542 $\pm$ 0.005 & 32.6 $\pm$ 0.37 & 38.4 $\pm$ 0.4 \\
-2 & 38.4 &  0.349 $\pm$ 0.005  & -0.840  $\pm$ 0.005 & -0.491 $\pm$ 0.005 & 35.35  & 42.47 \\
- \bottomrule
-\label{table:deltaG_conc} 
-\end{tabular}
-\end{threeparttable}
-\end{adjustbox}
-\end{table*}
+\begin{figure}[ht]
+\includegraphics[width=\linewidth]{pressure_est.pdf}
+\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, which was modeled according to the force fields of (circles) Koller \textit{et al.} \cite{Koller_2012}, (squares) Batista \textit{et al.} \cite{Batista_2015}, (up triangles) Liu \textit{et al.} \cite{Liu_2014}, and (x) Weber y Kirchner \cite{Weber_2016}.}
+\label{fig:pressure}
+\end{figure}
 

### 2018-08-03 ionic_liquids.tex
high conc review

@@
 \centering
-\includegraphics[width=\linewidth]{ions_paper.pdf}
+\includegraphics[width=\linewidth]{atoms_id.pdf}
 \caption{Adopted nomenclature for 1-ethyl-3-methylimidazolium  (\ce{[emim]^+}), tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
@@
 }
+
+\subfloat[]{%
+  \includegraphics[width=\linewidth]{anionanion.pdf}%
+}
 \caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[NTf_2]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
-Fig. (c) corresponds to the SDFs of the anions, only.}
+Fig. (c) corresponds to the SDFs of the anions plotted together.}
 \label{fig:sdf_ions}
@@
 
-In Fig.
-we present the results of each iteration according to the scheme proposed in Sec.
-\ref{sec:partial_pressure}.
-The predicted values of pressure ($P_s$) reproduce what is observed experimentaly, in the sense that $P_s$ for the system \ce{CO_2}-\ce{[emim][B(CN)_4]} is considerably smaller than the value obtained for \ce{CO_2}-[emim][Tf\textsubscript{2}N].
+In Fig.~\ref{fig:pressure} we present for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
+The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
+Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably smaller for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
+In addition, we see that for  this system the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
 
@@
 \includegraphics[width=\linewidth]{pressure_est.pdf}
-\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, which was modeled according to the force fields of (circles) Koller \textit{et al.} \cite{Koller_2012}, (squares) Batista \textit{et al.} \cite{Batista_2015}, (up triangles) Liu \textit{et al.} \cite{Liu_2014}, and (x) Weber y Kirchner \cite{Weber_2016}.}
+\caption{ \ce{CO_2} \ce{[emim][B(CN)_4]} Koller \textit{et al.} \cite{Koller_2012}, (squares)}
 \label{fig:pressure}
@@
 \label{sec:conclusion}
+
+On of the goals of this study was to compare available force fields for \ce{[emim][B(CN)_4]}.
+The model that best reproduces the experimental density is the one developed by Koller.
+This is the only model that reparametrizes the LJ parameters for the boron atom.
+We demonstrate that it is possible to employ rigid bodies and the DSF method for the simulation. 
+computationally more efficient.
+Using the expanded ensemble method, we reproduced the solvation free energy.
+Koller best reproduces the experimental henry constants. 
+This model was evaluated also to predict inifinite-dilution activity coefficient.
+This property also depends in the solvation free energy of the pure solutes.
+The results at infinite-dilution suggest a more favorable solvation. and high concentrations 
+The pictures changes
 

### 2018-08-04 ionic_liquids.tex
some comments on conclusions

@@
 Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].
+The differences in \ce{CO_2} molar fractions for this ILs exemplifies the observations made by Carvalho \textit{et al.} \cite{Carvalho_2016}, mentioned at the introduction of this paper.
 
@@
 
-In Fig.~\ref{fig:pressure} we present for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
+In Fig.~\ref{fig:pressure} we show for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
 The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
@@
 
-On of the goals of this study was to compare available force fields for \ce{[emim][B(CN)_4]}.
-The model that best reproduces the experimental density is the one developed by Koller.
-This is the only model that reparametrizes the LJ parameters for the boron atom.
-We demonstrate that it is possible to employ rigid bodies and the DSF method for the simulation. 
-computationally more efficient.
-Using the expanded ensemble method, we reproduced the solvation free energy.
-Koller best reproduces the experimental henry constants. 
+One of the goals of this paper was to compare available models of \ce{[emim][B(CN)_4]} in terms of their capability to reproduce the experimental Henry constant of \ce{CO_2}.
+We have found that only the model of Koller \textit{et al.} \cite{Koller_2012} achieves this goal.
+A key factor for this success seems to be the reparametrization of the LJ parameters for the boron atom, which is only performed in the work of Koller \textit{et al.}  \cite{Koller_2012} in order to reproduce the experimental density of the pure substance.
+
+In the case of \ce{[emim][B(CN)_4]}, we were able to
+
+to introduce computationally efficient strategies, such as the use of rigid bodies and the DSF method for evaluating the Co the simulations and perform them in a more computationally efficient way: the ILs were modelled as rigid bodies and using the DSF method to calculate the Coulombic interactions.
+This required some preliminary simulations in order to analyze the most probable conformations of the ions.
+This was carried out in a simple way and with very good results.
+
+Using the expanded ensemble method, we reproduced the solvation free energy for both systems of interest:
+\ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} and at different thermodyanamic conditions. 
+At infinite-dilution those solvents performs in the solvation in \ce{[emim][B(CN)_4]} only slightly more favorable.
+This picture completely changed when we analyzed the systems at higher concentrations: the pressure required to dissolved a certain mass of \ce{CO_2} is considerable smaller that for \ce{[emim][NTf_2]}.
+
 This model was evaluated also to predict inifinite-dilution activity coefficient.
 This property also depends in the solvation free energy of the pure solutes.
-The results at infinite-dilution suggest a more favorable solvation. and high concentrations 
-The pictures changes
 

### 2018-08-06 ionic_liquids.tex
conclusion revision

--- 2018-08-03 ionic_liquids.tex
@@
 }
+
+\subfloat[]{%
+  \includegraphics[width=\linewidth]{anionanion.pdf}%
+}
 \caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[NTf_2]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
-Fig. (c) corresponds to the SDFs of the anions, only.}
+Fig. (c) corresponds to the SDFs of the anions plotted together.}
 \label{fig:sdf_ions}
+\end{figure}
+
+\subsection{Study of concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]}
+\label{sec:results_conc}
+
+Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].
+The differences in the \ce{CO_2} molar fractions in this case exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, mentioned at the introduction of this paper.
+
+\begin{table*}
+\centering
+\begin{threeparttable}
+\caption{Thermodynamic conditions employed in the simulations of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]~\cite{Makino_2014,Schilderman_2007}}
+\begin{tabular}{ c  c  c  c  c  }  
+\toprule
+Ionic liquid & T (K)  & P (atm)  & molar fraction $x_s$ & molality $m_s$ \\
+\midrule		
+$\text{[emim]}$[B(CN)\textsubscript{4}]~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
+$\text{[emim]}$[Tf\textsubscript{2}N]~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
+ \bottomrule
+\label{table:solv} 
+\end{tabular}
+\end{threeparttable}
+\end{table*}
+
+In Fig.~\ref{fig:pressure} we show for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
+The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
+Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably lower for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
+In addition, we see that for  this system the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
+The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] were -0.755 $\pm$ 0.01 kcal/mol and -0.542 $\pm$ 0.005, respectively.
+However, since we employed a different molecule number of \ce{CO_2}, we cannot draw any conclusion regarding the presence of strong interactions with \ce{[emim][B(CN)_4]} that could explain the higher solubility.
+
+\begin{figure}[ht]
+\includegraphics[width=\linewidth]{pressure_est.pdf}
+\caption{ \ce{CO_2} \ce{[emim][B(CN)_4]} Koller \textit{et al.} \cite{Koller_2012}, (squares)}
+\label{fig:pressure}
 \end{figure}
@@
 \end{table*}
-
-\subsection{Study of concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]}
-\label{sec:results_conc}
-
-Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].
-
-\begin{table*}
-\centering
-\begin{threeparttable}
-\caption{Thermodynamic conditions employed in the simulations of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]~\cite{Makino_2014,Schilderman_2007}}
-\begin{tabular}{ c  c  c  c  c  }  
-\toprule
-Ionic liquid & T (K)  & P (atm)  & molar fraction $x_s$ & molality $m_s$ \\
-\midrule		
-$\text{[emim]}$[B(CN)\textsubscript{4}]~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
-$\text{[emim]}$[Tf\textsubscript{2}N]~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
- \bottomrule
-\label{table:solv} 
-\end{tabular}
-\end{threeparttable}
-\end{table*}
-
-In Fig.
-we present the results of each iteration according to the scheme proposed in Sec.
-\ref{sec:partial_pressure}.
-The predicted values of pressure ($P_s$) reproduce what is observed experimentaly, in the sense that $P_s$ for the system \ce{CO_2}-\ce{[emim][B(CN)_4]} is considerably smaller than the value obtained for \ce{CO_2}-[emim][Tf\textsubscript{2}N].
-
-\begin{figure}[ht]
-\includegraphics[width=\linewidth]{pressure_est.pdf}
-\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, which was modeled according to the force fields of (circles) Koller \textit{et al.} \cite{Koller_2012}, (squares) Batista \textit{et al.} \cite{Batista_2015}, (up triangles) Liu \textit{et al.} \cite{Liu_2014}, and (x) Weber y Kirchner \cite{Weber_2016}.}
-\label{fig:pressure}
-\end{figure}
-
 \section{Concluding remarks}
 \label{sec:conclusion}
+
+One of the goals of this paper was to compare various available models of \ce{[emim][B(CN)_4]} in terms of their capability to reproduce the experimental Henry constant of \ce{CO_2}.
+We have found that only the force field developed by Koller \textit{et al.} \cite{Koller_2012} is able to perform such task, with a small relative error of 2.8 \%.
+A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in that work, which also allows to accurately reproduce the experimental density of the pure substance.
+
+We focused also on exploring alternative simulation strategies with the goal of gaining computational efficiency.
+Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, we concluded that the DSF method with $\alpha$ = 0.2 {\AA}$^{-1}$ is a suitable strategy.
+Other improvement was the use of rigid bodies to simulate \ce{[emim][B(CN)_4]}.
+This required preliminary simulations in order to examine the flexibility of the ethyl chain in \ce{[emim]^+} and the analysis was greatly facilitated by employing useful visualization tools.
+It should be remarked that the different models presented a different behavior, as well; reflecting ?
+
+The solvation free energy results at infinite-dilution condition suggest a slightly more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in  \ce{[emim][NTf_2]}.
+However, this picture completely changes at high concentrations: the simulations correctly predicted a considerable lower pressure to dissolve a certain mass of \ce{CO_2} in \ce{[emim][B(CN)_4]}.
+
+Finally, we employed the model of Koller \textit{et al.} \cite{Koller_2012} to predict infinite-dilution activity coefficient of various solutes.
+In this case, the results were not satisfactory given the high errors associated to the free energy calculations of the pure solutes, making necessary a revision of the force fields for the solutes in a future work.
 
@@
 \end{document}
-%rigid treatment of the imidazolium ring \cite{Kobrak_2004,Lynden_Bell_2006}\cite{Rey_Castro_2007}
-
-%\begin{equation}
-%\begin{split}
-%\Delta G_{\text{sim}} - k_b T \ln \left( \frac{V^{\ast}}{V_1} \right) &= k_b T \ln \left(\frac{P_s}{x_s} \frac{1}{\tilde{\rho}_{\scaleto{LI}{4pt}}} \right) \\
-%&= k_b T \ln \left( \frac{K_s}{\tilde{\rho}_{\scaleto{LI}{4pt}} R T} \right),
-%\end{split}
-%\end{equation}

### 2018-08-06 ionic_liquids.tex

@@
 
-In Table \ref{table:henry} we present the results of solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}.
+In Table \ref{table:henry} we present the results of the solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}.
 Table~\ref{table:henry} also contains the experimental $K_s$ reported by Mahurin \textit{et al.} \cite{Mahurin_2010} and Finotello \textit{et al.} \cite{Finotello_2008}.
@@
 \begin{threeparttable}
-\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at T = 298.15 K and P = 1 atm.
+\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at $T$ = $298.15~\text{K}$ and $P$ = $1~\text{atm}$.
 The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
@@
 If we compare Figs.~\ref{fig:sdf_ions} (a) and (b), one notes that the region with a low probability of finding an ion is larger for \ce{[emim][NTf_2]}.
-Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.
+Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.~\ref{fig:sdf_ions} (c).
 \begin{figure}[ht]
@@
 
-Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].
-The differences in the \ce{CO_2} molar fractions in this case exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, mentioned at the introduction of this paper.
+Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table~\ref{table:solv}, which correspond to similar values of \ce{CO_2} molality.
+Note that the differences in the \ce{CO_2} molar fractions clearly exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, which was mentioned at the introduction of this paper.
 
@@
 \begin{threeparttable}
-\caption{Thermodynamic conditions employed in the simulations of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]~\cite{Makino_2014,Schilderman_2007}}
+\caption{Thermodynamic conditions employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}~\cite{Makino_2014,Schilderman_2007}.}
 \begin{tabular}{ c  c  c  c  c  }  
@@
 
-In Fig.~\ref{fig:pressure} we show for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
+For each system, in Fig.~\ref{fig:pressure} we show our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
 The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
 Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably lower for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
-In addition, we see that for  this system the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
-The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] were -0.755 $\pm$ 0.01 kcal/mol and -0.542 $\pm$ 0.005, respectively.
-However, since we employed a different molecule number of \ce{CO_2}, we cannot draw any conclusion regarding the presence of strong interactions with \ce{[emim][B(CN)_4]} that could explain the higher solubility.
+In addition, we see that in this case the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
+The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} were -0.755 $\pm$ 0.01 kcal/mol and -0.542 $\pm$ 0.005, respectively.
+However, since we simulated a different molecule number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could be a factor contributing to the higher solubility.
 
@@
 \includegraphics[width=\linewidth]{pressure_est.pdf}
-\caption{ \ce{CO_2} \ce{[emim][B(CN)_4]} Koller \textit{et al.} \cite{Koller_2012}, (squares)}
+\caption{Prediction of the gas-phase fugacity and partial pressure of \ce{CO_2} for the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}.}
 \label{fig:pressure}
@@
 Note that only in the case of ethanol we successfully predicted the $\Delta G^{0}_\text{exp}$.
-The relative errors for the other solutes is around 10\%.
+The relative errors for the other solutes are around 10\%.
 
@@
 \begin{threeparttable}
-\caption{Solvation free energy at $T = 298.15~/text{K}$ for the pure solutes benzene, hexane, cyclohexane, ethanol and water.}
+\caption{Solvation free energy at $T = 298.15~\text{K}$ for the pure solutes benzene, hexane, cyclohexane, ethanol and water.}
 \begin{tabular}{ c c c c c c c c }
@@
 \begin{threeparttable}
-\caption{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]} at $T = 298.15~/text{K}$ of the pure solutes benzene, hexane, cyclohexane, ethanol, and water.}
+\caption{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]} at $T = 298.15~\text{K}$ of the pure solutes benzene, hexane, cyclohexane, ethanol, and water.}
 \begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  

### 2018-08-06 supp_material.tex
Supp Info

--- 2018-08-04 ionic_liquids.tex
@@
-%\documentclass[3p,preprint]{elsarticle}
-\documentclass[3p,twocolumn]{elsarticle}
-\usepackage[colorlinks,citecolor=blue]{hyperref}
-\usepackage{lineno}
-\usepackage{amsmath}
-\usepackage{ifthen}
-\usepackage{commath}
-\usepackage{amssymb}
-\usepackage{scalerel}
+\documentclass[3p,onecolumn]{elsarticle}
+
 \usepackage{natbib}
 \usepackage[version=4]{mhchem}
-
-\usepackage{adjustbox}   
-\usepackage{threeparttable}
-\usepackage{booktabs}
-\usepackage{colortbl} 
-\usepackage{xcolor}
-\usepackage{mhchem}
-
-\newcommand{\diff}[2]{\dfrac{\partial #1}{\partial #2}}
-
-\usepackage{amsmath}
-\usepackage{commath}
 \usepackage{graphicx,bm}
-\usepackage{epstopdf}
-\usepackage{float}
-\biboptions{sort&compress}
-\modulolinenumbers[5]
-\usepackage{subfig}
-
-\usepackage[T1]{fontenc}
-
 \journal{Journal of \LaTeX\ Templates}
 
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
 \bibliographystyle{elsarticle-num}
@@
 
-\title{A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
+\title{Supporting material for ``A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}''}
 
@@
 \cortext[cor1]{Corresponding author}
-
-\begin{abstract}
-In this paper, we calculate solvation free energies in ionic liquids and predict macroscopic properties required in the design of chemical processes.
-Carbon dioxide from combustion processes is one of the main sources of anthropogenic generation of greenhouse gases.
-On the other hand, the potential of \ce{[emim][B(CN)_4]} for its capture has recently been reported.
-For comparison, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} are analyzed, both at infinite dilution and at high concentrations of \ce{CO_2}.
-Our results confirm what is experimentally observed, namely a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}.
-The infinite-dilution activity coefficients of hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} are also calculated, and a comparison is made with experimental values recently reported in literature.
-\end{abstract}
-
-\begin{keyword}
-ionic liquids \sep solvation free energy \sep  \ce{CO_2} Henry constant \sep infinite-dilution activity coefficient 
-\end{keyword}
-
 \end{frontmatter}
 
-\linenumbers
-
-\section{Introduction}
-\ce{CO_2} emissions from fossil-fuel power generation plants account for a large portion of the anthropogenic greenhouse gases \cite{totalenergy}.
-International efforts aimed at regulating and reducing \ce{CO_2} emissions are increasing \cite{Tong_2018} and, in this context, the development of technologies for the capture and storage of \ce{CO_2} plays an essential role \cite{Markewitz_2014}.
-
-The conventional process for \ce{CO_2} removal comprises a chemical absorption followed by stripping at high temperatures.
-The most commonly used solvents are volatile organic compounds, specially aqueous solutions of monoethanolamine (MEA).
-Despite its high absorption capability, the use of MEA suffers from a serious drawback due to the high cost of solvent recovery \cite{Merkel_2010}.
-Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes to increase the environmental pollution and generates extra costs for replacing the solvent.
-
-The use of ionic liquids (ILs) as solvents for \ce{CO_2} sequestration occupies a central place in the investigation of alternative technologies.
-The reasons are their well known properties, such as their almost negligible vapor pressure and high thermal stability.
-Furthermore, they are particularly attractive since they can be designed for specific applications, giving rise to the so-called task-specific ILs \cite{Seo_2014}.
-These remarkable properties makes ILs suitable for a wide variety of applications in separation processes \cite{Han_2010,Werner_2010}, catalysis \cite{P_rvulescu_2007}, energy \cite{MacFarlane_2014}, and material science \cite{Mecerreyes_2011,Tom_2015,Dupont_2010,Leones_2017,Kinik_2017}.
-
-Recently, the potentiality of ILs for \ce{CO_2} capture has been called into question by Carvalho \textit{et al.} \cite{Carvalho_2016}, who warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposed absorption capability of certain ILs.
-Although most thermodynamic models are formulated in terms of molar fraction, a key factor that dictates the absorption process efficiency is given by the amount of \ce{CO_2} that can be dissolved in a certain \textit{volume} or \textit{mass} of solvent.
-By expressing the solubility values in terms of molality and performing an exhaustive comparison between various ILs, Ref.
-\cite{Carvalho_2016} shows that most systems which promote a physical absorption of \ce{CO_2} exhibit a solubility similar, or even lower, than that observed for the heavy alkane eicosane.
-This is true for the ``popular'' \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}; the only exception being the family of ILs containing the anion tetracyanoborate \ce{[B(CN)_4]^-}.
-
-There is no obvious explanation accounting for the enhanced solubility promoted by the presence of \ce{[B(CN)_4]^-}.
-In this context, molecular simulation provides with a powerful tool for studying solvation processes.
-To the best of our knowledge, only one study in literature reports the free energy of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} \cite{Liu_2014_1} which, in addition, is overestimated.
-This motivated us to evaluate different force fields of \ce{[emim][B(CN)_4]} and, as we will show below, it was possible to find a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2}.
-For comparison, \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both at infinite dilution and at high concentrations of \ce{CO_2}.
-The simulations confirmed what is observed in experiments: for \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}.
-The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} were also calculated, and a comparison was made with experimental values recently reported in literature.
-
-This paper is organized as follows: in Sec.~\ref{sec:theory} we present the theoretical background, which is followed by a brief description of the force fields used in this work.
-The methodological details are provided in Sec.~\ref{sec:sim_details} and the corresponding numerical results are given in Sec.~\ref{sec:results}.
-Finally, we present some concluding remarks in Sec.~\ref{sec:conclusion}.
-
-\section{Theoretical background}
-\label{sec:theory}
-
-In this section, we present the formalism that allows us to compute the Henry constant and activity coefficient, both at infinite dilution, from the simulated free energy.
-For this, we rely on the work of Shirts \textit{et al.} \cite{Shirts_2003}.
-Then, we reformulate the equations in order to study concentrated solutions, which would be the more likely scenario in \ce{CO_2} capture processes.
-
-\subsection*{Solvation free energy}
-The solvation free energy, $\Delta G_{\text{solv}}$, is defined as the reversible work needed to transfer a solute molecule from the gas phase to the solution.
-For dense systems, an efficient computation of solvation properties via molecular simulation is possible by means of the so-called alchemical methods, which employ non-physical pathways to connect the ``endpoint'' states, whose free energy difference is to be estimated.
-In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through the use of a coupling parameter $\lambda$, which scales the intermolecular interactions taking values in the interval [0,1]: $\lambda$ = 1 corresponds to a fully interacting system, while for $\lambda$ = 0 the interactions between the solute and solvent molecules are completely turned-off.
-
-In the following, the subscripts ``$s$'' and ``$\text{IL}$'' refer to the solute and the solvent (ionic liquid), respectively.
-For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
-\begin{equation}
-\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 0)}, 
-\end{equation}
-where superscript ``$l$'' refers to the liquid solution, $\bigtriangleup$ denotes the isobaric-isothermal partition function, and $k_b$ is the Boltzmann's constant.
-Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy.
-They found out that
-\begin{equation}
-\begin{split}
-\label{eq:free_solv}
- \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
-\end{split}
-\end{equation}
-where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid phase and $P_s$ is the partial pressure of the solute in the gas phase.
-It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.
-
-For small solutes, such as those considered in this work, the magnitude of the term $V^{\ast}/V_1$ is typically on the order of the free energy uncertainties \cite{Shirts_2003}.
-Hence, that term can be neglected and will be omitted hereafter.
-
-\subsection*{Henry constant}
-If both $P_s$ and $c_s^{\ast}$ were not large, we can resort to Eq.~\eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
-\begin{equation}
-\text{K}_s =\frac{P_s}{x_s}.
-\end{equation}
-Therefore, by simply expressing Eq.~\eqref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that MW (molecular weight of the solution) = $\text{MW}_{\scaleto{IL}{4pt}}$, as well as $\rho$ (mass density of the solution) = $\rho_{\scaleto{IL}{4pt}}$, we obtain that
-\begin{equation}
-\label{eq:henry_eq}
-K_s = \tilde{\rho}_{\scaleto{IL}{4pt}} R \, T \exp(\beta \, \Delta G_{\text{sim}}),
-\end{equation}
-where $\tilde{\rho}_{\scaleto{IL}{4pt}}$ is the molar density of the solvent and $R$ is the gas constant.
-
-\subsection*{Infinite-dilution activity coefficient}
-
-As will be shown below, the prediction of activity coefficients requires extra simulations involving the pure solute.
-In what follows, we use the superscript ``$0$'' to denote the pure solute properties.
-
-Using standard thermodynamic relations \cite{Tester}, we write the activity coefficient $\gamma_s$ in terms of residual chemical potentials, as follows:
-\begin{equation}
-\label{eq:gamma}
-\ln \gamma_s = \frac{1}{RT} (\mu_s^R - \mu_s^{R,0}),
-\end{equation}
-where $\mu_s^R$ and $\mu_s^{R,0}$ are the residual chemical potentials of the solute in the solution and in the pure solute, respectively.
-It is worth noting that we have used the definition $\mu_s^{R}$ (P,T) = $\mu_s$ (P,T) - $\mu_s^{ig}$ (P,T), where the superscript $ig$ refers to a solution of ideal gases.
-Also, recall that $\mu_s^{ig} (P,T)$ = $\mu_s^{ig,0} (P,T)$ + $RT \ln x_s$, so we have that
-\begin{equation}
-\mu_s^R = \mu_s^l(N_s^l,N_{LI},P,T) - \mu_s^{ig,0}(P,T) - k_b T \ln x_s.
-\end{equation}
-Replacing $\mu_s^{l}$ and $\mu_s^{ig,0}$ by the corresponding expressions derived in Ref.~\cite{Shirts_2003} yields
-\begin{equation}
-\label{eq:mu_res}
-\mu_s^R = \Delta G_{\text{sim}} - k_b T \ln \left( \frac{V^{\ast} P}{N_s^l k_b T} \right) -  k_b T \ln x_s.
-\end{equation}
-Of course, an analogous equation holds for $\mu_s^{R,0}$:
-\begin{equation}
-\label{eq:mu_res_0}
-\mu_s^{R,0} = \Delta G_{\text{sim}}^{0} - k_b T \ln \left( \frac{V^{\ast,0} P}{N_s^{l,0} k_b T} \right).
-\end{equation}
-
-If one makes $N_s^{l}$ = 1, and substitute Eqs.~\eqref{eq:mu_res} and~\eqref{eq:mu_res_0} into Eq.~\eqref{eq:gamma}, the infinite-dilution activity coefficient, $\gamma^{\infty}_s$, can be predicted according to the following equation:
-\begin{equation}
-\label{eq:gamma_inf}
-\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_{\text{sim}} - \Delta G_{\text{sim}}^{0} \right) + \frac{c_{\scaleto{LI}{4pt}}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
-\end{equation}
-where $c_{\scaleto{IL}{4pt}}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ are the numerical densities of the solvent and the pure solute, respectively.
-
-\subsection*{Partial pressure estimation}
-\label{sec:partial_pressure}
-
-For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} are found at pressure values for which, in principle, the ideal gas assumption may be not valid.
-In this case, we shall correct the ideal gas contribution to the chemical potential, as follows
-\begin{equation}
-\label{eq:mu_gas_real}
-\mu^{g}_s = \mu^{ig}_s + RT \ln \phi_s,
-\end{equation}
-where $\phi_s$ is the fugacity coefficient of the solute.
-This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate $\mu^{l}_s$ = $\mu^{g}_s$, which yields
-\begin{equation}
-\label{eq:fgas_d}
-f^{g}_s = \exp  \left( \beta \Delta G_{\text{sim}} \right) +  k_b T c_s^{\ast}, 
-\end{equation}
-where $f^{g}_s$ is the fugacity of the solute in the gas phase.
-Having calculated $f^{g}_s$, $P_s$ can be predicted using the following equation
-\begin{equation}
-\label{eq:fgas}
-f^{g}_s = P_s \exp\left[ \frac{B_s(T) P_s}{R T} \right],
-\end{equation}
-where $B_s$ corresponds to the second virial coefficient.
-Here, we employ the correlation of $B_s$ for \ce{CO_2} introduced by Holste \textit{et al.} \cite{Holste_1987}, which is
-\begin{equation}
-B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
-\end{equation}
-where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = -2.455297 $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol).
-
-As supported by preliminary simulations, it seems reasonable to assume $\Delta G_{\text{sim}}$ as independent of pressure over the range of experimental data considered in this work.
-Then, the equilibrium pressure is determined by directly solving Eq.~\eqref{eq:fgas} for $P_s$.
-
-\section{Force fields}
-\label{sec:force_field}
-\subsection{Ionic liquids}
-\label{sec:force_field_il}
-
-The versatility of ILs for different applications is in part due to the fact that their physical properties strongly depend on the particular cation-anion combination.
-On the other hand, this feature also explains why the desirable transferability of force fields is particularly difficult to attain.
-Indeed, it is a common practice to extract the potential parameters of the intramolecular (bond stretching, angle bending, torsion rotation) and Lennard-Jones (LJ) interactions from a well established force field and, then, only derive the partial atomic charges with the aim of ``adjusting'' the model for a specific pair of ions.
-This procedure is, however, inaccurate as in conventional force fields the determination of the atomic charges precedes the dihedrals parametrization.
-Another ad-hoc strategy, which intends to crudely incorporate polarization effects, is to scale the partial charges uniformly with a factor which normally takes values in the range 0.8-0.9.
-This has proven to be effective for predicting dynamic properties \cite{Schr_der_2012}.
-
-In this paper, we consider four models of \ce{[emim][B(CN)_4]}.
-Koller \textit{et al.} \cite{Koller_2012} were the first to introduce a specific non-polarizable force field for that IL.
-They tested three variations of a \textit{united-atoms} model, in which the alkyl groups \ce{CH_3} and \ce{CH_2} of \ce{[emim]^+} are replaced by pseudo-atoms.
-Among them, the ``FF-3'' model best reproduces the experimental values of density, self-diffusion coefficients and viscosity.
-In short, both the intramolecular and LJ parameters of the cation were taken from the work of Liu \textit{et al.} \cite{Liu_2006}, which in turn is based on the AMBER \cite{Cornell_1995} framework.
-The intramolecular parameters involving the boron atom were extracted from the DREIDING \cite{Mayo_1990} force field and the anionic vdW parameters were refined based on the values reported by Price \textit{et al.} \cite{Price_2001}.
-The atomic partial charges were derived using the EA-RESP method \cite{Basma_2001} from \textit{Post-Hartree-Fock ab-initio} calculations at MP2/6-31G$^\ast$+ level of theory, which automatically resulted in total charges on the ions of $\pm$0.8426$e$.
-
-The potential parameters of \ce{[B(CN)_4]^-} derived by Koller \textit{et al.} \cite{Koller_2012} were then used by Batista \textit{et al.} \cite{Batista_2015} to study aqueous solutions of \ce{[emim][B(CN)_4]}.
-In this case, the authors considered the \textit{all-atom} model of \ce{[emim]^+} developed by Cadena and Maginn \cite{Cadena_2006}.
-The atomic partial charges were obtained using the CHELP procedure \cite{Breneman_1990}, resulting in net charges of $\pm$0.889$e$ on the ions.
-It should be noted that the factors for scaling the 1-4 non-bonded interactions are different for these force fields: Cadena and Maginn \cite{Cadena_2006} apply factors of 1.0 and 0.4 for the LJ and Coulombic interactions, respectively; while in Koller \textit{et al.} \cite{Koller_2012} the corresponding values are 0.5 and 5/6, in accordance with the AMBER force field.
-Batista \textit{et al.} \cite{Batista_2015} used the first ones (J.P. Coutinho, personal communication).
-
-Another set of parameters for \ce{[emim][B(CN)_4]} was derived by Liu \textit{et al.} \cite{Liu_2014} in a study that investigates the dynamics of \ce{CO_2} and \ce{N_2} in that IL.
-Parameters corresponding to the intramolecular and LJ interactions were extracted from GAFF \cite{Wang_2004}, while the atomic partial charges were computed using the RESP method \cite{Bayly_1993} from \textit{DFT}/B3LYP/6-311+G(d) calculations.
-The net charges of the ions were manually adjusted to a value of $\pm$0.8$e$.
-
-We also consider the parametrization reported by Weber and Kirchner \cite{Weber_2016}, which is based on the force field developed by P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}.
-The potential parameters for the anion are not specified in Refs.~\citenum{Weber_2016} and~\citenum{Canongia_Lopes_2006}, and we obtained them by a direct communication with the authors of Ref.~\citenum{Weber_2016}.
-The atomic partial charges were derived using the RESP procedure from \textit{Hartree-Fock} calculations at 6-31++G$^{\ast \ast}$ level of theory, resulting in net charges of $\pm$0.8$e$.
-
-Finally, for [emim][Tf\textsubscript{2}N] we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which was derived by refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
-This refining was characterized by their authors as ``unusual'', given that the LJ parameters were modified, while keeping the partial charges at their original values.
-This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry constants of \ce{CO_2} at several temperatures.
-
-\subsection{Solutes}
-\label{sec:force_field_sol}
-
-The solutes considered in this work are hexane, benzene, \ce{CO_2}, ethanol, cyclohexane and water.
-Hexane and benzene were modeled using the OPLS-AA force field \cite{Jorgensen_1996}, while the TRAPPE potential \cite{Chen_2001,Potoff_2001} was employed for ethanol and \ce{CO_2}.
-Cyclohexane was simulated using a rigid-body model \cite{munoz2015lennard} whose sites only interact via a LJ potential
-For water, we employ the TIP4P/2005 model \cite{Abascal_2005,Vega_2011}.
-
-\section{Computational methods}
-\label{sec:sim_details}
-
-With the aim of setting up a computationally efficient protocol for the ILs, in this work we assess the possibility of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method \cite{Fennell2006} for computing the electrostatic interactions.
-As an alternative to the Ewald schemes \cite{Ewald_1921,Darden_1993,Hockney_1988}, McCann \textit{et al.} \cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force fields.
-They concluded that using $\alpha$ = 0.2 {\AA}$^{-1}$ and a cutoff distance ($r_c$) of 15 {\AA} provide the best energetic agreement with the Ewald method.
-In this work, comparisons are made in terms of the simulated densities and radial distribution functions for which, as will be shown in the next section, $\alpha$ = 0.2 {\AA}$^{-1}$ and $r_c$ = 12 {\AA} resulted in a good agreement.
-These values were also employed for the charged solutes, with the exception of hexane, for which we applied undamped Coulombic interactions improving the prediction of the chemical potential.
-
-The NPT algorithm of Kamberaj \textit{et al.} \cite{Kamberaj_2005} was used to perform the simulations with rigid bodies.
-For flexible molecules, we applied the scheme due to Shinoda \textit{et al.} \cite{Shinoda2004} and C-H bonds were constrained by the SHAKE method \cite{Ryckaert1977}.
-For both integrators, we used a time-step size ($\Delta t$) of 1 fs.
-
-The gradual insertion/deletion of charged solutes involves scaling both the van der Waals (vdW) and the electrostatic intermolecular interactions.
-In order to avoid numerical instabilities associated to the vdW scaling, a standard approach is to employ a soft-core potential with a nonlinear coupling.
-In this paper we use the modified LJ potential due to Beutler \textit{et al.} \cite{Beutler_1994}.
-The electrostatic interactions, on the other hand, can be handled by a linear scaling \cite{Naden_2015}.
-Furthermore, the contributions to $\Delta G$ originating at the different couplings are taken into account separately, as follows:
-\begin{equation}
-\begin{split}
-\Delta G_{\text{sim}} =& \; \Delta G_{\,\text{vdW}} (\lambda_{\,\text{vdW}} = 0\rightarrow  1, \lambda_{\, \text{Coul}} = 0) \\
-+ \; &\Delta G_{\,\text{Coul}} (\lambda_{\, \text{vdW}} = 1,\lambda_{\,\text{Coul}} = 0 \rightarrow 1),
-\end{split}
-\end{equation}
-where $\lambda_{\,\text{vdW}}$ and $\lambda_{\,\text{Coul}}$ are the coupling parameters of the soft-core and electrostatic potentials, respectively.
-Note that in the process of coupling the vdW interactions, the Coulombic interactions are turned-off, while we set $\lambda_{\,\text{vdW}}$ = 1 when computing $\Delta G_{\,\text{Coul}}$.
-This results in the ``end-point'' states given by ($\lambda_{\,\text{vdW}}$=0,$\lambda_{\,\text{Coul}}$=0) and ($\lambda_{\,\text{vdW}}$=1,$\lambda_{\,\text{Coul}}$=1), as expected.
-The complete sets of the coupling parameters we use here are $\lambda_{\text{vdW}}$ = $\{0.0$, $0.05$, $0.1$, $0.2$, $0.25$, $0.3$, $0.35$, $0.4$, $0.45$, $0.5$, $0.6$, $0.7$, $0.8$, $0.9$, $1.0\}$ and $\lambda_{\text{Coul}}$ = $\{0.0$, $0.1$, $0.4$, $0.7$, $0.1\}$.
-
-In this work, we carried out independent simulation at each state of $\lambda_{\text{Coul}}$, while the expanded ensemble (EE) method~\cite{Lyubartsev_1992} was applied for sampling the $\lambda_{\,\text{vdW}}$ set.
-In short, an EE is constructed as a weighted sum of subensembles, each assuming a different value of the variable chosen to explore the free energy landscape, which in our case is $\lambda_{\,\text{vdW}}$.
-This way, the sampling of an EE comprises both sampling each subensamble with fixed variables (N,P,T,$\lambda_{\,\text{vdW}}$) and transitions in $\lambda_{\,\text{vdW}}$.
-Thus, a remarkable feature of the EE method is the possibility of exploring the whole alchemical route in a single simulation.
-In this work, we perform a sequential sampling of the EE \cite{Chodera_2011_2}, which consists in sampling each subensamble via NPT molecular dynamics (MD) for a determined number of steps $N^{\text{EE}}$ followed by an attempt to change $\lambda_{\,\text{vdW}}$ using MC, and so on.
-The $\lambda_{\,\text{vdW}}$ transitions are performed according to an independent sampling scheme \cite{Chodera_2011_2}.
-In addition, the set of (arbitrary) weights $\eta$ of the subensambles enters in the acceptance criteria of MC, so it is possible to tune $\eta$ in order to enhance the sampling.
-If differences $\eta_i$ - $\eta_j$ were closed to $\Delta G_{ji}$, we expect an uniform sampling in $\lambda_{\,\text{vdW}}$ \cite{Lyubartsev_1992}.
-Of course, this can be achieved only iteratively.
-The EE procedure, together with the \textit{soft-core} potential and the DSF method with linear coupling were implemented in the LAMMPS software package \cite{Plimpton1995}, which we used for carrying out all the simulations.
-
-As demonstrated in Ref.~\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ yield more decorrelated samples in each subensemble.
-In this work, we employ $N^{EE}$ = 5 which, together with the specified $\lambda_{\, \text{vdW}}$ set, resulted to be satisfactory as up to 3 preliminary runs of the EE were enough to determine the weights $\eta$ that yielded, in a final simulation, a ``sufficient'' sampling of each subensamble.
-By ``sufficient'', we mean that the sampling provides an acceptable uncertainty in $\Delta G$.
-The simulation times for the preliminary and final EE runs were 10 and 40 ns, respectively; and each $\lambda_{\text{Coul}}$ state was simulated for 10 ns.
-Finally, the MBAR method \cite{Shirts_2008}, as implemented by Klimovich \textit{et al.} \cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$.
-
-The initial configurations were obtained with PLAYMOL \cite{playmol}, a software integrated with PACKMOL \cite{Mart_nez_2009}, using the tool \textit{build} to specify geometric data (bond and angle lengths, and dihedral angles), from which PLAYMOL automatically determines the Cartesian coordinates.
-We first carried out NVT MD simulations of the isolated ion pairs in order to obtain a minimum energy conformation.
-For this, we used the Nos\'{e}-Hoover thermostat \cite{Martyna1992} and a cubic box of length L = 50 {\AA} with non-periodic boundary conditions.
-After a short run with $\Delta t$ = $0.5~\text{fs}$, we carried out a ``quenching'' simulation with $\Delta t$ = $1 ~\text{fs}$, in which the temperature is gradually reduced until reaching a value close to $0~\text{K}$.
-The resulting coordinates were then specified in PLAYMOL \cite{playmol} to build the configurations of the liquid phases.
-
-\section{Results and discussion}
-\label{sec:results}
-
-\subsection{Simulation strategies of ILs}
-\label{sec:prel_results}
-
-In this section, we present results for the following two cases: (1) flexible ions together with the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for calculating the Coulombic interactions, and (2) ions modeled as rigid bodies with the DSF method \cite{Fennell2006} ($\alpha$ = 0.2 {\AA}$^{-1}$) as the alternative to the PPPM scheme.
-In both cases, $r_c$ = 12 {\AA}.
-The nomenclature used in this paper is shown in Fig~\ref{fig:atoms_id}.
-In the \textit{united-atoms} version of \ce{[emim]^+}, hydrogens ranging from H4 to H11 are eliminated.
-
-The rigid bodies were built after carrying out an analysis of key dihedrals, whose flexibility could lead to significant conformational changes in \ce{[emim]^+} and \ce{[NTf_2]^-}.
-On the other hand, small and highly symmetric anions, such as \ce{PF_6} and \ce{BF_4} are usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies the strategy in the case of \ce{[B(CN)_4]^-}.
-
 \begin{figure}[ht]
-\centering
-\includegraphics[width=\linewidth]{atoms_id.pdf}
-\caption{Adopted nomenclature for 1-ethyl-3-methylimidazolium  (\ce{[emim]^+}), tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
-\label{fig:atoms_id}
-\end{figure}
-
-Using the software TRAVIS \cite{Brehm_2011}, we obtained the combined distribution functions (CDFs) of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs at $T = 298.0~\text{K}$ and $P = 1.0~\text{bar}$.
-In Fig.~\ref{fig:dihedrals_emim} we show the CDFs for each force field of \ce{[emim][B(CN)_4]}.
-A first inspection of this figure reveals a similar behavior of the models due to Koller \textit{et al.} \cite{Koller_2012} and Liu \textit{et al.} \cite{Liu_2014}.
-This was expected as both are based on the AMBER framework \cite{Cornell_1995}.
-In addition, Figs.~\ref{fig:dihedrals_emim}(a) and \ref{fig:dihedrals_emim}(b) are symmetric, which means that atoms C1, N2, and C2 are coplanar.
-In Fig.~\ref{fig:dihedrals_emim}(a), the most likely angles can be found in a narrow region around 90$^{\circ}$ and 270$^{\circ}$.
-Since these angles correspond to an equivalent configuration in the \textit{united-atom} \ce{[emim]^+}, in the case of Koller \textit{et al.} \cite{Koller_2012} we built all the rigid bodies by specifying 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1.
-The other models show a larger flexibility with high probability regions that extend in a broad range of angle values.
-Despite this, it was possible to build more than one type of rigid body by specifying the most probables angles of C6-C5-N2-C1.
-In the case of Liu \textit{et al.} \cite{Liu_2014}, these angles correspond to 90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed 102.6$^{\circ}$ and -102.6$^{\circ}$.
-These two types of rigid bodies were built in equal proportion.
-Fig.~\ref{fig:dihedrals_emim}(d) corresponds to Weber and Kirchner \cite{Weber_2016}. 
-Given the wide range of sampled angles, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of them, respectively; and 0$^{\circ}$ for the remaining 15~\%.
-
-In Table~\ref{table:props_dsf} we present the results of density for the strategies mentioned at the beginning of this section.
-When comparing cases (1) and (2) for each model, we note that the simulated densities practically do not differ.
-In addition, the models of Koller \textit{et al.} \cite{Koller_2012} and Weber and Kirchner \cite{Weber_2016} best reproduce the experimental value.
-We have also computed radial distribution functions (RDFs), which can be found in the Supplementary material.
-The better agreement is found for the models of Koller \textit{et al.} \cite{Koller_2012} and Batista \textit{et al.} \cite{Batista_2015}.
-Despite the small deviations observed for the model of Liu \textit{et al.} \cite{Liu_2014}, the simulation with rigid bodies qualitatively reproduces the RDFs obtained for the flexible ions.
-Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion).
-The model of Weber and Kirchner \cite{Weber_2016}, on the other hand, presents important discrepancies in the RDFs of the pairs C5(cation)-N(anion) and C2(cation)-B(anion) when using rigid bodies.
-That is why, in this case only the imidazolium ring was considered rigid and the ethyl chain was left unconstrained.
-
-\begin{figure*}
-\centering
-\subfloat[Koller~\textit{et al.}~\cite{Koller_2012}]{%
-  \includegraphics[width=.4\linewidth]{koller.png}}%
-\subfloat[Batista~\textit{et al.}~\cite{Batista_2015}]{%  
-  \includegraphics[width=.4\linewidth]{batista.png}}%
-
-\subfloat[Liu~\textit{et al.}~\cite{Liu_2014}]{%
-  \includegraphics[width=.4\linewidth]{Liu.png}}%
-\subfloat[Weber and Kirchner~\cite{Weber_2016}]{%
-  \includegraphics[width=.4\linewidth]{Weber.png}}%
-\caption{Combined distribution function of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs for each model of \ce{[emim][B(CN)_4]}.}
-\label{fig:dihedrals_emim}
-\end{figure*}
-
-A study of dihedrals was also carried out for \ce{[emim][NTf_2]}.
-The CDF of the dihedrals angles of C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the results of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 is 0$^{\circ}$.
-This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
-With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.} \cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
-Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
-Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy for building the rigid bodies is required.
-Thus, the simulations of \ce{[emim][NTf_2]} were performed considering flexible ions and the DSF method, which results in a computed density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.
-
-\begin{figure}[ht]
-\centering
-  \includegraphics[width=\linewidth]{Ludwig.png}%
-
-  \includegraphics[width=\linewidth]{Ludwig_anion.png}%
-\caption{Combined distribution function of (a) the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, and (b) of the dihedral angles of the contiguous  C1-S1-N1-S2 and S1-N1-S2-C2 chains, obtained from NPT-MD simulations of 250 molecules of \ce{[emim][NTf_2]}.}
-\label{fig:die_ntf2}
-\end{figure}
-
-\begin{table*}
-\begin{threeparttable}
-\caption{Comparison of predicted and experimental densities for differents models of \ce{[emim][B(CN)_4]} via NPT-MD simulations at $T = 298.0~\text{K}$ and $P = 1.0~\text{atm}$.
-The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
-\begin{tabular}{ c  c  c  c  c}  
-\hline \hline
-$\text{[emim]}$[B(CN)\textsubscript{4}] &  $\rho_{\text{sim}}$ & error (\%)\tnote{a}  & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
-model & (g/cm$^{3}$) &  &  (g/cm$^{3}$) &  \\
-			\hline
-& \multicolumn{2}{c}{Flexible ions/Ewald method} & \multicolumn{2}{c}{Rigid ions/DSF method} \\
-Koller y col. \cite{Koller_2012}    & 1.046 & 1.0 & 1.038 & 0.2 \\
-Batista y col. \cite{Batista_2015}  & 0.989 & 4.6 & 0.988 & 4.7 \\
-Liu y col. \cite{Liu_2014}          & 1.001 & 3.4 & 0.991 & 4.4 \\
-Weber y Kirchner. \cite{Weber_2016} & 1.015 & 2.1 & 1.022 & 1.4  \\
- \hline \hline
-\label{table:props_dsf} 
-\end{tabular}
-\begin{tablenotes}
-\item[a] error = 100 $\times$($\rho^{\text{exp}}$$ - $$\rho^{\text{sim}}$)/$\rho^{\text{exp}}$.
-\end{tablenotes}
-\end{threeparttable}
-\end{table*}
-
-\subsection{Henry constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
-\label{sec:henry_results}
-
-In Table \ref{table:henry} we present the results of solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}.
-Table~\ref{table:henry} also contains the experimental $K_s$ reported by Mahurin \textit{et al.} \cite{Mahurin_2010} and Finotello \textit{et al.} \cite{Finotello_2008}.
-The uncertainties in $K_s$ were calculated using standard error propagation.
-
-\begin{table*}
-\centering
-\begin{adjustbox}{width=1\textwidth}
-\begin{threeparttable}
-\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at T = 298.15 K and P = 1 atm.
-The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
-\begin{tabular}{ c c c  c  c  c  c }  
-\toprule
-Model & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
-& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
-			\hline
-			\multicolumn{4}{c}{\ce{[emim][B(CN)_4]}} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
-			\hline
-Koller \textit{et al.} \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
-Batista \textit{et al.} \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
-Liu \textit{et al.} \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
-Weber y Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
-\hline
-		\multicolumn{4}{c}{[emim][Tf\textsubscript{2}N]} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
-		\hline
- K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
- \bottomrule
-\label{table:henry} 
-\end{tabular}
-\begin{tablenotes}
-\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
-\end{tablenotes}
-\end{threeparttable}
-\end{adjustbox}
-\end{table*}
-
-It should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent sampling of $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
-Moreover, the $\Delta G_{\text{sim}}$ in [emim][Tf\textsubscript{2}N] is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
-These consistencies have served for validating the methodological approaches of this work.
-
-From Table \ref{table:henry} one can see that the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental value of $K_s$.
-If we look at the $\Delta G_{\lambda_{\,\text{vdW}}}$ profiles in Fig.~\ref{fig:deltag}, we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014} the maximum occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which may also explain their failure to reproduce the experimental density.
-
-\begin{figure}[ht]
-\includegraphics[width=\linewidth]{free_energy_paper}
-\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, which was modeled according to the force fields of (circles) Koller \textit{et al.} \cite{Koller_2012}, (squares) Batista \textit{et al.} \cite{Batista_2015}, (up triangles) Liu \textit{et al.} \cite{Liu_2014}, and (x) Weber y Kirchner \cite{Weber_2016}.}
-\label{fig:deltag}
-\end{figure}
-
-The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf\textsubscript{2}]}.
-The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm this result.
-The SDFs of the ions around a \ce{CO_2} molecule were obtained by using the software packages TRAVIS \cite{Brehm_2011} and VMD \cite{HUMP96}.
-For that, we carried out NPT-MD simulations of \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] systems with a \ce{CO_2} molar fraction of 0.1.
-The isovalues were visually determined so as to observe the first solvation shell.
-If we compare Figs.~\ref{fig:sdf_ions} (a) and (b), one notes that the region with a low probability of finding an ion is larger for \ce{[emim][NTf_2]}.
-Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.
-\begin{figure}[ht]
-\centering
-\subfloat[]{%
-  \includegraphics[width=\linewidth]{kollerall.pdf}%
-}
-
-\subfloat[]{%
-  \includegraphics[width=\linewidth]{ludwigall.pdf}%
-}
-
-\subfloat[]{%
-  \includegraphics[width=\linewidth]{anionanion.pdf}%
-}
-\caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[NTf_2]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
-Fig. (c) corresponds to the SDFs of the anions plotted together.}
-\label{fig:sdf_ions}
-\end{figure}
-
-\subsection{Inifinite-dilution activity coefficient in \ce{[emim][B(CN)_4]}}
-\label{sec:act_results}
-
-Having selected the model of \ce{[emim][B(CN)_4]} that best reproduces the experimental $K_s$ of \ce{CO_2}, we next calculate the infinite-dilution activity coefficients ($\gamma^{\, \infty}$) of benzene, hexane, cyclohexane, ethanol and water in \ce{[emim][B(CN)_4]}.
-
-The task of accurately predicting $\gamma^{\, \infty}$ is challenging since, according to Eq.~\eqref{eq:gamma_inf}, one should reproduce the solvation free energies in both the pure solute and the solvent.
-In Table~\ref{table:mu_solutes} we show the simulated densities and the solvation free energies $(\Delta G^{0}_{\text{sim}})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}.
-It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ for cyclohexane.
-Note that only in the case of ethanol we successfully predicted the $\Delta G^{0}_\text{exp}$.
-The relative errors for the other solutes is around 10\%.
-
-The results of $\gamma^{\, \infty}$ are presented in Table~\ref{table:gamma}.
-For benzene and water, the predictions are very accurate, but this may be due to fortuitous error compensations given the divergences shown in Table~\ref{table:mu_solutes}.
-From Table \ref{table:gamma}, one sees that the experimental $\gamma^{\, \infty}$ for hexane at $298.15~\text{K}$ and $303~\text{K}$ considerably differ.
-It is therefore difficult to assess the reliability of our results in this case.
-
-\begin{table*}
-\centering
-\begin{adjustbox}{width=1\textwidth}
-\begin{threeparttable}
-\caption{Solvation free energy at $T = 298.15~/text{K}$ for the pure solutes benzene, hexane, cyclohexane, ethanol and water.}
-\begin{tabular}{ c c c c c c c c }
-\toprule
-Solute & $\rho_{\text{sim}}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
- & (g/cm$^{3}$) &  & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   &  \\
-\hline
-benzene OPLS-AA   & 0.8611 $\pm$ 0.0002 & 1.4 & -3.75  $\pm$ 0.02 & -0.381 $\pm$ 0.007 & -4.14 $\pm$ 0.02 & -4.56 & 9.32  \\
-hexane OPLS-AA    & 0.6513 $\pm$ 0.0003 & 0.5 & -3.67  $\pm$  0.03 & 0.011 $\pm$ 0 & -3.66 $\pm$ 0.03 & -4.06 & 9.90 \\
-cyclohexane & 0.7692 $\pm$ 0.0007 & 0.6 & -4.39 $\pm$ 0.01 & 0 & -4.39 $\pm$ 0.01 & - & -  \\
-ethanol TRAPPE-UA   & 0.781 $\pm$ 0.008 & 1.01  &-0.93 $\pm$ 0.01 & -4.15 $\pm$ 0.02  & -5.08  $\pm$ 0.02  & -5.08 & 0 \\
-water TIP4P/2005   &  0.9948 $\pm$ 0.0003 & 0.2 & 2.015 $\pm$ 0.004 & -9.01 $\pm$ 0.02 & -6.99 $\pm$ 0.02 & -6.33  &10.43 \\
- \bottomrule
-\label{table:mu_solutes} 
-\end{tabular}
-\begin{tablenotes}
-\item[a] error = 100 $\times$ $\abs{(Z^{\text{exp}} - Z^{\text{sim}})/Z^{\text{exp}}}$.
-\end{tablenotes}
-\end{threeparttable}
-\end{adjustbox}
-\end{table*}
-
-\begin{table*}
-\centering
-\begin{adjustbox}{width=1\textwidth}
-\begin{threeparttable}
-\caption{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]} at $T = 298.15~/text{K}$ of the pure solutes benzene, hexane, cyclohexane, ethanol, and water.}
-\begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
-\toprule
-Solute & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
- & (kcal/mol) & (kcal/mol) &  (kcal/mol)  &  & (298.15 K) \cite{Doma_ska_2011} & (303 K) \cite{Yan_2010} \\
-\midrule % inserts single-line
-hexane OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
-cyclohexane& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
-benzene OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
-ethanol TRAPPE-UA& -0.73 $\pm$ 0.02 & -4.10 $\pm$ 0.04 & -4.83 $\pm$ 0.04 & 0.41 $\pm$ 0.03 & 1.58 & 1.64  \\
-water TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
- \bottomrule
-\label{table:gamma} 
-\end{tabular}
-\end{threeparttable}
-\end{adjustbox}
-\end{table*}
-
-\subsection{Study of concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]}
-\label{sec:results_conc}
-
-Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table \ref{table:solv}, which correspond to close values of \ce{CO_2} molality in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N].
-The differences in \ce{CO_2} molar fractions for this ILs exemplifies the observations made by Carvalho \textit{et al.} \cite{Carvalho_2016}, mentioned at the introduction of this paper.
-
-\begin{table*}
-\centering
-\begin{threeparttable}
-\caption{Thermodynamic conditions employed in the simulations of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]~\cite{Makino_2014,Schilderman_2007}}
-\begin{tabular}{ c  c  c  c  c  }  
-\toprule
-Ionic liquid & T (K)  & P (atm)  & molar fraction $x_s$ & molality $m_s$ \\
-\midrule		
-$\text{[emim]}$[B(CN)\textsubscript{4}]~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
-$\text{[emim]}$[Tf\textsubscript{2}N]~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
- \bottomrule
-\label{table:solv} 
-\end{tabular}
-\end{threeparttable}
-\end{table*}
-
-In Fig.~\ref{fig:pressure} we show for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
-The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
-Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably smaller for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
-In addition, we see that for  this system the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
-
-\begin{figure}[ht]
-\includegraphics[width=\linewidth]{pressure_est.pdf}
-\caption{ \ce{CO_2} \ce{[emim][B(CN)_4]} Koller \textit{et al.} \cite{Koller_2012}, (squares)}
+\includegraphics[]{rdf-koller}
+\caption{\ce{[emim][B(CN)_4]}}
 \label{fig:pressure}
@@
 
-\section{Concluding remarks}
-\label{sec:conclusion}
+\begin{figure}[ht]
+\includegraphics[]{rdf-Batista.pdf}
+\caption{\ce{[emim][B(CN)_4]}}
+\label{fig:pressure}
+\end{figure}
 
-One of the goals of this paper was to compare available models of \ce{[emim][B(CN)_4]} in terms of their capability to reproduce the experimental Henry constant of \ce{CO_2}.
-We have found that only the model of Koller \textit{et al.} \cite{Koller_2012} achieves this goal.
-A key factor for this success seems to be the reparametrization of the LJ parameters for the boron atom, which is only performed in the work of Koller \textit{et al.}  \cite{Koller_2012} in order to reproduce the experimental density of the pure substance.
+\begin{figure}[ht]
+\includegraphics[]{rdf-Liu.pdf}
+\caption{\ce{[emim][B(CN)_4]}}
+\label{fig:pressure}
+\end{figure}
 
-In the case of \ce{[emim][B(CN)_4]}, we were able to
-
-to introduce computationally efficient strategies, such as the use of rigid bodies and the DSF method for evaluating the Co the simulations and perform them in a more computationally efficient way: the ILs were modelled as rigid bodies and using the DSF method to calculate the Coulombic interactions.
-This required some preliminary simulations in order to analyze the most probable conformations of the ions.
-This was carried out in a simple way and with very good results.
-
-Using the expanded ensemble method, we reproduced the solvation free energy for both systems of interest:
-\ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} and at different thermodyanamic conditions. 
-At infinite-dilution those solvents performs in the solvation in \ce{[emim][B(CN)_4]} only slightly more favorable.
-This picture completely changed when we analyzed the systems at higher concentrations: the pressure required to dissolved a certain mass of \ce{CO_2} is considerable smaller that for \ce{[emim][NTf_2]}.
-
-This model was evaluated also to predict inifinite-dilution activity coefficient.
-This property also depends in the solvation free energy of the pure solutes.
-
-\section*{Acknowledgments}
-The authors acknowledge the financial support provided by Petrobras (project code CENPES 16113).
-
-\section*{References}
-
-\bibliography{mybibfile}
+\begin{figure}[ht]
+\includegraphics[]{rdf-Weber.pdf}
+\caption{\ce{[emim][B(CN)_4]}}
+\label{fig:pressure}
+\end{figure}
 
 \end{document}
-%rigid treatment of the imidazolium ring \cite{Kobrak_2004,Lynden_Bell_2006}\cite{Rey_Castro_2007}
-
-%\begin{equation}
-%\begin{split}
-%\Delta G_{\text{sim}} - k_b T \ln \left( \frac{V^{\ast}}{V_1} \right) &= k_b T \ln \left(\frac{P_s}{x_s} \frac{1}{\tilde{\rho}_{\scaleto{LI}{4pt}}} \right) \\
-%&= k_b T \ln \left( \frac{K_s}{\tilde{\rho}_{\scaleto{LI}{4pt}} R T} \right),
-%\end{split}
-%\end{equation}

### 2018-08-29 ionic_liquids.tex

@@
 \usepackage[T1]{fontenc}
+\usepackage{xr}
+\externaldocument{supp_material}
 
@@
 \end{equation}
-where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid phase and $P_s$ is the partial pressure of the solute in the gas phase.
+where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid-phase and $P_s$ is the partial pressure of the solute in the gas phase.
 It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.
@@
 where $\tilde{\rho}_{\scaleto{IL}{4pt}}$ is the molar density of the solvent and $R$ is the gas constant.
+
+\subsection*{Partial pressure estimation}
+\label{sec:partial_pressure}
+
+For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} are found at pressure values for which, in principle, the ideal gas assumption may be not valid.
+In this case, we shall correct the ideal gas contribution to the chemical potential, as follows
+\begin{equation}
+\label{eq:mu_gas_real}
+\mu^{g}_s = \mu^{ig}_s + RT \ln \phi_s,
+\end{equation}
+where $\phi_s$ is the fugacity coefficient of the solute.
+This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate $\mu^{l}_s$ = $\mu^{g}_s$, which yields
+\begin{equation}
+\label{eq:fgas_d}
+f^{g}_s = \exp  \left( \beta \Delta G_{\text{sim}} \right) +  k_b T c_s^{\ast}, 
+\end{equation}
+where $f^{g}_s$ is the fugacity of the solute in the gas phase.
+Having calculated $f^{g}_s$, $P_s$ can be predicted using the following equation
+\begin{equation}
+\label{eq:fgas}
+f^{g}_s = P_s \exp\left[ \frac{B_s(T) P_s}{R T} \right],
+\end{equation}
+where $B_s$ corresponds to the second virial coefficient.
+Here, we employ the correlation of $B_s$ for \ce{CO_2} introduced by Holste \textit{et al.} \cite{Holste_1987}, which is
+\begin{equation}
+B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
+\end{equation}
+where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = -2.455297 $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol).
+
+As supported by preliminary simulations, it seems reasonable to assume $\Delta G_{\text{sim}}$ as independent of pressure over the range of experimental data considered in this work.
+Then, the equilibrium pressure is determined by directly solving Eq.~\eqref{eq:fgas} for $P_s$.
 
@@
 
-\subsection*{Partial pressure estimation}
-\label{sec:partial_pressure}
-
-For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} are found at pressure values for which, in principle, the ideal gas assumption may be not valid.
-In this case, we shall correct the ideal gas contribution to the chemical potential, as follows
-\begin{equation}
-\label{eq:mu_gas_real}
-\mu^{g}_s = \mu^{ig}_s + RT \ln \phi_s,
-\end{equation}
-where $\phi_s$ is the fugacity coefficient of the solute.
-This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate $\mu^{l}_s$ = $\mu^{g}_s$, which yields
-\begin{equation}
-\label{eq:fgas_d}
-f^{g}_s = \exp  \left( \beta \Delta G_{\text{sim}} \right) +  k_b T c_s^{\ast}, 
-\end{equation}
-where $f^{g}_s$ is the fugacity of the solute in the gas phase.
-Having calculated $f^{g}_s$, $P_s$ can be predicted using the following equation
-\begin{equation}
-\label{eq:fgas}
-f^{g}_s = P_s \exp\left[ \frac{B_s(T) P_s}{R T} \right],
-\end{equation}
-where $B_s$ corresponds to the second virial coefficient.
-Here, we employ the correlation of $B_s$ for \ce{CO_2} introduced by Holste \textit{et al.} \cite{Holste_1987}, which is
-\begin{equation}
-B_s = B_0 + \frac{B_1}{T} + \frac{B_2}{T^2},
-\end{equation}
-where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = -2.455297 $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol).
-
-As supported by preliminary simulations, it seems reasonable to assume $\Delta G_{\text{sim}}$ as independent of pressure over the range of experimental data considered in this work.
-Then, the equilibrium pressure is determined by directly solving Eq.~\eqref{eq:fgas} for $P_s$.
-
 \section{Force fields}
@@
 
-Finally, for [emim][Tf\textsubscript{2}N] we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which was derived by refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
+Finally, for \ce{[emim][NTf_2]} we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which was derived by refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
 This refining was characterized by their authors as ``unusual'', given that the LJ parameters were modified, while keeping the partial charges at their original values.
@@
 As demonstrated in Ref.~\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ yield more decorrelated samples in each subensemble.
-In this work, we employ $N^{EE}$ = 5 which, together with the specified $\lambda_{\, \text{vdW}}$ set, resulted to be satisfactory as up to 3 preliminary runs of the EE were enough to determine the weights $\eta$ that yielded, in a final simulation, a ``sufficient'' sampling of each subensamble.
+In this work, we employed $N^{EE}$ = 5 which, together with the specified $\lambda_{\, \text{vdW}}$ set, required up to 3 preliminary runs of the EE for determining the weights $\eta$ that yielded, in a final simulation, a ``sufficient'' sampling of each subensamble.
 By ``sufficient'', we mean that the sampling provides an acceptable uncertainty in $\Delta G$.
@@
 This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
-With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.} \cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
+With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.} \cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
 Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
@@
 \hline \hline
-$\text{[emim]}$[B(CN)\textsubscript{4}] &  $\rho_{\text{sim}}$ & error (\%)\tnote{a}  & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
+\ce{[emim][B(CN)_4]}&  $\rho_{\text{sim}}$ & error (\%)\tnote{a}  & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
 model & (g/cm$^{3}$) &  &  (g/cm$^{3}$) &  \\
@@
 \begin{threeparttable}
-\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at $T$ = $298.15~\text{K}$ and $P$ = $1~\text{atm}$.
-The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
+\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} at $T$ = $298.15~\text{K}$ and $P$ = $1~\text{atm}$.
+The experimental Henry constants in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
 \begin{tabular}{ c c c  c  c  c  c }  
@@
 \hline
-		\multicolumn{4}{c}{[emim][Tf\textsubscript{2}N]} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
+		\multicolumn{4}{c}{\ce{[emim][NTf_2]}} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
 		\hline
@@
 It should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent sampling of $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
-Moreover, the $\Delta G_{\text{sim}}$ in [emim][Tf\textsubscript{2}N] is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
+Moreover, the $\Delta G_{\text{sim}}$ in \ce{[emim][NTf_2]} is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
 These consistencies have served for validating the methodological approaches of this work.
@@
 
-The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf\textsubscript{2}]}.
+The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}.
 The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm this result.
 The SDFs of the ions around a \ce{CO_2} molecule were obtained by using the software packages TRAVIS \cite{Brehm_2011} and VMD \cite{HUMP96}.
-For that, we carried out NPT-MD simulations of \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] systems with a \ce{CO_2} molar fraction of 0.1.
+For that, we carried out NPT-MD simulations of \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} systems with a \ce{CO_2} molar fraction of 0.1.
 The isovalues were visually determined so as to observe the first solvation shell.
@@
 
-\subsection{Study of concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N]}
+\subsection{Study of concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 \label{sec:results_conc}
 
-Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we carried out simulations at the thermodynamic conditions specified in Table~\ref{table:solv}, which correspond to similar values of \ce{CO_2} molality.
-Note that the differences in the \ce{CO_2} molar fractions clearly exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, which was mentioned at the introduction of this paper.
+Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we have also carried out simulations at the thermodynamic conditions specified in Table~\ref{table:solv}, which correspond to similar values of \ce{CO_2} molality.
+Note that the differences in the \ce{CO_2} molar fractions clearly exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, mentioned at the introduction of this paper.
 
@@
 \midrule		
-$\text{[emim]}$[B(CN)\textsubscript{4}]~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
-$\text{[emim]}$[Tf\textsubscript{2}N]~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
+\ce{[emim][B(CN)_4]}~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
+\ce{[emim][NTf_2]}~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
  \bottomrule
@@
 The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} were -0.755 $\pm$ 0.01 kcal/mol and -0.542 $\pm$ 0.005, respectively.
-However, since we simulated a different molecule number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could be a factor contributing to the higher solubility.
+However, since we simulated a different number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could explain the higher solubility.
 
@@
 This required preliminary simulations in order to examine the flexibility of the ethyl chain in \ce{[emim]^+} and the analysis was greatly facilitated by employing useful visualization tools.
-It should be remarked that the different models presented a different behavior, as well; reflecting ?
+Besides the properties already mentioned, the different models showed quite different behaviors, as well.
+This lack of consistency is one of the reasons why in industry molecular simulation has not become a routinely tool yet.
 
 The solvation free energy results at infinite-dilution condition suggest a slightly more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in  \ce{[emim][NTf_2]}.
-However, this picture completely changes at high concentrations: the simulations correctly predicted a considerable lower pressure to dissolve a certain mass of \ce{CO_2} in \ce{[emim][B(CN)_4]}.
+However, this picture changes at high concentrations: the simulations correctly predicted a considerable lower pressure to dissolve a certain mass of \ce{CO_2} in \ce{[emim][B(CN)_4]}.
 
-Finally, we employed the model of Koller \textit{et al.} \cite{Koller_2012} to predict infinite-dilution activity coefficient of various solutes.
-In this case, the results were not satisfactory given the high errors associated to the free energy calculations of the pure solutes, making necessary a revision of the force fields for the solutes in a future work.
+Finally, we employed the model of Koller \textit{et al.} \cite{Koller_2012} to predict infinite-dilution activity coefficients of various solutes.
+In this case, the results were not satisfactory given the large errors in the free energy calculations of the pure solutes, making necessary a revision of their force fields in a future work.
 

### 2018-08-30 ionic_liquids.tex
Changes in author affiliations

@@
 %% Group authors per affiliation:
-\author[rvt]{A.J.~Silveira}
-\author[rvt]{S.~Pereda}
-\author[focal,els]{F.W.~Tavares}
-\author[focal]{C.R.A.~Abreu\corref{cor1}}
+\author[plapiqui,msk]{A.J.~Silveira}
+\author[plapiqui]{S.~Pereda}
+\author[eq-ufrj,coppe-ufrj]{F.W.~Tavares}
+\author[eq-ufrj]{C.R.A.~Abreu\corref{cor1}}
 \ead{abreu@eq.ufrj.br}
 
-\address[rvt]{Planta Piloto de Ingenier\'ia Qu\'imica, PLAPIQUI, Universidad Nacional del Sur,Camino La Carrindanga Km 7-CC: 717, Bah\'ia Blanca, Argentina}
-\address[focal]{Chemical Engineering Department, Escola de Qu\'imica, Universidade Federal do Rio de Janeiro,Rio de Janeiro, RJ 21941-909, Brazil}
-\address[els]{COPPE, Universidade Federal do Rio de Janeiro, Rio de Janeiro, RJ 21941-909, Brazil}
+\address[plapiqui]{Planta Piloto de Ingenier\'ia Qu\'imica (PLAPIQUI), Universidad Nacional del Sur, Bah\'ia Blanca, Argentina}
+\address[msk]{Computational \& Systems Biology Program, Memorial Sloan Kettering Cancer Center, New York, NY, USA}
+\address[eq-ufrj]{Chemical Engineering Department, Escola de Qu\'imica, Universidade Federal do Rio de Janeiro, Rio de Janeiro, Brazil}
+\address[coppe-ufrj]{Chemical Engineering Program, Alberto Luiz Coimbra Institute for Graduate Studies and Research in Engineering (COPPE), Universidade Federal do Rio de Janeiro, Rio de Janeiro, Brazil}
 

### 2018-08-30 ionic_liquids.tex
Change in IL subscripts

@@
 \usepackage{amssymb}
-\usepackage{scalerel}
+%\usepackage{scalerel}
 \usepackage{natbib}
@@
 \end{equation}
-where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_{\text{LI}}$,P,T) and ($N_s^l$,$N_{\text{LI}}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid-phase and $P_s$ is the partial pressure of the solute in the gas phase.
+where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_\text{\tiny IL}$,P,T) and ($N_s^l$,$N_\text{\tiny IL}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid-phase and $P_s$ is the partial pressure of the solute in the gas phase.
 It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.
@@
 \end{equation}
-Therefore, by simply expressing Eq.~\eqref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that MW (molecular weight of the solution) = $\text{MW}_{\scaleto{IL}{4pt}}$, as well as $\rho$ (mass density of the solution) = $\rho_{\scaleto{IL}{4pt}}$, we obtain that
+Therefore, by simply expressing Eq.~\eqref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that MW (molecular weight of the solution) = $\text{MW}_\text{\tiny IL}$, as well as $\rho$ (mass density of the solution) = $\rho_\text{\tiny IL}$, we obtain that
 \begin{equation}
 \label{eq:henry_eq}
-K_s = \tilde{\rho}_{\scaleto{IL}{4pt}} R \, T \exp(\beta \, \Delta G_{\text{sim}}),
+K_s = \tilde{\rho}_\text{\tiny IL} R \, T \exp(\beta \, \Delta G_{\text{sim}}),
 \end{equation}
-where $\tilde{\rho}_{\scaleto{IL}{4pt}}$ is the molar density of the solvent and $R$ is the gas constant.
+where $\tilde{\rho}_\text{\tiny IL}$ is the molar density of the solvent and $R$ is the gas constant.
 
@@
 \label{eq:gamma_inf}
-\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_{\text{sim}} - \Delta G_{\text{sim}}^{0} \right) + \frac{c_{\scaleto{LI}{4pt}}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
+\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_{\text{sim}} - \Delta G_{\text{sim}}^{0} \right) + \frac{c_\text{\tiny IL}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
 \end{equation}
-where $c_{\scaleto{IL}{4pt}}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ are the numerical densities of the solvent and the pure solute, respectively.
+where $c_\text{\tiny IL}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ are the numerical densities of the solvent and the pure solute, respectively.
 

### 2018-08-30 convert_eps.sh
Figures can be converted to pdf to save compilation time

@@ -1,5 +1,5 @@
 #!/bin/bash
 for file in `ls *.eps`; do
     echo "Converting $file"
-    convert -density 300 "$file" "$(basename "$file" .eps).png"
+    convert -density 300 "$file" "$(basename "$file" .eps).pdf"
 done

### 2018-09-02 ionic_liquids.tex
Figures can be converted to pdf to save compilation time
Elimination of some packages for faster compilation
Changes in the abstract

@@
 \documentclass[3p,twocolumn]{elsarticle}
+
 \usepackage[colorlinks,citecolor=blue]{hyperref}
 \usepackage{lineno}
+\modulolinenumbers[5]
 \usepackage{amsmath}
@@
 \usepackage{amssymb}
-%\usepackage{scalerel}
 \usepackage{natbib}
@@
 \usepackage{commath}
-\usepackage{graphicx,bm}
-\usepackage{epstopdf}
+\usepackage{graphicx}
+\DeclareGraphicsExtensions{.pdf,.eps,.png}
 \usepackage{float}
-\biboptions{sort&compress}
-\modulolinenumbers[5]
 \usepackage{subfig}
 
-\usepackage[T1]{fontenc}
-\usepackage{xr}
-\externaldocument{supp_material}
+\journal{Fluid Phase Equilibria}
 
-\journal{Journal of \LaTeX\ Templates}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
 \bibliographystyle{elsarticle-num}
@@
 
-\title{A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
+\title{A molecular dynamics study of the solvation of carbon dioxide in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
+%\title{A molecular dynamics study of the solvation of \ce{CO_2}, \ce{H_2O}, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 
@@
 \begin{abstract}
-In this paper, we calculate solvation free energies in ionic liquids and predict macroscopic properties required in the design of chemical processes.
-Carbon dioxide from combustion processes is one of the main sources of anthropogenic generation of greenhouse gases.
-On the other hand, the potential of \ce{[emim][B(CN)_4]} for its capture has recently been reported.
-For comparison, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} are analyzed, both at infinite dilution and at high concentrations of \ce{CO_2}.
-Our results confirm what is experimentally observed, namely a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}.
-The infinite-dilution activity coefficients of hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} are also calculated, and a comparison is made with experimental values recently reported in literature.
+In this paper, we calculate solvation free energies of several compounds in ionic liquids.
+These free energies are used to compute properties such as Henry's law constants and activity coefficients, generally required to the design of environmentally sustainable processes.
+It is known, for instance, that carbon dioxide from combustion is one of the main sources of anthropogenic greenhouse gases.
+Recently, the propensity of ionic liquid \ce{[emim][B(CN)_4]} for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
+In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} are carried out both at infinite dilution and at high concentrations.
+A systematic study is performed by comparing several force fields and assessing the efficacy of simplification measures such as rigid-body dynamics and pairwise electrostatics.
+Our results confirm recent experimental observations that, for a given volume of solvent, lower pressure is required to absorb a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in other ionic liquids.
 \end{abstract}
@@
 \subfloat[Koller~\textit{et al.}~\cite{Koller_2012}]{%
-  \includegraphics[width=.4\linewidth]{koller.png}}%
+  \includegraphics[width=.4\linewidth]{koller}}%
 \subfloat[Batista~\textit{et al.}~\cite{Batista_2015}]{%  
-  \includegraphics[width=.4\linewidth]{batista.png}}%
+  \includegraphics[width=.4\linewidth]{batista}}%
 
 \subfloat[Liu~\textit{et al.}~\cite{Liu_2014}]{%
-  \includegraphics[width=.4\linewidth]{Liu.png}}%
+  \includegraphics[width=.4\linewidth]{Liu}}%
 \subfloat[Weber and Kirchner~\cite{Weber_2016}]{%
-  \includegraphics[width=.4\linewidth]{Weber.png}}%
+  \includegraphics[width=.4\linewidth]{Weber}}%
 \caption{Combined distribution function of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs for each model of \ce{[emim][B(CN)_4]}.}
@@
 \centering
-  \includegraphics[width=\linewidth]{Ludwig.png}%
+  \includegraphics[width=\linewidth]{Ludwig}%
 
-  \includegraphics[width=\linewidth]{Ludwig_anion.png}%
+  \includegraphics[width=\linewidth]{Ludwig_anion}%
 \caption{Combined distribution function of (a) the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, and (b) of the dihedral angles of the contiguous  C1-S1-N1-S2 and S1-N1-S2-C2 chains, obtained from NPT-MD simulations of 250 molecules of \ce{[emim][NTf_2]}.}

### 2018-09-02 ionic_liquids.tex
Revision of the introduction

@@
 \usepackage{amssymb}
-\usepackage{natbib}
+\usepackage[]{natbib}
 \usepackage[version=4]{mhchem}
@@
 \section{Introduction}
+
 \ce{CO_2} emissions from fossil-fuel power generation plants account for a large portion of the anthropogenic greenhouse gases \cite{totalenergy}.
@@
 The most commonly used solvents are volatile organic compounds, specially aqueous solutions of monoethanolamine (MEA).
-Despite its high absorption capability, the use of MEA suffers from a serious drawback due to the high cost of solvent recovery \cite{Merkel_2010}.
-Other disadvantages include corrosion and degradation by oxidation, solvent loss by evaporation, which also contributes to increase the environmental pollution and generates extra costs for replacing the solvent.
+Despite its high absorption capability, the use of MEA has a serious drawback, which is the high cost of solvent recovery \cite{Merkel_2010}.
+Other disadvantages include corrosion and degradation by oxidation, as well as solvent loss by evaporation.
+The latter also contributes to the increase of environmental pollution and generates extra costs for replacing the solvent.
 
-The use of ionic liquids (ILs) as solvents for \ce{CO_2} sequestration occupies a central place in the investigation of alternative technologies.
-The reasons are their well known properties, such as their almost negligible vapor pressure and high thermal stability.
+The use of ionic liquids (ILs) as solvents for \ce{CO_2} sequestration receives special attention in the investigation of alternative technologies.
+The reasons are their well-known properties such as almost negligible vapor pressure and high thermal stability.
 Furthermore, they are particularly attractive since they can be designed for specific applications, giving rise to the so-called task-specific ILs \cite{Seo_2014}.
-These remarkable properties makes ILs suitable for a wide variety of applications in separation processes \cite{Han_2010,Werner_2010}, catalysis \cite{P_rvulescu_2007}, energy \cite{MacFarlane_2014}, and material science \cite{Mecerreyes_2011,Tom_2015,Dupont_2010,Leones_2017,Kinik_2017}.
+These remarkable properties make ILs suitable for a wide variety of applications in separation processes \cite{Han_2010,Werner_2010}, catalysis \cite{P_rvulescu_2007}, energy management \cite{MacFarlane_2014}, and material science \cite{Mecerreyes_2011,Tom_2015,Dupont_2010,Leones_2017,Kinik_2017}.
 
-Recently, the potentiality of ILs for \ce{CO_2} capture has been called into question by Carvalho \textit{et al.} \cite{Carvalho_2016}, who warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposed absorption capability of certain ILs.
-Although most thermodynamic models are formulated in terms of molar fraction, a key factor that dictates the absorption process efficiency is given by the amount of \ce{CO_2} that can be dissolved in a certain \textit{volume} or \textit{mass} of solvent.
-By expressing the solubility values in terms of molality and performing an exhaustive comparison between various ILs, Ref.
-\cite{Carvalho_2016} shows that most systems which promote a physical absorption of \ce{CO_2} exhibit a solubility similar, or even lower, than that observed for the heavy alkane eicosane.
-This is true for the ``popular'' \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}; the only exception being the family of ILs containing the anion tetracyanoborate \ce{[B(CN)_4]^-}.
+Recently, Carvalho \textit{et al}. \cite{Carvalho_2016} called into question the potentiality of ILs for \ce{CO_2} capture.
+They warn that the use of molar fraction to express solubility has, to some extent, perpetuated misconceptions regarding the supposedly high absorption capability of certain ILs.
+Although most thermodynamic models are formulated in terms of molar fractions, a key factor that dictates the efficiency of absorption process  is given by the amount of \ce{CO_2} that can be dissolved in a certain \textit{volume} or \textit{mass} of solvent.
+By expressing the solubility values in terms of molality and performing an exhaustive comparison among various ILs, Carvalho \textit{et al}.
+\cite{Carvalho_2016} show that most systems which promote physical absorption of \ce{CO_2} exhibit solubilities which are similar, or even lower, than that observed for heavy alkanes such as eicosane.
+This is true for the popular ILs \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}.
+The only exception they found was the family of ILs containing the anion \ce{[B(CN)_4]^-} (tetracyanoborate).
 
 There is no obvious explanation accounting for the enhanced solubility promoted by the presence of \ce{[B(CN)_4]^-}.
-In this context, molecular simulation provides with a powerful tool for studying solvation processes.
-To the best of our knowledge, only one study in literature reports the free energy of solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} \cite{Liu_2014_1} which, in addition, is overestimated.
-This motivated us to evaluate different force fields of \ce{[emim][B(CN)_4]} and, as we will show below, it was possible to find a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2}.
-For comparison, \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} were analyzed, both at infinite dilution and at high concentrations of \ce{CO_2}.
-The simulations confirmed what is observed in experiments: for \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}.
-The infinite-dilution activity coefficients of solutes hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} were also calculated, and a comparison was made with experimental values recently reported in literature.
+In this context, molecular simulation provides us with a powerful tool for studying solvation processes.
+To the best of our knowledge, only one study in the literature reports computation of solvation free energy for \ce{CO_2} in \ce{[emim][B(CN)_4]} by molecular simulation \cite{Liu_2014_1}.
+Nonetheless, the computed value is overestimated, as observed by deriving a Henry's law constant and comparing it to available experimental data.
+Such scarcity motivated us to carry out the present investigation, in which we have evaluated different force fields for \ce{[emim][B(CN)_4]} proposed in the literature.
+As we show here, it was possible to find a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2} in this IL.
+For comparison, we analyzed the solvation of \ce{CO_2} not only in \ce{[emim][B(CN)_4]}, but also in \ce{[emim][NTf_2]}, both at infinite dilution and at high concentrations.
+The simulations confirmed what is observed in experiments.
+For \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}, considering a given volume of solvent.
+In addition, we also calculated infinite-dilution activity coefficients of other solutes in \ce{[emim][B(CN)_4]} and compared the results with experimental values recently reported in literature.
+The solutes we considered were hexane, benzene, cyclohexane, ethanol, and water.
 
-This paper is organized as follows: in Sec.~\ref{sec:theory} we present the theoretical background, which is followed by a brief description of the force fields used in this work.
-The methodological details are provided in Sec.~\ref{sec:sim_details} and the corresponding numerical results are given in Sec.~\ref{sec:results}.
+This paper is organized as follows.
+In Sec.~\ref{sec:theory}, we present the theoretical background of this work, which is followed by a brief description of the employed force fields in Sec.~\ref{sec:force_field}.
+The methodological details are provided in Sec.~\ref{sec:sim_details}, while the corresponding numerical results are given in Sec.~\ref{sec:results}.
 Finally, we present some concluding remarks in Sec.~\ref{sec:conclusion}.

### 2018-09-03 ionic_liquids.tex
Some changes in the beginning of Sec 2

@@
 
-In this section, we present the formalism that allows us to compute the Henry constant and activity coefficient, both at infinite dilution, from the simulated free energy.
-For this, we rely on the work of Shirts \textit{et al.} \cite{Shirts_2003}.
-Then, we reformulate the equations in order to study concentrated solutions, which would be the more likely scenario in \ce{CO_2} capture processes.
+In this section, we present the formalism that allows us to compute solvation free energies from molecular dynamics simulations and, after that, obtain Henry constants and activity coefficients.
+For dealing with systems at infinite dilution, we rely on the work of Shirts \textit{et al}. \cite{Shirts_2003}.
+Then, we reformulate the equations in order to study concentrated solutions, which is a more likely scenario in the case of \ce{CO_2} capture processes.
 
 \subsection*{Solvation free energy}
-The solvation free energy, $\Delta G_{\text{solv}}$, is defined as the reversible work needed to transfer a solute molecule from the gas phase to the solution.
-For dense systems, an efficient computation of solvation properties via molecular simulation is possible by means of the so-called alchemical methods, which employ non-physical pathways to connect the ``endpoint'' states, whose free energy difference is to be estimated.
-In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through the use of a coupling parameter $\lambda$, which scales the intermolecular interactions taking values in the interval [0,1]: $\lambda$ = 1 corresponds to a fully interacting system, while for $\lambda$ = 0 the interactions between the solute and solvent molecules are completely turned-off.
 
-In the following, the subscripts ``$s$'' and ``$\text{IL}$'' refer to the solute and the solvent (ionic liquid), respectively.
+The solvation free energy, $\Delta G_{\text{solv}}$, is defined as the reversible work needed to transfer a solute molecule from a gas phase to the solution.
+For dense systems, an efficient computation of solvation properties via molecular simulation is possible by means of the so-called alchemical methods, which employ non-physical pathways to reversibly connect the endpoint states whose difference in free energy is to be estimated.
+In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through the use of a coupling parameter $\lambda$, which scales the solute-solvent interactions by taking values in the interval [0,1].
+By convention, $\lambda = 1$ corresponds to a fully interacting system, while for $\lambda$ = 0 the solute-solvent interactions are turned off completely .
+
+In what follows, the subscripts ``s'' and ``IL'' refer to the solute and the solvent (ionic liquid), respectively.
 For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as

### 2018-09-03 ionic_liquids.tex
Subscripts IL and sim

@@
 In what follows, the subscripts ``s'' and ``IL'' refer to the solute and the solvent (ionic liquid), respectively.
-For a system containing $N_{\text{IL}}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
+For a system containing $N_\text{\tiny IL}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
 \begin{equation}
-\Delta G_{\text{sim}} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_{\text{IL}},P,T,\lambda = 0)}, 
+\Delta G_\text{sim} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_\text{\tiny IL},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_\text{\tiny IL},P,T,\lambda = 0)}, 
 \end{equation}
 where superscript ``$l$'' refers to the liquid solution, $\bigtriangleup$ denotes the isobaric-isothermal partition function, and $k_b$ is the Boltzmann's constant.
-Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_{\text{sim}}$ to what is experimentally known as the solvation free energy.
+Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_\text{sim}$ to what is experimentally known as the solvation free energy.
 They found out that
@@
 \label{eq:free_solv}
- \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_{\text{sim}} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
+ \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_\text{sim} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
 \end{split}
@@
 \label{eq:henry_eq}
-K_s = \tilde{\rho}_\text{\tiny IL} R \, T \exp(\beta \, \Delta G_{\text{sim}}),
+K_s = \tilde{\rho}_\text{\tiny IL} R \, T \exp(\beta \, \Delta G_\text{sim}),
 \end{equation}
@@
 \label{eq:fgas_d}
-f^{g}_s = \exp  \left( \beta \Delta G_{\text{sim}} \right) +  k_b T c_s^{\ast}, 
+f^{g}_s = \exp  \left( \beta \Delta G_\text{sim} \right) +  k_b T c_s^{\ast}, 
 \end{equation}
@@
 
-As supported by preliminary simulations, it seems reasonable to assume $\Delta G_{\text{sim}}$ as independent of pressure over the range of experimental data considered in this work.
+As supported by preliminary simulations, it seems reasonable to assume $\Delta G_\text{sim}$ as independent of pressure over the range of experimental data considered in this work.
 Then, the equilibrium pressure is determined by directly solving Eq.~\eqref{eq:fgas} for $P_s$.
@@
 \label{eq:mu_res}
-\mu_s^R = \Delta G_{\text{sim}} - k_b T \ln \left( \frac{V^{\ast} P}{N_s^l k_b T} \right) -  k_b T \ln x_s.
+\mu_s^R = \Delta G_\text{sim} - k_b T \ln \left( \frac{V^{\ast} P}{N_s^l k_b T} \right) -  k_b T \ln x_s.
 \end{equation}
@@
 \label{eq:mu_res_0}
-\mu_s^{R,0} = \Delta G_{\text{sim}}^{0} - k_b T \ln \left( \frac{V^{\ast,0} P}{N_s^{l,0} k_b T} \right).
+\mu_s^{R,0} = \Delta G_\text{sim}^{0} - k_b T \ln \left( \frac{V^{\ast,0} P}{N_s^{l,0} k_b T} \right).
 \end{equation}
@@
 \label{eq:gamma_inf}
-\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_{\text{sim}} - \Delta G_{\text{sim}}^{0} \right) + \frac{c_\text{\tiny IL}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
+\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_\text{sim} - \Delta G_\text{sim}^{0} \right) + \frac{c_\text{\tiny IL}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
 \end{equation}
@@
 \begin{split}
-\Delta G_{\text{sim}} =& \; \Delta G_{\,\text{vdW}} (\lambda_{\,\text{vdW}} = 0\rightarrow  1, \lambda_{\, \text{Coul}} = 0) \\
+\Delta G_\text{sim} =& \; \Delta G_{\,\text{vdW}} (\lambda_{\,\text{vdW}} = 0\rightarrow  1, \lambda_{\, \text{Coul}} = 0) \\
 + \; &\Delta G_{\,\text{Coul}} (\lambda_{\, \text{vdW}} = 1,\lambda_{\,\text{Coul}} = 0 \rightarrow 1),
@@
 \hline \hline
-\ce{[emim][B(CN)_4]}&  $\rho_{\text{sim}}$ & error (\%)\tnote{a}  & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
+\ce{[emim][B(CN)_4]}&  $\rho_\text{sim}$ & error (\%)\tnote{a}  & $\rho_\text{sim}$ & error (\%)\tnote{a} \\
 model & (g/cm$^{3}$) &  &  (g/cm$^{3}$) &  \\
@@
 \begin{tablenotes}
-\item[a] error = 100 $\times$($\rho^{\text{exp}}$$ - $$\rho^{\text{sim}}$)/$\rho^{\text{exp}}$.
+\item[a] error = 100 $\times$($\rho^{\text{exp}}$$ - $$\rho^\text{sim}$)/$\rho^{\text{exp}}$.
 \end{tablenotes}
@@
 \toprule
-Model & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
+Model & $\tilde{\rho}_\text{sim}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
 & (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
@@
 \begin{tablenotes}
-\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
+\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^\text{sim})/K_s^{\text{exp}}}$.
 \end{tablenotes}
@@
 
-It should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent sampling of $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
-Moreover, the $\Delta G_{\text{sim}}$ in \ce{[emim][NTf_2]} is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
+It should be pointed out that the result of $\Delta G_\text{sim}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent sampling of $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
+Moreover, the $\Delta G_\text{sim}$ in \ce{[emim][NTf_2]} is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
 These consistencies have served for validating the methodological approaches of this work.
@@
 The task of accurately predicting $\gamma^{\, \infty}$ is challenging since, according to Eq.~\eqref{eq:gamma_inf}, one should reproduce the solvation free energies in both the pure solute and the solvent.
-In Table~\ref{table:mu_solutes} we show the simulated densities and the solvation free energies $(\Delta G^{0}_{\text{sim}})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}.
+In Table~\ref{table:mu_solutes} we show the simulated densities and the solvation free energies $(\Delta G^{0}_\text{sim})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}.
 It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ for cyclohexane.
@@
 \toprule
-Solute & $\rho_{\text{sim}}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
+Solute & $\rho_\text{sim}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
  & (g/cm$^{3}$) &  & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   &  \\
@@
 \begin{tablenotes}
-\item[a] error = 100 $\times$ $\abs{(Z^{\text{exp}} - Z^{\text{sim}})/Z^{\text{exp}}}$.
+\item[a] error = 100 $\times$ $\abs{(Z^{\text{exp}} - Z^\text{sim})/Z^{\text{exp}}}$.
 \end{tablenotes}

### 2018-09-04 ionic_liquids.tex
Reformulation of the Solvation Free Energy subsection

@@
 In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through the use of a coupling parameter $\lambda$, which scales the solute-solvent interactions by taking values in the interval [0,1].
-By convention, $\lambda = 1$ corresponds to a fully interacting system, while for $\lambda$ = 0 the solute-solvent interactions are turned off completely .
+By convention, $\lambda = 1$ corresponds to a fully interacting system, while for $\lambda$ = 0 the solute-solvent interactions are turned off completely.
 
 In what follows, the subscripts ``s'' and ``IL'' refer to the solute and the solvent (ionic liquid), respectively.
-For a system containing $N_\text{\tiny IL}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
+For a liquid phase containing $N_\text{\tiny IL}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
 \begin{equation}
-\Delta G_\text{sim} \equiv k_b T \ln \frac{\bigtriangleup (N_s^l,N_\text{\tiny IL},P,T,\lambda = 1)}{\bigtriangleup (N_s^l,N_\text{\tiny IL},P,T,\lambda = 0)}, 
+\Delta G_\text{sim} \equiv k_b T \ln \frac{\Xi (N_s,N_\text{\tiny IL},P,T,\lambda = 1)}{\Xi (N_s,N_\text{\tiny IL},P,T,\lambda = 0)}, 
 \end{equation}
-where superscript ``$l$'' refers to the liquid solution, $\bigtriangleup$ denotes the isobaric-isothermal partition function, and $k_b$ is the Boltzmann's constant.
-Shirts \textit{et al.} \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_\text{sim}$ to what is experimentally known as the solvation free energy.
-They found out that
+where $\Xi$ denotes the isobaric-isothermal partition function and $k_b$ is the Boltzmann constant.
+Shirts \textit{et al}. \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_\text{sim}$ to what is experimentally measured as the solvation free energy, namely
+\begin{equation}
+\Delta G_{\text{solv}} =  k_b T \ln \left( \frac{P_s}{c^l_s R T} \right),
+\end{equation}
+where $R=N_Ak_b$ is the gas constant ($N_A$ is the Avogadro number) and, for a system at phase equilibrium, $P_s$ is the partial pressure of the solute in the gas phase and $c^l_s$ is its molar concentration in the liquid phase.
+For obtaining the mentioned relation, the authors derived an expression for the chemical potential of the solute in the liquid phase ($\mu^l_s$) as a function of $\Delta G_\text{sim}$, which can be written as
+\begin{equation}
+\mu^l_s = \mu^{ig}_s + \Delta G_\text{sim} - k_bT \ln \left( \frac{V^{\ast}}{V_1}\right) - k_bT \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right),
+\end{equation}
+where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and solute partial pressure $P_s$, $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{\tiny IL}$,P,T) and ($N_s$,$N_\text{\tiny IL}$,P,T), respectively, while $c_s^{\ast} = N_s/V_1$ is the number concentration of the solute in the latter.
+For small solutes, such as those considered in this work, the term containing the ratio $V^{\ast}/V_1$ is typically in the order of magnitude of the free-energy uncertainties \cite{Shirts_2003}.
+Hence, it can be neglected and will be omitted hereafter.
+
+Finally, by treating the gas phase as an ideal gas and considering a system at phase equilibrium ($\mu^l_s = \mu^{ig}_s$), Shirts \textit{et al}. \cite{Shirts_2003} then found out that
 \begin{equation}
@@
 \label{eq:free_solv}
- \Delta G_{\text{solv}}& =  k_b T \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right)\\ &= \Delta G_\text{sim} - k_bT \ln \left( \frac{V^{\ast}}{V_1} \right),
+ \Delta G_{\text{solv}} \approx \Delta G_\text{sim}.
 \end{split}
 \end{equation}
-where $V^{\ast}$ and $V_1$ refer to the mean volumes of the systems specified by ($N_s^l-1$,$N_\text{\tiny IL}$,P,T) and ($N_s^l$,$N_\text{\tiny IL}$,P,T), respectively; $c_s^{\ast}$ = $N_s^l/V_1$ is the numerical concentration of the solute in the liquid-phase and $P_s$ is the partial pressure of the solute in the gas phase.
-It should be noted that in the derivation of Eq.~\eqref{eq:free_solv}, the gas phase is treated as an ideal gas.
-
-For small solutes, such as those considered in this work, the magnitude of the term $V^{\ast}/V_1$ is typically on the order of the free energy uncertainties \cite{Shirts_2003}.
-Hence, that term can be neglected and will be omitted hereafter.
 
 \subsection*{Henry constant}
-If both $P_s$ and $c_s^{\ast}$ were not large, we can resort to Eq.~\eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
+
+If both $P_s$ and $c_s^{\ast}$ are small, we can resort to Eq.~\eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
 \begin{equation}
@@
 \end{equation}
-Therefore, by simply expressing Eq.~\eqref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that MW (molecular weight of the solution) = $\text{MW}_\text{\tiny IL}$, as well as $\rho$ (mass density of the solution) = $\rho_\text{\tiny IL}$, we obtain that
+
+Therefore, by simply expressing Eq.~\eqref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that the molar density of the solution does not perceivably differ from than of the solvent ($\tilde{\rho}_\text{\tiny solution} \approx \tilde{\rho}_\text{\tiny IL}$), we obtain that
 \begin{equation}
@@
 \end{equation}
-where $\tilde{\rho}_\text{\tiny IL}$ is the molar density of the solvent and $R$ is the gas constant.
+where $R$ is the gas constant and $\beta = (k_b T)^{-1}$.
 
@@
 For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} are found at pressure values for which, in principle, the ideal gas assumption may be not valid.
-In this case, we shall correct the ideal gas contribution to the chemical potential, as follows
+In this case, we can compute the chemical potential of the solute in the real gas phase as
 \begin{equation}
@@
 where $\phi_s$ is the fugacity coefficient of the solute.
-This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate $\mu^{l}_s$ = $\mu^{g}_s$, which yields
+This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate the phase equilibrium equation $\mu^{l}_s$ = $\mu^{g}_s$, which yields
 \begin{equation}

### 2018-09-06 ionic_liquids.tex
Substancial changes in the theoretical background section

@@
 
-\subsection*{Solvation free energy}
+\subsection*{Solvation Free Energy}
 
@@
 \begin{equation}
-\Delta G_{\text{solv}} =  k_b T \ln \left( \frac{P_s}{c^l_s R T} \right),
+\label{eq:solvation free energy definition}
+\Delta G_{\text{solv}} \equiv k_b T \ln \left( \frac{P_s}{c_s R T} \right),
 \end{equation}
-where $R=N_Ak_b$ is the gas constant ($N_A$ is the Avogadro number) and, for a system at phase equilibrium, $P_s$ is the partial pressure of the solute in the gas phase and $c^l_s$ is its molar concentration in the liquid phase.
+where $R = N_A k_b$ is the gas constant,
+$N_A$ is the Avogadro number,
+$P_s$ is the partial pressure of the solute in the gas phase, and
+$c_s$ is the molar concentration of the solute in the liquid phase.
+Note that these quantities correspond to a phase equilibrium condition.
 For obtaining the mentioned relation, the authors derived an expression for the chemical potential of the solute in the liquid phase ($\mu^l_s$) as a function of $\Delta G_\text{sim}$, which can be written as
 \begin{equation}
-\mu^l_s = \mu^{ig}_s + \Delta G_\text{sim} - k_bT \ln \left( \frac{V^{\ast}}{V_1}\right) - k_bT \ln \left( \frac{P_s}{c_s^{\ast} k_b T} \right),
+\mu^l_s = \mu^{ig}_s + \Delta G_\text{sim} - k_bT \ln \left( \frac{V^{\ast}}{V_1}\right) - k_bT \ln \left( \frac{P_s}{c_s R T} \right),
 \end{equation}
-where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and solute partial pressure $P_s$, $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{\tiny IL}$,P,T) and ($N_s$,$N_\text{\tiny IL}$,P,T), respectively, while $c_s^{\ast} = N_s/V_1$ is the number concentration of the solute in the latter.
+where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and partial pressure of solute $P_s$, while $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{\tiny IL}$,P,T) and ($N_s$,$N_\text{\tiny IL}$,P,T), respectively.
+Note that $c_s = \frac{N_s}{N_A V_1}$.
 For small solutes, such as those considered in this work, the term containing the ratio $V^{\ast}/V_1$ is typically in the order of magnitude of the free-energy uncertainties \cite{Shirts_2003}.
@@
 
-Finally, by treating the gas phase as an ideal gas and considering a system at phase equilibrium ($\mu^l_s = \mu^{ig}_s$), Shirts \textit{et al}. \cite{Shirts_2003} then found out that
+Finally, by treating the gas phase as an ideal gas and considering the system to be at equilibrium ($\mu^l_s = \mu^{ig}_s$), Shirts \textit{et al}. \cite{Shirts_2003} found out that
 \begin{equation}
@@
 
-\subsection*{Henry constant}
+\subsection*{Henry's Law Constant}
 
-If both $P_s$ and $c_s^{\ast}$ are small, we can resort to Eq.~\eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
+If both $P_s$ and $c_s^{\ast}$ are small, we can resort to Eqs.~\eqref{eq:solvation free energy definition} and \eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
 \begin{equation}
@@
 
-Therefore, by simply expressing Eq.~\eqref{eq:free_solv} in terms of the molar fraction $x_s$ and assuming that the molar density of the solution does not perceivably differ from than of the solvent ($\tilde{\rho}_\text{\tiny solution} \approx \tilde{\rho}_\text{\tiny IL}$), we obtain that
+Therefore, by simply expressing Eq.~\eqref{eq:solvation free energy definition} in terms of the molar fraction of the solute in the liquid phase ($x_s$) and assuming that the molar density of the solution does not perceivably differ from that of the solvent ($\tilde{\rho} \approx \tilde{\rho}_\text{\tiny IL}$), we obtain that
 \begin{equation}
 \label{eq:henry_eq}
-K_s = \tilde{\rho}_\text{\tiny IL} R \, T \exp(\beta \, \Delta G_\text{sim}),
+K_s = \tilde{\rho}_\text{\tiny IL} R \, T \exp\left(\frac{\Delta G_\text{sim}}{k_b T}\right).
 \end{equation}
-where $R$ is the gas constant and $\beta = (k_b T)^{-1}$.
 
-\subsection*{Partial pressure estimation}
+\subsection*{Higher Pressure Conditions}
 \label{sec:partial_pressure}
 
-For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} are found at pressure values for which, in principle, the ideal gas assumption may be not valid.
+For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} in the liquid phase are obtained at pressure values for which, in principle, the ideal gas assumption may not be valid.
 In this case, we can compute the chemical potential of the solute in the real gas phase as
@@
 \label{eq:mu_gas_real}
-\mu^{g}_s = \mu^{ig}_s + RT \ln \phi_s,
+\mu^{g}_s = \mu^{ig}_s + k_b T \ln \left(\frac{f^{g}_s}{P_s}\right),
 \end{equation}
-where $\phi_s$ is the fugacity coefficient of the solute.
-This equation, together with the fact that $f^{g}_s$ = $P_s \phi_s$, are used to evaluate the phase equilibrium equation $\mu^{l}_s$ = $\mu^{g}_s$, which yields
+where $f^{g}_s$ is the fugacity of the solute in the gas phase.
+Then, by considering a system at phase equilibrium ($\mu^{l}_s$ = $\mu^{g}_s$), it follows that
 \begin{equation}
 \label{eq:fgas_d}
-f^{g}_s = \exp  \left( \beta \Delta G_\text{sim} \right) +  k_b T c_s^{\ast}, 
+f^{g}_s = \exp \left( \frac{\Delta G_\text{sim}}{k_b T} \right) +  c_s R T. 
 \end{equation}
-where $f^{g}_s$ is the fugacity of the solute in the gas phase.
-Having calculated $f^{g}_s$, $P_s$ can be predicted using the following equation
+
+Three additional assumptions are made here.
+First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems with which we compare our simulations) or can be approximated by an ideal solution.
+Second, we assume that the system pressure is moderate, so that a truncated virial equation is enough to represent the gas phase.
+In this case, Eq.~\eqref{eq:fgas_d} becomes
 \begin{equation}
-\label{eq:fgas}
-f^{g}_s = P_s \exp\left[ \frac{B_s(T) P_s}{R T} \right],
+\label{eq:equation for pressure}
+y_s P \exp\left( \frac{B_s P}{R T} \right) = \exp \left( \frac{\Delta G_\text{sim}}{k_b T} \right) +  c_s R T,
 \end{equation}
-where $B_s$ corresponds to the second virial coefficient.
-Here, we employ the correlation of $B_s$ for \ce{CO_2} introduced by Holste \textit{et al.} \cite{Holste_1987}, which is
+where $y_s$ is the molar fraction of solute in the gas phase ($y_s \rightarrow 1$ for the systems we analyze here) and $B_s$ is the second virial coefficient of the solute.
+In the case of \ce{CO_2}, we employ the correlation for $B_s$ developed by Holste \textit{et al}. \cite{Holste_1987}, which is
 \begin{equation}
@@
 \end{equation}
-where $B_0$ = 23.02991 cm$^3$/mol, $B_1$ = -2.455297 $\times$ 10$^3$ (Kcm$^3$/mol) and $B_2$ = -1.22675$\times$10$^7$ (K$^2$cm$^3$/mol).
+where $B_0 = 23.02991~\mathrm{\frac{cm^3}{mol}}$, $B_1 = -2455.297~\mathrm{\frac{K \cdot cm^3}{mol}}$, and $B_2 = -1.22675 \times 10^7~\mathrm{\frac{K^2 \cdot cm^3}{mol}}$.
 
-As supported by preliminary simulations, it seems reasonable to assume $\Delta G_\text{sim}$ as independent of pressure over the range of experimental data considered in this work.
-Then, the equilibrium pressure is determined by directly solving Eq.~\eqref{eq:fgas} for $P_s$.
+Our third assumption, supported by preliminary simulations, is that $\Delta G_\text{sim}$ does not vary appreciably with pressure, at least over the range of experimental data considered here.
+In this way, no iterative simulations are required to compute the equilibrium pressure by solving Eq.~\eqref{eq:equation for pressure} for $P$.
 

### 2018-09-07 ionic_liquids.tex
Revision of Activity Coefficients subsection

@@
 \begin{equation}
+\label{eq:solute chemical potential}
 \mu^l_s = \mu^{ig}_s + \Delta G_\text{sim} - k_bT \ln \left( \frac{V^{\ast}}{V_1}\right) - k_bT \ln \left( \frac{P_s}{c_s R T} \right),
 \end{equation}
-where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and partial pressure of solute $P_s$, while $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{\tiny IL}$,P,T) and ($N_s$,$N_\text{\tiny IL}$,P,T), respectively.
+where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and solute partial pressure $P_s$, while $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{\tiny IL}$,P,T) and ($N_s$,$N_\text{\tiny IL}$,P,T), respectively.
 Note that $c_s = \frac{N_s}{N_A V_1}$.
@@
 
-If both $P_s$ and $c_s^{\ast}$ are small, we can resort to Eqs.~\eqref{eq:solvation free energy definition} and \eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
+If both $P_s$ and $c_s$ are small, we can resort to Eqs.~\eqref{eq:solvation free energy definition} and \eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
 \begin{equation}
@@
 
-Therefore, by simply expressing Eq.~\eqref{eq:solvation free energy definition} in terms of the molar fraction of the solute in the liquid phase ($x_s$) and assuming that the molar density of the solution does not perceivably differ from that of the solvent ($\tilde{\rho} \approx \tilde{\rho}_\text{\tiny IL}$), we obtain that
+Therefore, by simply expressing Eq.~\eqref{eq:solvation free energy definition} in terms of the molar fraction of the solute in the liquid phase ($x_s$) and assuming a dilute solution, whose molar density does not perceivably differ from that of pure solvent (that is, $\tilde{\rho} \approx \tilde{\rho}_\text{\tiny IL}$), we obtain that
 \begin{equation}
@@
 
-\subsection*{Infinite-dilution activity coefficient}
+\subsection*{Activity Coefficients}
 
-As will be shown below, the prediction of activity coefficients requires extra simulations involving the pure solute.
-In what follows, we use the superscript ``$0$'' to denote the pure solute properties.
-
-Using standard thermodynamic relations \cite{Tester}, we write the activity coefficient $\gamma_s$ in terms of residual chemical potentials, as follows:
+As will be shown below, the prediction of activity coefficients requires additional simulations of the solute as a pure liquid phase, whose properties we denote here by a superscript ``$0$''.
+We start by using standard thermodynamic relations \cite{Tester} to write the solute activity coefficient $\gamma_s$ in terms of chemical potentials as
 \begin{equation}
 \label{eq:gamma}
-\ln \gamma_s = \frac{1}{RT} (\mu_s^R - \mu_s^{R,0}),
-\end{equation}
-where $\mu_s^R$ and $\mu_s^{R,0}$ are the residual chemical potentials of the solute in the solution and in the pure solute, respectively.
-It is worth noting that we have used the definition $\mu_s^{R}$ (P,T) = $\mu_s$ (P,T) - $\mu_s^{ig}$ (P,T), where the superscript $ig$ refers to a solution of ideal gases.
-Also, recall that $\mu_s^{ig} (P,T)$ = $\mu_s^{ig,0} (P,T)$ + $RT \ln x_s$, so we have that
-\begin{equation}
-\mu_s^R = \mu_s^l(N_s^l,N_{LI},P,T) - \mu_s^{ig,0}(P,T) - k_b T \ln x_s.
-\end{equation}
-Replacing $\mu_s^{l}$ and $\mu_s^{ig,0}$ by the corresponding expressions derived in Ref.~\cite{Shirts_2003} yields
-\begin{equation}
-\label{eq:mu_res}
-\mu_s^R = \Delta G_\text{sim} - k_b T \ln \left( \frac{V^{\ast} P}{N_s^l k_b T} \right) -  k_b T \ln x_s.
-\end{equation}
-Of course, an analogous equation holds for $\mu_s^{R,0}$:
-\begin{equation}
-\label{eq:mu_res_0}
-\mu_s^{R,0} = \Delta G_\text{sim}^{0} - k_b T \ln \left( \frac{V^{\ast,0} P}{N_s^{l,0} k_b T} \right).
+\ln \gamma_s = \frac{\mu_s^l - \mu_s^{l,0}}{k_B T} - \ln x_s,
 \end{equation}
 
-If one makes $N_s^{l}$ = 1, and substitute Eqs.~\eqref{eq:mu_res} and~\eqref{eq:mu_res_0} into Eq.~\eqref{eq:gamma}, the infinite-dilution activity coefficient, $\gamma^{\infty}_s$, can be predicted according to the following equation:
+Next, we replace $\mu_s^l$ and $\mu_s^{l,0}$ by their corresponding instances of Eq.~\eqref{eq:solute chemical potential}.
+In this step, we note that $c_s = \tilde{\rho} x_s$ and $c_s^0 = \tilde{\rho}_s^0$, where $\tilde{\rho}$ and $\tilde{\rho}_s^0$ are the molar densities of the solution and of the pure liquid solute, respectively.
+Thus, the expression we obtain for computing an activity coefficient from two independent simulations is
 \begin{equation}
-\label{eq:gamma_inf}
-\ln \gamma^{\infty}_s = \frac{1}{k_b T} \left( \Delta G_\text{sim} - \Delta G_\text{sim}^{0} \right) + \frac{c_\text{\tiny IL}^{\, \ast}}{c_{\, s}^{\, \ast,0}},
+\ln \gamma_s = \frac{\Delta G_\text{sim} - \Delta G_\text{sim}^{0}}{k_b T} + \ln \frac{\tilde{\rho}}{\tilde{\rho}_s^0}.
 \end{equation}
-where $c_\text{\tiny IL}^{\, \ast}$ y $c_{\, s}^{\, \ast,0}$ are the numerical densities of the solvent and the pure solute, respectively.
+
+In the special case of a solute at infinite dilution in an ionic liquid solvent, its activity coefficient $\gamma^\infty_s$ can be computed by replacing $\tilde{\rho}$ in the equation above by the molar density of the pure solvent, $\tilde{\rho}_\textit{\tiny IL}$.
 

### 2018-09-07 ionic_liquids.tex
Refinement of Theoretical Background section

@@
 
-In this section, we present the formalism that allows us to compute solvation free energies from molecular dynamics simulations and, after that, obtain Henry constants and activity coefficients.
-For dealing with systems at infinite dilution, we rely on the work of Shirts \textit{et al}. \cite{Shirts_2003}.
-Then, we reformulate the equations in order to study concentrated solutions, which is a more likely scenario in the case of \ce{CO_2} capture processes.
+In this section, we present the formalism that allows us to compute solvation free energies from molecular dynamics simulations and, after that, to obtain Henry constants and activity coefficients.
+For dealing with systems at infinite dilution at low pressures, we rely on the work of Shirts \textit{et al}. \cite{Shirts_2003}.
+Then, we reformulate the equations in order to study concentrated solutions and systems at higher pressures, which is a more likely scenario in the case of \ce{CO_2} capture processes.
 
@@
 
-The solvation free energy, $\Delta G_{\text{solv}}$, is defined as the reversible work needed to transfer a solute molecule from a gas phase to the solution.
+The solvation free energy, $\Delta G_{\text{solv}}$, is defined as the reversible work needed to transfer a solute molecule from a gas phase to a liquid solution.
 For dense systems, an efficient computation of solvation properties via molecular simulation is possible by means of the so-called alchemical methods, which employ non-physical pathways to reversibly connect the endpoint states whose difference in free energy is to be estimated.
-In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through the use of a coupling parameter $\lambda$, which scales the solute-solvent interactions by taking values in the interval [0,1].
+In the case of $\Delta G_{\text{solv}}$, the alchemical route involves a gradual insertion/deletion of the solute through the definition of a coupling parameter $\lambda$, which scales the solute-solvent interactions by taking values in the interval [0,1].
 By convention, $\lambda = 1$ corresponds to a fully interacting system, while for $\lambda$ = 0 the solute-solvent interactions are turned off completely.
@@
 Note that $c_s = \frac{N_s}{N_A V_1}$.
-For small solutes, such as those considered in this work, the term containing the ratio $V^{\ast}/V_1$ is typically in the order of magnitude of the free-energy uncertainties \cite{Shirts_2003}.
-Hence, it can be neglected and will be omitted hereafter.
 
@@
 \label{eq:free_solv}
- \Delta G_{\text{solv}} \approx \Delta G_\text{sim}.
+ \Delta G_{\text{solv}} = \Delta G_\text{sim} - k_bT \ln \left( \frac{V^{\ast}}{V_1}\right).
 \end{split}
@@
 
+For small solutes, such as those considered in this work, the term containing the ratio $V^{\ast}/V_1$ is typically in the order of magnitude of the free-energy uncertainties \cite{Shirts_2003}.
+Hence, it can be neglected and will be omitted hereafter.
+
 \subsection*{Henry's Law Constant}
 
-If both $P_s$ and $c_s$ are small, we can resort to Eqs.~\eqref{eq:solvation free energy definition} and \eqref{eq:free_solv} to predict Henry's law constant $\text{K}_s$, which is defined as \cite{Prausnitz}
-\begin{equation}
-\text{K}_s =\frac{P_s}{x_s}.
-\end{equation}
-
+If both $P_s$ and $c_s$ are small, we can resort to Eqs.~\eqref{eq:solvation free energy definition} and \eqref{eq:free_solv} to predict Henry's law constant, which is defined as $\text{K}_s =\frac{P_s}{x_s}$ \cite{Prausnitz}.
+%\begin{equation}
+%\text{K}_s =\frac{P_s}{x_s}.
+%\end{equation}
+%
 Therefore, by simply expressing Eq.~\eqref{eq:solvation free energy definition} in terms of the molar fraction of the solute in the liquid phase ($x_s$) and assuming a dilute solution, whose molar density does not perceivably differ from that of pure solvent (that is, $\tilde{\rho} \approx \tilde{\rho}_\text{\tiny IL}$), we obtain that
@@
 
-For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} in the liquid phase are obtained at pressure values for which, in principle, the ideal gas assumption may not be valid.
+For the ILs of interest to the present investigation, high concentrations of \ce{CO_2} in the liquid phase are obtained at pressure values for which, in principle, the ideal gas assumption might no longer be valid.
 In this case, we can compute the chemical potential of the solute in the real gas phase as
@@
 \label{eq:equation for pressure}
-y_s P \exp\left( \frac{B_s P}{R T} \right) = \exp \left( \frac{\Delta G_\text{sim}}{k_b T} \right) +  c_s R T,
+y_s \exp\left( \frac{B_s P}{R T} \right) P = \exp \left( \frac{\Delta G_\text{sim}}{k_b T} \right) +  c_s R T,
 \end{equation}
@@
 Our third assumption, supported by preliminary simulations, is that $\Delta G_\text{sim}$ does not vary appreciably with pressure, at least over the range of experimental data considered here.
-In this way, no iterative simulations are required to compute the equilibrium pressure by solving Eq.~\eqref{eq:equation for pressure} for $P$.
+In this way, no iterative simulations are required to compute the equilibrium pressure when solving Eq.~\eqref{eq:equation for pressure} for $P$.
 
@@
 As will be shown below, the prediction of activity coefficients requires additional simulations of the solute as a pure liquid phase, whose properties we denote here by a superscript ``$0$''.
-We start by using standard thermodynamic relations \cite{Tester} to write the solute activity coefficient $\gamma_s$ in terms of chemical potentials as
+We start by using a standard thermodynamic relation \cite{Tester} to write the solute activity coefficient $\gamma_s$ in terms of chemical potentials as
 \begin{equation}
@@
 Next, we replace $\mu_s^l$ and $\mu_s^{l,0}$ by their corresponding instances of Eq.~\eqref{eq:solute chemical potential}.
-In this step, we note that $c_s = \tilde{\rho} x_s$ and $c_s^0 = \tilde{\rho}_s^0$, where $\tilde{\rho}$ and $\tilde{\rho}_s^0$ are the molar densities of the solution and of the pure liquid solute, respectively.
+In this step, we note that $c_s = \tilde{\rho} x_s$ and $c_s^0 = \tilde{\rho}_s^0$, where $\tilde{\rho}$ and $\tilde{\rho}_s^0$ are the molar densities of the solution and of pure liquid solute, respectively.
 Thus, the expression we obtain for computing an activity coefficient from two independent simulations is
@@
 \label{sec:force_field}
+
 \subsection{Ionic liquids}

### 2018-09-07 ionic_liquids.tex
Review of Force Fields section

@@
 On the other hand, this feature also explains why the desirable transferability of force fields is particularly difficult to attain.
-Indeed, it is a common practice to extract the potential parameters of the intramolecular (bond stretching, angle bending, torsion rotation) and Lennard-Jones (LJ) interactions from a well established force field and, then, only derive the partial atomic charges with the aim of ``adjusting'' the model for a specific pair of ions.
-This procedure is, however, inaccurate as in conventional force fields the determination of the atomic charges precedes the dihedrals parametrization.
-Another ad-hoc strategy, which intends to crudely incorporate polarization effects, is to scale the partial charges uniformly with a factor which normally takes values in the range 0.8-0.9.
+Indeed, it is a common practice to extract the potential parameters of the intramolecular (bond stretching, angle bending, torsion rotation) and Lennard-Jones (LJ) interactions from a well established force field and, then, only derive the partial atomic charges with the aim of adjusting the model for a specific pair of ions.
+This procedure is, however, inconsistent with conventional force field parameterization in which the determination of atomic charges precedes the establishment of torsional terms.
+Another ad-hoc strategy, which intends to roughly incorporate polarization effects, is to scale the partial charges uniformly with a factor which normally takes values in the range from 0.8 to 0.9.
 This has proven to be effective for predicting dynamic properties \cite{Schr_der_2012}.
 
-In this paper, we consider four models of \ce{[emim][B(CN)_4]}.
-Koller \textit{et al.} \cite{Koller_2012} were the first to introduce a specific non-polarizable force field for that IL.
-They tested three variations of a \textit{united-atoms} model, in which the alkyl groups \ce{CH_3} and \ce{CH_2} of \ce{[emim]^+} are replaced by pseudo-atoms.
-Among them, the ``FF-3'' model best reproduces the experimental values of density, self-diffusion coefficients and viscosity.
-In short, both the intramolecular and LJ parameters of the cation were taken from the work of Liu \textit{et al.} \cite{Liu_2006}, which in turn is based on the AMBER \cite{Cornell_1995} framework.
-The intramolecular parameters involving the boron atom were extracted from the DREIDING \cite{Mayo_1990} force field and the anionic vdW parameters were refined based on the values reported by Price \textit{et al.} \cite{Price_2001}.
-The atomic partial charges were derived using the EA-RESP method \cite{Basma_2001} from \textit{Post-Hartree-Fock ab-initio} calculations at MP2/6-31G$^\ast$+ level of theory, which automatically resulted in total charges on the ions of $\pm$0.8426$e$.
+In this paper, we analyze four different models for \ce{[emim][B(CN)_4]}.
+Koller \textit{et al}. \cite{Koller_2012} were the first to introduce a specific non-polarizable force field for this IL.
+They tested three variations of a united-atoms model, in which the hydrogen atoms of alkyl groups \ce{CH_3} and \ce{CH_2} of cation \ce{[emim]^+} are treated implicitly.
+Among these variations, the one named FF-3 best reproduces the experimental values of density, self-diffusion coefficients, and viscosity.
+In short, Koller \textit{et al}.
+\cite{Koller_2012} took both the intramolecular and LJ parameters for the cation from the work of Liu \textit{et al}.
+\cite{Liu_2006}, which in turn based their model on the AMBER \cite{Cornell_1995} framework.
+The intramolecular parameters involving the boron atom were extracted from the DREIDING \cite{Mayo_1990} force field and the anionic van der Waals parameters were refined based on the values reported by Price \textit{et al.} \cite{Price_2001}.
+The atomic partial charges were derived using the EA-RESP method \cite{Basma_2001} from Post-Hartree-Fock \textit{ab-initio} calculations at MP2/6-31G\textsuperscript{*}+ level of theory, which automatically resulted in total charges on the ions of $\pm0.8426~\mathrm{e}$.
 
-The potential parameters of \ce{[B(CN)_4]^-} derived by Koller \textit{et al.} \cite{Koller_2012} were then used by Batista \textit{et al.} \cite{Batista_2015} to study aqueous solutions of \ce{[emim][B(CN)_4]}.
-In this case, the authors considered the \textit{all-atom} model of \ce{[emim]^+} developed by Cadena and Maginn \cite{Cadena_2006}.
-The atomic partial charges were obtained using the CHELP procedure \cite{Breneman_1990}, resulting in net charges of $\pm$0.889$e$ on the ions.
-It should be noted that the factors for scaling the 1-4 non-bonded interactions are different for these force fields: Cadena and Maginn \cite{Cadena_2006} apply factors of 1.0 and 0.4 for the LJ and Coulombic interactions, respectively; while in Koller \textit{et al.} \cite{Koller_2012} the corresponding values are 0.5 and 5/6, in accordance with the AMBER force field.
-Batista \textit{et al.} \cite{Batista_2015} used the first ones (J.P. Coutinho, personal communication).
+Batista \textit{et al}. \cite{Batista_2015} then used the parameters of Ref.~\citenum{Koller_2012} for \ce{[B(CN)_4]^-} to study aqueous solutions of \ce{[emim][B(CN)_4]}.
+In this case, the authors considered the all-atom model of Cadena and Maginn \cite{Cadena_2006} for \ce{[emim]^+}.
+The atomic partial charges were obtained using the CHELP procedure \cite{Breneman_1990}, resulting in net charges of $\pm 0.889~\mathrm{e}$.
+It should be noted that the factors for scaling the 1-4 non-bonded interactions are different for these force fields.
+Cadena and Maginn \cite{Cadena_2006} apply factors of 1.0 and 0.4 for the LJ and Coulombic interactions, respectively, while for Koller \textit{et al}.
+\cite{Koller_2012} the corresponding values are 1/2 and 5/6, in accordance with the AMBER force field.
+Batista \textit{et al}. \cite{Batista_2015} used the former throughout (J. Coutinho, personal communication).
 
-Another set of parameters for \ce{[emim][B(CN)_4]} was derived by Liu \textit{et al.} \cite{Liu_2014} in a study that investigates the dynamics of \ce{CO_2} and \ce{N_2} in that IL.
-Parameters corresponding to the intramolecular and LJ interactions were extracted from GAFF \cite{Wang_2004}, while the atomic partial charges were computed using the RESP method \cite{Bayly_1993} from \textit{DFT}/B3LYP/6-311+G(d) calculations.
-The net charges of the ions were manually adjusted to a value of $\pm$0.8$e$.
+Another set of parameters for \ce{[emim][B(CN)_4]} was derived by Liu \textit{et al}.
+\cite{Liu_2014} in a study that investigates the dynamics of \ce{CO_2} and \ce{N_2} dissolved in this ionic liquid.
+Parameters corresponding to the intramolecular and LJ interactions were extracted from GAFF \cite{Wang_2004}, while the atomic partial charges were computed using the RESP method \cite{Bayly_1993} with B3LYP/6-311+G(d) DFT calculations.
+The net charges of the ions were manually adjusted to $\pm 0.8 \mathrm{e}$.
 
-We also consider the parametrization reported by Weber and Kirchner \cite{Weber_2016}, which is based on the force field developed by P{\'{a}}dua and Canongia Lopes~\cite{Canongia_Lopes_2006}.
-The potential parameters for the anion are not specified in Refs.~\citenum{Weber_2016} and~\citenum{Canongia_Lopes_2006}, and we obtained them by a direct communication with the authors of Ref.~\citenum{Weber_2016}.
-The atomic partial charges were derived using the RESP procedure from \textit{Hartree-Fock} calculations at 6-31++G$^{\ast \ast}$ level of theory, resulting in net charges of $\pm$0.8$e$.
+Finally, we also consider the parameterization which Weber and Kirchner \cite{Weber_2016} carried out for \ce{[emim][B(CN)_4]} based on the force field developed by P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
+As the potential parameters for the anion were specified neither in Ref.~\citenum{Weber_2016} nor in Ref.~\citenum{Canongia_Lopes_2006}, we obtained them by direct communication with the authors of Ref.~\citenum{Weber_2016}.
+The atomic partial charges were derived using the RESP procedure with Hartree-Fock calculations at the \mbox{6-31++G\textsuperscript{**}} level of theory, resulting in net charges of $\pm 0.8 \mathrm{e}$.
 
-Finally, for \ce{[emim][NTf_2]} we use the model of K\"{o}ddermann~\textit{et al.} \cite{K_ddermann_2007}, which was derived by refining the force field due to P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
-This refining was characterized by their authors as ``unusual'', given that the LJ parameters were modified, while keeping the partial charges at their original values.
-This model was recently employed by Kerl \textit{et al.} \cite{Kerl__2017}, who were able to accurately predict Henry constants of \ce{CO_2} at several temperatures.
+In the case of ionic liquid \ce{[emim][NTf_2]}, we use the model of K\"{o}ddermann \textit{et al}.
+\cite{K_ddermann_2007}, which was also derived by refining parameters of the force field by P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
+The authors characterized this refinement as unusual, given that they modified the LJ parameters while keeping the partial charges unchanged.
+Kerl \textit{et al}. \cite{Kerl__2017} recently employed this model to accurately predict Henry constants of \ce{CO_2} in \ce{[emim][NTf_2]} at several temperatures.
 
@@
 
-The solutes considered in this work are hexane, benzene, \ce{CO_2}, ethanol, cyclohexane and water.
+Besides \ce{CO_2}, the solutes considered in this work are hexane, benzene, ethanol, cyclohexane, and water.
 Hexane and benzene were modeled using the OPLS-AA force field \cite{Jorgensen_1996}, while the TRAPPE potential \cite{Chen_2001,Potoff_2001} was employed for ethanol and \ce{CO_2}.
-Cyclohexane was simulated using a rigid-body model \cite{munoz2015lennard} whose sites only interact via a LJ potential
+Cyclohexane was simulated using a rigid-body model \cite{munoz2015lennard} whose sites interact via a LJ potential only.
 For water, we employ the TIP4P/2005 model \cite{Abascal_2005,Vega_2011}.

### 2018-09-07 ionic_liquids.tex
Change from {et al.} to {et al}.

@@
 \cite{Liu_2006}, which in turn based their model on the AMBER \cite{Cornell_1995} framework.
-The intramolecular parameters involving the boron atom were extracted from the DREIDING \cite{Mayo_1990} force field and the anionic van der Waals parameters were refined based on the values reported by Price \textit{et al.} \cite{Price_2001}.
+The intramolecular parameters involving the boron atom were extracted from the DREIDING \cite{Mayo_1990} force field and the anionic van der Waals parameters were refined based on the values reported by Price \textit{et al}.
+\cite{Price_2001}.
 The atomic partial charges were derived using the EA-RESP method \cite{Basma_2001} from Post-Hartree-Fock \textit{ab-initio} calculations at MP2/6-31G\textsuperscript{*}+ level of theory, which automatically resulted in total charges on the ions of $\pm0.8426~\mathrm{e}$.
@@
 With the aim of setting up a computationally efficient protocol for the ILs, in this work we assess the possibility of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method \cite{Fennell2006} for computing the electrostatic interactions.
-As an alternative to the Ewald schemes \cite{Ewald_1921,Darden_1993,Hockney_1988}, McCann \textit{et al.} \cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force fields.
+As an alternative to the Ewald schemes \cite{Ewald_1921,Darden_1993,Hockney_1988}, McCann \textit{et al}.
+\cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force fields.
 They concluded that using $\alpha$ = 0.2 {\AA}$^{-1}$ and a cutoff distance ($r_c$) of 15 {\AA} provide the best energetic agreement with the Ewald method.
@@
 
-The NPT algorithm of Kamberaj \textit{et al.} \cite{Kamberaj_2005} was used to perform the simulations with rigid bodies.
-For flexible molecules, we applied the scheme due to Shinoda \textit{et al.} \cite{Shinoda2004} and C-H bonds were constrained by the SHAKE method \cite{Ryckaert1977}.
+The NPT algorithm of Kamberaj \textit{et al}. \cite{Kamberaj_2005} was used to perform the simulations with rigid bodies.
+For flexible molecules, we applied the scheme due to Shinoda \textit{et al}. \cite{Shinoda2004} and C-H bonds were constrained by the SHAKE method \cite{Ryckaert1977}.
 For both integrators, we used a time-step size ($\Delta t$) of 1 fs.
@@
 In order to avoid numerical instabilities associated to the vdW scaling, a standard approach is to employ a soft-core potential with a nonlinear coupling.
-In this paper we use the modified LJ potential due to Beutler \textit{et al.} \cite{Beutler_1994}.
+In this paper we use the modified LJ potential due to Beutler \textit{et al}. \cite{Beutler_1994}.
 The electrostatic interactions, on the other hand, can be handled by a linear scaling \cite{Naden_2015}.
@@
 The simulation times for the preliminary and final EE runs were 10 and 40 ns, respectively; and each $\lambda_{\text{Coul}}$ state was simulated for 10 ns.
-Finally, the MBAR method \cite{Shirts_2008}, as implemented by Klimovich \textit{et al.} \cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$.
+Finally, the MBAR method \cite{Shirts_2008}, as implemented by Klimovich \textit{et al}. \cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$.
 
@@
 In Fig.~\ref{fig:dihedrals_emim} we show the CDFs for each force field of \ce{[emim][B(CN)_4]}.
-A first inspection of this figure reveals a similar behavior of the models due to Koller \textit{et al.} \cite{Koller_2012} and Liu \textit{et al.} \cite{Liu_2014}.
+A first inspection of this figure reveals a similar behavior of the models due to Koller \textit{et al}. \cite{Koller_2012} and Liu \textit{et al}. \cite{Liu_2014}.
 This was expected as both are based on the AMBER framework \cite{Cornell_1995}.
@@
 In Fig.~\ref{fig:dihedrals_emim}(a), the most likely angles can be found in a narrow region around 90$^{\circ}$ and 270$^{\circ}$.
-Since these angles correspond to an equivalent configuration in the \textit{united-atom} \ce{[emim]^+}, in the case of Koller \textit{et al.} \cite{Koller_2012} we built all the rigid bodies by specifying 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1.
+Since these angles correspond to an equivalent configuration in the \textit{united-atom} \ce{[emim]^+}, in the case of Koller \textit{et al}.
+\cite{Koller_2012} we built all the rigid bodies by specifying 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1.
 The other models show a larger flexibility with high probability regions that extend in a broad range of angle values.
 Despite this, it was possible to build more than one type of rigid body by specifying the most probables angles of C6-C5-N2-C1.
-In the case of Liu \textit{et al.} \cite{Liu_2014}, these angles correspond to 90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed 102.6$^{\circ}$ and -102.6$^{\circ}$.
+In the case of Liu \textit{et al}.
+\cite{Liu_2014}, these angles correspond to 90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al}.
+\cite{Batista_2015}, we employed 102.6$^{\circ}$ and -102.6$^{\circ}$.
 These two types of rigid bodies were built in equal proportion.
@@
 When comparing cases (1) and (2) for each model, we note that the simulated densities practically do not differ.
-In addition, the models of Koller \textit{et al.} \cite{Koller_2012} and Weber and Kirchner \cite{Weber_2016} best reproduce the experimental value.
+In addition, the models of Koller \textit{et al}. \cite{Koller_2012} and Weber and Kirchner \cite{Weber_2016} best reproduce the experimental value.
 We have also computed radial distribution functions (RDFs), which can be found in the Supplementary material.
-The better agreement is found for the models of Koller \textit{et al.} \cite{Koller_2012} and Batista \textit{et al.} \cite{Batista_2015}.
-Despite the small deviations observed for the model of Liu \textit{et al.} \cite{Liu_2014}, the simulation with rigid bodies qualitatively reproduces the RDFs obtained for the flexible ions.
+The better agreement is found for the models of Koller \textit{et al}. \cite{Koller_2012} and Batista \textit{et al}. \cite{Batista_2015}.
+Despite the small deviations observed for the model of Liu \textit{et al}. \cite{Liu_2014}, the simulation with rigid bodies qualitatively reproduces the RDFs obtained for the flexible ions.
 Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion).
@@
 \centering
-\subfloat[Koller~\textit{et al.}~\cite{Koller_2012}]{%
+\subfloat[Koller~\textit{et al}.~\cite{Koller_2012}]{%
   \includegraphics[width=.4\linewidth]{koller}}%
-\subfloat[Batista~\textit{et al.}~\cite{Batista_2015}]{%  
+\subfloat[Batista~\textit{et al}.~\cite{Batista_2015}]{%  
   \includegraphics[width=.4\linewidth]{batista}}%
 
-\subfloat[Liu~\textit{et al.}~\cite{Liu_2014}]{%
+\subfloat[Liu~\textit{et al}.~\cite{Liu_2014}]{%
   \includegraphics[width=.4\linewidth]{Liu}}%
@@
 This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
-With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.} \cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
-Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al.} \cite{Deetlefs_2006}.
+With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al}.
+\cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
+Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al}. \cite{Deetlefs_2006}.
 Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy for building the rigid bodies is required.
@@
 In Table \ref{table:henry} we present the results of the solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}.
-Table~\ref{table:henry} also contains the experimental $K_s$ reported by Mahurin \textit{et al.} \cite{Mahurin_2010} and Finotello \textit{et al.} \cite{Finotello_2008}.
+Table~\ref{table:henry} also contains the experimental $K_s$ reported by Mahurin \textit{et al}. \cite{Mahurin_2010} and Finotello \textit{et al}. \cite{Finotello_2008}.
 The uncertainties in $K_s$ were calculated using standard error propagation.
@@
 			\hline
-Koller \textit{et al.} \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
-Batista \textit{et al.} \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
-Liu \textit{et al.} \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
+Koller \textit{et al}. \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
+Batista \textit{et al}. \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
+Liu \textit{et al}. \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
 Weber y Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
@@
 		\hline
- K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
+ K\"{o}ddermann \textit{et al}. \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
  \bottomrule
@@
 
-It should be pointed out that the result of $\Delta G_\text{sim}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent sampling of $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
-Moreover, the $\Delta G_\text{sim}$ in \ce{[emim][NTf_2]} is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
+It should be pointed out that the result of $\Delta G_\text{sim}$ obtained for the model of Liu \textit{et al}.
+\cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent sampling of $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
+Moreover, the $\Delta G_\text{sim}$ in \ce{[emim][NTf_2]} is very close to the value obtained by Kerl \textit{et al}.
+\cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
 These consistencies have served for validating the methodological approaches of this work.
 
-From Table \ref{table:henry} one can see that the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental value of $K_s$.
-If we look at the $\Delta G_{\lambda_{\,\text{vdW}}}$ profiles in Fig.~\ref{fig:deltag}, we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014} the maximum occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which may also explain their failure to reproduce the experimental density.
+From Table \ref{table:henry} one can see that the model of Koller \textit{et al}. \cite{Koller_2012} best reproduces the experimental value of $K_s$.
+If we look at the $\Delta G_{\lambda_{\,\text{vdW}}}$ profiles in Fig.~\ref{fig:deltag}, we observe that for the models of Batista \textit{et al}.
+\cite{Batista_2015} and Liu \textit{et al}.~\cite{Liu_2014} the maximum occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which may also explain their failure to reproduce the experimental density.
 
@@
 \includegraphics[width=\linewidth]{free_energy_paper}
-\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, which was modeled according to the force fields of (circles) Koller \textit{et al.} \cite{Koller_2012}, (squares) Batista \textit{et al.} \cite{Batista_2015}, (up triangles) Liu \textit{et al.} \cite{Liu_2014}, and (x) Weber y Kirchner \cite{Weber_2016}.}
+\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, which was modeled according to the force fields of (circles) Koller \textit{et al}.
+\cite{Koller_2012}, (squares) Batista \textit{et al}.
+\cite{Batista_2015}, (up triangles) Liu \textit{et al}.
+\cite{Liu_2014}, and (x) Weber y Kirchner \cite{Weber_2016}.}
 \label{fig:deltag}
@@
 
-The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}.
+The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al}.
+\cite{Koller_2012} and K\"{o}ddermann \textit{et al}.
+\cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}.
 The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm this result.
@@
 Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we have also carried out simulations at the thermodynamic conditions specified in Table~\ref{table:solv}, which correspond to similar values of \ce{CO_2} molality.
-Note that the differences in the \ce{CO_2} molar fractions clearly exemplifies the observation made by Carvalho \textit{et al.} \cite{Carvalho_2016}, mentioned at the introduction of this paper.
+Note that the differences in the \ce{CO_2} molar fractions clearly exemplifies the observation made by Carvalho \textit{et al}. \cite{Carvalho_2016}, mentioned at the introduction of this paper.
 
@@
 One of the goals of this paper was to compare various available models of \ce{[emim][B(CN)_4]} in terms of their capability to reproduce the experimental Henry constant of \ce{CO_2}.
-We have found that only the force field developed by Koller \textit{et al.} \cite{Koller_2012} is able to perform such task, with a small relative error of 2.8 \%.
+We have found that only the force field developed by Koller \textit{et al}. \cite{Koller_2012} is able to perform such task, with a small relative error of 2.8 \%.
 A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in that work, which also allows to accurately reproduce the experimental density of the pure substance.
@@
 
-Finally, we employed the model of Koller \textit{et al.} \cite{Koller_2012} to predict infinite-dilution activity coefficients of various solutes.
+Finally, we employed the model of Koller \textit{et al}. \cite{Koller_2012} to predict infinite-dilution activity coefficients of various solutes.
 In this case, the results were not satisfactory given the large errors in the free energy calculations of the pure solutes, making necessary a revision of their force fields in a future work.

### 2018-09-08 ionic_liquids.tex
Revision of the Computational Methods section

@@
 
-With the aim of setting up a computationally efficient protocol for the ILs, in this work we assess the possibility of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method \cite{Fennell2006} for computing the electrostatic interactions.
-As an alternative to the Ewald schemes \cite{Ewald_1921,Darden_1993,Hockney_1988}, McCann \textit{et al}.
-\cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force fields.
-They concluded that using $\alpha$ = 0.2 {\AA}$^{-1}$ and a cutoff distance ($r_c$) of 15 {\AA} provide the best energetic agreement with the Ewald method.
-In this work, comparisons are made in terms of the simulated densities and radial distribution functions for which, as will be shown in the next section, $\alpha$ = 0.2 {\AA}$^{-1}$ and $r_c$ = 12 {\AA} resulted in a good agreement.
-These values were also employed for the charged solutes, with the exception of hexane, for which we applied undamped Coulombic interactions improving the prediction of the chemical potential.
+With the aim of setting up a computationally efficient protocol for the IL simulations, in this work we assess the possibilities of modeling the ions as rigid bodies and employing the damped shifted force (DSF) method \cite{Fennell2006} for computing electrostatic interactions.
+In this method, the electrostatic potential between two atoms with charges $q_i$ and $q_j$ interacting at a distance $r$ is given by
+\begin{equation}
+V_\text{\tiny DSF}(r) = V(r) - V(r_c) - V^\prime(r_c)(r-r_c),
+\end{equation}
+where $V(r) = q_i q_j {\text{erfc}(\alpha r)}/{r}$ is a damped Coulomb potential.
+This potential is cut off at $r = r_c$, which makes it short-ranged and thus a cheaper alternative to Ewald-type schemes \cite{Ewald_1921,Darden_1993,Hockney_1988}.
+McCann \textit{et al}. \cite{McCann_2013} tested the DSF method for various ILs modeled with the OPLS-AA force field.
+They concluded that using $\alpha = 0.2~\text{\AA}^{-1}$ and $r_c = 15~\text{\AA}$ provides the best energetic agreement with the Ewald method.
+In this work, detailed comparisons are made in terms of the simulated densities and radial distribution functions.
+In Sec.~\ref{sec:results}, we show that by using the same $\alpha$ value but a considerably smaller cutoff distance ($r_c = 12 \text{\AA}$) one can obtain suitable results.
+These values were employed here for the ILs as well as for solutes containing partially charged atoms.
+The only exception was hexane, for which the use of undamped Coulombic interactions (i.e. $\alpha = 0$) resulted in improved chemical potential predictions.
 
-The NPT algorithm of Kamberaj \textit{et al}. \cite{Kamberaj_2005} was used to perform the simulations with rigid bodies.
-For flexible molecules, we applied the scheme due to Shinoda \textit{et al}. \cite{Shinoda2004} and C-H bonds were constrained by the SHAKE method \cite{Ryckaert1977}.
-For both integrators, we used a time-step size ($\Delta t$) of 1 fs.
+The NPT algorithm of Kamberaj \textit{et al}. \cite{Kamberaj_2005} was used to integrate the equations of motion for rigid bodies.
+For flexible molecules, we applied the integration scheme of Shinoda \textit{et al}. \cite{Shinoda2004}, with the lengths of all C-H bonds constrained by the SHAKE method \cite{Ryckaert1977}.
+For both integrators, we used a small time-step size ($\Delta t$) of 1 fs in order to avoid discretization-induced artifacts \cite{Eastwood_2010, Silveira_2017}.
 
-The gradual insertion/deletion of charged solutes involves scaling both the van der Waals (vdW) and the electrostatic intermolecular interactions.
-In order to avoid numerical instabilities associated to the vdW scaling, a standard approach is to employ a soft-core potential with a nonlinear coupling.
-In this paper we use the modified LJ potential due to Beutler \textit{et al}. \cite{Beutler_1994}.
-The electrostatic interactions, on the other hand, can be handled by a linear scaling \cite{Naden_2015}.
-Furthermore, the contributions to $\Delta G$ originating at the different couplings are taken into account separately, as follows:
+The gradual insertion/deletion of solutes involves scaling both the van der Waals (vdW) and the electrostatic intermolecular interactions.
+To avoid numerical instabilities associated to the vdW scaling, it is usual to employ a soft-core potential with nonlinear coupling.
+In this paper, we use the modified LJ potential proposed by Beutler \textit{et al}.
+\cite{Beutler_1994}, given by $V_\text{\tiny vdW}(r) = 4 \epsilon \lambda_\text{\tiny vdW} (s^{-2} - s^{-1})$, where $s = (r/\sigma)^6 + (1 - \lambda_\text{\tiny vdW})/2$.
+The electrostatic interactions, on the other hand, can be simply multiplied by a coupling parameter $\lambda_\text{\tiny Coul}$ \cite{Naden_2015}.
+Furthermore, the vdW and Coulomb contributions to the free energy difference are taken into account separately.
+That is,
 \begin{equation}
-\begin{split}
-\Delta G_\text{sim} =& \; \Delta G_{\,\text{vdW}} (\lambda_{\,\text{vdW}} = 0\rightarrow  1, \lambda_{\, \text{Coul}} = 0) \\
-+ \; &\Delta G_{\,\text{Coul}} (\lambda_{\, \text{vdW}} = 1,\lambda_{\,\text{Coul}} = 0 \rightarrow 1),
-\end{split}
+\Delta G_\text{sim} = \Delta G_\text{\tiny vdW} + \Delta G_\text{\tiny Coul},
 \end{equation}
-where $\lambda_{\,\text{vdW}}$ and $\lambda_{\,\text{Coul}}$ are the coupling parameters of the soft-core and electrostatic potentials, respectively.
-Note that in the process of coupling the vdW interactions, the Coulombic interactions are turned-off, while we set $\lambda_{\,\text{vdW}}$ = 1 when computing $\Delta G_{\,\text{Coul}}$.
-This results in the ``end-point'' states given by ($\lambda_{\,\text{vdW}}$=0,$\lambda_{\,\text{Coul}}$=0) and ($\lambda_{\,\text{vdW}}$=1,$\lambda_{\,\text{Coul}}$=1), as expected.
-The complete sets of the coupling parameters we use here are $\lambda_{\text{vdW}}$ = $\{0.0$, $0.05$, $0.1$, $0.2$, $0.25$, $0.3$, $0.35$, $0.4$, $0.45$, $0.5$, $0.6$, $0.7$, $0.8$, $0.9$, $1.0\}$ and $\lambda_{\text{Coul}}$ = $\{0.0$, $0.1$, $0.4$, $0.7$, $0.1\}$.
+where $\Delta G_\text{\tiny vdW}$ is computed by varying $\lambda_\text{\tiny vdW} \in [0,1]$ while keeping $\lambda_\text{\tiny Coul} = 0$, whereas $\Delta G_\text{\tiny Coul}$ is computed by varying $\lambda_\text{\tiny Coul} \in [0,1]$ while keeping $\lambda_\text{\tiny vdW} = 1$.
+The sets of coupling parameter values we use here in all alchemical simulations are $\lambda_{\text{\tiny vdW}}$ = $\{0.0$, $0.05$, $0.1$, $0.2$, $0.25$, $0.3$, $0.35$, $0.4$, $0.45$, $0.5$, $0.6$, $0.7$, $0.8$, $0.9$, $1.0\}$ and $\lambda_{\text{\tiny Coul}}$ = $\{0.0$, $0.1$, $0.4$, $0.7$, $0.1\}$.
 
-In this work, we carried out independent simulation at each state of $\lambda_{\text{Coul}}$, while the expanded ensemble (EE) method~\cite{Lyubartsev_1992} was applied for sampling the $\lambda_{\,\text{vdW}}$ set.
-In short, an EE is constructed as a weighted sum of subensembles, each assuming a different value of the variable chosen to explore the free energy landscape, which in our case is $\lambda_{\,\text{vdW}}$.
-This way, the sampling of an EE comprises both sampling each subensamble with fixed variables (N,P,T,$\lambda_{\,\text{vdW}}$) and transitions in $\lambda_{\,\text{vdW}}$.
-Thus, a remarkable feature of the EE method is the possibility of exploring the whole alchemical route in a single simulation.
-In this work, we perform a sequential sampling of the EE \cite{Chodera_2011_2}, which consists in sampling each subensamble via NPT molecular dynamics (MD) for a determined number of steps $N^{\text{EE}}$ followed by an attempt to change $\lambda_{\,\text{vdW}}$ using MC, and so on.
-The $\lambda_{\,\text{vdW}}$ transitions are performed according to an independent sampling scheme \cite{Chodera_2011_2}.
-In addition, the set of (arbitrary) weights $\eta$ of the subensambles enters in the acceptance criteria of MC, so it is possible to tune $\eta$ in order to enhance the sampling.
-If differences $\eta_i$ - $\eta_j$ were closed to $\Delta G_{ji}$, we expect an uniform sampling in $\lambda_{\,\text{vdW}}$ \cite{Lyubartsev_1992}.
-Of course, this can be achieved only iteratively.
-The EE procedure, together with the \textit{soft-core} potential and the DSF method with linear coupling were implemented in the LAMMPS software package \cite{Plimpton1995}, which we used for carrying out all the simulations.
+In this work, we compute $\Delta G_\text{\tiny Coul}$ by carrying out an independent simulation of 10 ns at each state of $\lambda_{\text{\tiny Coul}}$.
+In the end, we apply the Multistate Bennett Acceptance Ratio (MBAR) method \cite{Shirts_2008} by using the \textit{Alchemical Analysis} package \cite{Klimovich_2015}.
 
-As demonstrated in Ref.~\citenum{Chodera_2011_2}, smaller values of $N^{EE}$ yield more decorrelated samples in each subensemble.
-In this work, we employed $N^{EE}$ = 5 which, together with the specified $\lambda_{\, \text{vdW}}$ set, required up to 3 preliminary runs of the EE for determining the weights $\eta$ that yielded, in a final simulation, a ``sufficient'' sampling of each subensamble.
-By ``sufficient'', we mean that the sampling provides an acceptable uncertainty in $\Delta G$.
-The simulation times for the preliminary and final EE runs were 10 and 40 ns, respectively; and each $\lambda_{\text{Coul}}$ state was simulated for 10 ns.
-Finally, the MBAR method \cite{Shirts_2008}, as implemented by Klimovich \textit{et al}. \cite{Klimovich_2015}, was applied to estimate $\Delta G_{\text{vdW}}$ and $\Delta G_{\text{Coul}}$.
+In the case of $\Delta G_\text{\tiny vdW}$, the Expanded Ensemble method \cite{Lyubartsev_1992} is applied for sampling the whole $\lambda_\text{\tiny vdW}$ set in a single simulation.
+An expanded ensemble is constructed as a weighted sum of subensembles, each one assuming a different value of the parameter selected for exploring the free energy landscape, which in our case is $\lambda_\text{\tiny vdW}$.
+In the method adopted here \cite{Chodera_2011_2}, simulating an expanded ensemble comprises doing molecular dynamics (MD) at fixed N, P, T, and $\lambda_\text{\tiny vdW}$ amid Monte Carlo (MC) transitions in the value of $\lambda_\text{\tiny vdW}$.
+The number of MD steps between transitions is fixed and, at each transition, one of the $\lambda_\text{\tiny vdW}$ states is picked at random according to a corresponding set of probabilities \cite{Chodera_2011_2}.
+In addition, a set of biasing weights is included in the MC acceptance criterion, thus making it possible to enhance the sampling procedure by iteratively tuning these weights until all $\lambda_\text{\tiny vdW}$ states are visited with equal frequency \cite{Lyubartsev_1992}.
+Given that sample decorrelation is improved by having short MD runs between MC transitions \cite{Chodera_2011_2}, we used only 5 steps in each run.
+In the iteration process for tuning the biasing weights, the simulation times for the preliminary and the final expanded ensemble rounds are 10 and 40 ns, respectively.
+In this way, 3 iterations were sufficient in all cases for attaining, in the final round, an acceptable uncertainty in $\Delta G_\text{sim}$ estimated via MBAR \cite{Shirts_2008, Klimovich_2015}.
 
-The initial configurations were obtained with PLAYMOL \cite{playmol}, a software integrated with PACKMOL \cite{Mart_nez_2009}, using the tool \textit{build} to specify geometric data (bond and angle lengths, and dihedral angles), from which PLAYMOL automatically determines the Cartesian coordinates.
-We first carried out NVT MD simulations of the isolated ion pairs in order to obtain a minimum energy conformation.
-For this, we used the Nos\'{e}-Hoover thermostat \cite{Martyna1992} and a cubic box of length L = 50 {\AA} with non-periodic boundary conditions.
-After a short run with $\Delta t$ = $0.5~\text{fs}$, we carried out a ``quenching'' simulation with $\Delta t$ = $1 ~\text{fs}$, in which the temperature is gradually reduced until reaching a value close to $0~\text{K}$.
-The resulting coordinates were then specified in PLAYMOL \cite{playmol} to build the configurations of the liquid phases.
+We first carried out MD simulations of isolated ion pairs in order to obtain minimum-energy conformations.
+For this, we used a Nos\'{e}-Hoover chain thermostat \cite{Martyna1992} with set-point temperature gradually changing down to nearly $0~\text{K}$.
+The resulting coordinates were then used with the PACKMOL algorithm \cite{Mart_nez_2009} via the Playmol package \cite{playmol} to obtain initial liquid-phase configurations.
+The expanded ensemble procedure, the softcore potential, and the DSF method  with linear coupling were implemented by customizing the LAMMPS package \cite{Plimpton1995}, which we used for carrying out all the simulations in this work.
 

### 2018-09-08 ionic_liquids.tex
Changes in Table 1

@@
 \label{eq:gamma}
-\ln \gamma_s = \frac{\mu_s^l - \mu_s^{l,0}}{k_B T} - \ln x_s,
+\ln \gamma_s = \frac{\mu_s^l - \mu_s^{l,0}}{k_b T} - \ln x_s,
 \end{equation}
@@
 \begin{table*}
-\begin{threeparttable}
-\caption{Comparison of predicted and experimental densities for differents models of \ce{[emim][B(CN)_4]} via NPT-MD simulations at $T = 298.0~\text{K}$ and $P = 1.0~\text{atm}$.
-The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
-\begin{tabular}{ c  c  c  c  c}  
-\hline \hline
-\ce{[emim][B(CN)_4]}&  $\rho_\text{sim}$ & error (\%)\tnote{a}  & $\rho_\text{sim}$ & error (\%)\tnote{a} \\
-model & (g/cm$^{3}$) &  &  (g/cm$^{3}$) &  \\
+\centering
+\caption{Comparison of predicted and experimental densities for different models of \ce{[emim][B(CN)_4]} via NPT-MD simulations at $T = 298.0~\text{K}$ and $P = 1.0~\text{atm}$.
+The experimental density is $1.036~\mathrm{g/cm^3}$ \cite{Doma_ska_2011}.}
+\begin{tabular}{ccccc}
 \hline
-& \multicolumn{2}{c}{Flexible ions/Ewald method} & \multicolumn{2}{c}{Rigid ions/DSF method} \\
-Koller y col. \cite{Koller_2012}    & 1.046 & 1.0 & 1.038 & 0.2 \\
-Batista y col. \cite{Batista_2015}  & 0.989 & 4.6 & 0.988 & 4.7 \\
-Liu y col. \cite{Liu_2014}          & 1.001 & 3.4 & 0.991 & 4.4 \\
-Weber y Kirchner. \cite{Weber_2016} & 1.015 & 2.1 & 1.022 & 1.4  \\
- \hline \hline
+\hline
+\ce{[emim][B(CN)_4]} model                        & 
+\multicolumn{2}{c}{Flexible ions \& Ewald method} &
+\multicolumn{2}{c}{Rigid ions \& DSF method}      \\
+                                            &
+$\rho_\text{sim}$ (g/cm\textsuperscript{3}) &
+error (\%)                                  &
+$\rho_\text{sim}$ (g/cm\textsuperscript{3}) &
+error (\%)                                  \\
+\hline
+Koller \textit{et al}. \cite{Koller_2012}    & 1.046 & 1.0 & 1.038 & 0.2 \\
+Batista \textit{et al}. \cite{Batista_2015}  & 0.989 & 4.6 & 0.988 & 4.7 \\
+Liu \textit{et al}. \cite{Liu_2014}          & 1.001 & 3.4 & 0.991 & 4.4 \\
+Weber and Kirchner \cite{Weber_2016}         & 1.015 & 2.1 & 1.022 & 1.4  \\
+\hline
+\hline
 \label{table:props_dsf}
 \end{tabular}
-\begin{tablenotes}
-\item[a] error = 100 $\times$($\rho^{\text{exp}}$$ - $$\rho^\text{sim}$)/$\rho^{\text{exp}}$.
-\end{tablenotes}
-\end{threeparttable}
 \end{table*}

### 2018-09-11 ionic_liquids.tex
Rigid body construction

@@
 
+\usepackage{color,soul} % TEMPORARY
+
 \usepackage[colorlinks,citecolor=blue]{hyperref}
-\usepackage{lineno}
-\modulolinenumbers[5]
+%\usepackage{lineno}
+%\modulolinenumbers[5]
 \usepackage{amsmath}
@@
 
-\usepackage{amsmath}
-\usepackage{commath}
 \usepackage{graphicx}
 \DeclareGraphicsExtensions{.pdf,.eps,.png}
-\usepackage{float}
-\usepackage{subfig}
+%\usepackage{float}
+\usepackage[position=top,captionskip=-15pt]{subfig}
 
@@
 
-\linenumbers
+%\linenumbers
 
@@
 
-\section{Results and discussion}
+\section{Results and Discussion}
 \label{sec:results}
 
-\subsection{Simulation strategies of ILs}
+\subsection{Ionic-Liquid Simulation Strategies}
 \label{sec:prel_results}
 
-In this section, we present results for the following two cases: (1) flexible ions together with the Particle-Particle-Particle-Mesh (PPPM) method~\cite{Hockney_1988} with a tolerance of 1$\times$10$^{-4}$ for calculating the Coulombic interactions, and (2) ions modeled as rigid bodies with the DSF method \cite{Fennell2006} ($\alpha$ = 0.2 {\AA}$^{-1}$) as the alternative to the PPPM scheme.
-In both cases, $r_c$ = 12 {\AA}.
-The nomenclature used in this paper is shown in Fig~\ref{fig:atoms_id}.
-In the \textit{united-atoms} version of \ce{[emim]^+}, hydrogens ranging from H4 to H11 are eliminated.
+In this section, we analyze the possibility of introducing simplifications in the molecular modeling and simulation of ionic liquids without substantially affecting the resulting thermodynamics properties.
+For this, we compare results obtained with a standard methodology to those obtained with a simplified one.
+The standard setup comprises simulating ions with moving bonds, angles, and dihedrals and using the Particle-Particle/Particle-Mesh (PPPM) Ewald method \cite{Hockney_1988} for calculating the Coulomb interactions.
+In this case, a real-space cutoff of $12~\text{\AA}$ and a tolerance of $10^{-4}$ are used in LAMMPS for automatic determination of PPPM parameters such as damping factor and FFT grid spacing.
+In the simplified setup, the ions are modeled as rigid bodies and the DSF method \cite{Fennell2006} with $r_c = 12 ~\text{\AA}$ and $\alpha = 0.2 ~\text{\AA}^{-1}$) is used as and alternative to the PPPM scheme.
+For building the rigid bodies, we carry out a frequency analysis of some key dihedrals present in ions \ce{[emim]^+} and \ce{[NTf_2]^-}, whose flexibility could lead to significant conformational changes.
+On the other hand, small and highly symmetric anions such as \ce{PF_6} and \ce{BF_4} are already usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies the strategy in the case of \ce{[B(CN)_4]^-}.
 
-The rigid bodies were built after carrying out an analysis of key dihedrals, whose flexibility could lead to significant conformational changes in \ce{[emim]^+} and \ce{[NTf_2]^-}.
-On the other hand, small and highly symmetric anions, such as \ce{PF_6} and \ce{BF_4} are usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies the strategy in the case of \ce{[B(CN)_4]^-}.
+As a guide to the discussions we put forward in this section, in Fig~\ref{fig:atoms_id} we introduce a nomenclature for all atoms present in the ions \ce{[emim]^+}, \ce{[B(CN)_4]^-}, and \ce{[NTf_2]^-}.
+Please note that, in the united-atom version of \ce{[emim]^+}, all hydrogen atoms ranging from H4 to H11 are incorporated to their corresponding carbon atoms.
 
-\begin{figure}[ht]
+\begin{figure}
 \centering
 \includegraphics[width=\linewidth]{atoms_id.pdf}
-\caption{Adopted nomenclature for 1-ethyl-3-methylimidazolium  (\ce{[emim]^+}), tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
+\caption{Adopted nomenclature for individual atoms in the cation 1-ethyl-3-methylimidazolium (\ce{[emim]^+}) and anions tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
 \label{fig:atoms_id}
@@
 
-Using the software TRAVIS \cite{Brehm_2011}, we obtained the combined distribution functions (CDFs) of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs at $T = 298.0~\text{K}$ and $P = 1.0~\text{bar}$.
-In Fig.~\ref{fig:dihedrals_emim} we show the CDFs for each force field of \ce{[emim][B(CN)_4]}.
-A first inspection of this figure reveals a similar behavior of the models due to Koller \textit{et al}. \cite{Koller_2012} and Liu \textit{et al}. \cite{Liu_2014}.
-This was expected as both are based on the AMBER framework \cite{Cornell_1995}.
-In addition, Figs.~\ref{fig:dihedrals_emim}(a) and \ref{fig:dihedrals_emim}(b) are symmetric, which means that atoms C1, N2, and C2 are coplanar.
-In Fig.~\ref{fig:dihedrals_emim}(a), the most likely angles can be found in a narrow region around 90$^{\circ}$ and 270$^{\circ}$.
-Since these angles correspond to an equivalent configuration in the \textit{united-atom} \ce{[emim]^+}, in the case of Koller \textit{et al}.
-\cite{Koller_2012} we built all the rigid bodies by specifying 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1.
-The other models show a larger flexibility with high probability regions that extend in a broad range of angle values.
-Despite this, it was possible to build more than one type of rigid body by specifying the most probables angles of C6-C5-N2-C1.
-In the case of Liu \textit{et al}.
-\cite{Liu_2014}, these angles correspond to 90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al}.
-\cite{Batista_2015}, we employed 102.6$^{\circ}$ and -102.6$^{\circ}$.
-These two types of rigid bodies were built in equal proportion.
-Fig.~\ref{fig:dihedrals_emim}(d) corresponds to Weber and Kirchner \cite{Weber_2016}. 
-Given the wide range of sampled angles, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of them, respectively; and 0$^{\circ}$ for the remaining 15~\%.
+Using the software TRAVIS \cite{Brehm_2011}, we obtained combined distribution functions (CDFs) of the dihedral angles formed in \ce{[emim]^+} by atoms C1-N2-C5-C6 and atoms C2-N2-C5-C6.
+These angles will be referred to as $\psi$ and $\chi$, respectively.
+In Fig.~\ref{fig:dihedrals_emim}, we show the CDFs obtained for all force fields employed here for \ce{[emim][B(CN)_4]}.
+The CDFs were generated from NPT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using our standard setup.
+Initial inspection reveals that, in all cases, $\psi$ and $\chi$ populate regions of the diagrams around the two straight lines given by
+\begin{equation}
+\label{eq:dihedral angles}
+\psi = \begin{cases}
+\chi + 180^\circ & \text{if} \quad \chi \leq 180^\circ \\
+\chi - 180^\circ & \text{if} \quad \chi > 180^\circ
+\end{cases},
+\end{equation}
+both corresponding to a coplanar structure formed by atoms C1, C2, N2, and C5.
+There are two such lines in each diagram because atom C6 can be located on either side of the plan.
+One can note in Fig.~\ref{fig:dihedrals_emim} that the CDF peaks (i.e. the most likely dihedral angle combinations) lie either precisely above these lines or very close to them.
+The largest distortions from coplanarity occur for the Batista \textit{et al}. \cite{Batista_2015} model, as observed by the peak locations in Fig.~\ref{fig:dihedrals_emim}(b).
+Despite this, all rigid bodies considered here for \ce{[emim]^+} are built in such a way that atoms C[1-5], H[1-3], and N[1-2] all lie in a single plan.
+Therefore, for specifying the torsion of bond N2-C5 it is enough to set a value for $\chi$ and then compute $\psi$ by means of Eq.~\eqref{eq:dihedral angles}.
+All other structural features (bond lengths, bending angles, and hydrogen-involving dihedrals) are taken from the minimum-energy structure obtained for each force field.
+
+One can note in Figs.~\ref{fig:dihedrals_emim}(a) and \ref{fig:dihedrals_emim}(c) that the Koller \textit{et al}.
+\cite{Koller_2012} and Liu \textit{et al}.
+\cite{Liu_2014} models display a very similar, orderly behavior with regard to the torsion angles.
+The similarity is not surprising since both models are based on the AMBER framework \cite{Cornell_1995}.
+In both diagrams, the most likely angle combinations can be found in narrow regions around $\chi = 90^\circ$ and $\chi = 270^\circ$.
+These angles correspond to similar configurations (imagine, for instance, the effect of rotating the whole cation around the axis defined by bond N2-C5).
+Hence, we decided to build a single rigid-body structure with $\chi = 90^\circ$ for the united-atom version of \ce{[emim]^+}, which is the model of Koller \textit{et al}. \cite{Koller_2012}.
+In the case of the all-atom model of Liu \textit{et al}. \cite{Liu_2014}, we considered a system composed by equal amounts of two rigid-body structures with $\chi = 90^\circ$ and $\chi = 270^\circ$.
+For the Batista \textit{et al}. \cite{Batista_2015} model, the regions of likely angle combinations comprise convoluted peaks.
+By means of weighted averages, we decided to set $\chi = 77.4^\circ$ and $\chi = 282.6^\circ$ so as to build two types of rigid bodies, also considered in equal amounts.
+Finally, given the wide ranges of likely angle combinations in the case of the Weber and Kirchner model \cite{Weber_2016}, as observed in Fig.~\ref{fig:dihedrals_emim}(d), we defined four types of rigid bodies in this case to fulfill the system in different proportions.
+The $\chi$-angle values for these types are $0^\circ$, $30^\circ$, $180^\circ$, and $330^\circ$, while their fractions in the system are 25\%, 30\%, 15\%, and 30\%, respectively.
 
@@
 \centering
-\subfloat[Koller~\textit{et al}.~\cite{Koller_2012}]{%
-  \includegraphics[width=.4\linewidth]{koller}}%
-\subfloat[Batista~\textit{et al}.~\cite{Batista_2015}]{%  
-  \includegraphics[width=.4\linewidth]{batista}}%
+\subfloat[][Koller~\textit{et al}.~\cite{Koller_2012}]{
+  \includegraphics[width=.4\linewidth]{koller}}
+\subfloat[Batista~\textit{et al}.~\cite{Batista_2015}]{  
+  \includegraphics[width=.4\linewidth]{batista}}
 
@@
   \includegraphics[width=.4\linewidth]{Weber}}%
+
 \caption{Combined distribution function of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs for each model of \ce{[emim][B(CN)_4]}.}
+
 \label{fig:dihedrals_emim}
@@
 
-\begin{figure}[ht]
+\begin{figure}
 \centering
@@
 Liu \textit{et al}. \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
-Weber y Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
+Weber and Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
 \hline
@@
 
-\begin{figure}[ht]
+\begin{figure}
 \includegraphics[width=\linewidth]{free_energy_paper}
@@
 \cite{Batista_2015}, (up triangles) Liu \textit{et al}.
-\cite{Liu_2014}, and (x) Weber y Kirchner \cite{Weber_2016}.}
+\cite{Liu_2014}, and (x) Weber and Kirchner \cite{Weber_2016}.}
 \label{fig:deltag}
@@
 Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.~\ref{fig:sdf_ions} (c).
-\begin{figure}[ht]
+\begin{figure}
 \centering
@@
 
-\begin{figure}[ht]
+\begin{figure}
 \includegraphics[width=\linewidth]{pressure_est.pdf}

### 2018-09-11 ionic_liquids.tex
Further revision of rigid body strategies

@@
 
-\title{A molecular dynamics study of the solvation of carbon dioxide in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
+\title{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 %\title{A molecular dynamics study of the solvation of \ce{CO_2}, \ce{H_2O}, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
@@
 In this section, we analyze the possibility of introducing simplifications in the molecular modeling and simulation of ionic liquids without substantially affecting the resulting thermodynamics properties.
-For this, we compare results obtained with a standard methodology to those obtained with a simplified one.
+For this, we compare results obtained with a \textit{standard} methodology to those obtained with a \textit{simplified} one.
 The standard setup comprises simulating ions with moving bonds, angles, and dihedrals and using the Particle-Particle/Particle-Mesh (PPPM) Ewald method \cite{Hockney_1988} for calculating the Coulomb interactions.
@@
 Using the software TRAVIS \cite{Brehm_2011}, we obtained combined distribution functions (CDFs) of the dihedral angles formed in \ce{[emim]^+} by atoms C1-N2-C5-C6 and atoms C2-N2-C5-C6.
-These angles will be referred to as $\psi$ and $\chi$, respectively.
+These angles will be referred to as $\psi_1$ and $\psi_2$, respectively.
 In Fig.~\ref{fig:dihedrals_emim}, we show the CDFs obtained for all force fields employed here for \ce{[emim][B(CN)_4]}.
-The CDFs were generated from NPT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using our standard setup.
-Initial inspection reveals that, in all cases, $\psi$ and $\chi$ populate regions of the diagrams around the two straight lines given by
+The CDFs were generated from NPT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using our standard setup (i.e. flexible ions with PPPM Ewald electrostatics).
+Initial inspection reveals that, in all cases, $\psi_1$ and $\psi_2$ populate regions of the diagrams around the two straight lines given by
 \begin{equation}
 \label{eq:dihedral angles}
-\psi = \begin{cases}
-\chi + 180^\circ & \text{if} \quad \chi \leq 180^\circ \\
-\chi - 180^\circ & \text{if} \quad \chi > 180^\circ
+\psi_2 = \begin{cases}
+\psi_1 + 180^\circ & \text{if} \quad \psi_1 \leq 180^\circ \\
+\psi_1 - 180^\circ & \text{if} \quad \psi_1 > 180^\circ
 \end{cases},
@@
 There are two such lines in each diagram because atom C6 can be located on either side of the plan.
-One can note in Fig.~\ref{fig:dihedrals_emim} that the CDF peaks (i.e. the most likely dihedral angle combinations) lie either precisely above these lines or very close to them.
+One can note in Fig.~\ref{fig:dihedrals_emim} that the CDF peaks, which indicate the most likely dihedral angle combinations, lie either precisely above these lines or very close to them.
 The largest distortions from coplanarity occur for the Batista \textit{et al}. \cite{Batista_2015} model, as observed by the peak locations in Fig.~\ref{fig:dihedrals_emim}(b).
 Despite this, all rigid bodies considered here for \ce{[emim]^+} are built in such a way that atoms C[1-5], H[1-3], and N[1-2] all lie in a single plan.
-Therefore, for specifying the torsion of bond N2-C5 it is enough to set a value for $\chi$ and then compute $\psi$ by means of Eq.~\eqref{eq:dihedral angles}.
+Therefore, for specifying the torsion of bond N2-C5 it is enough to set a value for $\psi_1$ and then compute $\psi_2$ by means of Eq.~\eqref{eq:dihedral angles}.
 All other structural features (bond lengths, bending angles, and hydrogen-involving dihedrals) are taken from the minimum-energy structure obtained for each force field.
@@
 The similarity is not surprising since both models are based on the AMBER framework \cite{Cornell_1995}.
-In both diagrams, the most likely angle combinations can be found in narrow regions around $\chi = 90^\circ$ and $\chi = 270^\circ$.
+In both diagrams, the most likely angle combinations can be found in narrow regions around $\psi_1 = 90^\circ$ and $\psi_1 = 270^\circ$.
 These angles correspond to similar configurations (imagine, for instance, the effect of rotating the whole cation around the axis defined by bond N2-C5).
-Hence, we decided to build a single rigid-body structure with $\chi = 90^\circ$ for the united-atom version of \ce{[emim]^+}, which is the model of Koller \textit{et al}. \cite{Koller_2012}.
-In the case of the all-atom model of Liu \textit{et al}. \cite{Liu_2014}, we considered a system composed by equal amounts of two rigid-body structures with $\chi = 90^\circ$ and $\chi = 270^\circ$.
-For the Batista \textit{et al}. \cite{Batista_2015} model, the regions of likely angle combinations comprise convoluted peaks.
-By means of weighted averages, we decided to set $\chi = 77.4^\circ$ and $\chi = 282.6^\circ$ so as to build two types of rigid bodies, also considered in equal amounts.
-Finally, given the wide ranges of likely angle combinations in the case of the Weber and Kirchner model \cite{Weber_2016}, as observed in Fig.~\ref{fig:dihedrals_emim}(d), we defined four types of rigid bodies in this case to fulfill the system in different proportions.
-The $\chi$-angle values for these types are $0^\circ$, $30^\circ$, $180^\circ$, and $330^\circ$, while their fractions in the system are 25\%, 30\%, 15\%, and 30\%, respectively.
-
-In Table~\ref{table:props_dsf} we present the results of density for the strategies mentioned at the beginning of this section.
-When comparing cases (1) and (2) for each model, we note that the simulated densities practically do not differ.
-In addition, the models of Koller \textit{et al}. \cite{Koller_2012} and Weber and Kirchner \cite{Weber_2016} best reproduce the experimental value.
-We have also computed radial distribution functions (RDFs), which can be found in the Supplementary material.
-The better agreement is found for the models of Koller \textit{et al}. \cite{Koller_2012} and Batista \textit{et al}. \cite{Batista_2015}.
-Despite the small deviations observed for the model of Liu \textit{et al}. \cite{Liu_2014}, the simulation with rigid bodies qualitatively reproduces the RDFs obtained for the flexible ions.
-Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion).
-The model of Weber and Kirchner \cite{Weber_2016}, on the other hand, presents important discrepancies in the RDFs of the pairs C5(cation)-N(anion) and C2(cation)-B(anion) when using rigid bodies.
-That is why, in this case only the imidazolium ring was considered rigid and the ethyl chain was left unconstrained.
+Hence, we decided to build a single rigid-body structure with $\psi_1 = 90^\circ$ for the united-atom version of \ce{[emim]^+}, which is the model of Koller \textit{et al}. \cite{Koller_2012}.
+In the case of the all-atom model of Liu \textit{et al}.
+\cite{Liu_2014}, we considered a system composed by equal amounts of two rigid-body structures with $\psi_1 = 90^\circ$ and $\psi_1 = 270^\circ$.
+For the Batista \textit{et al}.
+\cite{Batista_2015} model, once again we took the most likely values of $\psi_1$ ($102.6^\circ$ and $257.4^\circ$) so as to build two types of rigid bodies and consider them in equal amounts.
+Finally, given the wide ranges of likely angle combinations in the case of the Weber and Kirchner model \cite{Weber_2016}, as observed in Fig.~\ref{fig:dihedrals_emim}(d), we defined four types of rigid bodies in this case.
+The $\psi_1$-angle values for these types are $0^\circ$, $150^\circ$, $180^\circ$, and $210^\circ$, while their fractions in the system are 15\%, 30\%, 25\%, and 30\%, respectively.
 
@@
   \includegraphics[width=.4\linewidth]{Weber}}%
-
 \caption{Combined distribution function of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs for each model of \ce{[emim][B(CN)_4]}.}
-
 \label{fig:dihedrals_emim}
@@
 
-A study of dihedrals was also carried out for \ce{[emim][NTf_2]}.
-The CDF of the dihedrals angles of C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the results of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 is 0$^{\circ}$.
-This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
-With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al}.
-\cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
-Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al}. \cite{Deetlefs_2006}.
-Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy for building the rigid bodies is required.
-Thus, the simulations of \ce{[emim][NTf_2]} were performed considering flexible ions and the DSF method, which results in a computed density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.
-
-\begin{figure}
-\centering
-  \includegraphics[width=\linewidth]{Ludwig}%
-
-  \includegraphics[width=\linewidth]{Ludwig_anion}%
-\caption{Combined distribution function of (a) the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, and (b) of the dihedral angles of the contiguous  C1-S1-N1-S2 and S1-N1-S2-C2 chains, obtained from NPT-MD simulations of 250 molecules of \ce{[emim][NTf_2]}.}
-\label{fig:die_ntf2}
-\end{figure}
+Once the rigid body structures have been determined, we carried out NPT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using the simplified setup (i.e.
+rigid ions with DSF electrostatics) and all force fields in question.
+In Table~\ref{table:props_dsf}, we compare results for density obtained by using the two methodologies.
+In all cases, the simplified method displays excellent agreement with the standard one.
+In addition, we note that the models of Koller \textit{et al}. \cite{Koller_2012} and Weber and Kirchner \cite{Weber_2016} are the ones that most closely reproduce the experimental density.
+In order to perform a more detailed analysis, we have also computed several radial distribution functions (RDFs), some of which are made available as Supplementary Material.
+Excellent agreement is also observed in the RDFs obtained with both methods in the case of the models by Koller \textit{et al}. \cite{Koller_2012} and by Batista \textit{et al}. \cite{Batista_2015}.
+Small deviations are observed in the case of the Liu \textit{et al}. \cite{Liu_2014} model, but the reproducibility of RDFs by the simplified method is still very good.
+%Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion).
+The model of Weber and Kirchner \cite{Weber_2016}, on the other hand, presents RDFs for the pairs C5\textsubscript{cation}-N\textsubscript{anion} (that is, C5\textsubscript{cation} with any nitrogen atom in the anion) and C2\textsubscript{cation}-B\textsubscript{anion} with important discrepancies when rigid bodies are used.
+Note that both RDFs are supposed to be affected by the orientations of the ethyl group in the cation.
 
@@
 \end{table*}
+
+In view of the results presented thus far, our guideline for forthcoming \ce{[emim][B(CN)_4]} simulations goes as follows.
+First, the DSF model replaces Ewald-like electrostatics throughout.
+Second, both \ce{[emim]^+} and \ce{[B(CN)_4]^-} are set as rigid bodies in all cases except when the Weber and Kirchner \cite{Weber_2016} model is employed.
+In this case, rigid-body constraints are applied to the imidazolium ring and methyl group of \ce{[emim]^+} altogether, but the ethyl group is left unconstrained.
+
+A study of dihedrals was also carried out for \ce{[emim][NTf_2]}.
+The CDF of the dihedrals angles of C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the results of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 is 0$^{\circ}$.
+This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
+With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al}.
+\cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
+Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al}. \cite{Deetlefs_2006}.
+Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy for building the rigid bodies is required.
+Thus, the simulations of \ce{[emim][NTf_2]} were performed considering flexible ions and the DSF method, which results in a computed density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.
+
+\begin{figure}
+\centering
+  \includegraphics[width=\linewidth]{Ludwig}%
+
+  \includegraphics[width=\linewidth]{Ludwig_anion}%
+\caption{Combined distribution function of (a) the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, and (b) of the dihedral angles of the contiguous  C1-S1-N1-S2 and S1-N1-S2-C2 chains, obtained from NPT-MD simulations of 250 molecules of \ce{[emim][NTf_2]}.}
+\label{fig:die_ntf2}
+\end{figure}
 

### 2018-09-11 ionic_liquids.tex
Table Formatting

@@
 \documentclass[3p,twocolumn]{elsarticle}
-
-\usepackage{color,soul} % TEMPORARY
 
@@
 \usepackage{amsmath}
-\usepackage{ifthen}
-\usepackage{commath}
 \usepackage{amssymb}
@@
 \usepackage[version=4]{mhchem}
-
 \usepackage{adjustbox}   
-\usepackage{threeparttable}
-\usepackage{booktabs}
-\usepackage{colortbl} 
-\usepackage{xcolor}
-\usepackage{mhchem}
+\usepackage[position=top,captionskip=-12pt]{subfig}
+\usepackage{graphicx}
+\DeclareGraphicsExtensions{.pdf,.eps,.png}
 
 \newcommand{\diff}[2]{\dfrac{\partial #1}{\partial #2}}
-
-\usepackage{graphicx}
-\DeclareGraphicsExtensions{.pdf,.eps,.png}
-%\usepackage{float}
-\usepackage[position=top,captionskip=-15pt]{subfig}
 
@@
   \includegraphics[width=.4\linewidth]{Weber}}%
-\caption{Combined distribution function of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs for each model of \ce{[emim][B(CN)_4]}.}
+\caption{Combined distribution functions of the dihedral angles corresponding to atoms C1-N2-C5-C6 and C2-N2-C5-C6 in the cation \ce{[emim]^+} (see Fig.~\ref{fig:atoms_id}), as sampled in NPT-MD simulations of 250 ion pairs using each model for \ce{[emim][B(CN)_4]}.}
 \label{fig:dihedrals_emim}
@@
 		\ce{[emim][B(CN)_4]} model                        & 
-		\multicolumn{2}{c}{Flexible ions \& Ewald method} &
-		\multicolumn{2}{c}{Rigid ions \& DSF method}      \\
+		\multicolumn{2}{c}{Flexible ions \& PPPM-Ewald} &
+		\multicolumn{2}{c}{Rigid ions \& DSF}      \\
 		&
@@
 \centering
-  \includegraphics[width=\linewidth]{Ludwig}%
-
 \includegraphics[width=\linewidth]{Ludwig_anion}%
-\caption{Combined distribution function of (a) the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, and (b) of the dihedral angles of the contiguous  C1-S1-N1-S2 and S1-N1-S2-C2 chains, obtained from NPT-MD simulations of 250 molecules of \ce{[emim][NTf_2]}.}
+\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[NTf_2]^-}, obtained from NPT-MD simulations of 250 ion pairs of \ce{[emim][NTf_2]} using the model of K\"{o}ddermann \textit{et al}.
+\cite{K_ddermann_2007}.}
 \label{fig:die_ntf2}
@@
 
-\subsection{Henry constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
+\subsection{Henry's Law Constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 \label{sec:henry_results}
@@
 	\centering
-\begin{adjustbox}{width=1\textwidth}
-\begin{threeparttable}
-\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} at $T$ = $298.15~\text{K}$ and $P$ = $1~\text{atm}$.
-The experimental Henry constants in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
-\begin{tabular}{ c c c  c  c  c  c }  
-\toprule
-Model & $\tilde{\rho}_\text{sim}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
-& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
+	\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} at $T = 298.15~\mathrm{K}$ and $P = 1~\mathrm{atm}$.
+The experimental Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and in \ce{[emim][NTf_2]} are, respectively, $38.9 \pm 0.03 ~\mathrm{atm}$ \cite{Mahurin_2010} and $39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008}.}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{ccccccc}  
+			\hline\hline
+			Model & $\tilde{\rho}_\text{sim}$ & $\Delta G_\text{\tiny vdW}$  & $\Delta G_\text{\tiny Coul}$  & $\Delta G_\text{sim}$ & $K_s$ & error \\
+			& (mol/dm\textsuperscript{3}) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  & (\%) \\
 			\hline
-			\multicolumn{4}{c}{\ce{[emim][B(CN)_4]}} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
+%			\multicolumn{7}{c}{\ce{[emim][B(CN)_4]}: $K_{s}^{\text{exp}} = 38.9 \pm 0.03 ~\mathrm{atm}$ \cite{Mahurin_2010}} \\
+			\multicolumn{7}{c}{\ce{[emim][B(CN)_4]}} \\
+			Koller \textit{et al}. \cite{Koller_2012} & $4.5925$ & $0.45 \pm 0.01$ & $-1.06 \pm 0.02$ & $-0.61 \pm 0.02$ & $40 \pm 1$ & $2.8$ \\
+			Batista \textit{et al}. \cite{Batista_2015} & $4.3700$ & $0.378 \pm 0.008$ & $-1.24 \pm 0.01$  & $-0.86 \pm 0.01$ & $24.9 \pm 0.5$ & $38.9$ \\
+			Liu \textit{et al}. \cite{Liu_2014} & $4.3815$ & $0.226 \pm 0.009$ & $-1.11 \pm 0.01$ & $-0.88 \pm 0.01$ & $24.3 \pm 0.5$ & $37.6$  \\
+			Weber and Kirchner \cite{Weber_2016} & $4.5221$ & $0.478 \pm 0.009$ & $-1.23 \pm 0.02$ & $-0.75 \pm 0.02$ & $31 \pm 1$ & $20.3$  \\
 			\hline
-Koller \textit{et al}. \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
-Batista \textit{et al}. \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
-Liu \textit{et al}. \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
-Weber and Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
-\hline
-		\multicolumn{4}{c}{\ce{[emim][NTf_2]}} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
-		\hline
- K\"{o}ddermann \textit{et al}. \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
- \bottomrule
+%			\multicolumn{7}{c}{\ce{[emim][NTf_2]}: $K_{s}^{\text{exp}} = 39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008} }\\
+			\multicolumn{7}{c}{\ce{[emim][NTf_2]}} \\
+			K\"{o}ddermann \textit{et al}. \cite{K_ddermann_2007} & $3.8205$ & $0.389 \pm 0.005$ & $-0.901 \pm 0.006$ & $-0.512 \pm 0.008$ & $39.4 \pm 0.5$  & $0.97$  \\
+			\hline\hline
 			\label{table:henry} 
 		\end{tabular}
-\begin{tablenotes}
-\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^\text{sim})/K_s^{\text{exp}}}$.
-\end{tablenotes}
-\end{threeparttable}
 	\end{adjustbox}
@@
 Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.~\ref{fig:sdf_ions} (c).
+
 \begin{figure}
@@
 
-\begin{table*}
+\begin{table}
 	\centering
-\begin{threeparttable}
 	\caption{Thermodynamic conditions employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}~\cite{Makino_2014,Schilderman_2007}.}
-\begin{tabular}{ c  c  c  c  c  }  
-\toprule
-Ionic liquid & T (K)  & P (atm)  & molar fraction $x_s$ & molality $m_s$ \\
-\midrule		
-\ce{[emim][B(CN)_4]}~\cite{Koller_2012} & 313.15 & 21 & 0.352 & 2.4  \\
-\ce{[emim][NTf_2]}~\cite{K_ddermann_2007}  & 312.13 & 37 & 0.479 & 2.35  \\
- \bottomrule
+	\begin{tabular}{ c  c  c  }  
+		\hline\hline
+		IL & \ce{[emim][B(CN)_4]}  & \ce{[emim][NTf_2]} \\
+		\hline
+		model &  Ref.~\citenum{Koller_2012} & Ref.~\citenum{K_ddermann_2007} \\
+		T  & 313.15 K & 312.13 K \\
+		P  & 21 atm & 37 atm \\
+		$x_s$ & 0.352 & 0.479 \\
+		$m_s$ & 2.4 mol/kg & 2.35 mol/kg \\
+		\hline\hline
 		\label{table:solv} 
 	\end{tabular}
-\end{threeparttable}
-\end{table*}
+\end{table}
 
@@
 	\centering
-\begin{adjustbox}{width=1\textwidth}
-\begin{threeparttable}
 	\caption{Solvation free energy at $T = 298.15~\text{K}$ for the pure solutes benzene, hexane, cyclohexane, ethanol and water.}
-\begin{tabular}{ c c c c c c c c }
-\toprule
-Solute & $\rho_\text{sim}$ & error (\%)\tnote{a} & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G^{0}_{\,\text{sim}}$ & $\Delta G^{\text{0,exp}}$   & error (\%)\tnote{a}\\
- & (g/cm$^{3}$) &  & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   &  \\
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{ccccccccc}
+			\hline\hline
+			Solute & $\rho_\text{sim}$ & error & $\Delta G_\text{\tiny vdW}$  & $\Delta G_\text{\tiny Coul}$  & $\Delta G^0_\text{sim}$ & $\Delta G^0_\text{exp}$   & error \\
+			& (g/cm\textsuperscript{3}) & (\%) & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   & (kcal/mol)   & (\%) \\
 			\hline
-benzene OPLS-AA   & 0.8611 $\pm$ 0.0002 & 1.4 & -3.75  $\pm$ 0.02 & -0.381 $\pm$ 0.007 & -4.14 $\pm$ 0.02 & -4.56 & 9.32  \\
-hexane OPLS-AA    & 0.6513 $\pm$ 0.0003 & 0.5 & -3.67  $\pm$  0.03 & 0.011 $\pm$ 0 & -3.66 $\pm$ 0.03 & -4.06 & 9.90 \\
-cyclohexane & 0.7692 $\pm$ 0.0007 & 0.6 & -4.39 $\pm$ 0.01 & 0 & -4.39 $\pm$ 0.01 & - & -  \\
-ethanol TRAPPE-UA   & 0.781 $\pm$ 0.008 & 1.01  &-0.93 $\pm$ 0.01 & -4.15 $\pm$ 0.02  & -5.08  $\pm$ 0.02  & -5.08 & 0 \\
-water TIP4P/2005   &  0.9948 $\pm$ 0.0003 & 0.2 & 2.015 $\pm$ 0.004 & -9.01 $\pm$ 0.02 & -6.99 $\pm$ 0.02 & -6.33  &10.43 \\
- \bottomrule
+			hexane & $0.6513 \pm 0.0003$ & $0.5$ & $-3.67  \pm  0.03$ & $0.011 \pm 0.007$ & $-3.66 \pm 0.03$ & $-4.06$ & $9.90$ \\
+			cyclohexane & $0.7692 \pm 0.0007$ & $0.6$ & $-4.39 \pm 0.01$ & $0$ & $-4.39 \pm 0.01$ & n/a & n/a  \\
+			benzene & $0.8611 \pm 0.0002$ & $1.4$ & $-3.75  \pm 0.02$ & $-0.381 \pm 0.007$ & $-4.14 \pm 0.02$ & $-4.56$ & $9.32$  \\
+			ethanol & $0.781 \pm 0.008$ & $1.01$  & $-0.93 \pm 0.01$ & $-4.15 \pm 0.02$  & $-5.08  \pm 0.02$  & $-5.08$ & $0$ \\
+			water & $0.9948 \pm 0.0003$ & $0.2$ & $2.015 \pm 0.004$ & $-9.01 \pm 0.02$ & $-6.99 \pm 0.02$ & $-6.33$  & $10.43$ \\
+			\hline\hline
 			\label{table:mu_solutes} 
 		\end{tabular}
-\begin{tablenotes}
-\item[a] error = 100 $\times$ $\abs{(Z^{\text{exp}} - Z^\text{sim})/Z^{\text{exp}}}$.
-\end{tablenotes}
-\end{threeparttable}
 	\end{adjustbox}
@@
 	\centering
+	\caption{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]} at $T = 298.15~\text{K}$ of the pure solutes benzene, hexane, cyclohexane, ethanol, and water.}
 	\begin{adjustbox}{width=1\textwidth}
-\begin{threeparttable}
-\caption{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]} at $T = 298.15~\text{K}$ of the pure solutes benzene, hexane, cyclohexane, ethanol, and water.}
-\begin{tabular}{c c c c c c  >{\columncolor[gray]{0.8}} c}  
-\toprule
-Solute & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$  & $\gamma^{\,\infty,\text{sim}}$ & $\gamma^{\, \infty,\text{exp}}$ & $\gamma^{\, \infty,\text{exp}}$  \\
- & (kcal/mol) & (kcal/mol) &  (kcal/mol)  &  & (298.15 K) \cite{Doma_ska_2011} & (303 K) \cite{Yan_2010} \\
-\midrule % inserts single-line
-hexane OPLS-AA & -2.13 $\pm$ 0.04 & -0.152 $\pm$ 0.007 & -2.282 $\pm$ 0.04 & 6.2 $\pm$ 0.5 & 33.8 & 20.97  \\
-cyclohexane& -2.75 $\pm$ 0.06 & - & -2.75 $\pm$ 0.06 & 9 $\pm$ 1 & 16.7 & 13.82 \\
-benzene OPLS-AA  & -2.23 $\pm$ 0.05 & -1.29 $\pm$ 0.04 & -3.52 $\pm$ 0.06 & 1.2 $\pm$ 0.1 & 1.13 & 1.31 \\ 
-ethanol TRAPPE-UA& -0.73 $\pm$ 0.02 & -4.10 $\pm$ 0.04 & -4.83 $\pm$ 0.04 & 0.41 $\pm$ 0.03 & 1.58 & 1.64  \\
-water TIP4P/2005& 1.38 $\pm$ 0.008 & -6.32 $\pm$ 0.03 & -4.94 $\pm$ 0.03 & 2 $\pm$ 1 & 2.65 & 2.24 \\
- \bottomrule
+		\begin{tabular}{cccccccc}  
+			\hline\hline
+			Solute & $\Delta G_\text{\tiny vdW}$  & $\Delta G_\text{\tiny Coul}$  & $\Delta G_\text{sim}$  & $\gamma^\infty_\text{sim}$ & $\gamma^\infty_\text{exp}$ \cite{Doma_ska_2011} & $\gamma^\infty_\text{exp}$ \cite{Yan_2010} \\
+			& (kcal/mol) & (kcal/mol) &  (kcal/mol)  & (298 K) & (298 K)  & (303 K) \\
+			\hline
+			hexane & $-2.13 \pm 0.04$ & $-0.152 \pm 0.007$ & $-2.282 \pm 0.04$ & $6.2 \pm 0.5$ & $33.8$ & $20.97$  \\
+			cyclohexane & $-2.75 \pm 0.06$ & 0 & $-2.75 \pm 0.06$ & $9 \pm 1$ & $16.7$ & $13.82$ \\
+			benzene & $-2.23 \pm 0.05$ & $-1.29 \pm 0.04$ & $-3.52 \pm 0.06$ & $1.2 \pm 0.1$ & $1.13$ & $1.31$ \\ 
+			ethanol & $-0.73 \pm 0.02$ & $-4.10 \pm 0.04$ & $-4.83 \pm 0.04$ & $0.41 \pm 0.03$ & $1.58$ & $1.64$  \\
+			water & $1.38 \pm 0.008$ & $-6.32 \pm 0.03$ & $-4.94 \pm 0.03$ & $2 \pm 1$ & $2.65$ & $2.24$ \\
+			\hline\hline
 			\label{table:gamma} 
 		\end{tabular}
-\end{threeparttable}
 	\end{adjustbox}
 \end{table*}
+
 \section{Concluding remarks}

### 2018-09-14 ionic_liquids.tex
Simulation strategy for emin-NTf2

@@
 Parameters corresponding to the intramolecular and LJ interactions were extracted from GAFF \cite{Wang_2004}, while the atomic partial charges were computed using the RESP method \cite{Bayly_1993} with B3LYP/6-311+G(d) DFT calculations.
-The net charges of the ions were manually adjusted to $\pm 0.8 \mathrm{e}$.
+The net charges of the ions were manually adjusted to $\pm 0.8 ~\mathrm{e}$.
 
@@
 As the potential parameters for the anion were specified neither in Ref.~\citenum{Weber_2016} nor in Ref.~\citenum{Canongia_Lopes_2006}, we obtained them by direct communication with the authors of Ref.~\citenum{Weber_2016}.
-The atomic partial charges were derived using the RESP procedure with Hartree-Fock calculations at the \mbox{6-31++G\textsuperscript{**}} level of theory, resulting in net charges of $\pm 0.8 \mathrm{e}$.
+The atomic partial charges were derived using the RESP procedure with Hartree-Fock calculations at the \mbox{6-31++G\textsuperscript{**}} level of theory, resulting in net charges of $\pm 0.8 ~\mathrm{e}$.
 
@@
 
-As a guide to the discussions we put forward in this section, in Fig~\ref{fig:atoms_id} we introduce a nomenclature for all atoms present in the ions \ce{[emim]^+}, \ce{[B(CN)_4]^-}, and \ce{[NTf_2]^-}.
+As a guide to the discussions in this section, in Fig~\ref{fig:atoms_id} we introduce a nomenclature for all atoms present in the ions \ce{[emim]^+}, \ce{[B(CN)_4]^-}, and \ce{[NTf_2]^-}.
 Please note that, in the united-atom version of \ce{[emim]^+}, all hydrogen atoms ranging from H4 to H11 are incorporated to their corresponding carbon atoms.
@@
 In Fig.~\ref{fig:dihedrals_emim}, we show the CDFs obtained for all force fields employed here for \ce{[emim][B(CN)_4]}.
-The CDFs were generated from NPT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using our standard setup (i.e. flexible ions with PPPM Ewald electrostatics).
+All CDFs shown in this section were generated from NPT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using our standard setup (i.e.
+flexible ions with PPPM Ewald electrostatics).
 Initial inspection reveals that, in all cases, $\psi_1$ and $\psi_2$ populate regions of the diagrams around the two straight lines given by
@@
 
-A study of dihedrals was also carried out for \ce{[emim][NTf_2]}.
-The CDF of the dihedrals angles of C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the results of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 is 0$^{\circ}$.
-This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}.
-With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al}.
-\cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation.
-Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2 chains, qualitatively verifies the observation of Deetlefs \textit{et al}. \cite{Deetlefs_2006}.
-Given the considerable flexibility of \ce{[NTf_2]^-}, a more rigorous strategy for building the rigid bodies is required.
-Thus, the simulations of \ce{[emim][NTf_2]} were performed considering flexible ions and the DSF method, which results in a computed density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.
+A study of conformations was also carried out for \ce{[emim][NTf_2]} using the model of K\"{o}ddermann \textit{et al}. \cite{K_ddermann_2007}.
+A CDF obtained for the dihedral angles of sequences C1-N2-C5-C6 and C2-N2-C5-C6 in \ce{[emim]^+}, which is made available in the Supplementary Material, resembles the one in Fig.~\ref{fig:dihedrals_emim}(d).
+The resemblance was expected because the intramolecular parameters employed for \ce{[emim]^+} are identical in these two cases, since the corresponding models are both based on the force field developed by Canongia-Lopes and P\'{a}dua \cite{Canongia_Lopes_2006}.
+However, the most likely value of $\psi_1$ is shifted to $0^{\circ}$ in the case of \ce{[emim][NTf_2]}.
+This highlights the fact that altering atomic charges can induce conformational changes and should, therefore, be accompanied by a revision of torsion parameters in some cases.
+With regard to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al}.
+\cite{Deetlefs_2006} experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly found in its \textit{trans} conformation.
+In Fig.~\ref{fig:die_ntf2}, we present the CDF obtained for the contiguous sequences C1-S1-N1-S2 and S1-N1-S2-C2 in \ce{[NTf_2]^-}, which qualitatively confirms the observation of Deetlefs \textit{et al}.
+\cite{Deetlefs_2006}.
+This CDF also makes clear that \ce{[NTf_2]^-} exhibits a considerable degree of flexibility.
+Due to this observed behaviors of both ions, all simulations of \ce{[emim][NTf_2]} in the present work are performed considering flexible cations and anions, as well as DSF electrostatics.
+This approach results in a mean density of $1.495 \pm 0.009 ~\mathrm{g/cm^3}$ at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$.
+The relative error of this result with respect to the experimental value obtained by Tokuda \textit{et al}. \cite{Tokuda_2005} is only 1.12\%.
 
@@
 \centering
-\includegraphics[width=\linewidth]{Ludwig_anion}%
+\includegraphics[width=\linewidth]{Ludwig_anion}
 \caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[NTf_2]^-}, obtained from NPT-MD simulations of 250 ion pairs of \ce{[emim][NTf_2]} using the model of K\"{o}ddermann \textit{et al}.

### 2018-09-15 ionic_liquids.tex
Some changes in Dilute CO2 solvation

@@
 \DeclareGraphicsExtensions{.pdf,.eps,.png}
+
+\usepackage{xcolor}
+\usepackage{pdfcomment}
 
@@
 %
-Therefore, by simply expressing Eq.~\eqref{eq:solvation free energy definition} in terms of the molar fraction of the solute in the liquid phase ($x_s$) and assuming a dilute solution, whose molar density does not perceivably differ from that of pure solvent (that is, $\tilde{\rho} \approx \tilde{\rho}_\text{\tiny IL}$), we obtain that
+Therefore, by simply expressing Eq.~\eqref{eq:solvation free energy definition} in terms of the molar fraction of the solute in the liquid phase ($x_s$), we can conclude that
 \begin{equation}
 \label{eq:henry_eq}
-K_s = \tilde{\rho}_\text{\tiny IL} R \, T \exp\left(\frac{\Delta G_\text{sim}}{k_b T}\right).
+K_s = \tilde{\rho}_\text{sim} R \, T \exp\left(\frac{\Delta G_\text{sim}}{k_b T}\right),
 \end{equation}
+where $\tilde{\rho}_\text{sim}$ is the simulated molar density of the solution.
+Assuming that this solution is very dilute, one can use the molar density of pure solvent ($\tilde{\rho}_\text{\tiny IL}$) instead.
 
@@
 
-\subsection{Henry's Law Constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
+\subsection{Dilute Solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 \label{sec:henry_results}
 
-In Table \ref{table:henry} we present the results of the solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\eqref{eq:henry_eq}.
-Table~\ref{table:henry} also contains the experimental $K_s$ reported by Mahurin \textit{et al}. \cite{Mahurin_2010} and Finotello \textit{et al}. \cite{Finotello_2008}.
-The uncertainties in $K_s$ were calculated using standard error propagation.
+In Table \ref{table:henry}, we present results obtained from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][NTf_2]} under periodic boundary conditions.
+The simulations were carried out at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$.
+Table~\ref{table:henry} contains simulated molar densities, partial and total solvation free energies, as well as Henry's law constants ($K_s$) computed via Eq.~\eqref{eq:henry_eq}.
+It also contains the experimental $K_s$ values reported by Mahurin \textit{et al}. \cite{Mahurin_2010} and by Finotello \textit{et al}. \cite{Finotello_2008}.
+The uncertainties in $K_s$ were calculated by using a standard error propagation formula.
 
@@
 	\centering
-	\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} at $T = 298.15~\mathrm{K}$ and $P = 1~\mathrm{atm}$.
+	\caption{Results of solvation free energies and Henry's law constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} at $T = 298.15~\mathrm{K}$ and $P = 1~\mathrm{atm}$.
 The experimental Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and in \ce{[emim][NTf_2]} are, respectively, $38.9 \pm 0.03 ~\mathrm{atm}$ \cite{Mahurin_2010} and $39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008}.}
@@
 
-It should be pointed out that the result of $\Delta G_\text{sim}$ obtained for the model of Liu \textit{et al}.
-\cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent sampling of $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$.
-Moreover, the $\Delta G_\text{sim}$ in \ce{[emim][NTf_2]} is very close to the value obtained by Kerl \textit{et al}.
-\cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}.
-These consistencies have served for validating the methodological approaches of this work.
+The result of $\Delta G_\text{sim}$ obtained with the model of Liu \textit{et al}.
+\cite{Liu_2014} is statistically identical to the value reported by the same authors \cite{Liu_2014_1}, who applied the Bennett Acceptance Ratio (BAR) method \cite{Bennett_1976} to independent samples obtained with different values of $\lambda_\text{\tiny vdW}$ and $\lambda_\text{\tiny Coul}$.
+Moreover, the $\Delta G_\text{sim}$ result for \ce{[emim][NTf_2]} is very close to the value obtained by Kerl \textit{et al}.
+\cite{Kerl__2017} ($-0.534 ~\mathrm{kcal/mol}$, with no uncertainty reported) using the Free-Energy Perturbation (FEP) method \cite{Zwanzig_1954}.
+%These consistencies have served for validating the methodological approaches of this work.
 
-From Table \ref{table:henry} one can see that the model of Koller \textit{et al}. \cite{Koller_2012} best reproduces the experimental value of $K_s$.
-If we look at the $\Delta G_{\lambda_{\,\text{vdW}}}$ profiles in Fig.~\ref{fig:deltag}, we observe that for the models of Batista \textit{et al}.
+From Table \ref{table:henry}, one can see that no model other than that of Koller \textit{et al}.
+\cite{Koller_2012} was able to reproduce the experimental Henry's law constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} with small deviation.
+If we look at the $\Delta G_\text{\tiny vdW}$ profiles in Fig.~\ref{fig:deltag}, we observe that for the models of Batista \textit{et al}.
 \cite{Batista_2015} and Liu \textit{et al}.~\cite{Liu_2014} the maximum occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which may also explain their failure to reproduce the experimental density.
@@
 \includegraphics[width=\linewidth]{free_energy_paper}
-\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, which was modeled according to the force fields of (circles) Koller \textit{et al}.
-\cite{Koller_2012}, (squares) Batista \textit{et al}.
-\cite{Batista_2015}, (up triangles) Liu \textit{et al}.
-\cite{Liu_2014}, and (x) Weber and Kirchner \cite{Weber_2016}.}
+\caption{Profile of $\Delta G_\text{\tiny vdW}$ corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, modeled according to the force fields of Koller \textit{et al}.
+\cite{Koller_2012} ($\bullet$), Batista \textit{et al}.
+\cite{Batista_2015} ($\blacksquare$), Liu \textit{et al}.
+\cite{Liu_2014} ($\times$), and Weber and Kirchner \cite{Weber_2016} ($\blacktriangle$).}
 \label{fig:deltag}
@@
 If we compare Figs.~\ref{fig:sdf_ions} (a) and (b), one notes that the region with a low probability of finding an ion is larger for \ce{[emim][NTf_2]}.
-Also, the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.~\ref{fig:sdf_ions} (c).
+Also, the first solvation shell due to \ce{[B(CN)_4^-} occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.~\ref{fig:sdf_ions}(c).
 
@@
 
-\subsection{Study of concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
+\subsection{Concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 \label{sec:results_conc}

### 2018-09-15 ionic_liquids.tex
Replacement of Boltzmann constant by R

@@
 \begin{equation}
-\Delta G_\text{sim} \equiv k_b T \ln \frac{\Xi (N_s,N_\text{\tiny IL},P,T,\lambda = 1)}{\Xi (N_s,N_\text{\tiny IL},P,T,\lambda = 0)}, 
+\Delta G_\text{sim} \equiv R T \ln \frac{\Xi (N_s,N_\text{\tiny IL},P,T,\lambda = 1)}{\Xi (N_s,N_\text{\tiny IL},P,T,\lambda = 0)}, 
 \end{equation}
-where $\Xi$ denotes the isobaric-isothermal partition function and $k_b$ is the Boltzmann constant.
+where $\Xi$ denotes the isobaric-isothermal partition function and $R$ is the gas constant.
 Shirts \textit{et al}. \cite{Shirts_2003} rigorously derived the working expression that relates $\Delta G_\text{sim}$ to what is experimentally measured as the solvation free energy, namely
@@
 \label{eq:solvation free energy definition}
-\Delta G_{\text{solv}} \equiv k_b T \ln \left( \frac{P_s}{c_s R T} \right),
+\Delta G_{\text{solv}} \equiv R \ln \left( \frac{P_s}{c_s R T} \right),
 \end{equation}
-where $R = N_A k_b$ is the gas constant,
-$N_A$ is the Avogadro number,
-$P_s$ is the partial pressure of the solute in the gas phase, and
+where $P_s$ is the partial pressure of the solute in the gas phase and
 $c_s$ is the molar concentration of the solute in the liquid phase.
@@
 \label{eq:solute chemical potential}
-\mu^l_s = \mu^{ig}_s + \Delta G_\text{sim} - k_bT \ln \left( \frac{V^{\ast}}{V_1}\right) - k_bT \ln \left( \frac{P_s}{c_s R T} \right),
+\mu^l_s = \mu^{ig}_s + \Delta G_\text{sim} - RT \ln \left( \frac{V^{\ast}}{V_1}\right) - RT \ln \left( \frac{P_s}{c_s R T} \right),
 \end{equation}
@@
 \label{eq:free_solv}
- \Delta G_{\text{solv}} = \Delta G_\text{sim} - k_bT \ln \left( \frac{V^{\ast}}{V_1}\right).
+ \Delta G_{\text{solv}} = \Delta G_\text{sim} - RT \ln \left( \frac{V^{\ast}}{V_1}\right).
 \end{split}
@@
 \label{eq:henry_eq}
-K_s = \tilde{\rho}_\text{sim} R \, T \exp\left(\frac{\Delta G_\text{sim}}{k_b T}\right),
+K_s = \tilde{\rho}_\text{sim} R \, T \exp\left(\frac{\Delta G_\text{sim}}{R T}\right),
 \end{equation}
@@
 \label{eq:mu_gas_real}
-\mu^{g}_s = \mu^{ig}_s + k_b T \ln \left(\frac{f^{g}_s}{P_s}\right),
+\mu^{g}_s = \mu^{ig}_s + R T \ln \left(\frac{f^{g}_s}{P_s}\right),
 \end{equation}
@@
 \label{eq:fgas_d}
-f^{g}_s = \exp \left( \frac{\Delta G_\text{sim}}{k_b T} \right) +  c_s R T. 
+f^{g}_s = \exp \left( \frac{\Delta G_\text{sim}}{R T} \right) +  c_s R T. 
 \end{equation}
@@
 \label{eq:equation for pressure}
-y_s \exp\left( \frac{B_s P}{R T} \right) P = \exp \left( \frac{\Delta G_\text{sim}}{k_b T} \right) +  c_s R T,
+y_s \exp\left( \frac{B_s P}{R T} \right) P = \exp \left( \frac{\Delta G_\text{sim}}{R T} \right) +  c_s R T,
 \end{equation}
@@
 \label{eq:gamma}
-\ln \gamma_s = \frac{\mu_s^l - \mu_s^{l,0}}{k_b T} - \ln x_s,
+\ln \gamma_s = \frac{\mu_s^l - \mu_s^{l,0}}{R T} - \ln x_s,
 \end{equation}
@@
 \begin{equation}
-\ln \gamma_s = \frac{\Delta G_\text{sim} - \Delta G_\text{sim}^{0}}{k_b T} + \ln \frac{\tilde{\rho}}{\tilde{\rho}_s^0}.
+\ln \gamma_s = \frac{\Delta G_\text{sim} - \Delta G_\text{sim}^{0}}{R T} + \ln \frac{\tilde{\rho}}{\tilde{\rho}_s^0}.
 \end{equation}
@@
 
-In Table \ref{table:henry}, we present results obtained from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][NTf_2]} under periodic boundary conditions.
+In Table \ref{table:henry}, we present results from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][NTf_2]} under periodic boundary conditions.
 The simulations were carried out at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$.

### 2018-09-15 ionic_liquids.tex
Changes in figures

@@
 Table~\ref{table:henry} contains simulated molar densities, partial and total solvation free energies, as well as Henry's law constants ($K_s$) computed via Eq.~\eqref{eq:henry_eq}.
-It also contains the experimental $K_s$ values reported by Mahurin \textit{et al}. \cite{Mahurin_2010} and by Finotello \textit{et al}. \cite{Finotello_2008}.
 The uncertainties in $K_s$ were calculated by using a standard error propagation formula.
+The computed values should be compared to the experimental data reported by Mahurin \textit{et al}.
+\cite{Mahurin_2010} ($K_s = 38.9 \pm 0.03 ~\mathrm{atm}$ for \ce{CO_2} in \ce{[emim][B(CN)_4]}) and by Finotello \textit{et al}.
+\cite{Finotello_2008} ($K_s = 39.0 \pm 0.1 ~\mathrm{atm}$ for \ce{CO_2} in \ce{[emim][NTf_2]}).
 
@@
 
-The result of $\Delta G_\text{sim}$ obtained with the model of Liu \textit{et al}.
-\cite{Liu_2014} is statistically identical to the value reported by the same authors \cite{Liu_2014_1}, who applied the Bennett Acceptance Ratio (BAR) method \cite{Bennett_1976} to independent samples obtained with different values of $\lambda_\text{\tiny vdW}$ and $\lambda_\text{\tiny Coul}$.
-Moreover, the $\Delta G_\text{sim}$ result for \ce{[emim][NTf_2]} is very close to the value obtained by Kerl \textit{et al}.
-\cite{Kerl__2017} ($-0.534 ~\mathrm{kcal/mol}$, with no uncertainty reported) using the Free-Energy Perturbation (FEP) method \cite{Zwanzig_1954}.
+Is it worth remarking that the result of $\Delta G_\text{sim}$ obtained with the model of Liu \textit{et al}.
+\cite{Liu_2014} is statistically identical to a value reported by the same authors in Ref.~\citenum{Liu_2014_1}, where they applied the Bennett Acceptance Ratio (BAR) method \cite{Bennett_1976} to independent samples obtained with different values of $\lambda_\text{\tiny vdW}$ and $\lambda_\text{\tiny Coul}$.
+Moreover, the $\Delta G_\text{sim}$ value we computed for \ce{[emim][NTf_2]} is very close to the one obtained by Kerl \textit{et al}.
+\cite{Kerl__2017} ($-0.534 ~\mathrm{kcal/mol}$, with no reported uncertainty) using the Free-Energy Perturbation (FEP) method \cite{Zwanzig_1954}.
 %These consistencies have served for validating the methodological approaches of this work.
 
-From Table \ref{table:henry}, one can see that no model other than that of Koller \textit{et al}.
-\cite{Koller_2012} was able to reproduce the experimental Henry's law constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} with small deviation.
+One can see in Table \ref{table:henry} that the only model able to reproduce the experimental Henry's law constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} with small deviation is that of Koller \textit{et al}.
+\cite{Koller_2012}.
+The worst results are obtained with the models of Batista \textit{et al}. \cite{Batista_2015} and Liu \textit{et al}. \cite{Liu_2014}.
+These models fail in part because of the small values they predict for $\Delta G_\text{\tiny vdW}$.
+In order to analyze the model distinctions in more detail, in Fig.~\ref{fig:deltag} we plot the profiles of $\Delta G_\text{\tiny vdW}$ as a function of the coupling parameter $\lambda_\text{\tiny vdW}$.
+
 If we look at the $\Delta G_\text{\tiny vdW}$ profiles in Fig.~\ref{fig:deltag}, we observe that for the models of Batista \textit{et al}.
-\cite{Batista_2015} and Liu \textit{et al}.~\cite{Liu_2014} the maximum occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which may also explain their failure to reproduce the experimental density.
+\cite{Batista_2015} and Liu \textit{et al}.~\cite{Liu_2014} the maximum occurs at lower values of energy, suggesting that these models underestimate the atomic interactions, which may also explain their failure to reproduce the experimental density.
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
 \subfloat[]{%
-  \includegraphics[width=\linewidth]{kollerall.pdf}%
+  \includegraphics[width=\linewidth/3,trim={2cm 0 1.5cm 0},clip]{kollerall.pdf}
 }
-
 \subfloat[]{%
-  \includegraphics[width=\linewidth]{ludwigall.pdf}%
+  \includegraphics[width=\linewidth/3,trim={1.75cm 0 1.75cm 0},clip]{ludwigall.pdf}
 }
-
 \subfloat[]{%
-  \includegraphics[width=\linewidth]{anionanion.pdf}%
+  \includegraphics[width=\linewidth/3,trim={2.5cm 0 1cm 0},clip]{anionanion.pdf}
 }
@@
 \label{fig:sdf_ions}
-\end{figure}
+\end{figure*}
 
@@
 In addition, we see that in this case the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
-The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} were -0.755 $\pm$ 0.01 kcal/mol and -0.542 $\pm$ 0.005, respectively.
+The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} were $-0.755 \pm 0.01 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005$, respectively.
 However, since we simulated a different number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could explain the higher solubility.
@@
 
-\subsection{Inifinite-dilution activity coefficient in \ce{[emim][B(CN)_4]}}
+\subsection{Infinite-dilution activity coefficients in \ce{[emim][B(CN)_4]}}
 \label{sec:act_results}

### 2018-09-15 ionic_liquids.tex
Further changes in dilute CO2 solutions

@@
 %% Group authors per affiliation:
-\author[plapiqui,msk]{A.J.~Silveira}
+\author[plapiqui]{A.J.~Silveira\corref{curradd}}
 \author[plapiqui]{S.~Pereda}
@@
 \address[plapiqui]{Planta Piloto de Ingenier\'ia Qu\'imica (PLAPIQUI), Universidad Nacional del Sur, Bah\'ia Blanca, Argentina}
-\address[msk]{Computational \& Systems Biology Program, Memorial Sloan Kettering Cancer Center, New York, NY, USA}
 \address[eq-ufrj]{Chemical Engineering Department, Escola de Qu\'imica, Universidade Federal do Rio de Janeiro, Rio de Janeiro, Brazil}
@@
 
+\cortext[curradd]{Current address: Computational \& Systems Biology Program, Memorial Sloan Kettering Cancer Center, New York, NY, USA}
 \cortext[cor1]{Corresponding author}
@@
 \begin{keyword}
-ionic liquids \sep solvation free energy \sep  \ce{CO_2} Henry constant \sep infinite-dilution activity coefficient 
+ionic liquids \sep solvation free energy \sep \ce{CO_2} Henry's law constant \sep infinite-dilution activity coefficient
 \end{keyword}
@@
 These models fail in part because of the small values they predict for $\Delta G_\text{\tiny vdW}$.
-In order to analyze the model distinctions in more detail, in Fig.~\ref{fig:deltag} we plot the profiles of $\Delta G_\text{\tiny vdW}$ as a function of the coupling parameter $\lambda_\text{\tiny vdW}$.
-
-If we look at the $\Delta G_\text{\tiny vdW}$ profiles in Fig.~\ref{fig:deltag}, we observe that for the models of Batista \textit{et al}.
-\cite{Batista_2015} and Liu \textit{et al}.~\cite{Liu_2014} the maximum occurs at lower values of energy, suggesting that these models underestimate the atomic interactions, which may also explain their failure to reproduce the experimental density.
+In order to analyze the model distinctions in more detail, in Fig.~\ref{fig:deltag} we plot free energy profiles with respect to the coupling parameter $\lambda_\text{\tiny vdW}$, as obtained from the simulations with all \ce{[emim][B(CN)_4]} models.
+We observe that the model of Batista \textit{et al}.
+\cite{Batista_2015} is the one that predicts the smallest free-energy barrier, immediately followed by the model of Liu \textit{et al}.
+\cite{Liu_2014}.
+This observation suggests that these models underestimate the magnitude of the solvent-solvent interactions, thus making it easier to open a cavity in the system for inserting the solute.
+Besides, it also explains why these models underestimate the density of \ce{[emim][B(CN)_4]}, such as seen in Table~\ref{table:props_dsf}.
+The Liu \textit{et al}. \cite{Liu_2014} model predicts the smallest value of $\Delta G_\text{\tiny vdW}$ in spite of exhibiting only the second smallest free-energy barrier.
+This occurs because the attractive van der Waals interactions compensate the cavity formation more favorably than in the case of Batista \textit{et al}.
+\cite{Batista_2015}, as one can observe in Fig.~\ref{fig:deltag} as $\lambda_\text{\tiny vdW}$ approaches unity.
+Nevertheless, these distinctions end up being canceled out when the charges of the \ce{CO_2} molecule are introduced, since $\Delta G_\text{\tiny vdW}$ and $\Delta G_\text{\tiny Coul}$ sum up to very similar $\Delta G_\text{sim}$ results for both models.
 
@@
 
-The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al}.
+The $\Delta G_\text{sim}$ values for the models of Koller \textit{et al}.
 \cite{Koller_2012} and K\"{o}ddermann \textit{et al}.

### 2018-09-15 ionic_liquids.tex
Elimination of tiny formatting in math symbols

@@
 In what follows, the subscripts ``s'' and ``IL'' refer to the solute and the solvent (ionic liquid), respectively.
-For a liquid phase containing $N_\text{\tiny IL}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
+For a liquid phase containing $N_\text{IL}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
 \begin{equation}
-\Delta G_\text{sim} \equiv R T \ln \frac{\Xi (N_s,N_\text{\tiny IL},P,T,\lambda = 1)}{\Xi (N_s,N_\text{\tiny IL},P,T,\lambda = 0)}, 
+\Delta G_\text{sim} \equiv R T \ln \frac{\Xi (N_s,N_\text{IL},P,T,\lambda = 1)}{\Xi (N_s,N_\text{IL},P,T,\lambda = 0)}, 
 \end{equation}
@@
 \end{equation}
-where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and solute partial pressure $P_s$, while $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{\tiny IL}$,P,T) and ($N_s$,$N_\text{\tiny IL}$,P,T), respectively.
+where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and solute partial pressure $P_s$, while $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{IL}$,P,T) and ($N_s$,$N_\text{IL}$,P,T), respectively.
 Note that $c_s = \frac{N_s}{N_A V_1}$.
@@
 where $\tilde{\rho}_\text{sim}$ is the simulated molar density of the solution.
-Assuming that this solution is very dilute, one can use the molar density of pure solvent ($\tilde{\rho}_\text{\tiny IL}$) instead.
+Assuming that this solution is very dilute, one can use the molar density of pure solvent ($\tilde{\rho}_\text{IL}$) instead.
 
@@
 
-In the special case of a solute at infinite dilution in an ionic liquid solvent, its activity coefficient $\gamma^\infty_s$ can be computed by replacing $\tilde{\rho}$ in the equation above by the molar density of the pure solvent, $\tilde{\rho}_\textit{\tiny IL}$.
+In the special case of a solute at infinite dilution in an ionic liquid solvent, its activity coefficient $\gamma^\infty_s$ can be computed by replacing $\tilde{\rho}$ in the equation above by the molar density of the pure solvent, $\tilde{\rho}_\textit{IL}$.
 
@@
 \begin{equation}
-V_\text{\tiny DSF}(r) = V(r) - V(r_c) - V^\prime(r_c)(r-r_c),
+V_\text{DSF}(r) = V(r) - V(r_c) - V^\prime(r_c)(r-r_c),
 \end{equation}
@@
 In this paper, we use the modified LJ potential proposed by Beutler \textit{et al}.
-\cite{Beutler_1994}, given by $V_\text{\tiny vdW}(r) = 4 \epsilon \lambda_\text{\tiny vdW} (s^{-2} - s^{-1})$, where $s = (r/\sigma)^6 + (1 - \lambda_\text{\tiny vdW})/2$.
-The electrostatic interactions, on the other hand, can be simply multiplied by a coupling parameter $\lambda_\text{\tiny Coul}$ \cite{Naden_2015}.
+\cite{Beutler_1994}, given by $V_\text{vdW}(r) = 4 \epsilon \lambda_\text{vdW} (s^{-2} - s^{-1})$, where $s = (r/\sigma)^6 + (1 - \lambda_\text{vdW})/2$.
+The electrostatic interactions, on the other hand, can be linearly scaled by a coupling parameter $\lambda_\text{Coul}$ \cite{Naden_2015}, meaning that $V_\text{Coul}(r) = V_\text{Coul} V_\text{DSF}(r)$.
 Furthermore, the vdW and Coulomb contributions to the free energy difference are taken into account separately.
@@
 \begin{equation}
-\Delta G_\text{sim} = \Delta G_\text{\tiny vdW} + \Delta G_\text{\tiny Coul},
+\Delta G_\text{sim} = \Delta G_\text{vdW} + \Delta G_\text{Coul},
 \end{equation}
-where $\Delta G_\text{\tiny vdW}$ is computed by varying $\lambda_\text{\tiny vdW} \in [0,1]$ while keeping $\lambda_\text{\tiny Coul} = 0$, whereas $\Delta G_\text{\tiny Coul}$ is computed by varying $\lambda_\text{\tiny Coul} \in [0,1]$ while keeping $\lambda_\text{\tiny vdW} = 1$.
-The sets of coupling parameter values we use here in all alchemical simulations are $\lambda_{\text{\tiny vdW}}$ = $\{0.0$, $0.05$, $0.1$, $0.2$, $0.25$, $0.3$, $0.35$, $0.4$, $0.45$, $0.5$, $0.6$, $0.7$, $0.8$, $0.9$, $1.0\}$ and $\lambda_{\text{\tiny Coul}}$ = $\{0.0$, $0.1$, $0.4$, $0.7$, $0.1\}$.
+where $\Delta G_\text{vdW}$ is computed by varying $\lambda_\text{vdW} \in [0,1]$ while keeping $\lambda_\text{Coul} = 0$, whereas $\Delta G_\text{Coul}$ is computed by varying $\lambda_\text{Coul} \in [0,1]$ while keeping $\lambda_\text{vdW} = 1$.
+The sets of coupling parameter values we use here in all alchemical simulations are $\lambda_{\text{vdW}}$ = $\{0.0$, $0.05$, $0.1$, $0.2$, $0.25$, $0.3$, $0.35$, $0.4$, $0.45$, $0.5$, $0.6$, $0.7$, $0.8$, $0.9$, $1.0\}$ and $\lambda_{\text{Coul}}$ = $\{0.0$, $0.1$, $0.4$, $0.7$, $0.1\}$.
 
-In this work, we compute $\Delta G_\text{\tiny Coul}$ by carrying out an independent simulation of 10 ns at each state of $\lambda_{\text{\tiny Coul}}$.
+In this work, we compute $\Delta G_\text{Coul}$ by carrying out an independent simulation of 10 ns at each state of $\lambda_{\text{Coul}}$.
 In the end, we apply the Multistate Bennett Acceptance Ratio (MBAR) method \cite{Shirts_2008} by using the \textit{Alchemical Analysis} package \cite{Klimovich_2015}.
 
-In the case of $\Delta G_\text{\tiny vdW}$, the Expanded Ensemble method \cite{Lyubartsev_1992} is applied for sampling the whole $\lambda_\text{\tiny vdW}$ set in a single simulation.
-An expanded ensemble is constructed as a weighted sum of subensembles, each one assuming a different value of the parameter selected for exploring the free energy landscape, which in our case is $\lambda_\text{\tiny vdW}$.
-In the method adopted here \cite{Chodera_2011_2}, simulating an expanded ensemble comprises doing molecular dynamics (MD) at fixed N, P, T, and $\lambda_\text{\tiny vdW}$ amid Monte Carlo (MC) transitions in the value of $\lambda_\text{\tiny vdW}$.
-The number of MD steps between transitions is fixed and, at each transition, one of the $\lambda_\text{\tiny vdW}$ states is picked at random according to a corresponding set of probabilities \cite{Chodera_2011_2}.
-In addition, a set of biasing weights is included in the MC acceptance criterion, thus making it possible to enhance the sampling procedure by iteratively tuning these weights until all $\lambda_\text{\tiny vdW}$ states are visited with equal frequency \cite{Lyubartsev_1992}.
+In the case of $\Delta G_\text{vdW}$, the Expanded Ensemble method \cite{Lyubartsev_1992} is applied for sampling the whole $\lambda_\text{vdW}$ set in a single simulation.
+An expanded ensemble is constructed as a weighted sum of subensembles, each one assuming a different value of the parameter selected for exploring the free energy landscape, which in our case is $\lambda_\text{vdW}$.
+In the method adopted here \cite{Chodera_2011_2}, simulating an expanded ensemble comprises doing molecular dynamics (MD) at fixed N, P, T, and $\lambda_\text{vdW}$ amid Monte Carlo (MC) transitions in the value of $\lambda_\text{vdW}$.
+The number of MD steps between transitions is fixed and, at each transition, one of the $\lambda_\text{vdW}$ states is picked at random according to a corresponding set of probabilities \cite{Chodera_2011_2}.
+In addition, a set of biasing weights is included in the MC acceptance criterion, thus making it possible to enhance the sampling procedure by iteratively tuning these weights until all $\lambda_\text{vdW}$ states are visited with equal frequency \cite{Lyubartsev_1992}.
 Given that sample decorrelation is improved by having short MD runs between MC transitions \cite{Chodera_2011_2}, we used only 5 steps in each run.
@@
 			\hline\hline
-			Model & $\tilde{\rho}_\text{sim}$ & $\Delta G_\text{\tiny vdW}$  & $\Delta G_\text{\tiny Coul}$  & $\Delta G_\text{sim}$ & $K_s$ & error \\
+			Model & $\tilde{\rho}_\text{sim}$ & $\Delta G_\text{vdW}$  & $\Delta G_\text{Coul}$  & $\Delta G_\text{sim}$ & $K_s$ & error \\
 			& (mol/dm\textsuperscript{3}) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  & (\%) \\
@@
 Is it worth remarking that the result of $\Delta G_\text{sim}$ obtained with the model of Liu \textit{et al}.
-\cite{Liu_2014} is statistically identical to a value reported by the same authors in Ref.~\citenum{Liu_2014_1}, where they applied the Bennett Acceptance Ratio (BAR) method \cite{Bennett_1976} to independent samples obtained with different values of $\lambda_\text{\tiny vdW}$ and $\lambda_\text{\tiny Coul}$.
+\cite{Liu_2014} is statistically identical to a value reported by the same authors in Ref.~\citenum{Liu_2014_1}, where they applied the Bennett Acceptance Ratio (BAR) method \cite{Bennett_1976} to independent samples obtained with different values of $\lambda_\text{vdW}$ and $\lambda_\text{Coul}$.
 Moreover, the $\Delta G_\text{sim}$ value we computed for \ce{[emim][NTf_2]} is very close to the one obtained by Kerl \textit{et al}.
@@
 The worst results are obtained with the models of Batista \textit{et al}. \cite{Batista_2015} and Liu \textit{et al}. \cite{Liu_2014}.
-These models fail in part because of the small values they predict for $\Delta G_\text{\tiny vdW}$.
-In order to analyze the model distinctions in more detail, in Fig.~\ref{fig:deltag} we plot free energy profiles with respect to the coupling parameter $\lambda_\text{\tiny vdW}$, as obtained from the simulations with all \ce{[emim][B(CN)_4]} models.
+These models fail in part because of the small values they predict for $\Delta G_\text{vdW}$.
+In order to analyze the model distinctions in more detail, in Fig.~\ref{fig:deltag} we plot free energy profiles with respect to the coupling parameter $\lambda_\text{vdW}$, as obtained from the simulations with all \ce{[emim][B(CN)_4]} models.
 We observe that the model of Batista \textit{et al}.
@@
 Besides, it also explains why these models underestimate the density of \ce{[emim][B(CN)_4]}, such as seen in Table~\ref{table:props_dsf}.
-The Liu \textit{et al}. \cite{Liu_2014} model predicts the smallest value of $\Delta G_\text{\tiny vdW}$ in spite of exhibiting only the second smallest free-energy barrier.
+The Liu \textit{et al}. \cite{Liu_2014} model predicts the smallest value of $\Delta G_\text{vdW}$ in spite of exhibiting only the second smallest free-energy barrier.
 This occurs because the attractive van der Waals interactions compensate the cavity formation more favorably than in the case of Batista \textit{et al}.
-\cite{Batista_2015}, as one can observe in Fig.~\ref{fig:deltag} as $\lambda_\text{\tiny vdW}$ approaches unity.
-Nevertheless, these distinctions end up being canceled out when the charges of the \ce{CO_2} molecule are introduced, since $\Delta G_\text{\tiny vdW}$ and $\Delta G_\text{\tiny Coul}$ sum up to very similar $\Delta G_\text{sim}$ results for both models.
+\cite{Batista_2015}, as one can observe in Fig.~\ref{fig:deltag} as $\lambda_\text{vdW}$ approaches unity.
+Nevertheless, these distinctions end up being canceled out when the charges of the \ce{CO_2} molecule are introduced, since $\Delta G_\text{vdW}$ and $\Delta G_\text{Coul}$ sum up to very similar $\Delta G_\text{sim}$ results for both models.
 
@@
 \includegraphics[width=\linewidth]{free_energy_paper}
-\caption{Profile of $\Delta G_\text{\tiny vdW}$ corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, modeled according to the force fields of Koller \textit{et al}.
+\caption{Profile of $\Delta G_\text{vdW}$ corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, modeled according to the force fields of Koller \textit{et al}.
 \cite{Koller_2012} ($\bullet$), Batista \textit{et al}.
@@
 			\hline\hline
-			Solute & $\rho_\text{sim}$ & error & $\Delta G_\text{\tiny vdW}$  & $\Delta G_\text{\tiny Coul}$  & $\Delta G^0_\text{sim}$ & $\Delta G^0_\text{exp}$   & error \\
+			Solute & $\rho_\text{sim}$ & error & $\Delta G_\text{vdW}$  & $\Delta G_\text{Coul}$  & $\Delta G^0_\text{sim}$ & $\Delta G^0_\text{exp}$   & error \\
 			& (g/cm\textsuperscript{3}) & (\%) & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   & (kcal/mol)   & (\%) \\
@@
 			\hline\hline
-			Solute & $\Delta G_\text{\tiny vdW}$  & $\Delta G_\text{\tiny Coul}$  & $\Delta G_\text{sim}$  & $\gamma^\infty_\text{sim}$ & $\gamma^\infty_\text{exp}$ \cite{Doma_ska_2011} & $\gamma^\infty_\text{exp}$ \cite{Yan_2010} \\
+			Solute & $\Delta G_\text{vdW}$  & $\Delta G_\text{Coul}$  & $\Delta G_\text{sim}$  & $\gamma^\infty_\text{sim}$ & $\gamma^\infty_\text{exp}$ \cite{Doma_ska_2011} & $\gamma^\infty_\text{exp}$ \cite{Yan_2010} \\
 			& (kcal/mol) & (kcal/mol) &  (kcal/mol)  & (298 K) & (298 K)  & (303 K) \\

### 2018-09-16 ionic_liquids.tex
Revision of Dilute CO2 solutions section

@@
 \usepackage{adjustbox}   
-\usepackage[position=top,captionskip=-12pt]{subfig}
+\usepackage[position=top,captionskip=0pt]{subfig}
 \usepackage{graphicx}
@@
 In the case of ionic liquid \ce{[emim][NTf_2]}, we use the model of K\"{o}ddermann \textit{et al}.
-\cite{K_ddermann_2007}, which was also derived by refining parameters of the force field by P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
+\cite{Koddermann_2007}, which was also derived by refining parameters of the force field by P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
 The authors characterized this refinement as unusual, given that they modified the LJ parameters while keeping the partial charges unchanged.
@@
 \subfloat[][Koller~\textit{et al}.~\cite{Koller_2012}]{
-  \includegraphics[width=.4\linewidth]{koller}}
+  \includegraphics[width=.4\linewidth,trim={0 0 0 12pt},clip]{koller}}
 \subfloat[Batista~\textit{et al}.~\cite{Batista_2015}]{  
-  \includegraphics[width=.4\linewidth]{batista}}
+  \includegraphics[width=.4\linewidth,trim={0 0 0 12pt},clip]{batista}}
 
 \subfloat[Liu~\textit{et al}.~\cite{Liu_2014}]{%
-  \includegraphics[width=.4\linewidth]{Liu}}%
+  \includegraphics[width=.4\linewidth,trim={0 0 0 12pt},clip]{Liu}}%
 \subfloat[Weber and Kirchner~\cite{Weber_2016}]{%
-  \includegraphics[width=.4\linewidth]{Weber}}%
+  \includegraphics[width=.4\linewidth,trim={0 0 0 12pt},clip]{Weber}}%
 \caption{Combined distribution functions of the dihedral angles corresponding to atoms C1-N2-C5-C6 and C2-N2-C5-C6 in the cation \ce{[emim]^+} (see Fig.~\ref{fig:atoms_id}), as sampled in NPT-MD simulations of 250 ion pairs using each model for \ce{[emim][B(CN)_4]}.}
@@
 
-A study of conformations was also carried out for \ce{[emim][NTf_2]} using the model of K\"{o}ddermann \textit{et al}. \cite{K_ddermann_2007}.
+A study of conformations was also carried out for \ce{[emim][NTf_2]} using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.
 A CDF obtained for the dihedral angles of sequences C1-N2-C5-C6 and C2-N2-C5-C6 in \ce{[emim]^+}, which is made available in the Supplementary Material, resembles the one in Fig.~\ref{fig:dihedrals_emim}(d).
@@
 \caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[NTf_2]^-}, obtained from NPT-MD simulations of 250 ion pairs of \ce{[emim][NTf_2]} using the model of K\"{o}ddermann \textit{et al}.
-\cite{K_ddermann_2007}.}
+\cite{Koddermann_2007}.}
 \label{fig:die_ntf2}
@@
 			\multicolumn{7}{c}{\ce{[emim][NTf_2]}} \\
-			K\"{o}ddermann \textit{et al}. \cite{K_ddermann_2007} & $3.8205$ & $0.389 \pm 0.005$ & $-0.901 \pm 0.006$ & $-0.512 \pm 0.008$ & $39.4 \pm 0.5$  & $0.97$  \\
+			K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007} & $3.8205$ & $0.389 \pm 0.005$ & $-0.901 \pm 0.006$ & $-0.512 \pm 0.008$ & $39.4 \pm 0.5$  & $0.97$  \\
 			\hline\hline
@@
 
-The $\Delta G_\text{sim}$ values for the models of Koller \textit{et al}.
-\cite{Koller_2012} and K\"{o}ddermann \textit{et al}.
-\cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}.
-The spatial distribution functions (SDFs) \cite{Svishchev_1993} shown in Figs.~\ref{fig:sdf_ions} confirm this result.
-The SDFs of the ions around a \ce{CO_2} molecule were obtained by using the software packages TRAVIS \cite{Brehm_2011} and VMD \cite{HUMP96}.
-For that, we carried out NPT-MD simulations of \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} systems with a \ce{CO_2} molar fraction of 0.1.
-The isovalues were visually determined so as to observe the first solvation shell.
-If we compare Figs.~\ref{fig:sdf_ions} (a) and (b), one notes that the region with a low probability of finding an ion is larger for \ce{[emim][NTf_2]}.
-Also, the first solvation shell due to \ce{[B(CN)_4^-} occurs at a slightly shorter distance than for \ce{[NTf_2]^-}, as one sees from Fig.~\ref{fig:sdf_ions}(c).
+Such as the model of Koller \textit{et al}.
+\cite{Koller_2012} does in the case of \ce{[emim][B(CN)_4]}, the one of K\"{o}ddermann \textit{et al}.
+\cite{Koddermann_2007} accurately predicts the Henry's law constant of \ce{CO_2} in \ce{[emim][NTf_2]}.
+A comparison between the values of $\Delta G_\text{sim}$ obtained from these models, shown in Table \ref{table:henry}, suggests that the solvation of \ce{CO_2} takes place more favorably in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}.
+The fact that $K_s$ has almost the same value in both cases is due to a compensation promoted by the distinct molar densities of these ionic liquids.
+Spatial distribution functions (SDFs) \cite{Svishchev_1993} can help us visualizing how differently the solvent ions interact with the solute molecule.
+By using TRAVIS \cite{Brehm_2011}, we have obtained SDFs of both cation and anion around a \ce{CO_2} molecule, sampled from MD trajectories of either \ce{CO_2}+\ce{[emim][B(CN)_4]} or \ce{CO_2}+\ce{[emim][NTf_2]} systems simulated at $T = 298.0~\text{K}$, $P = 1.0~\mathrm{bar}$, and $x_\mathrm{CO_2} = 0.1$.
+The slightly larger \ce{CO_2} concentration considered here is meant to improve statistics.
+The obtained SDFs were depicted as isosurfaces using VMD \cite{HUMP96}, with isovalues determined so as to highlight the first solvation shell.
+The resulting images are shown in Fig.~\ref{fig:sdf_ions}.
+By comparing Figs.~\ref{fig:sdf_ions}(a) and \ref{fig:sdf_ions}(b), we note that the gap between the regions occupied by the anion and the cation is smaller in the case of \ce{[emim][B(CN)_4]}.
+In addition, the first solvation shell corresponding to \ce{[B(CN)_4]^-} occurs at a slightly shorter distance than that corresponding to \ce{[NTf_2]^-}, as one can clearly see by a direct comparison done in Fig.~\ref{fig:sdf_ions}(c).
+This is in part due to the difference in size of these two anions.
+The result is a higher density of negative charges around the carbon atom of \ce{CO_2}, whose point-charge is positive as a consequence of the oxygen's high electronegativity.
+This seems to induce a greater stability of \ce{CO_2} when solvated in \ce{[emim][B(CN)_4]}, rather than in \ce{[emim][NTf_2]}, possibly resulting in enhanced solubility.
+However, the mentioned similarity in the Henry's law constants could cause such enhancement to go unnoticed.
+This makes clear the importance of carrying out a study at high \ce{CO_2} concentrations.
 
@@
 		\hline
-		model &  Ref.~\citenum{Koller_2012} & Ref.~\citenum{K_ddermann_2007} \\
+		model &  Ref.~\citenum{Koller_2012} & Ref.~\citenum{Koddermann_2007} \\
 		T  & 313.15 K & 312.13 K \\
@@
 
-\bibliography{mybibfile}
+\bibliography{ionic_liquids}
 

### 2018-09-16 ionic_liquids.tex
Initial revision of the concentrated CO2 solutions section

@@
 \section{Introduction}
+\label{sec:intro}
 
@@
 \begin{equation}
-\label{eq:equation for pressure}
+\label{eq:equilibrium pressure}
 y_s \exp\left( \frac{B_s P}{R T} \right) P = \exp \left( \frac{\Delta G_\text{sim}}{R T} \right) +  c_s R T,
@@
 Our third assumption, supported by preliminary simulations, is that $\Delta G_\text{sim}$ does not vary appreciably with pressure, at least over the range of experimental data considered here.
-In this way, no iterative simulations are required to compute the equilibrium pressure when solving Eq.~\eqref{eq:equation for pressure} for $P$.
+In this way, no iterative simulations are required to compute the equilibrium pressure when solving Eq.~\eqref{eq:equilibrium pressure} for $P$.
 
@@
 
-Since concentrated solutions are the more likely scenario in \ce{CO_2} capture processes, we have also carried out simulations at the thermodynamic conditions specified in Table~\ref{table:solv}, which correspond to similar values of \ce{CO_2} molality.
-Note that the differences in the \ce{CO_2} molar fractions clearly exemplifies the observation made by Carvalho \textit{et al}. \cite{Carvalho_2016}, mentioned at the introduction of this paper.
+Since concentrated solutions are the more likely scenario in carbon capture processes, we have also carried out simulations of systems with higher \ce{CO_2} concentrations.
+The thermodynamic conditions specified for these simulations, which are based on experimental investigations \cite{Makino_2014,Schilderman_2007}, are shown in Table~\ref{table:solv}.
+We have selected these specific conditions because of the proximity observed in the molality of \ce{CO_2} ($m_s$).
+It is worth noting that the marked difference in the molar fractions of \ce{CO_2} in Table~\ref{table:solv} does not imply that \ce{[emim][NTf_2]} is a better solvent than \ce{[emim][B(CN)_4]}, thus exemplifying the observation made by Carvalho \textit{et al}.
+\cite{Carvalho_2016} and discussed here in Sec.~\ref{sec:intro}.
 
@@
 	\centering
-	\caption{Thermodynamic conditions employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}~\cite{Makino_2014,Schilderman_2007}.}
-	\begin{tabular}{ c  c  c  }  
+	\caption{Thermodynamic conditions employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, based on the experimental observations of Refs.~ \citenum{Makino_2014} and \citenum{Schilderman_2007}.}
+	\begin{tabular}{ccc}
 		\hline\hline
@@
 		\hline
-		model &  Ref.~\citenum{Koller_2012} & Ref.~\citenum{Koddermann_2007} \\
+%		model & Ref.~\citenum{Koller_2012} & Ref.~\citenum{Koddermann_2007} \\
 		T  & 313.15 K & 312.13 K \\
@@
 
-For each system, in Fig.~\ref{fig:pressure} we show our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
-The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
-Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably lower for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
+We carried out expanded ensemble simulations of liquid solutions at the conditions of Table~\ref{table:solv}.
+The model of Koller \textit{et al}. \cite{Koller_2012} was the one employed for \ce{[emim][B(CN)_4]}.
+The computed solvation free energies for the systems \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]} were $-0.755 \pm 0.01 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005~\mathrm{kcal/mol}$, respectively.
+In Fig.~\ref{fig:pressure}, we present our predictions of the equilibrium pressure ($P$) obtained by solving Eq.~\eqref{eq:equilibrium pressure}, as well as the corresponding gas-phase fugacities of \ce{CO_2} ($f_s^g$) computed by Eq.~\eqref{eq:fgas_d}.
+The dotted lines correspond to the experimental values (i.e. the ones used to simulate the liquid solutions).
+First, the results make clear that assuming ideal gas would have been an oversimplification, specially in the case of \ce{[emim][NTf_2]}.
+Second, the computed pressures did not depart considerably from the specified values, meaning that our results sustain the experimental observation that $P$ is considerably lower for the system \ce{CO_2}+\ce{[emim][B(CN)_4]} than for the system \ce{CO_2}+\ce{[emim][NTf_2]}.
 In addition, we see that in this case the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
-The solvation free energies obtained for \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-\ce{[emim][NTf_2]} were $-0.755 \pm 0.01 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005$, respectively.
-However, since we simulated a different number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could explain the higher solubility.
+%However, since we simulated a different number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could explain the higher solubility.
 

### 2018-09-16 ionic_liquids.tex
Revision of the concentrated CO2 section

@@
 In this paper, we calculate solvation free energies of several compounds in ionic liquids.
-These free energies are used to compute properties such as Henry's law constants and activity coefficients, generally required to the design of environmentally sustainable processes.
+These free energies are used to compute properties such as Henry's law constants and activity coefficients, generally required in the design of environmentally sustainable processes.
 It is known, for instance, that carbon dioxide from combustion is one of the main sources of anthropogenic greenhouse gases.
-Recently, the propensity of ionic liquid \ce{[emim][B(CN)_4]} for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
+Recently, the propensity of the ionic liquid \ce{[emim][B(CN)_4]} for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
 In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} are carried out both at infinite dilution and at high concentrations.
@@
 The simulations confirmed what is observed in experiments.
-For \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}, considering a given volume of solvent.
+For \ce{[emim][B(CN)_4]}, a considerably lower pressure is required to dissolve the same amount of \ce{CO_2}, considering a given mass of solvent.
 In addition, we also calculated infinite-dilution activity coefficients of other solutes in \ce{[emim][B(CN)_4]} and compared the results with experimental values recently reported in literature.
@@
 \label{eq:solvation free energy definition}
-\Delta G_{\text{solv}} \equiv R \ln \left( \frac{P_s}{c_s R T} \right),
+\Delta G_{\text{solv}} \equiv R T \ln \left( \frac{P_s}{c_s R T} \right),
 \end{equation}
@@
 where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and solute partial pressure $P_s$, while $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{IL}$,P,T) and ($N_s$,$N_\text{IL}$,P,T), respectively.
-Note that $c_s = \frac{N_s}{N_A V_1}$.
+Note that $c_s = \frac{N_s}{N_A V_1}$, where $N_A$ is the Avogadro number.
 
@@
 \label{eq:fgas_d}
-f^{g}_s = \exp \left( \frac{\Delta G_\text{sim}}{R T} \right) +  c_s R T. 
+f^{g}_s = c_s R T \exp \left( \frac{\Delta G_\text{sim}}{R T} \right). 
 \end{equation}
@@
 \label{eq:equilibrium pressure}
-y_s \exp\left( \frac{B_s P}{R T} \right) P = \exp \left( \frac{\Delta G_\text{sim}}{R T} \right) +  c_s R T,
+y_s \exp\left( \frac{B_s P}{R T} \right) P = c_s R T \exp \left( \frac{\Delta G_\text{sim}}{R T} \right),
 \end{equation}
@@
 \cite{Beutler_1994}, given by $V_\text{vdW}(r) = 4 \epsilon \lambda_\text{vdW} (s^{-2} - s^{-1})$, where $s = (r/\sigma)^6 + (1 - \lambda_\text{vdW})/2$.
-The electrostatic interactions, on the other hand, can be linearly scaled by a coupling parameter $\lambda_\text{Coul}$ \cite{Naden_2015}, meaning that $V_\text{Coul}(r) = V_\text{Coul} V_\text{DSF}(r)$.
+The electrostatic interactions, on the other hand, can be linearly scaled by a coupling parameter $\lambda_\text{Coul}$ \cite{Naden_2015}, meaning that $V_\text{Coul}(r) = \lambda_\text{Coul} V_\text{DSF}(r)$.
 Furthermore, the vdW and Coulomb contributions to the free energy difference are taken into account separately.
@@
 both corresponding to a coplanar structure formed by atoms C1, C2, N2, and C5.
-There are two such lines in each diagram because atom C6 can be located on either side of the plan.
+%There are two such lines in each diagram because atom C6 can be located on either side of the plane.
 One can note in Fig.~\ref{fig:dihedrals_emim} that the CDF peaks, which indicate the most likely dihedral angle combinations, lie either precisely above these lines or very close to them.
 The largest distortions from coplanarity occur for the Batista \textit{et al}. \cite{Batista_2015} model, as observed by the peak locations in Fig.~\ref{fig:dihedrals_emim}(b).
-Despite this, all rigid bodies considered here for \ce{[emim]^+} are built in such a way that atoms C[1-5], H[1-3], and N[1-2] all lie in a single plan.
+Despite this, all rigid bodies considered here for \ce{[emim]^+} are built in such a way that atoms C[1-5], H[1-3], and N[1-2] all lie in a single plane.
 Therefore, for specifying the torsion of bond N2-C5 it is enough to set a value for $\psi_1$ and then compute $\psi_2$ by means of Eq.~\eqref{eq:dihedral angles}.
@@
 	\centering
-	\caption{Thermodynamic conditions employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, based on the experimental observations of Refs.~ \citenum{Makino_2014} and \citenum{Schilderman_2007}.}
+	\caption{Thermodynamic conditions, based on the experimental observations of Refs.~\citenum{Makino_2014} and \citenum{Schilderman_2007}, employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, as well as the results obtained via expanded ensemble simulations.}
 	\begin{tabular}{ccc}
@@
 %		model & Ref.~\citenum{Koller_2012} & Ref.~\citenum{Koddermann_2007} \\
-		T  & 313.15 K & 312.13 K \\
-		P  & 21 atm & 37 atm \\
-		$x_s$ & 0.352 & 0.479 \\
-		$m_s$ & 2.4 mol/kg & 2.35 mol/kg \\
+		\multicolumn{3}{c}{Specification} \\
+		$T$  & $313.15~\mathrm{K}$ & $312.13~\mathrm{K}$ \\
+		$P$  & $21~\mathrm{atm}$ & $37~\mathrm{atm}$ \\
+		$x_s$ & $0.352$ & $0.479$ \\
+		$m_s$ & $2.4~\mathrm{mol/kg}$ & $2.35~\mathrm{mol/kg}$ \\
+		\hline
+		\multicolumn{3}{c}{Simulation Result} \\
+		$c_s$ & $3.04~\mathrm{mol/dm^3}$ & $2.22~\mathrm{mol/dm^3}$ \\ 
+		$\Delta G_\text{sim}$ & $-0.755~\mathrm{kcal/mol}$ & $-0.542~\mathrm{kcal/mol}$ \\
+		$P$ & $18.3~\mathrm{atm}$ & $38.4~\mathrm{atm}$ \\
 		\hline\hline
@@
 We carried out expanded ensemble simulations of liquid solutions at the conditions of Table~\ref{table:solv}.
-The model of Koller \textit{et al}. \cite{Koller_2012} was the one employed for \ce{[emim][B(CN)_4]}.
-The computed solvation free energies for the systems \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]} were $-0.755 \pm 0.01 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005~\mathrm{kcal/mol}$, respectively.
+The model of Koller \textit{et al}. \cite{Koller_2012} was the one employed for simulating \ce{[emim][B(CN)_4]}.
+The computed solvation free energies for the systems \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]} were $-0.755 \pm 0.009 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005~\mathrm{kcal/mol}$, respectively.
 In Fig.~\ref{fig:pressure}, we present our predictions of the equilibrium pressure ($P$) obtained by solving Eq.~\eqref{eq:equilibrium pressure}, as well as the corresponding gas-phase fugacities of \ce{CO_2} ($f_s^g$) computed by Eq.~\eqref{eq:fgas_d}.
-The dotted lines correspond to the experimental values (i.e. the ones used to simulate the liquid solutions).
-First, the results make clear that assuming ideal gas would have been an oversimplification, specially in the case of \ce{[emim][NTf_2]}.
-Second, the computed pressures did not depart considerably from the specified values, meaning that our results sustain the experimental observation that $P$ is considerably lower for the system \ce{CO_2}+\ce{[emim][B(CN)_4]} than for the system \ce{CO_2}+\ce{[emim][NTf_2]}.
-In addition, we see that in this case the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).
-%However, since we simulated a different number of \ce{CO_2}, we cannot draw any definite conclusion regarding the presence of stronger interactions with \ce{[emim][B(CN)_4]}, which could explain the higher solubility.
+The dotted lines correspond to the experimental values (i.e. those used to simulate the liquid solutions).
+First, the results make clear that assuming ideal gas ($P = f_s^g$) would have been an oversimplification, specially in the case of \ce{[emim][NTf_2]}.
+Second, and most importantly, the computed pressures did not depart considerably from the specified values, meaning that our results sustain the experimental observations.
+Therefore, as the pressure required to reach the same equilibrium molal concentration of \ce{CO_2} in the liquid phase is smaller for \ce{[emim][B(CN)_4]} than for \ce{[emim][NTf_2]}, our results confirm that the former is a better solvent than the latter.
+This confirmation was possible by simulating a purely physical absorption, without considering any quantum effect.
 

### 2018-09-16 ionic_liquids.tex
Revision of activity coefficients section

@@
 \begin{equation}
-\label{eq:gamma}
 \ln \gamma_s = \frac{\mu_s^l - \mu_s^{l,0}}{R T} - \ln x_s,
@@
 \begin{equation}
+\label{eq:gamma}
 \ln \gamma_s = \frac{\Delta G_\text{sim} - \Delta G_\text{sim}^{0}}{R T} + \ln \frac{\tilde{\rho}}{\tilde{\rho}_s^0}.
@@
 
-Having selected the model of \ce{[emim][B(CN)_4]} that best reproduces the experimental $K_s$ of \ce{CO_2}, we next calculate the infinite-dilution activity coefficients ($\gamma^{\, \infty}$) of benzene, hexane, cyclohexane, ethanol and water in \ce{[emim][B(CN)_4]}.
+Having selected the model of \ce{[emim][B(CN)_4]} that best reproduces the experimental Henry's law constant of \ce{CO_2}, we extend its use to the calculation of infinite-dilution activity coefficients ($\gamma^\infty$) of other solutes in \ce{[emim][B(CN)_4]}.
+Due to the availability of experimental data \cite{Yan_2010, Doma_ska_2011}, the solutes chosen for this study are benzene, hexane, cyclohexane, ethanol, and water.
 
-The task of accurately predicting $\gamma^{\, \infty}$ is challenging since, according to Eq.~\eqref{eq:gamma_inf}, one should reproduce the solvation free energies in both the pure solute and the solvent.
-In Table~\ref{table:mu_solutes} we show the simulated densities and the solvation free energies $(\Delta G^{0}_\text{sim})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}.
-It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ for cyclohexane.
+The task of accurately predicting $\gamma^\infty$ is challenging because, according to Eq.~\eqref{eq:gamma}, one needs to reproduce the solvation free energies of a solute molecule in both the solvent and the solute itself as a pure liquid.
+In Table~\ref{table:mu_solutes}, we show the simulated densities ($\rho^0_s$) and solvation free energies $(\Delta G^{0}_\text{sim})$ of the pure solutes, which we compare against experimental data extracted from the work of Chang \cite{Chang_2009}.
+It is worth remarking that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ for cyclohexane.
 Note that only in the case of ethanol we successfully predicted the $\Delta G^{0}_\text{exp}$.
 The relative errors for the other solutes are around 10\%.
-
-The results of $\gamma^{\, \infty}$ are presented in Table~\ref{table:gamma}.
-For benzene and water, the predictions are very accurate, but this may be due to fortuitous error compensations given the divergences shown in Table~\ref{table:mu_solutes}.
-From Table \ref{table:gamma}, one sees that the experimental $\gamma^{\, \infty}$ for hexane at $298.15~\text{K}$ and $303~\text{K}$ considerably differ.
-It is therefore difficult to assess the reliability of our results in this case.
 
@@
 			\hline\hline
-			Solute & $\rho_\text{sim}$ & error & $\Delta G_\text{vdW}$  & $\Delta G_\text{Coul}$  & $\Delta G^0_\text{sim}$ & $\Delta G^0_\text{exp}$   & error \\
+			Solute & $\rho^0_s$ & error & $\Delta G_\text{vdW}$  & $\Delta G_\text{Coul}$  & $\Delta G^0_\text{sim}$ & $\Delta G^0_\text{exp}$   & error \\
 			& (g/cm\textsuperscript{3}) & (\%) & (kcal/mol) &  (kcal/mol) &  (kcal/mol)   & (kcal/mol)   & (\%) \\
@@
 \end{table*}
+
+The results concerning the solvation free energies of all solutes in the ionic liquid are presented in Table~\ref{table:gamma}, as well as the computed infinite-dilution activity coefficients.
+For benzene and water, the predictions are very accurate, but this is certainly due to fortuitous error compensations, given the discrepancies observed in Table~\ref{table:mu_solutes}.
+In the case of hexane, one can see in Table \ref{table:gamma} that the available experimental values of $\gamma^\infty$ in \ce{[emim][B(CN)_4]} at very close temperatures ($298.15~\text{K}$ and $303~\text{K}$) differ considerably.
+It is, therefore, difficult to assess the reliability of our results in this case.
 

### 2018-09-16 ionic_liquids.tex
Review of the conclusions and supplemental material

@@
 \title{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
-%\title{A molecular dynamics study of the solvation of \ce{CO_2}, \ce{H_2O}, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 
@@
 \includegraphics[width=\linewidth]{Ludwig_anion}
-\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[NTf_2]^-}, obtained from NPT-MD simulations of 250 ion pairs of \ce{[emim][NTf_2]} using the model of K\"{o}ddermann \textit{et al}.
+\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[NTf_2]^-}, obtained from NPT-MD simulations of 250 ion pairs of \ce{[emim][NTf_2]} at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using the model of K\"{o}ddermann \textit{et al}.
 \cite{Koddermann_2007}.}
@@
 
-One of the goals of this paper was to compare various available models of \ce{[emim][B(CN)_4]} in terms of their capability to reproduce the experimental Henry constant of \ce{CO_2}.
-We have found that only the force field developed by Koller \textit{et al}. \cite{Koller_2012} is able to perform such task, with a small relative error of 2.8 \%.
-A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in that work, which also allows to accurately reproduce the experimental density of the pure substance.
+One of the goals of this paper was to compare various available molecular models of \ce{[emim][B(CN)_4]} in terms of their capabilities to reproduce the experimental Henry's law constant of \ce{CO_2}.
+We have found that only the force field developed by Koller \textit{et al}. \cite{Koller_2012} is able to perform such task, with a small relative error of 2.8\%.
+A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in the original work, which also allows one to accurately reproduce the experimental density of the pure substance.
 
 We focused also on exploring alternative simulation strategies with the goal of gaining computational efficiency.
-Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, we concluded that the DSF method with $\alpha$ = 0.2 {\AA}$^{-1}$ is a suitable strategy.
+Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, we concluded that the Damped-Shifted-Force method for electrostatic interactions, with a damping factor $\alpha = 0.2 ~\text{\AA}^{-1}$, is a suitable strategy.
 Other improvement was the use of rigid bodies to simulate \ce{[emim][B(CN)_4]}.
 This required preliminary simulations in order to examine the flexibility of the ethyl chain in \ce{[emim]^+} and the analysis was greatly facilitated by employing useful visualization tools.
-Besides the properties already mentioned, the different models showed quite different behaviors, as well.
-This lack of consistency is one of the reasons why in industry molecular simulation has not become a routinely tool yet.
+Besides the properties already mentioned, the different models showed quite distinct behaviors, as well, in terms of conformational statistics.
+%This lack of consistency is one of the reasons why in industry molecular simulation has not become a routinely tool yet.
 
-The solvation free energy results at infinite-dilution condition suggest a slightly more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in  \ce{[emim][NTf_2]}.
-However, this picture changes at high concentrations: the simulations correctly predicted a considerable lower pressure to dissolve a certain mass of \ce{CO_2} in \ce{[emim][B(CN)_4]}.
+The solvation free energy results at infinite-dilution condition suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}, despite the similarity in the Henry's law constants observed in both cases.
+This picture is further confirmed at high \ce{CO_2} concentrations, in which the simulations correctly predicted that a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}, as compared to \ce{[emim][NTf_2]} in an equal-mass basis.
 
-Finally, we employed the model of Koller \textit{et al}. \cite{Koller_2012} to predict infinite-dilution activity coefficients of various solutes.
-In this case, the results were not satisfactory given the large errors in the free energy calculations of the pure solutes, making necessary a revision of their force fields in a future work.
+Finally, we employed the model of Koller \textit{et al}. \cite{Koller_2012} in an attempt to predict infinite-dilution activity coefficients of various solutes in \ce{[emim][B(CN)_4]}.
+In this case, the results were not satisfactory, given the large errors in the free energy calculations of the pure solutes, making necessary a future revision of the employed force fields.
 
 \section*{Acknowledgments}
+
 The authors acknowledge the financial support provided by Petrobras (project code CENPES 16113).

### 2018-09-16 supp_material.tex
Elimination of some packages for faster compilation
Table Formatting
Review of the conclusions and supplemental material

@@
 \usepackage[version=4]{mhchem}
-\usepackage{graphicx,bm}
-\journal{Journal of \LaTeX\ Templates}
+\usepackage{graphicx}
+\journal{Fluid Phase Equilibria}
 
@@
 
-\title{Supporting material for ``A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}''}
+\title{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 
 %% Group authors per affiliation:
-\author[rvt]{A.J.~Silveira}
-\author[rvt]{S.~Pereda}
-\author[focal,els]{F.W.~Tavares}
-\author[focal]{C.R.A.~Abreu\corref{cor1}}
+\author[plapiqui]{A.J.~Silveira\corref{curradd}}
+\author[plapiqui]{S.~Pereda}
+\author[eq-ufrj,coppe-ufrj]{F.W.~Tavares}
+\author[eq-ufrj]{C.R.A.~Abreu\corref{cor1}}
 \ead{abreu@eq.ufrj.br}
 
-\address[rvt]{Planta Piloto de Ingenier\'ia Qu\'imica, PLAPIQUI, Universidad Nacional del Sur,Camino La Carrindanga Km 7-CC: 717, Bah\'ia Blanca, Argentina}
-\address[focal]{Chemical Engineering Department, Escola de Qu\'imica, Universidade Federal do Rio de Janeiro,Rio de Janeiro, RJ 21941-909, Brazil}
-\address[els]{COPPE, Universidade Federal do Rio de Janeiro, Rio de Janeiro, RJ 21941-909, Brazil}
+\address[plapiqui]{Planta Piloto de Ingenier\'ia Qu\'imica (PLAPIQUI), Universidad Nacional del Sur, Bah\'ia Blanca, Argentina}
+\address[eq-ufrj]{Chemical Engineering Department, Escola de Qu\'imica, Universidade Federal do Rio de Janeiro, Rio de Janeiro, Brazil}
+\address[coppe-ufrj]{Chemical Engineering Program, Alberto Luiz Coimbra Institute for Graduate Studies and Research in Engineering (COPPE), Universidade Federal do Rio de Janeiro, Rio de Janeiro, Brazil}
 
+\cortext[curradd]{Current address: Computational \& Systems Biology Program, Memorial Sloan Kettering Cancer Center, New York, NY, USA}
 \cortext[cor1]{Corresponding author}
+
 \end{frontmatter}
@@
 \includegraphics[]{rdf-koller}
-\caption{\ce{[emim][B(CN)_4]}}
-\label{fig:pressure}
+\caption{Radial distribution functions $g(r)$ obtained in NPT-MD simulations of 250 ion pairs of \ce{[emim][B(CN)4]} at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using the model of Koller \textit{et al}.
+\cite{Koller_2012}.}
+\label{fig:rdf-koller}
 \end{figure}
@@
 \begin{figure}[ht]
-\includegraphics[]{rdf-Batista.pdf}
-\caption{\ce{[emim][B(CN)_4]}}
-\label{fig:pressure}
+\includegraphics[]{rdf-Batista}
+\caption{Radial distribution functions $g(r)$ obtained in NPT-MD simulations of 250 ion pairs of \ce{[emim][B(CN)4]} at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using the model of Batista \textit{et al}.
+\cite{Batista_2015}.}
+\label{fig:rdf-Batista}
 \end{figure}
@@
 \begin{figure}[ht]
-\includegraphics[]{rdf-Liu.pdf}
-\caption{\ce{[emim][B(CN)_4]}}
-\label{fig:pressure}
+\includegraphics[]{rdf-Liu}
+\caption{Radial distribution functions $g(r)$ obtained in NPT-MD simulations of 250 ion pairs of \ce{[emim][B(CN)4]} at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using the model of Liu \textit{et al}.
+\cite{Liu_2014}.}
+\label{fig:rdf-Liu}
 \end{figure}
@@
 \begin{figure}[ht]
-\includegraphics[]{rdf-Weber.pdf}
-\caption{\ce{[emim][B(CN)_4]}}
-\label{fig:pressure}
+\includegraphics[]{rdf-Weber}
+\caption{Radial distribution functions $g(r)$ obtained in NPT-MD simulations of 250 ion pairs of \ce{[emim][B(CN)4]} at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using the model of Weber and Kirchner \cite{Weber_2016}.}
+\label{fig:rdf-Weber}
 \end{figure}
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{Ludwig}%
+
+	%\includegraphics[width=\linewidth]{Ludwig_anion}%
+	\caption{Combined distribution function of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6 obtained from NPT-MD simulations of 250 ion pairs of \ce{[emim][NTf_2]} at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using the model of K\"{o}ddermann \textit{et al}.
+\cite{Koddermann_2007}.}
+	\label{fig:die_ntf2}
+\end{figure}
+
+\bibliography{ionic_liquids}
+
 \end{document}

### 2019-02-12 ionic_liquids.tex
Submitted version
revision I

@@
 \usepackage[colorlinks,citecolor=blue]{hyperref}
-%\usepackage{lineno}
-%\modulolinenumbers[5]
+\usepackage{lineno}
+\modulolinenumbers[5]
 \usepackage{amsmath}
@@
 \usepackage{xcolor}
+
 \usepackage{pdfcomment}
@@
 
-\title{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
+\title{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}
 
@@
 It is known, for instance, that carbon dioxide from combustion is one of the main sources of anthropogenic greenhouse gases.
-Recently, the propensity of the ionic liquid \ce{[emim][B(CN)_4]} for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
-In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} are carried out both at infinite dilution and at high concentrations.
-A systematic study is performed by comparing several force fields and assessing the efficacy of simplification measures such as rigid-body dynamics and pairwise electrostatics.
+Recently, the propensity of the ionic liquid 1-ethyl-3-methylimidazolium tetracyanoborate (\ce{[emim][B(CN)_4]}) for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
+In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and 1-ethyl-3-methylimidazolium bis (trifluoromethylsulfonyl) imide (\ce{[emim][Tf_2N]}) are carried out both at infinite dilution and at high concentrations.
+A systematic study is performed by comparing several force fields and assessing the efficacy of simplifications in the simulations by using rigid-body dynamics and pairwise electrostatics.
 Our results confirm recent experimental observations that, for a given volume of solvent, lower pressure is required to absorb a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in other ionic liquids.
@@
 The conventional process for \ce{CO_2} removal comprises a chemical absorption followed by stripping at high temperatures.
-The most commonly used solvents are volatile organic compounds, specially aqueous solutions of monoethanolamine (MEA).
+The most commonly used solvents are aqueous solutions of primary and secondary alkanolamines, such as monoethanolamine (MEA).
 Despite its high absorption capability, the use of MEA has a serious drawback, which is the high cost of solvent recovery \cite{Merkel_2010}.
@@
 \cite{Carvalho_2016} show that most systems which promote physical absorption of \ce{CO_2} exhibit solubilities which are similar, or even lower, than that observed for heavy alkanes such as eicosane.
-This is true for the popular ILs \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}.
+This is true for the popular ILs \ce{[bmim][Tf_2N]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][Tf_2N]} and \ce{[hmim][pFAP]}.
 The only exception they found was the family of ILs containing the anion \ce{[B(CN)_4]^-} (tetracyanoborate).
@@
 As we show here, it was possible to find a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2} in this IL.
-For comparison, we analyzed the solvation of \ce{CO_2} not only in \ce{[emim][B(CN)_4]}, but also in \ce{[emim][NTf_2]}, both at infinite dilution and at high concentrations.
+For comparison, we analyzed the solvation of \ce{CO_2} not only in \ce{[emim][B(CN)_4]}, but also in \ce{[emim][Tf_2N]}, both at infinite dilution and at high concentrations.
 The simulations confirmed what is observed in experiments.
@@
 In what follows, the subscripts ``s'' and ``IL'' refer to the solute and the solvent (ionic liquid), respectively.
-For a liquid phase containing $N_\text{IL}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (P) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
+For a liquid phase containing $N_\text{IL}$ solvent molecules and $N_{\text{s}}$ solute molecules at fixed pressure (p) and temperature (T), the difference in free energy between the states associated to $\lambda$ = 1 and $\lambda$ = 0 is formally defined as
 \begin{equation}
-\Delta G_\text{sim} \equiv R T \ln \frac{\Xi (N_s,N_\text{IL},P,T,\lambda = 1)}{\Xi (N_s,N_\text{IL},P,T,\lambda = 0)}, 
+\Delta G_\text{sim} \equiv R T \ln \frac{\Xi (N_s,N_\text{IL},p,T,\lambda = 1)}{\Xi (N_s,N_\text{IL},p,T,\lambda = 0)}, 
 \end{equation}
@@
 \label{eq:solvation free energy definition}
-\Delta G_{\text{solv}} \equiv R T \ln \left( \frac{P_s}{c_s R T} \right),
+\Delta G_{\text{solv}} \equiv R T \ln \left( \frac{p_s}{c_s R T} \right),
 \end{equation}
-where $P_s$ is the partial pressure of the solute in the gas phase and
+where $p_s$ is the partial pressure of the solute in the gas phase and
 $c_s$ is the molar concentration of the solute in the liquid phase.
@@
 \label{eq:solute chemical potential}
-\mu^l_s = \mu^{ig}_s + \Delta G_\text{sim} - RT \ln \left( \frac{V^{\ast}}{V_1}\right) - RT \ln \left( \frac{P_s}{c_s R T} \right),
+\mu^l_s = \mu^{ig}_s + \Delta G_\text{sim} - RT \ln \left( \frac{V^{\ast}}{V_1}\right) - RT \ln \left( \frac{p_s}{c_s R T} \right),
 \end{equation}
-where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and solute partial pressure $P_s$, while $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{IL}$,P,T) and ($N_s$,$N_\text{IL}$,P,T), respectively.
+where $\mu^{ig}_s$ is the chemical potential of the solute in an ideal gas at temperature $T$ and solute partial pressure $p_s$, while $V^{\ast}$ and $V_1$ are the mean volumes of liquid solutions specified by ($N_s-1$,$N_\text{IL}$,p,T) and ($N_s$,$N_\text{IL}$,p,T), respectively.
 Note that $c_s = \frac{N_s}{N_A V_1}$, where $N_A$ is the Avogadro number.
@@
 
-If both $P_s$ and $c_s$ are small, we can resort to Eqs.~\eqref{eq:solvation free energy definition} and \eqref{eq:free_solv} to predict Henry's law constant, which is defined as $\text{K}_s =\frac{P_s}{x_s}$ \cite{Prausnitz}.
+If both $p_s$ and $c_s$ are small, we can resort to Eqs.~\eqref{eq:solvation free energy definition} and \eqref{eq:free_solv} to predict Henry's law constant, which is defined as $\text{K}_s =\frac{p_s}{x_s}$ \cite{Prausnitz}.
 %\begin{equation}
-%\text{K}_s =\frac{P_s}{x_s}.
+%\text{K}_s =\frac{p_s}{x_s}.
 %\end{equation}
@@
 \label{eq:mu_gas_real}
-\mu^{g}_s = \mu^{ig}_s + R T \ln \left(\frac{f^{g}_s}{P_s}\right),
+\mu^{g}_s = \mu^{ig}_s + R T \ln \left(\frac{f^{g}_s}{p_s}\right),
 \end{equation}
@@
 
-Three additional assumptions are made here.
-First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems with which we compare our simulations) or can be approximated by an ideal solution.
+Two additional assumptions are made here.
+First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems investigated) or can be approximated by an ideal solution.
 Second, we assume that the system pressure is moderate, so that a truncated virial equation is enough to represent the gas phase.
@@
 \label{eq:equilibrium pressure}
-y_s \exp\left( \frac{B_s P}{R T} \right) P = c_s R T \exp \left( \frac{\Delta G_\text{sim}}{R T} \right),
+y_s \exp\left( \frac{B_s p}{R T} \right) p = c_s(p) R T \exp \left( \frac{\Delta G_\text{sim}}{R T} \right),
 \end{equation}
@@
 
-Our third assumption, supported by preliminary simulations, is that $\Delta G_\text{sim}$ does not vary appreciably with pressure, at least over the range of experimental data considered here.
-In this way, no iterative simulations are required to compute the equilibrium pressure when solving Eq.~\eqref{eq:equilibrium pressure} for $P$.
+The equilibrium pressure will be given by the value for which the function $\Delta G_{\text{sim}}(p) $, defined by Eq.~\eqref{eq:equilibrium pressure}, intersects $\Delta G_{\text{sim}} (p)$, as obtained in simulations.
+Note that besides  $\Delta G_{\text{sim}}$, we are also considering  variations of $c_s$ with pressure.
+These computations are greatly facilitated by the technique of reweighting \cite{McDonald1967,McDonald1969}, which uses simulation results from different states to improve the statistics and, particularly important to our case, allows to interpolate expectation values of thermodynamic observables along unsampled states.
+This implies a significant reduction in computational cost.
+In particular, we use the Multistate Bennett Acceptance Ratio (MBAR) estimator \cite{Shirts_2008}, which has been successfully used for the purpose of reweighing ~\cite{Aimoli2014, Nichele2018, Schieber2018}.
 
@@
 
-As will be shown below, the prediction of activity coefficients requires additional simulations of the solute as a pure liquid phase, whose properties we denote here by a superscript ``$0$''.
+The prediction of activity coefficients requires additional simulations of the solute as a pure liquid phase, whose properties we denote here by a superscript ``$0$''.
 We start by using a standard thermodynamic relation \cite{Tester} to write the solute activity coefficient $\gamma_s$ in terms of chemical potentials as
@@
 
-In the special case of a solute at infinite dilution in an ionic liquid solvent, its activity coefficient $\gamma^\infty_s$ can be computed by replacing $\tilde{\rho}$ in the equation above by the molar density of the pure solvent, $\tilde{\rho}_\textit{IL}$.
+In the special case of a solute at infinite dilution in an ionic liquid solvent, its activity coefficient ($\gamma^\infty_s$) can be computed by replacing $\tilde{\rho}$ in the equation above by the molar density of the pure solvent, $\tilde{\rho}_\textit{IL}$.
 
@@
 
-Finally, we also consider the parameterization which Weber and Kirchner \cite{Weber_2016} carried out for \ce{[emim][B(CN)_4]} based on the force field developed by P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
+Finally, we also consider the parameterization Weber and Kirchner \cite{Weber_2016} carried out for \ce{[emim][B(CN)_4]} based on the force field developed by P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
 As the potential parameters for the anion were specified neither in Ref.~\citenum{Weber_2016} nor in Ref.~\citenum{Canongia_Lopes_2006}, we obtained them by direct communication with the authors of Ref.~\citenum{Weber_2016}.
@@
 
-In the case of ionic liquid \ce{[emim][NTf_2]}, we use the model of K\"{o}ddermann \textit{et al}.
+In the case of ionic liquid \ce{[emim][Tf_2N]}, we use the model of K\"{o}ddermann \textit{et al}.
 \cite{Koddermann_2007}, which was also derived by refining parameters of the force field by P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
 The authors characterized this refinement as unusual, given that they modified the LJ parameters while keeping the partial charges unchanged.
-Kerl \textit{et al}. \cite{Kerl__2017} recently employed this model to accurately predict Henry constants of \ce{CO_2} in \ce{[emim][NTf_2]} at several temperatures.
+Kerl \textit{et al}. \cite{Kerl__2017} recently employed this model to accurately predict Henry constants of \ce{CO_2} in \ce{[emim][Tf_2N]} at several temperatures.
 
@@
 These values were employed here for the ILs as well as for solutes containing partially charged atoms.
-The only exception was hexane, for which the use of undamped Coulombic interactions (i.e. $\alpha = 0$) resulted in improved chemical potential predictions.
+The only exception was hexane, for which the use of undamped Coulombic interactions (i.e.
+$\alpha = 0$) resulted in improved chemical potential predictions.
+That cutoff distance was also used for truncating the LJ interactions, for which we applied analytical tail corrections \cite{allen}.
+In addition, we used the Lorentz-Berthelot mixing rules to calculate the cross LJ interactions, except for the solutes modeled with the OPLS-AA force fields, which employs geometric combining rules.
 
-The NPT algorithm of Kamberaj \textit{et al}. \cite{Kamberaj_2005} was used to integrate the equations of motion for rigid bodies.
+The NpT algorithm of Kamberaj \textit{et al}. \cite{Kamberaj_2005} was used to integrate the equations of motion for rigid bodies.
 For flexible molecules, we applied the integration scheme of Shinoda \textit{et al}. \cite{Shinoda2004}, with the lengths of all C-H bonds constrained by the SHAKE method \cite{Ryckaert1977}.
@@
 In this work, we compute $\Delta G_\text{Coul}$ by carrying out an independent simulation of 10 ns at each state of $\lambda_{\text{Coul}}$.
-In the end, we apply the Multistate Bennett Acceptance Ratio (MBAR) method \cite{Shirts_2008} by using the \textit{Alchemical Analysis} package \cite{Klimovich_2015}.
+In the end, we apply the MBAR method \cite{Shirts_2008} by using the \textit{Alchemical Analysis} package \cite{Klimovich_2015}.
 
@@
 An expanded ensemble is constructed as a weighted sum of subensembles, each one assuming a different value of the parameter selected for exploring the free energy landscape, which in our case is $\lambda_\text{vdW}$.
-In the method adopted here \cite{Chodera_2011_2}, simulating an expanded ensemble comprises doing molecular dynamics (MD) at fixed N, P, T, and $\lambda_\text{vdW}$ amid Monte Carlo (MC) transitions in the value of $\lambda_\text{vdW}$.
+In the method adopted here \cite{Chodera_2011_2}, simulating an expanded ensemble comprises doing molecular dynamics (MD) at fixed N, p, T, and $\lambda_\text{vdW}$ amid Monte Carlo (MC) transitions in the value of $\lambda_\text{vdW}$.
 The number of MD steps between transitions is fixed and, at each transition, one of the $\lambda_\text{vdW}$ states is picked at random according to a corresponding set of probabilities \cite{Chodera_2011_2}.
@@
 In this way, 3 iterations were sufficient in all cases for attaining, in the final round, an acceptable uncertainty in $\Delta G_\text{sim}$ estimated via MBAR \cite{Shirts_2008, Klimovich_2015}.
+Considering also the MD runs at each $\lambda_{\text{Coul}}$, the simulation time was 110 ns for each system.
 
-We first carried out MD simulations of isolated ion pairs in order to obtain minimum-energy conformations.
+In order to obtain minimum-energy conformations, we first carried out MD simulations of isolated ion pairs.
 For this, we used a Nos\'{e}-Hoover chain thermostat \cite{Martyna1992} with set-point temperature gradually changing down to nearly $0~\text{K}$.
@@
 In the simplified setup, the ions are modeled as rigid bodies and the DSF method \cite{Fennell2006} with $r_c = 12 ~\text{\AA}$ and $\alpha = 0.2 ~\text{\AA}^{-1}$) is used as and alternative to the PPPM scheme.
-For building the rigid bodies, we carry out a frequency analysis of some key dihedrals present in ions \ce{[emim]^+} and \ce{[NTf_2]^-}, whose flexibility could lead to significant conformational changes.
+For building the rigid bodies, we carry out a frequency analysis of some key dihedrals present in ions \ce{[emim]^+} and \ce{[Tf_2N]^-}, whose flexibility could lead to significant conformational changes.
 On the other hand, small and highly symmetric anions such as \ce{PF_6} and \ce{BF_4} are already usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies the strategy in the case of \ce{[B(CN)_4]^-}.
 
-As a guide to the discussions in this section, in Fig~\ref{fig:atoms_id} we introduce a nomenclature for all atoms present in the ions \ce{[emim]^+}, \ce{[B(CN)_4]^-}, and \ce{[NTf_2]^-}.
+As a guide to the discussions in this section, in Fig~\ref{fig:atoms_id} we introduce a nomenclature for all atoms present in the ions \ce{[emim]^+}, \ce{[B(CN)_4]^-}, and \ce{[Tf_2N]^-}.
 Please note that, in the united-atom version of \ce{[emim]^+}, all hydrogen atoms ranging from H4 to H11 are incorporated to their corresponding carbon atoms.
@@
 \includegraphics[width=\linewidth]{atoms_id.pdf}
-\caption{Adopted nomenclature for individual atoms in the cation 1-ethyl-3-methylimidazolium (\ce{[emim]^+}) and anions tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
+\caption{Adopted nomenclature for individual atoms in the cation 1-ethyl-3-methylimidazolium (\ce{[emim]^+}) and anions tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[Tf_2N]^-}).}
 \label{fig:atoms_id}
@@
 In Fig.~\ref{fig:dihedrals_emim}, we show the CDFs obtained for all force fields employed here for \ce{[emim][B(CN)_4]}.
-All CDFs shown in this section were generated from NPT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using our standard setup (i.e.
+All CDFs shown in this section were generated from NpT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$ using our standard setup (i.e.
 flexible ions with PPPM Ewald electrostatics).
@@
   \includegraphics[width=.4\linewidth,trim={0 0 0 12pt},clip]{Weber}}%
-\caption{Combined distribution functions of the dihedral angles corresponding to atoms C1-N2-C5-C6 and C2-N2-C5-C6 in the cation \ce{[emim]^+} (see Fig.~\ref{fig:atoms_id}), as sampled in NPT-MD simulations of 250 ion pairs using each model for \ce{[emim][B(CN)_4]}.}
+\caption{Combined distribution functions of the dihedral angles corresponding to atoms C1-N2-C5-C6 and C2-N2-C5-C6 in the cation \ce{[emim]^+} (see Fig.~\ref{fig:atoms_id}), as sampled in NpT-MD simulations of 250 ion pairs using each model for \ce{[emim][B(CN)_4]}.}
 \label{fig:dihedrals_emim}
@@
 
-Once the rigid body structures have been determined, we carried out NPT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using the simplified setup (i.e.
+Once the rigid body structures have been determined, we carried out NpT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$ using the simplified setup (i.e.
 rigid ions with DSF electrostatics) and all force fields in question.
@@
 	\centering
-	\caption{Comparison of predicted and experimental densities for different models of \ce{[emim][B(CN)_4]} via NPT-MD simulations at $T = 298.0~\text{K}$ and $P = 1.0~\text{atm}$.
+	\caption{Comparison of predicted and experimental densities for different models of \ce{[emim][B(CN)_4]} via NpT-MD simulations at $T = 298.0~\text{K}$ and $p = 1.0~\text{atm}$.
 The experimental density is $1.036~\mathrm{g/cm^3}$ \cite{Doma_ska_2011}.}
@@
 
-A study of conformations was also carried out for \ce{[emim][NTf_2]} using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.
+A study of conformations was also carried out for \ce{[emim][Tf_2N]} using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.
 A CDF obtained for the dihedral angles of sequences C1-N2-C5-C6 and C2-N2-C5-C6 in \ce{[emim]^+}, which is made available in the Supplementary Material, resembles the one in Fig.~\ref{fig:dihedrals_emim}(d).
 The resemblance was expected because the intramolecular parameters employed for \ce{[emim]^+} are identical in these two cases, since the corresponding models are both based on the force field developed by Canongia-Lopes and P\'{a}dua \cite{Canongia_Lopes_2006}.
-However, the most likely value of $\psi_1$ is shifted to $0^{\circ}$ in the case of \ce{[emim][NTf_2]}.
+However, the most likely value of $\psi_1$ is shifted to $0^{\circ}$ in the case of \ce{[emim][Tf_2N]}.
 This highlights the fact that altering atomic charges can induce conformational changes and should, therefore, be accompanied by a revision of torsion parameters in some cases.
-With regard to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al}.
-\cite{Deetlefs_2006} experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly found in its \textit{trans} conformation.
-In Fig.~\ref{fig:die_ntf2}, we present the CDF obtained for the contiguous sequences C1-S1-N1-S2 and S1-N1-S2-C2 in \ce{[NTf_2]^-}, which qualitatively confirms the observation of Deetlefs \textit{et al}.
+With regard to the anion \ce{[Tf_2N]^-}, Deetlefs \textit{et al}.
+\cite{Deetlefs_2006} experimentally determined the conformer population of the liquid-phase and observed that \ce{[Tf_2N]^-} is mostly found in its \textit{trans} conformation.
+In Fig.~\ref{fig:die_ntf2}, we present the CDF obtained for the contiguous sequences C1-S1-N1-S2 and S1-N1-S2-C2 in \ce{[Tf_2N]^-}, which qualitatively confirms the observation of Deetlefs \textit{et al}.
 \cite{Deetlefs_2006}.
-This CDF also makes clear that \ce{[NTf_2]^-} exhibits a considerable degree of flexibility.
-Due to this observed behaviors of both ions, all simulations of \ce{[emim][NTf_2]} in the present work are performed considering flexible cations and anions, as well as DSF electrostatics.
-This approach results in a mean density of $1.495 \pm 0.009 ~\mathrm{g/cm^3}$ at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$.
+This CDF also makes clear that \ce{[Tf_2N]^-} exhibits a considerable degree of flexibility.
+Due to this observed behaviors of both ions, all simulations of \ce{[emim][Tf_2N]} in the present work are performed considering flexible cations and anions, as well as DSF electrostatics.
+This approach results in a mean density of $1.495 \pm 0.009 ~\mathrm{g/cm^3}$ at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$.
 The relative error of this result with respect to the experimental value obtained by Tokuda \textit{et al}. \cite{Tokuda_2005} is only 1.12\%.
@@
 \includegraphics[width=\linewidth]{Ludwig_anion}
-\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[NTf_2]^-}, obtained from NPT-MD simulations of 250 ion pairs of \ce{[emim][NTf_2]} at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$ using the model of K\"{o}ddermann \textit{et al}.
+\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[Tf_2N]^-}, obtained from NpT-MD simulations of 250 ion pairs of \ce{[emim][Tf_2N]} at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$ using the model of K\"{o}ddermann \textit{et al}.
 \cite{Koddermann_2007}.}
@@
 
-\subsection{Dilute Solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
+\subsection{Dilute Solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}
 \label{sec:henry_results}
 
-In Table \ref{table:henry}, we present results from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][NTf_2]} under periodic boundary conditions.
-The simulations were carried out at $T = 298.0~\mathrm{K}$ and $P = 1.0~\mathrm{bar}$.
+In Table \ref{table:henry}, we present results from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][Tf_2N]} under periodic boundary conditions.
+The simulations were carried out at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$.
 Table~\ref{table:henry} contains simulated molar densities, partial and total solvation free energies, as well as Henry's law constants ($K_s$) computed via Eq.~\eqref{eq:henry_eq}.
-The uncertainties in $K_s$ were calculated by using a standard error propagation formula.
 The computed values should be compared to the experimental data reported by Mahurin \textit{et al}.
 \cite{Mahurin_2010} ($K_s = 38.9 \pm 0.03 ~\mathrm{atm}$ for \ce{CO_2} in \ce{[emim][B(CN)_4]}) and by Finotello \textit{et al}.
-\cite{Finotello_2008} ($K_s = 39.0 \pm 0.1 ~\mathrm{atm}$ for \ce{CO_2} in \ce{[emim][NTf_2]}).
+\cite{Finotello_2008} ($K_s = 39.0 \pm 0.1 ~\mathrm{atm}$ for \ce{CO_2} in \ce{[emim][Tf_2N]}).
+The uncertainties in $K_s$ were calculated by using a standard error propagation formula
+
+\begin{equation}
+\delta K_s = \beta K_s \sqrt{\left[ \delta^2 (\Delta G_{\text{vdW}}) + \delta^2(\Delta G_{\text{Coul}}) \right]},
+\end{equation}
+which are a function of the uncertainties in free energy, which are calculate using MBAR \cite{Shirts_2008}.
 
@@
 	\centering
-	\caption{Results of solvation free energies and Henry's law constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} at $T = 298.15~\mathrm{K}$ and $P = 1~\mathrm{atm}$.
-The experimental Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and in \ce{[emim][NTf_2]} are, respectively, $38.9 \pm 0.03 ~\mathrm{atm}$ \cite{Mahurin_2010} and $39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008}.}
+	\caption{Results of solvation free energies and Henry's law constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]} at $T = 298.15~\mathrm{K}$ and $p = 1~\mathrm{atm}$.
+The experimental Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and in \ce{[emim][Tf_2N]} are, respectively, $38.9 \pm 0.03 ~\mathrm{atm}$ \cite{Mahurin_2010} and $39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008}.}
 	\begin{adjustbox}{max width=\textwidth}
@@
 			\hline
-%			\multicolumn{7}{c}{\ce{[emim][NTf_2]}: $K_{s}^{\text{exp}} = 39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008} }\\
-			\multicolumn{7}{c}{\ce{[emim][NTf_2]}} \\
+%			\multicolumn{7}{c}{\ce{[emim][Tf_2N]}: $K_{s}^{\text{exp}} = 39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008} }\\
+			\multicolumn{7}{c}{\ce{[emim][Tf_2N]}} \\
 			K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007} & $3.8205$ & $0.389 \pm 0.005$ & $-0.901 \pm 0.006$ & $-0.512 \pm 0.008$ & $39.4 \pm 0.5$  & $0.97$  \\
@@
 \cite{Liu_2014} is statistically identical to a value reported by the same authors in Ref.~\citenum{Liu_2014_1}, where they applied the Bennett Acceptance Ratio (BAR) method \cite{Bennett_1976} to independent samples obtained with different values of $\lambda_\text{vdW}$ and $\lambda_\text{Coul}$.
-Moreover, the $\Delta G_\text{sim}$ value we computed for \ce{[emim][NTf_2]} is very close to the one obtained by Kerl \textit{et al}.
+Moreover, the $\Delta G_\text{sim}$ value we computed for \ce{[emim][Tf_2N]} is very close to the one obtained by Kerl \textit{et al}.
 \cite{Kerl__2017} ($-0.534 ~\mathrm{kcal/mol}$, with no reported uncertainty) using the Free-Energy Perturbation (FEP) method \cite{Zwanzig_1954}.
@@
 \cite{Koller_2012} does in the case of \ce{[emim][B(CN)_4]}, the one of K\"{o}ddermann \textit{et al}.
-\cite{Koddermann_2007} accurately predicts the Henry's law constant of \ce{CO_2} in \ce{[emim][NTf_2]}.
-A comparison between the values of $\Delta G_\text{sim}$ obtained from these models, shown in Table \ref{table:henry}, suggests that the solvation of \ce{CO_2} takes place more favorably in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}.
+\cite{Koddermann_2007} accurately predicts the Henry's law constant of \ce{CO_2} in \ce{[emim][Tf_2N]}.
+A comparison between the values of $\Delta G_\text{sim}$ obtained from these models, shown in Table \ref{table:henry}, suggests that the solvation of \ce{CO_2} takes place more favorably in \ce{[emim][B(CN)_4]} than in \ce{[emim][Tf_2N]}.
 The fact that $K_s$ has almost the same value in both cases is due to a compensation promoted by the distinct molar densities of these ionic liquids.
 Spatial distribution functions (SDFs) \cite{Svishchev_1993} can help us visualizing how differently the solvent ions interact with the solute molecule.
-By using TRAVIS \cite{Brehm_2011}, we have obtained SDFs of both cation and anion around a \ce{CO_2} molecule, sampled from MD trajectories of either \ce{CO_2}+\ce{[emim][B(CN)_4]} or \ce{CO_2}+\ce{[emim][NTf_2]} systems simulated at $T = 298.0~\text{K}$, $P = 1.0~\mathrm{bar}$, and $x_\mathrm{CO_2} = 0.1$.
+By using TRAVIS \cite{Brehm_2011}, we have obtained SDFs of both cation and anion around a \ce{CO_2} molecule, sampled from MD trajectories of either \ce{CO_2}+\ce{[emim][B(CN)_4]} or \ce{CO_2}+\ce{[emim][Tf_2N]} systems simulated at $T = 298.0~\text{K}$, $p = 1.0~\mathrm{bar}$, and $x_\mathrm{CO_2} = 0.1$.
 The slightly larger \ce{CO_2} concentration considered here is meant to improve statistics.
@@
 By comparing Figs.~\ref{fig:sdf_ions}(a) and \ref{fig:sdf_ions}(b), we note that the gap between the regions occupied by the anion and the cation is smaller in the case of \ce{[emim][B(CN)_4]}.
-In addition, the first solvation shell corresponding to \ce{[B(CN)_4]^-} occurs at a slightly shorter distance than that corresponding to \ce{[NTf_2]^-}, as one can clearly see by a direct comparison done in Fig.~\ref{fig:sdf_ions}(c).
+In addition, the first solvation shell corresponding to \ce{[B(CN)_4]^-} occurs at a slightly shorter distance than that corresponding to \ce{[Tf_2N]^-}, as one can clearly see by a direct comparison done in Fig.~\ref{fig:sdf_ions}(c).
 This is in part due to the difference in size of these two anions.
 The result is a higher density of negative charges around the carbon atom of \ce{CO_2}, whose point-charge is positive as a consequence of the oxygen's high electronegativity.
-This seems to induce a greater stability of \ce{CO_2} when solvated in \ce{[emim][B(CN)_4]}, rather than in \ce{[emim][NTf_2]}, possibly resulting in enhanced solubility.
+This seems to induce a greater stability of \ce{CO_2} when solvated in \ce{[emim][B(CN)_4]}, rather than in \ce{[emim][Tf_2N]}, possibly resulting in enhanced solubility.
 However, the mentioned similarity in the Henry's law constants could cause such enhancement to go unnoticed.
@@
 }
-\caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[NTf_2]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
+\caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[Tf_2N]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
 Fig. (c) corresponds to the SDFs of the anions plotted together.}
@@
 
-\subsection{Concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
+\subsection{Concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}
 \label{sec:results_conc}
@@
 We have selected these specific conditions because of the proximity observed in the molality of \ce{CO_2} ($m_s$).
-It is worth noting that the marked difference in the molar fractions of \ce{CO_2} in Table~\ref{table:solv} does not imply that \ce{[emim][NTf_2]} is a better solvent than \ce{[emim][B(CN)_4]}, thus exemplifying the observation made by Carvalho \textit{et al}.
+It is worth noting that the marked difference in the molar fractions of \ce{CO_2} in Table~\ref{table:solv} does not imply that \ce{[emim][Tf_2N]} is a better solvent than \ce{[emim][B(CN)_4]}, thus exemplifying the observation made by Carvalho \textit{et al}.
 \cite{Carvalho_2016} and discussed here in Sec.~\ref{sec:intro}.
@@
 	\centering
-	\caption{Thermodynamic conditions, based on the experimental observations of Refs.~\citenum{Makino_2014} and \citenum{Schilderman_2007}, employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, as well as the results obtained via expanded ensemble simulations.}
+	\caption{Thermodynamic conditions, based on the experimental observations of Refs.~\citenum{Makino_2014} and \citenum{Schilderman_2007}, employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}, as well as the results obtained via expanded ensemble simulations.}
 	\begin{tabular}{ccc}
 		\hline\hline
-		IL & \ce{[emim][B(CN)_4]}  & \ce{[emim][NTf_2]} \\
+		IL & \ce{[emim][B(CN)_4]}  & \ce{[emim][Tf_2N]} \\
 		\hline
@@
 		$T$  & $313.15~\mathrm{K}$ & $312.13~\mathrm{K}$ \\
-		$P$  & $21~\mathrm{atm}$ & $37~\mathrm{atm}$ \\
+		$p$  & $21~\mathrm{atm}$ & $37~\mathrm{atm}$ \\
 		$x_s$ & $0.352$ & $0.479$ \\
@@
 		$\Delta G_\text{sim}$ & $-0.755~\mathrm{kcal/mol}$ & $-0.542~\mathrm{kcal/mol}$ \\
-		$P$ & $18.3~\mathrm{atm}$ & $38.4~\mathrm{atm}$ \\
+		$f_g$ & $16.9~\mathrm{atm}$ & $32.6~\mathrm{atm}$ \\
+		$p$ & $18.3~\mathrm{atm}$ & $38.4~\mathrm{atm}$ \\
 		\hline\hline
@@
 
-We carried out expanded ensemble simulations of liquid solutions at the conditions of Table~\ref{table:solv}.
-The model of Koller \textit{et al}. \cite{Koller_2012} was the one employed for simulating \ce{[emim][B(CN)_4]}.
-The computed solvation free energies for the systems \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]} were $-0.755 \pm 0.009 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005~\mathrm{kcal/mol}$, respectively.
-In Fig.~\ref{fig:pressure}, we present our predictions of the equilibrium pressure ($P$) obtained by solving Eq.~\eqref{eq:equilibrium pressure}, as well as the corresponding gas-phase fugacities of \ce{CO_2} ($f_s^g$) computed by Eq.~\eqref{eq:fgas_d}.
-The dotted lines correspond to the experimental values (i.e. those used to simulate the liquid solutions).
-First, the results make clear that assuming ideal gas ($P = f_s^g$) would have been an oversimplification, specially in the case of \ce{[emim][NTf_2]}.
-Second, and most importantly, the computed pressures did not depart considerably from the specified values, meaning that our results sustain the experimental observations.
-Therefore, as the pressure required to reach the same equilibrium molal concentration of \ce{CO_2} in the liquid phase is smaller for \ce{[emim][B(CN)_4]} than for \ce{[emim][NTf_2]}, our results confirm that the former is a better solvent than the latter.
+We first carried out simulations of liquid solutions at the conditions of Table~\ref{table:solv}.
+The model of Koller \textit{et al}.
+\cite{Koller_2012} was the one employed for simulating \ce{[emim][B(CN)_4]}.
+The computed solvation free energies for the systems \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][Tf_2N]} were $-0.755 \pm 0.009 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005~\mathrm{kcal/mol}$, respectively.
+Using these values as inputs in Eq.~\eqref{eq:equilibrium pressure}, we obtained equilibrium pressures of p = 18.3 atm and 38.4 atm, as reported in Table~\ref{table:solv}.
+In this table, we also show the the corresponding gas-phase fugacities of \ce{CO_2} ($f_s^g$) computed by Eq.~\eqref{eq:fgas_d}.
+The results make clear that assuming ideal gas ($p = f_s^g$) would have been an oversimplification, specially in the case of \ce{[emim][Tf_2N]}.
+
+In order to obtain $\Delta G_\text{sim} (p)$ and $c_s(p)$, we carried out extra simulations at pressure values  of p = (17, 18) atm  for \ce{CO_2}+\ce{[emim][B(CN)_4]} and at p = (40, 44) atm for \ce{CO_2}+\ce{[emim][Tf_2N]}.
+In this case, we considered a wider range of pressure, given the departure from ideal gas behavior mentioned above.
+As described in Sec.~\ref{sec:partial_pressure}, $\Delta G_\text{sim}$ and $c_s$ were interpolated to intermediate pressures by reweighting.
+In Fig.~\ref{fig:pressure}, we show for both systems the simulated results of $\Delta G_\text{sim}$, together with the curve of $\Delta G_\text{sim}$ defined by Eq.~\eqref{eq:equilibrium pressure}.
+As expected, $\Delta G_\text{sim}$ does not vary appreciably with pressure, at least over the range of experimental data considered here.
+This results in small corrections to the equilibrium pressures of Table~\ref{table:solv}: the points of intersection are p = 17.8 atm and p = 40.5 atm, for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][Tf_2N]}, respectively.
+These values did not depart considerably from the specified values, meaning that our results sustain the experimental observations.
+Therefore, as the pressure required to reach the same equilibrium molal concentration of \ce{CO_2} in the liquid phase is smaller for \ce{[emim][B(CN)_4]} than for \ce{[emim][Tf_2N]}, our results confirm that the former is a better solvent than the latter.
 This confirmation was possible by simulating a purely physical absorption, without considering any quantum effect.
@@
 \begin{figure}
-\includegraphics[width=\linewidth]{pressure_est.pdf}
-\caption{Prediction of the gas-phase fugacity and partial pressure of \ce{CO_2} for the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}.}
+	\centering
+	\subfloat[][Koller~\textit{et al}.~\cite{Koller_2012}]{
+		\includegraphics[width=\linewidth]{pressure_koller.pdf}}
+
+	\subfloat[Batista~\textit{et al}.~\cite{Batista_2015}]{  
+		\includegraphics[width=\linewidth]{pressure_ludwig.pdf}}
 	\label{fig:pressure}
@@
 Due to the availability of experimental data \cite{Yan_2010, Doma_ska_2011}, the solutes chosen for this study are benzene, hexane, cyclohexane, ethanol, and water.
+Uncertainties in activity coefficients were calculated using error propagation formula, as done for $K_s$.
 
@@
 For benzene and water, the predictions are very accurate, but this is certainly due to fortuitous error compensations, given the discrepancies observed in Table~\ref{table:mu_solutes}.
-In the case of hexane, one can see in Table \ref{table:gamma} that the available experimental values of $\gamma^\infty$ in \ce{[emim][B(CN)_4]} at very close temperatures ($298.15~\text{K}$ and $303~\text{K}$) differ considerably.
+
+In Fig.~\ref{fig:deltag_solutes}, we show the simulated solvation free energies versus the experimental results.
+These were obtained by using $\Delta G^{0}_\text{exp}$ of Table~\ref{table:mu_solutes} and $\gamma^\infty$  from Ref.
+\cite{Doma_ska_2011} as inputs in Eq.~\eqref{eq:gamma}.
+Cyclohexane was not considered, given that $\Delta G^{0}_\text{exp}$ is not available.
+For benzene, ethanol and water the results from simulations are consistent with the negative experimental values.
+However, for hexane the simulations predict a favorable solvation, in clear contradiction with the experimental data.
+From the individual contributions of $\Delta G_\text{vdW}$ and $\Delta G_\text{Coul}$, we can conclude that the vdW contribution is largely underestimated.
+This makes sense since one would expect a less favorable insertion for a longer chain molecule in comparison, for instance, to benzene which has a comparable
+$\Delta G_\text{vdW}$.
+Also, in the case of hexane, one can see in Table \ref{table:gamma} that the available experimental values of $\gamma^\infty$ in \ce{[emim][B(CN)_4]} at very close temperatures ($298.15~\text{K}$ and $303~\text{K}$) differ considerably.
 It is, therefore, difficult to assess the reliability of our results in this case.
@@
 
+%\begin{figure}
+%	\includegraphics[width=\linewidth]{free_energy_solutes}
+%	\caption{Profile of $\Delta G_\text{vdW}$ corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, modeled according to the force fields of Koller \textit{et al}.
+\cite{Koller_2012} ($\bullet$), Batista \textit{et al}.
+\cite{Batista_2015} ($\blacksquare$), Liu \textit{et al}.
+\cite{Liu_2014} ($\times$), and Weber and Kirchner \cite{Weber_2016} ($\blacktriangle$).}
+%	\label{fig:deltag}
+%\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{delta_g_sim_exp}
+	\caption{Profile of $\Delta G_\text{vdW}$ corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, modeled according to the.}
+	\label{fig:deltag_solutes}
+\end{figure}
+
 \section{Concluding remarks}
@@
 We focused also on exploring alternative simulation strategies with the goal of gaining computational efficiency.
-Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, we concluded that the Damped-Shifted-Force method for electrostatic interactions, with a damping factor $\alpha = 0.2 ~\text{\AA}^{-1}$, is a suitable strategy.
+Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}, we concluded that the Damped-Shifted-Force method for electrostatic interactions, with a damping factor $\alpha = 0.2 ~\text{\AA}^{-1}$, is a suitable strategy.
 Other improvement was the use of rigid bodies to simulate \ce{[emim][B(CN)_4]}.
@@
 
-The solvation free energy results at infinite-dilution condition suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}, despite the similarity in the Henry's law constants observed in both cases.
-This picture is further confirmed at high \ce{CO_2} concentrations, in which the simulations correctly predicted that a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}, as compared to \ce{[emim][NTf_2]} in an equal-mass basis.
+The solvation free energy results at infinite-dilution condition suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][Tf_2N]}, despite the similarity in the Henry's law constants observed in both cases.
+This picture is further confirmed at high \ce{CO_2} concentrations, in which the simulations correctly predicted that a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}, as compared to \ce{[emim][Tf_2N]} in an equal-mass basis.
 

### 2019-02-12 ionic_liquids.tex
add figures of eq pressure

@@
 
-One can see in Table \ref{table:henry} that the only model able to reproduce the experimental Henry's law constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} with small deviation is that of Koller \textit{et al}.
+Table \ref{table:henry} shows that the only model able to reproduce the experimental Henry's law constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} with small deviation is that of Koller \textit{et al}.
 \cite{Koller_2012}.
@@
 We have found that only the force field developed by Koller \textit{et al}. \cite{Koller_2012} is able to perform such task, with a small relative error of 2.8\%.
-A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in the original work, which also allows one to accurately reproduce the experimental density of the pure substance.
+A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in the original work, which also allows to accurately reproduce the experimental density of the pure substance.
 
@@
 This required preliminary simulations in order to examine the flexibility of the ethyl chain in \ce{[emim]^+} and the analysis was greatly facilitated by employing useful visualization tools.
-Besides the properties already mentioned, the different models showed quite distinct behaviors, as well, in terms of conformational statistics.
+Besides the properties already mentioned, the different models showed quite distinct behaviors in terms of conformational statistics.
 %This lack of consistency is one of the reasons why in industry molecular simulation has not become a routinely tool yet.
 
-The solvation free energy results at infinite-dilution condition suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][Tf_2N]}, despite the similarity in the Henry's law constants observed in both cases.
+The solvation free energy results suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][Tf_2N]}, despite the similarity in the Henry's law constants observed in both cases.
 This picture is further confirmed at high \ce{CO_2} concentrations, in which the simulations correctly predicted that a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}, as compared to \ce{[emim][Tf_2N]} in an equal-mass basis.

### 2019-02-13 reviewer_response.tex
First round of revision

\documentclass[]{article}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage[version=4]{mhchem}
%opening
\title{\normalsize \textbf{Response to the Reviewer’s Comments on Manuscript FPE-D-18-00720}}
\author{}
\date{}

\begin{document}
\doublespacing
\maketitle

To: Prof. Jeffrey Potoff

Associate Editor

Fluid Phase Equlibria
\vspace{0.3cm}

Dear Prof. Jeffrey Potoff:

\hspace{0.5cm}Thank you for your message forwarding the reviewers’ comments on our manuscript entitled \textit{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquid \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}. We have carefully addressed the comments and suggestions of the reviewers, which required us to make changes in the text. The most substantial revision took place in section 5.3, for which we carried out additional simulations. In addition, we included the names of the ionic liquids and changed the acronym of one of the anions. To facilitate
your evaluation, we have crossed out all removed text and incorporated new content in color blue.

\hspace{0.5cm}Please find attached our detailed answers to the comments of each reviewer. We
hope that the revised version of the manuscript is suitable for publication.

\hspace{0.5cm}Sincerely yours,
\vspace{0.5cm}

Prof. Charlles R. A. Abreu

Federal University of Rio de Janeiro

\section{\textbf{Reviewer \#1}}
{\color{blue}{The manuscript submitted by Silveira \textit{et al.} presents their computational work on the study of solubility primarily of \ce{CO_2} but also for some additional compounds in ILs. They focus on the simulation of \ce{[emim][B(CN)_4]} IL in a comparative manner to \ce{[emim][NTF_2]} IL, using various existing force fields for the former and implementing simplifications in the simulation of the systems under study by introducing rigid body representations for the ions and by using the damped shifted force method to handle the electrostatics. The manuscript is suitable to be published in your journal, after addressing some problems: }}

\textbf{Answer}: We thank the reviewer for careful reading our manuscript and for the valuable comments and suggestions. We have tried to address them in the best possible way, considering the proposed scope of our work. Please find attached an annotated version of the revised manuscript. This is the one whose pages are mentioned in the answers that follow bellow.

{\color{blue}{1) The authors chose not to use an iterative scheme to correct the pressure of their simulations. They should justify their choice by including quantitative information from their simulations on how this correction would affect both the differences in the free energy but also the system's density at high concentrations.}}

\textbf{Answer}: Instead of performing an iterative scheme, we were able to correct the equilibrium pressure by using the technique of reweighting, as explained in page 4 of the manuscript. Although the correction term resulted to be small, this suggestion has allowed us to present the results in a rigorous way with considerable less computational effort, in comparison to the iterative scheme.

{\color{blue}{2) Among the various existing models used in this work, some explicitly report the use of LJ long range corrections in the energy and pressure. The authors should clearly state if they have taken that into account in their simulations.}}

\textbf{Answer}: The reviewer is right. We applied analytic tail corrections to the LJ interactions for all systems investigated. This information has been included in page 5 of the manuscript.

{\color{blue}{3) Results on densities of the various IL models at 298 K (Table 1) differ from the ones reported in the initial references. For example,  an 1\% error is presented in this manuscript for the FF-3 model of Koller \textit{et al.}, while an excellent agreement with the experimental density is reported in the original paper of Koller and his co-workers. The authors should explain this discrepancy.}}

\textbf{Answer}: The differences in density between our results and those reported by Koller \textit{et al.} \cite{Koller_2012}, Batista \textit{et al.} \cite{Batista_2015}, Liu \textit{et al.} \cite{Liu_2014} and Weber and Kirchner \cite{Weber_2016} are, respectively: 1 \% , 6.2 \%, 1.8 \% and 0.5 \%.
With the exception of the force field due to Batista \textit{et al.} \cite{Batista_2015}, the discrepancies are not considerable.
In general, we carefully followed the simulation setup reported by those authors, except for the number of ion pairs and the software package. For instance, Koller and co-workers \cite{Koller_2012} simulated 58 ions pairs using GROMACS, while we considered 250 ion pairs and the LAMMPS software package.
Small differences are then expected.
The discrepancy with the results of Batista and co-workers \cite{Batista_2015} stands out  from the others. In this case, however, important computational details are missing in the original paper, such as the method for computing electrostatic interactions, as well as the factors for scaling the 1-4 non-bonded interactions. 
Considering these various factors, we did not focus on reproducing the results of these references, but rather to use the force field parameters reported by the corresponding authors in order to find those that best reproduce the experimental Henry constant of \ce{CO_2}.

{\color{blue}{4) Simulating hybrid systems that include both rigid and non rigid bodies is complex and tricky. The authors should describe in detail how they performed these simulations in terms of barostatting and thermostatting.}}

\textbf{Answer}: In page 5 of the manuscript we specify the numerical integrators used to carry out the MD simulations. Considering hybrid systems of flexible and rigid molecules is straightforward in LAMMPS, since it allows to define groups of molecules and apply a different numerical integrator to each group.

{\color{blue}{5)It would be interesting if at least for the case of CO2 an isotherm was calculated and included in the paper.}}

\textbf{Answer}: We agree with the reviewer that computing an isotherm would be interesting. However, this computation requires to carry out extra simulations for different numbers of solute molecules, which is beyond the scope of this work.

\section{\textbf{Reviewer \#2}}

{\color{blue}{In the present manuscript, Silveira \textit{et al.} performed a systematic comparison of force fields used in Molecular Dynamic (MD) simulations of the solvation of carbon dioxide (\ce{CO_2}) and other compounds in two ionic liquids (ILs). For this purpose, solvation energies, Henry constants, and activity coefficients were calculated based on solid methodologies. A detailed review of the literature with respect to the theoretical background and the force fields is provided. Simplifications in the simulation strategies are analyzed by treating the IL ions as rigid instead of flexible bodies. A structural analysis of the molecular systems and their relationships with the studied properties are investigated thoroughly from a physico-chemical point of view. The authors could demonstrate that the IL \ce{[emim][B(CN)_4]} shows the largest solubility for \ce{CO_2} in comparison to other common ILs. Overall, the scientific findings are very clear, concise, and of high quality, and are presented in a good English. Formalities according to the guidelines of the journal are also fulfilled. In conclusion, the present manuscript is definitely worthy of publication taking into consideration a few minor comments from my side.}}

We are grateful for the comments and suggestions of the second reviewer.

{\color{blue}{1. In the context of the simulation protocol, information on the number simulation runs and the use of the mixing rules for the Lennard-Jones interactions should be given. The authors should also specify how the uncertainties of the various properties were calculated.}}

\textbf{Answer}: Instead of the number of runs, in page 6 we included the total simulation time for each system, since it might be a more informative measure of computational effort. The information about mixing rules and uncertainties calculations have been included in pages 5, 9 and 12.

{\color{blue}{2. The authors were focusing on several static properties for the pure ILs using different models. As reference property for force field validation, the density was selected where deviations between about (1 and 5) \% were found according to Table 1. Did the authors also study dynamic properties such as the self-diffusion coefficient and compare the results with the experiment? If so, a corresponding brief paragraph should be included in the revised manuscript. Relative deviations of 5\% in the liquid density can often come along with deviations of several dozens of percent for dynamic properties.
}}

\textbf{Answer}:We haven't done a study of dynamic properties. We have mainly focused on predicting solvation properties given the potential of the investigated ionic liquids in separation processes for \ce{CO_2}.

{\color{blue}{3. The results for the simulated solvation free energies of benzene, hexane, and water showed relatively large deviations from experimental data in the order of 10 \%, while the results for ethanol match. However, for the infinite-dilution activity coefficient of these solutes in the IL [emim][B(CN)4], hexane deviates significantly stronger than benzene, ethanol, and water. It would be interesting to discuss in some more detail why these different trends can be found by considering, for example, the force fields of the pure solute and the mixing rules for the binary mixtures. For sure, it seems that the authors will continue such investigations in their future studies.}}

\textbf{Answer}: The reviewer is right and in order to analyze the strong deviation observed for hexane, we computed an experimental solvation free energy of this solute in  \ce{[emim][B(CN)_4]}, as shown in page 14. The results from simulation show a favorable solvation, in contradiction with the experimental data. That is why we emphasize in the conclusions that a future revision of the models used for the solutes is necessary.

{\color{blue}{4. For the specification of the pressure, the symbol “p” instead of “P” should be used. Furthermore, the unit of the pressure should be given in “MPa” instead of “atm."}}

\textbf{Answer}: This has been acknowledged throughout the manuscript.

\bibliographystyle{ieeetr}
\bibliography{reviewer_response.bib}
\end{document}

### 2019-02-13 ionic_liquids.tex
First round of revision

@@
 \label{eq:fgas_d}
-f^{g}_s = c_s R T \exp \left( \frac{\Delta G_\text{sim}}{R T} \right). 
+f^{g}_s = c_s R T \exp \left( \frac{\Delta G_\text{solv}}{R T} \right). 
 \end{equation}
@@
 \label{eq:equilibrium pressure}
-y_s \exp\left( \frac{B_s p}{R T} \right) p = c_s(p) R T \exp \left( \frac{\Delta G_\text{sim}}{R T} \right),
+y_s \exp\left( \frac{B_s p}{R T} \right) p = c_s(p) R T \exp \left( \frac{\Delta G_\text{solv}}{R T} \right),
 \end{equation}
@@
 
-The equilibrium pressure will be given by the value for which the function $\Delta G_{\text{sim}}(p) $, defined by Eq.~\eqref{eq:equilibrium pressure}, intersects $\Delta G_{\text{sim}} (p)$, as obtained in simulations.
-Note that besides  $\Delta G_{\text{sim}}$, we are also considering  variations of $c_s$ with pressure.
+The equilibrium pressure will be the intersection point between the function $\Delta G_{\text{solv}}(p) $, defined by Eq.~\eqref{eq:equilibrium pressure}, and $\Delta G_{\text{sim}} (p)$, as obtained in simulations.
+Note that besides  $\Delta G_{\text{sim}}$, we are taking into account variations of $c_s$ with pressure.
 These computations are greatly facilitated by the technique of reweighting \cite{McDonald1967,McDonald1969}, which uses simulation results from different states to improve the statistics and, particularly important to our case, allows to interpolate expectation values of thermodynamic observables along unsampled states.
@@
 In Fig.~\ref{fig:dihedrals_emim}, we show the CDFs obtained for all force fields employed here for \ce{[emim][B(CN)_4]}.
-All CDFs shown in this section were generated from NpT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$ using our standard setup (i.e.
+All CDFs shown in this section were generated from NpT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$ using our standard setup (i.e.
 flexible ions with PPPM Ewald electrostatics).
@@
 
-Once the rigid body structures have been determined, we carried out NpT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$ using the simplified setup (i.e.
+Once the rigid body structures have been determined, we carried out NpT-MD simulations of 250 ion pairs at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$ using the simplified setup (i.e.
 rigid ions with DSF electrostatics) and all force fields in question.
@@
 	\centering
-	\caption{Comparison of predicted and experimental densities for different models of \ce{[emim][B(CN)_4]} via NpT-MD simulations at $T = 298.0~\text{K}$ and $p = 1.0~\text{atm}$.
+	\caption{Comparison of predicted and experimental densities for different models of \ce{[emim][B(CN)_4]} via NpT-MD simulations at $T = 298.0~\text{K}$ and $p = 0.1~\text{MPa}$.
 The experimental density is $1.036~\mathrm{g/cm^3}$ \cite{Doma_ska_2011}.}
@@
 Due to this observed behaviors of both ions, all simulations of \ce{[emim][Tf_2N]} in the present work are performed considering flexible cations and anions, as well as DSF electrostatics.
-This approach results in a mean density of $1.495 \pm 0.009 ~\mathrm{g/cm^3}$ at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$.
+This approach results in a mean density of $1.495 \pm 0.009 ~\mathrm{g/cm^3}$ at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
 The relative error of this result with respect to the experimental value obtained by Tokuda \textit{et al}. \cite{Tokuda_2005} is only 1.12\%.
@@
 \includegraphics[width=\linewidth]{Ludwig_anion}
-\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[Tf_2N]^-}, obtained from NpT-MD simulations of 250 ion pairs of \ce{[emim][Tf_2N]} at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$ using the model of K\"{o}ddermann \textit{et al}.
+\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[Tf_2N]^-}, obtained from NpT-MD simulations of 250 ion pairs of \ce{[emim][Tf_2N]} at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$ using the model of K\"{o}ddermann \textit{et al}.
 \cite{Koddermann_2007}.}
@@
 In Table \ref{table:henry}, we present results from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][Tf_2N]} under periodic boundary conditions.
-The simulations were carried out at $T = 298.0~\mathrm{K}$ and $p = 1.0~\mathrm{bar}$.
+The simulations were carried out at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
 Table~\ref{table:henry} contains simulated molar densities, partial and total solvation free energies, as well as Henry's law constants ($K_s$) computed via Eq.~\eqref{eq:henry_eq}.
-The computed values should be compared to the experimental data reported by Mahurin \textit{et al}.
-\cite{Mahurin_2010} ($K_s = 38.9 \pm 0.03 ~\mathrm{atm}$ for \ce{CO_2} in \ce{[emim][B(CN)_4]}) and by Finotello \textit{et al}.
-\cite{Finotello_2008} ($K_s = 39.0 \pm 0.1 ~\mathrm{atm}$ for \ce{CO_2} in \ce{[emim][Tf_2N]}).
-The uncertainties in $K_s$ were calculated by using a standard error propagation formula
-
+These should be compared to the experimental data reported by Mahurin \textit{et al}.
+\cite{Mahurin_2010} ($K_s = 3.941 \pm 0.003 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][B(CN)_4]}) and by Finotello \textit{et al}.
+\cite{Finotello_2008} ($K_s = 3.95 \pm 0.01 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][Tf_2N]}).
+Uncertainties in $K_s$ were calculated using a standard error propagation formula, given by
 \begin{equation}
@@
 \end{equation}
-which are a function of the uncertainties in free energy, which are calculate using MBAR \cite{Shirts_2008}.
+with uncertainties in free energy calculate using MBAR \cite{Shirts_2008}.
 
@@
 	\centering
-	\caption{Results of solvation free energies and Henry's law constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]} at $T = 298.15~\mathrm{K}$ and $p = 1~\mathrm{atm}$.
-The experimental Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and in \ce{[emim][Tf_2N]} are, respectively, $38.9 \pm 0.03 ~\mathrm{atm}$ \cite{Mahurin_2010} and $39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008}.}
+	\caption{Results of solvation free energies and Henry's law constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]} at $T = 298.15~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
+The experimental Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and in \ce{[emim][Tf_2N]} are, respectively, $3.941 \pm 0.003 ~\mathrm{MPa}$ \cite{Mahurin_2010} and $3.95 \pm 0.01 ~\mathrm{MPa}$ \cite{Finotello_2008}.}
 	\begin{adjustbox}{max width=\textwidth}
@@
 			Model & $\tilde{\rho}_\text{sim}$ & $\Delta G_\text{vdW}$  & $\Delta G_\text{Coul}$  & $\Delta G_\text{sim}$ & $K_s$ & error \\
-			& (mol/dm\textsuperscript{3}) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  & (\%) \\
+			& (mol/dm\textsuperscript{3}) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (MPa)  & (\%) \\
 			\hline
@@
 			\multicolumn{7}{c}{\ce{[emim][B(CN)_4]}} \\
-			Koller \textit{et al}. \cite{Koller_2012} & $4.5925$ & $0.45 \pm 0.01$ & $-1.06 \pm 0.02$ & $-0.61 \pm 0.02$ & $40 \pm 1$ & $2.8$ \\
-			Batista \textit{et al}. \cite{Batista_2015} & $4.3700$ & $0.378 \pm 0.008$ & $-1.24 \pm 0.01$  & $-0.86 \pm 0.01$ & $24.9 \pm 0.5$ & $38.9$ \\
-			Liu \textit{et al}. \cite{Liu_2014} & $4.3815$ & $0.226 \pm 0.009$ & $-1.11 \pm 0.01$ & $-0.88 \pm 0.01$ & $24.3 \pm 0.5$ & $37.6$  \\
-			Weber and Kirchner \cite{Weber_2016} & $4.5221$ & $0.478 \pm 0.009$ & $-1.23 \pm 0.02$ & $-0.75 \pm 0.02$ & $31 \pm 1$ & $20.3$  \\
+			Koller \textit{et al}. \cite{Koller_2012} & $4.5925$ & $0.45 \pm 0.01$ & $-1.06 \pm 0.02$ & $-0.61 \pm 0.02$ & $ 4.1 \pm 0.1$ & $2.8$ \\
+			Batista \textit{et al}. \cite{Batista_2015} & $4.3700$ & $0.378 \pm 0.008$ & $-1.24 \pm 0.01$  & $-0.86 \pm 0.01$ & $2.52 \pm 0.05$ & $38.9$ \\
+			Liu \textit{et al}. \cite{Liu_2014} & $4.3815$ & $0.226 \pm 0.009$ & $-1.11 \pm 0.01$ & $-0.88 \pm 0.01$ & $2.46 \pm 0.05$ & $37.6$  \\
+			Weber and Kirchner \cite{Weber_2016} & $4.5221$ & $0.478 \pm 0.009$ & $-1.23 \pm 0.02$ & $-0.75 \pm 0.02$ & $3.1 \pm 0.1$ & $20.3$  \\
 			\hline
@@
 			\multicolumn{7}{c}{\ce{[emim][Tf_2N]}} \\
-			K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007} & $3.8205$ & $0.389 \pm 0.005$ & $-0.901 \pm 0.006$ & $-0.512 \pm 0.008$ & $39.4 \pm 0.5$  & $0.97$  \\
+			K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007} & $3.8205$ & $0.389 \pm 0.005$ & $-0.901 \pm 0.006$ & $-0.512 \pm 0.008$ & $3.99\pm 0.05$  & $0.97$  \\
 			\hline\hline
@@
 Spatial distribution functions (SDFs) \cite{Svishchev_1993} can help us visualizing how differently the solvent ions interact with the solute molecule.
-By using TRAVIS \cite{Brehm_2011}, we have obtained SDFs of both cation and anion around a \ce{CO_2} molecule, sampled from MD trajectories of either \ce{CO_2}+\ce{[emim][B(CN)_4]} or \ce{CO_2}+\ce{[emim][Tf_2N]} systems simulated at $T = 298.0~\text{K}$, $p = 1.0~\mathrm{bar}$, and $x_\mathrm{CO_2} = 0.1$.
+By using TRAVIS \cite{Brehm_2011}, we have obtained SDFs of both cation and anion around a \ce{CO_2} molecule, sampled from MD trajectories of either \ce{CO_2}+\ce{[emim][B(CN)_4]} or \ce{CO_2}+\ce{[emim][Tf_2N]} systems simulated at $T = 298.0~\text{K}$, $p = 0.1~\mathrm{MPa}$, and $x_\mathrm{CO_2} = 0.1$.
 The slightly larger \ce{CO_2} concentration considered here is meant to improve statistics.
@@
 		$T$  & $313.15~\mathrm{K}$ & $312.13~\mathrm{K}$ \\
-		$p$  & $21~\mathrm{atm}$ & $37~\mathrm{atm}$ \\
+		$p$  & $2.128~\mathrm{MPa}$ & $3.749~\mathrm{MPa}$ \\
 		$x_s$ & $0.352$ & $0.479$ \\
@@
 		\multicolumn{3}{c}{Simulation Result} \\
-		$c_s$ & $3.04~\mathrm{mol/dm^3}$ & $2.22~\mathrm{mol/dm^3}$ \\ 
+		$c_s$ & $2.22~\mathrm{mol/dm^3}$ & $3.04~\mathrm{mol/dm^3}$ \\ 
 		$\Delta G_\text{sim}$ & $-0.755~\mathrm{kcal/mol}$ & $-0.542~\mathrm{kcal/mol}$ \\
-		$f_g$ & $16.9~\mathrm{atm}$ & $32.6~\mathrm{atm}$ \\
-		$p$ & $18.3~\mathrm{atm}$ & $38.4~\mathrm{atm}$ \\
+		$f_g$ & $1.712~\mathrm{MPa}$ & $3.303~\mathrm{MPa}$ \\
+		$p$ & $1.854~\mathrm{MPa}$ & $3.891~\mathrm{MPa}$ \\
 		\hline\hline
@@
 The computed solvation free energies for the systems \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][Tf_2N]} were $-0.755 \pm 0.009 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005~\mathrm{kcal/mol}$, respectively.
-Using these values as inputs in Eq.~\eqref{eq:equilibrium pressure}, we obtained equilibrium pressures of p = 18.3 atm and 38.4 atm, as reported in Table~\ref{table:solv}.
-In this table, we also show the the corresponding gas-phase fugacities of \ce{CO_2} ($f_s^g$) computed by Eq.~\eqref{eq:fgas_d}.
+Using these values as inputs in Eq.~\eqref{eq:equilibrium pressure}, we obtained pressure values of $1.854~\mathrm{MPa}$ and $3.893~\mathrm{MPa}$, as reported in Table~\ref{table:solv}.
+The corresponding gas-phase fugacities of \ce{CO_2} ($f_s^g$) computed by Eq.~\eqref{eq:fgas_d} are given in Table~\ref{table:solv}, as well.
 The results make clear that assuming ideal gas ($p = f_s^g$) would have been an oversimplification, specially in the case of \ce{[emim][Tf_2N]}.
 
-In order to obtain $\Delta G_\text{sim} (p)$ and $c_s(p)$, we carried out extra simulations at pressure values  of p = (17, 18) atm  for \ce{CO_2}+\ce{[emim][B(CN)_4]} and at p = (40, 44) atm for \ce{CO_2}+\ce{[emim][Tf_2N]}.
+In order to obtain $\Delta G_\text{sim} (p)$ and $c_s(p)$, we carried out extra simulations at pressure values  of p = (1.722, 1.823) MPa  for \ce{CO_2}+\ce{[emim][B(CN)_4]} and at p = (4.053, 4.458) MPa for \ce{CO_2}+\ce{[emim][Tf_2N]}.
 In this case, we considered a wider range of pressure, given the departure from ideal gas behavior mentioned above.
-As described in Sec.~\ref{sec:partial_pressure}, $\Delta G_\text{sim}$ and $c_s$ were interpolated to intermediate pressures by reweighting.
-In Fig.~\ref{fig:pressure}, we show for both systems the simulated results of $\Delta G_\text{sim}$, together with the curve of $\Delta G_\text{sim}$ defined by Eq.~\eqref{eq:equilibrium pressure}.
-As expected, $\Delta G_\text{sim}$ does not vary appreciably with pressure, at least over the range of experimental data considered here.
-This results in small corrections to the equilibrium pressures of Table~\ref{table:solv}: the points of intersection are p = 17.8 atm and p = 40.5 atm, for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][Tf_2N]}, respectively.
+As described in Sec.~\ref{sec:partial_pressure}, $\Delta G_\text{sim}$ and $c_s$ were interpolated to intermediate pressures by reweighting using MBAR \cite{Shirts_2008}.
+In Fig.~\ref{fig:pressure}, we show for both systems the results of $\Delta G_\text{sim}$, together with the curve of $\Delta G_\text{solv}$ defined by Eq.~\eqref{eq:equilibrium pressure}.
+Although not shown here, the changes in density are negligible: 0.05 \% and 0.07 \% for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][Tf_2N]}, respectively.
+In addition, $\Delta G_\text{sim}$ does not vary appreciably with pressure, at least over the range of experimental data considered here. 
+This results in small corrections to the equilibrium pressures of Table~\ref{table:solv}: the intersection points are 1.807 MPa and 4.106 MPa, for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][Tf_2N]}, respectively.
 These values did not depart considerably from the specified values, meaning that our results sustain the experimental observations.
@@
 	\centering
-	\subfloat[][Koller~\textit{et al}.~\cite{Koller_2012}]{
+	\subfloat[ \ce{CO_2}+\ce{[emim][B(CN)_4]} ]{
 		\includegraphics[width=\linewidth]{pressure_koller.pdf}}
 
-	\subfloat[Batista~\textit{et al}.~\cite{Batista_2015}]{  
+	\subfloat[\ce{CO_2}+\ce{[emim][Tf_2N]}]{  
 		\includegraphics[width=\linewidth]{pressure_ludwig.pdf}}
+	\caption{Solvation free energy $\Delta G_\text{sim}$ (solid line) and $\Delta G_\text{solv}$ of Eq.~\eqref{eq:equilibrium pressure} (dashed line) as a function of pressure.}
 	\label{fig:pressure}
@@
 Due to the availability of experimental data \cite{Yan_2010, Doma_ska_2011}, the solutes chosen for this study are benzene, hexane, cyclohexane, ethanol, and water.
-Uncertainties in activity coefficients were calculated using error propagation formula, as done for $K_s$.
+Uncertainties in activity coefficients were calculated using error propagation, as done for $K_s$.
 
@@
 From the individual contributions of $\Delta G_\text{vdW}$ and $\Delta G_\text{Coul}$, we can conclude that the vdW contribution is largely underestimated.
-This makes sense since one would expect a less favorable insertion for a longer chain molecule in comparison, for instance, to benzene which has a comparable
-$\Delta G_\text{vdW}$.
 Also, in the case of hexane, one can see in Table \ref{table:gamma} that the available experimental values of $\gamma^\infty$ in \ce{[emim][B(CN)_4]} at very close temperatures ($298.15~\text{K}$ and $303~\text{K}$) differ considerably.
@@
 	\includegraphics[width=\linewidth]{delta_g_sim_exp}
-	\caption{Profile of $\Delta G_\text{vdW}$ corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, modeled according to the.}
+	\caption{Simulated free energy $\Delta G_\text{sim}$ versus the experimental result at $T = 298.15~\text{K}$ for the solutes hexane, benzene, ethanol and water in \ce{[emim][B(CN)_4]}.}
 	\label{fig:deltag_solutes}

### 2019-02-14 reviewer_response.tex
Back to old acronym NTf_2

@@
 
-\hspace{0.5cm}Thank you for your message forwarding the reviewers’ comments on our manuscript entitled \textit{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquid \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}.
+\hspace{0.5cm}Thank you for your message forwarding the reviewers’ comments on our manuscript entitled \textit{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquid \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}.
 We have carefully addressed the comments and suggestions of the reviewers, which required us to make changes in the text.
 The most substantial revision took place in section 5.3, for which we carried out additional simulations.
-In addition, we included the names of the ionic liquids and changed the acronym of one of the anions.
-To facilitate
-your evaluation, we have crossed out all removed text and incorporated new content in color blue.
+In addition, we have included the full names of the ionic liquids in the abstract. To facilitate your evaluation, we have crossed out all removed text and incorporated new content in color blue.
 

### 2019-02-14 makediff.sh

@@ -1,0 +1,2 @@
+#!/bin/bash
+latexdiff -c ld.cfg ionic_liquids_submitted.tex ionic_liquids.tex > ionic_liquids_diff.tex

### 2019-02-19 reviewer_response.tex
Changes in the review: pressure calculation

@@
 Fluid Phase Equlibria
-\vspace{0.3cm}
+\vspace{1cm}
 
-Dear Prof. Jeffrey Potoff:
+Dear Prof. Potoff:
 
-\hspace{0.5cm}Thank you for your message forwarding the reviewers’ comments on our manuscript entitled \textit{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquid \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}.
+Thank you for your message forwarding the reviewers’ comments on our manuscript entitled \textit{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquid \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}.
 We have carefully addressed the comments and suggestions of the reviewers, which required us to make changes in the text.
-The most substantial revision took place in section 5.3, for which we carried out additional simulations.
-In addition, we have included the full names of the ionic liquids in the abstract. To facilitate your evaluation, we have crossed out all removed text and incorporated new content in color blue.
+The most substantial revision took place in Sec.~5.3, for which we carried out additional simulations.
+In addition, we have included the full names of the ionic liquids in the abstract.
+To facilitate your evaluation, we attached an annotated version in which all removed text has been crossed out in red and all new content is colored in blue.
 
-\hspace{0.5cm}Please find attached our detailed answers to the comments of each reviewer. We
+Please find attached our detailed answers to the comments of each reviewer.
+We
 hope that the revised version of the manuscript is suitable for publication.
 
-\hspace{0.5cm}Sincerely yours,
-\vspace{0.5cm}
-
-Prof. Charlles R. A. Abreu
+\begin{center}
+Sincerely yours,
+\end{center}
+\begin{flushright}
+Charlles R. A. Abreu
 
 Federal University of Rio de Janeiro
+\end{flushright}
 
@@
 
-\textbf{Answer}: We thank the reviewer for careful reading our manuscript and for the valuable comments and suggestions.
+\textbf{Answer}: We thank the reviewer for the careful examination of our manuscript and for the invaluable comments and suggestions.
 We have tried to address them in the best possible way, considering the proposed scope of our work.
 Please find attached an annotated version of the revised manuscript.
-This is the one whose pages are mentioned in the answers that follow bellow.
+This is the one whose pages are mentioned in the answers that follow.
 
@@
 
-\textbf{Answer}: Instead of performing an iterative scheme, we were able to correct the equilibrium pressure by using the technique of reweighting, as explained in page 4 of the manuscript.
-Although the correction term resulted to be small, this suggestion has allowed us to present the results in a rigorous way with considerable less computational effort, in comparison to the iterative scheme.
+\textbf{Answer}:
+In order to address the reviewer's concern on this topic, we decided to carry out a more rigorous strategy to compute the equilibrium pressure.
+Instead of performing an iterative scheme, we executed some simulations at different pressures in the vicinity of the experimental value.
+This allowed us to employ a multistate analysis method (MBAR) and compute the solvation free energy along a continuous range of pressures via reweighting.
+The resulting curves confirmed our previous assertion that such free energy depends only slightly on the pressure.
+Besides, we could use these curves to find, for each case, the pressure at which the equilibrium equations are satisfied.
+We believe that the new procedure, which is explained on page 4 of the annotated manuscript, improves our analysis of the equilibrium condition in a significant way.
 

### 2019-02-19 ionic_liquids.tex
Changes in the review: pressure calculation

@@
 
-\usepackage[colorlinks,citecolor=blue]{hyperref}
+%\usepackage[colorlinks,citecolor=blue]{hyperref}
 \usepackage{lineno}
@@
 
-\title{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}
+\title{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 
@@
 Recently, the propensity of the ionic liquid 1-ethyl-3-methylimidazolium tetracyanoborate (\ce{[emim][B(CN)_4]}) for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
-In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and 1-ethyl-3-methylimidazolium bis (trifluoromethylsulfonyl) imide (\ce{[emim][Tf_2N]}) are carried out both at infinite dilution and at high concentrations.
+In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and 1-ethyl-3-methylimidazolium bis (trifluoromethylsulfonyl) imide (\ce{[emim][NTf_2]}) are carried out both at infinite dilution and at high concentrations.
 A systematic study is performed by comparing several force fields and assessing the efficacy of simplifications in the simulations by using rigid-body dynamics and pairwise electrostatics.
@@
 \cite{Carvalho_2016} show that most systems which promote physical absorption of \ce{CO_2} exhibit solubilities which are similar, or even lower, than that observed for heavy alkanes such as eicosane.
-This is true for the popular ILs \ce{[bmim][Tf_2N]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][Tf_2N]} and \ce{[hmim][pFAP]}.
+This is true for the popular ILs \ce{[bmim][NTf_2]}, \ce{[bmim][PF_6]}, \ce{[bmim][BF_4]}, as well as for those synthesized from the fluorination of the cation or the anion, such as \ce{[(C_2H_2F_2)mim][NTf_2]} and \ce{[hmim][pFAP]}.
 The only exception they found was the family of ILs containing the anion \ce{[B(CN)_4]^-} (tetracyanoborate).
@@
 As we show here, it was possible to find a model that successfully reproduces the experimental value of the Henry constant of \ce{CO_2} in this IL.
-For comparison, we analyzed the solvation of \ce{CO_2} not only in \ce{[emim][B(CN)_4]}, but also in \ce{[emim][Tf_2N]}, both at infinite dilution and at high concentrations.
+For comparison, we analyzed the solvation of \ce{CO_2} not only in \ce{[emim][B(CN)_4]}, but also in \ce{[emim][NTf_2]}, both at infinite dilution and at high concentrations.
 The simulations confirmed what is observed in experiments.
@@
 Two additional assumptions are made here.
-First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems investigated) or can be approximated by an ideal solution.
+First, we assume that the gas phase is either pure solute (which is consistent with the ionic-liquid systems we investigate here) or can be approximated by an ideal solution.
 Second, we assume that the system pressure is moderate, so that a truncated virial equation is enough to represent the gas phase.
@@
 
-The equilibrium pressure will be the intersection point between the function $\Delta G_{\text{solv}}(p) $, defined by Eq.~\eqref{eq:equilibrium pressure}, and $\Delta G_{\text{sim}} (p)$, as obtained in simulations.
-Note that besides  $\Delta G_{\text{sim}}$, we are taking into account variations of $c_s$ with pressure.
-These computations are greatly facilitated by the technique of reweighting \cite{McDonald1967,McDonald1969}, which uses simulation results from different states to improve the statistics and, particularly important to our case, allows to interpolate expectation values of thermodynamic observables along unsampled states.
-This implies a significant reduction in computational cost.
-In particular, we use the Multistate Bennett Acceptance Ratio (MBAR) estimator \cite{Shirts_2008}, which has been successfully used for the purpose of reweighing ~\cite{Aimoli2014, Nichele2018, Schieber2018}.
+To determine the equilibrium condition, it is necessary to know how $\Delta G_{\text{sim}}$ and $c_s$ vary with pressure, so that Eqs.~\eqref{eq:free_solv} and \eqref{eq:equilibrium pressure} can be solved together.
+Fortunately, the Multistate Bennett Acceptance Ratio (MBAR) method \cite{Shirts_2008} allows us to combine simulation samples obtained at discrete thermodynamic states and compute interpolated expectation values along a continuous range of unsampled states.
+This technique, known as reweighting \cite{McDonald1967,McDonald1969}, has been successfully employed in previous work \cite{Aimoli2014, Nichele2018, Schieber2018}, where one can find more details about the calculation procedure.
+Here, we carry out solvation simulations at a few pressures in the vicinity of the experimental value and employ MBAR to determine both functions $\Delta G_{\text{sim}}(p)$ and $c_s(p)$.
 
@@
 
-In the case of ionic liquid \ce{[emim][Tf_2N]}, we use the model of K\"{o}ddermann \textit{et al}.
+In the case of ionic liquid \ce{[emim][NTf_2]}, we use the model of K\"{o}ddermann \textit{et al}.
 \cite{Koddermann_2007}, which was also derived by refining parameters of the force field by P{\'{a}}dua and Canongia Lopes \cite{Canongia_Lopes_2006}.
 The authors characterized this refinement as unusual, given that they modified the LJ parameters while keeping the partial charges unchanged.
-Kerl \textit{et al}. \cite{Kerl__2017} recently employed this model to accurately predict Henry constants of \ce{CO_2} in \ce{[emim][Tf_2N]} at several temperatures.
+Kerl \textit{et al}. \cite{Kerl__2017} recently employed this model to accurately predict Henry constants of \ce{CO_2} in \ce{[emim][NTf_2]} at several temperatures.
 
@@
 In this way, 3 iterations were sufficient in all cases for attaining, in the final round, an acceptable uncertainty in $\Delta G_\text{sim}$ estimated via MBAR \cite{Shirts_2008, Klimovich_2015}.
-Considering also the MD runs at each $\lambda_{\text{Coul}}$, the simulation time was 110 ns for each system.
+Considering also the MD runs at each $\lambda_{\text{Coul}}$, the simulation time was $110~\mathrm{ns}$ for each system.
 
@@
 In the simplified setup, the ions are modeled as rigid bodies and the DSF method \cite{Fennell2006} with $r_c = 12 ~\text{\AA}$ and $\alpha = 0.2 ~\text{\AA}^{-1}$) is used as and alternative to the PPPM scheme.
-For building the rigid bodies, we carry out a frequency analysis of some key dihedrals present in ions \ce{[emim]^+} and \ce{[Tf_2N]^-}, whose flexibility could lead to significant conformational changes.
+For building the rigid bodies, we carry out a frequency analysis of some key dihedrals present in ions \ce{[emim]^+} and \ce{[NTf_2]^-}, whose flexibility could lead to significant conformational changes.
 On the other hand, small and highly symmetric anions such as \ce{PF_6} and \ce{BF_4} are already usually modeled as rigid bodies \cite{HANKE_2001,Hanke_2003,Lynden_Bell_2006}, which justifies the strategy in the case of \ce{[B(CN)_4]^-}.
 
-As a guide to the discussions in this section, in Fig~\ref{fig:atoms_id} we introduce a nomenclature for all atoms present in the ions \ce{[emim]^+}, \ce{[B(CN)_4]^-}, and \ce{[Tf_2N]^-}.
+As a guide to the discussions in this section, in Fig~\ref{fig:atoms_id} we introduce a nomenclature for all atoms present in the ions \ce{[emim]^+}, \ce{[B(CN)_4]^-}, and \ce{[NTf_2]^-}.
 Please note that, in the united-atom version of \ce{[emim]^+}, all hydrogen atoms ranging from H4 to H11 are incorporated to their corresponding carbon atoms.
@@
 \includegraphics[width=\linewidth]{atoms_id.pdf}
-\caption{Adopted nomenclature for individual atoms in the cation 1-ethyl-3-methylimidazolium (\ce{[emim]^+}) and anions tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[Tf_2N]^-}).}
+\caption{Adopted nomenclature for individual atoms in the cation 1-ethyl-3-methylimidazolium (\ce{[emim]^+}) and anions tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
 \label{fig:atoms_id}
@@
 
-A study of conformations was also carried out for \ce{[emim][Tf_2N]} using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.
+A study of conformations was also carried out for \ce{[emim][NTf_2]} using the model of K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007}.
 A CDF obtained for the dihedral angles of sequences C1-N2-C5-C6 and C2-N2-C5-C6 in \ce{[emim]^+}, which is made available in the Supplementary Material, resembles the one in Fig.~\ref{fig:dihedrals_emim}(d).
 The resemblance was expected because the intramolecular parameters employed for \ce{[emim]^+} are identical in these two cases, since the corresponding models are both based on the force field developed by Canongia-Lopes and P\'{a}dua \cite{Canongia_Lopes_2006}.
-However, the most likely value of $\psi_1$ is shifted to $0^{\circ}$ in the case of \ce{[emim][Tf_2N]}.
+However, the most likely value of $\psi_1$ is shifted to $0^{\circ}$ in the case of \ce{[emim][NTf_2]}.
 This highlights the fact that altering atomic charges can induce conformational changes and should, therefore, be accompanied by a revision of torsion parameters in some cases.
-With regard to the anion \ce{[Tf_2N]^-}, Deetlefs \textit{et al}.
-\cite{Deetlefs_2006} experimentally determined the conformer population of the liquid-phase and observed that \ce{[Tf_2N]^-} is mostly found in its \textit{trans} conformation.
-In Fig.~\ref{fig:die_ntf2}, we present the CDF obtained for the contiguous sequences C1-S1-N1-S2 and S1-N1-S2-C2 in \ce{[Tf_2N]^-}, which qualitatively confirms the observation of Deetlefs \textit{et al}.
+With regard to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al}.
+\cite{Deetlefs_2006} experimentally determined the conformer population of the liquid-phase and observed that \ce{[NTf_2]^-} is mostly found in its \textit{trans} conformation.
+In Fig.~\ref{fig:die_ntf2}, we present the CDF obtained for the contiguous sequences C1-S1-N1-S2 and S1-N1-S2-C2 in \ce{[NTf_2]^-}, which qualitatively confirms the observation of Deetlefs \textit{et al}.
 \cite{Deetlefs_2006}.
-This CDF also makes clear that \ce{[Tf_2N]^-} exhibits a considerable degree of flexibility.
-Due to this observed behaviors of both ions, all simulations of \ce{[emim][Tf_2N]} in the present work are performed considering flexible cations and anions, as well as DSF electrostatics.
+This CDF also makes clear that \ce{[NTf_2]^-} exhibits a considerable degree of flexibility.
+Due to this observed behaviors of both ions, all simulations of \ce{[emim][NTf_2]} in the present work are performed considering flexible cations and anions, as well as DSF electrostatics.
 This approach results in a mean density of $1.495 \pm 0.009 ~\mathrm{g/cm^3}$ at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
@@
 \includegraphics[width=\linewidth]{Ludwig_anion}
-\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[Tf_2N]^-}, obtained from NpT-MD simulations of 250 ion pairs of \ce{[emim][Tf_2N]} at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$ using the model of K\"{o}ddermann \textit{et al}.
+\caption{Combined distribution function of the dihedral angles of the contiguous chains C1-S1-N1-S2 and S1-N1-S2-C2 of anion \ce{[NTf_2]^-}, obtained from NpT-MD simulations of 250 ion pairs of \ce{[emim][NTf_2]} at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$ using the model of K\"{o}ddermann \textit{et al}.
 \cite{Koddermann_2007}.}
@@
 
-\subsection{Dilute Solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}
+\subsection{Dilute Solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 \label{sec:henry_results}
 
-In Table \ref{table:henry}, we present results from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][Tf_2N]} under periodic boundary conditions.
+In Table \ref{table:henry}, we present results from expanded ensemble simulations of a single \ce{CO_2} molecule dissolved in 250 ion pairs of either \ce{[emim][B(CN)_4]} or \ce{[emim][NTf_2]} under periodic boundary conditions.
 The simulations were carried out at $T = 298.0~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
@@
 \cite{Mahurin_2010} ($K_s = 3.941 \pm 0.003 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][B(CN)_4]}) and by Finotello \textit{et al}.
-\cite{Finotello_2008} ($K_s = 3.95 \pm 0.01 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][Tf_2N]}).
+\cite{Finotello_2008} ($K_s = 3.95 \pm 0.01 ~\mathrm{MPa}$ for \ce{CO_2} in \ce{[emim][NTf_2]}).
 Uncertainties in $K_s$ were calculated using a standard error propagation formula, given by
@@
 \end{equation}
-with uncertainties in free energy calculate using MBAR \cite{Shirts_2008}.
+with the uncertainties in free energies calculated by MBAR \cite{Shirts_2008}.
 
@@
 	\centering
-	\caption{Results of solvation free energies and Henry's law constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]} at $T = 298.15~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
-The experimental Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and in \ce{[emim][Tf_2N]} are, respectively, $3.941 \pm 0.003 ~\mathrm{MPa}$ \cite{Mahurin_2010} and $3.95 \pm 0.01 ~\mathrm{MPa}$ \cite{Finotello_2008}.}
+	\caption{Results of solvation free energies and Henry's law constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} at $T = 298.15~\mathrm{K}$ and $p = 0.1~\mathrm{MPa}$.
+The experimental Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and in \ce{[emim][NTf_2]} are, respectively, $3.941 \pm 0.003 ~\mathrm{MPa}$ \cite{Mahurin_2010} and $3.95 \pm 0.01 ~\mathrm{MPa}$ \cite{Finotello_2008}.}
 	\begin{adjustbox}{max width=\textwidth}
@@
 			\hline
-%			\multicolumn{7}{c}{\ce{[emim][Tf_2N]}: $K_{s}^{\text{exp}} = 39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008} }\\
-			\multicolumn{7}{c}{\ce{[emim][Tf_2N]}} \\
+%			\multicolumn{7}{c}{\ce{[emim][NTf_2]}: $K_{s}^{\text{exp}} = 39.0 \pm 0.1 ~\mathrm{atm}$ \cite{Finotello_2008} }\\
+			\multicolumn{7}{c}{\ce{[emim][NTf_2]}} \\
 			K\"{o}ddermann \textit{et al}. \cite{Koddermann_2007} & $3.8205$ & $0.389 \pm 0.005$ & $-0.901 \pm 0.006$ & $-0.512 \pm 0.008$ & $3.99\pm 0.05$  & $0.97$  \\
@@
 \cite{Liu_2014} is statistically identical to a value reported by the same authors in Ref.~\citenum{Liu_2014_1}, where they applied the Bennett Acceptance Ratio (BAR) method \cite{Bennett_1976} to independent samples obtained with different values of $\lambda_\text{vdW}$ and $\lambda_\text{Coul}$.
-Moreover, the $\Delta G_\text{sim}$ value we computed for \ce{[emim][Tf_2N]} is very close to the one obtained by Kerl \textit{et al}.
+Moreover, the $\Delta G_\text{sim}$ value we computed for \ce{[emim][NTf_2]} is very close to the one obtained by Kerl \textit{et al}.
 \cite{Kerl__2017} ($-0.534 ~\mathrm{kcal/mol}$, with no reported uncertainty) using the Free-Energy Perturbation (FEP) method \cite{Zwanzig_1954}.
@@
 \cite{Koller_2012} does in the case of \ce{[emim][B(CN)_4]}, the one of K\"{o}ddermann \textit{et al}.
-\cite{Koddermann_2007} accurately predicts the Henry's law constant of \ce{CO_2} in \ce{[emim][Tf_2N]}.
-A comparison between the values of $\Delta G_\text{sim}$ obtained from these models, shown in Table \ref{table:henry}, suggests that the solvation of \ce{CO_2} takes place more favorably in \ce{[emim][B(CN)_4]} than in \ce{[emim][Tf_2N]}.
+\cite{Koddermann_2007} accurately predicts the Henry's law constant of \ce{CO_2} in \ce{[emim][NTf_2]}.
+A comparison between the values of $\Delta G_\text{sim}$ obtained from these models, shown in Table \ref{table:henry}, suggests that the solvation of \ce{CO_2} takes place more favorably in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}.
 The fact that $K_s$ has almost the same value in both cases is due to a compensation promoted by the distinct molar densities of these ionic liquids.
 Spatial distribution functions (SDFs) \cite{Svishchev_1993} can help us visualizing how differently the solvent ions interact with the solute molecule.
-By using TRAVIS \cite{Brehm_2011}, we have obtained SDFs of both cation and anion around a \ce{CO_2} molecule, sampled from MD trajectories of either \ce{CO_2}+\ce{[emim][B(CN)_4]} or \ce{CO_2}+\ce{[emim][Tf_2N]} systems simulated at $T = 298.0~\text{K}$, $p = 0.1~\mathrm{MPa}$, and $x_\mathrm{CO_2} = 0.1$.
+By using TRAVIS \cite{Brehm_2011}, we have obtained SDFs of both cation and anion around a \ce{CO_2} molecule, sampled from MD trajectories of either \ce{CO_2}+\ce{[emim][B(CN)_4]} or \ce{CO_2}+\ce{[emim][NTf_2]} systems simulated at $T = 298.0~\text{K}$, $p = 0.1~\mathrm{MPa}$, and $x_\mathrm{CO_2} = 0.1$.
 The slightly larger \ce{CO_2} concentration considered here is meant to improve statistics.
@@
 By comparing Figs.~\ref{fig:sdf_ions}(a) and \ref{fig:sdf_ions}(b), we note that the gap between the regions occupied by the anion and the cation is smaller in the case of \ce{[emim][B(CN)_4]}.
-In addition, the first solvation shell corresponding to \ce{[B(CN)_4]^-} occurs at a slightly shorter distance than that corresponding to \ce{[Tf_2N]^-}, as one can clearly see by a direct comparison done in Fig.~\ref{fig:sdf_ions}(c).
+In addition, the first solvation shell corresponding to \ce{[B(CN)_4]^-} occurs at a slightly shorter distance than that corresponding to \ce{[NTf_2]^-}, as one can clearly see by a direct comparison done in Fig.~\ref{fig:sdf_ions}(c).
 This is in part due to the difference in size of these two anions.
 The result is a higher density of negative charges around the carbon atom of \ce{CO_2}, whose point-charge is positive as a consequence of the oxygen's high electronegativity.
-This seems to induce a greater stability of \ce{CO_2} when solvated in \ce{[emim][B(CN)_4]}, rather than in \ce{[emim][Tf_2N]}, possibly resulting in enhanced solubility.
+This seems to induce a greater stability of \ce{CO_2} when solvated in \ce{[emim][B(CN)_4]}, rather than in \ce{[emim][NTf_2]}, possibly resulting in enhanced solubility.
 However, the mentioned similarity in the Henry's law constants could cause such enhancement to go unnoticed.
@@
 }
-\caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[Tf_2N]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
+\caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[NTf_2]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
 Fig. (c) corresponds to the SDFs of the anions plotted together.}
@@
 
-\subsection{Concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}}
+\subsection{Concentrated solutions of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
 \label{sec:results_conc}
@@
 We have selected these specific conditions because of the proximity observed in the molality of \ce{CO_2} ($m_s$).
-It is worth noting that the marked difference in the molar fractions of \ce{CO_2} in Table~\ref{table:solv} does not imply that \ce{[emim][Tf_2N]} is a better solvent than \ce{[emim][B(CN)_4]}, thus exemplifying the observation made by Carvalho \textit{et al}.
+It is worth noting that the marked difference in the molar fractions of \ce{CO_2} in Table~\ref{table:solv} does not imply that \ce{[emim][NTf_2]} is a better solvent than \ce{[emim][B(CN)_4]}, thus exemplifying the observation made by Carvalho \textit{et al}.
 \cite{Carvalho_2016} and discussed here in Sec.~\ref{sec:intro}.
@@
 	\centering
-	\caption{Thermodynamic conditions, based on the experimental observations of Refs.~\citenum{Makino_2014} and \citenum{Schilderman_2007}, employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}, as well as the results obtained via expanded ensemble simulations.}
+	\caption{Thermodynamic conditions, based on the experimental observations of Refs.~\citenum{Makino_2014} and \citenum{Schilderman_2007}, employed in the solvation study at high concentrations of \ce{CO_2} in \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, as well as the results obtained via expanded ensemble simulations.}
 	\begin{tabular}{ccc}
 		\hline\hline
-		IL & \ce{[emim][B(CN)_4]}  & \ce{[emim][Tf_2N]} \\
+		IL & \ce{[emim][B(CN)_4]}  & \ce{[emim][NTf_2]} \\
 		\hline
@@
 \cite{Koller_2012} was the one employed for simulating \ce{[emim][B(CN)_4]}.
-The computed solvation free energies for the systems \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][Tf_2N]} were $-0.755 \pm 0.009 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005~\mathrm{kcal/mol}$, respectively.
+The computed solvation free energies for the systems \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]} were $-0.755 \pm 0.009 ~\mathrm{kcal/mol}$ and $-0.542 \pm 0.005~\mathrm{kcal/mol}$, respectively.
 Using these values as inputs in Eq.~\eqref{eq:equilibrium pressure}, we obtained pressure values of $1.854~\mathrm{MPa}$ and $3.893~\mathrm{MPa}$, as reported in Table~\ref{table:solv}.
 The corresponding gas-phase fugacities of \ce{CO_2} ($f_s^g$) computed by Eq.~\eqref{eq:fgas_d} are given in Table~\ref{table:solv}, as well.
-The results make clear that assuming ideal gas ($p = f_s^g$) would have been an oversimplification, specially in the case of \ce{[emim][Tf_2N]}.
+The results make clear that assuming ideal gas ($p = f_s^g$) would have been an oversimplification, specially in the case of \ce{[emim][NTf_2]}.
 
-In order to obtain $\Delta G_\text{sim} (p)$ and $c_s(p)$, we carried out extra simulations at pressure values  of p = (1.722, 1.823) MPa  for \ce{CO_2}+\ce{[emim][B(CN)_4]} and at p = (4.053, 4.458) MPa for \ce{CO_2}+\ce{[emim][Tf_2N]}.
+In order to obtain $\Delta G_\text{sim} (p)$ and $c_s(p)$, we carried out extra simulations at pressure values  of p = (1.722, 1.823) MPa  for \ce{CO_2}+\ce{[emim][B(CN)_4]} and at p = (4.053, 4.458) MPa for \ce{CO_2}+\ce{[emim][NTf_2]}.
 In this case, we considered a wider range of pressure, given the departure from ideal gas behavior mentioned above.
@@
 In Fig.~\ref{fig:pressure}, we show for both systems the results of $\Delta G_\text{sim}$, together with the curve of $\Delta G_\text{solv}$ defined by Eq.~\eqref{eq:equilibrium pressure}.
-Although not shown here, the changes in density are negligible: 0.05 \% and 0.07 \% for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][Tf_2N]}, respectively.
+Although not shown here, the changes in density are negligible: 0.05 \% and 0.07 \% for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]}, respectively.
 In addition, $\Delta G_\text{sim}$ does not vary appreciably with pressure, at least over the range of experimental data considered here. 
-This results in small corrections to the equilibrium pressures of Table~\ref{table:solv}: the intersection points are 1.807 MPa and 4.106 MPa, for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][Tf_2N]}, respectively.
+This results in small corrections to the equilibrium pressures of Table~\ref{table:solv}: the intersection points are 1.807 MPa and 4.106 MPa, for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]}, respectively.
 These values did not depart considerably from the specified values, meaning that our results sustain the experimental observations.
-Therefore, as the pressure required to reach the same equilibrium molal concentration of \ce{CO_2} in the liquid phase is smaller for \ce{[emim][B(CN)_4]} than for \ce{[emim][Tf_2N]}, our results confirm that the former is a better solvent than the latter.
+Therefore, as the pressure required to reach the same equilibrium molal concentration of \ce{CO_2} in the liquid phase is smaller for \ce{[emim][B(CN)_4]} than for \ce{[emim][NTf_2]}, our results confirm that the former is a better solvent than the latter.
 This confirmation was possible by simulating a purely physical absorption, without considering any quantum effect.
@@
 
-	\subfloat[\ce{CO_2}+\ce{[emim][Tf_2N]}]{  
+	\subfloat[\ce{CO_2}+\ce{[emim][NTf_2]}]{  
 		\includegraphics[width=\linewidth]{pressure_ludwig.pdf}}
@@
 Due to the availability of experimental data \cite{Yan_2010, Doma_ska_2011}, the solutes chosen for this study are benzene, hexane, cyclohexane, ethanol, and water.
-Uncertainties in activity coefficients were calculated using error propagation, as done for $K_s$.
+Uncertainties in activity coefficients were calculated using error propagation, such as done for $K_s$.
 
@@
 We focused also on exploring alternative simulation strategies with the goal of gaining computational efficiency.
-Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}, we concluded that the Damped-Shifted-Force method for electrostatic interactions, with a damping factor $\alpha = 0.2 ~\text{\AA}^{-1}$, is a suitable strategy.
+Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}, we concluded that the Damped-Shifted-Force method for electrostatic interactions, with a damping factor $\alpha = 0.2 ~\text{\AA}^{-1}$, is a suitable strategy.
 Other improvement was the use of rigid bodies to simulate \ce{[emim][B(CN)_4]}.
@@
 
-The solvation free energy results suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][Tf_2N]}, despite the similarity in the Henry's law constants observed in both cases.
-This picture is further confirmed at high \ce{CO_2} concentrations, in which the simulations correctly predicted that a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}, as compared to \ce{[emim][Tf_2N]} in an equal-mass basis.
+The solvation free energy results suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}, despite the similarity in the Henry's law constants observed in both cases.
+This picture is further confirmed at high \ce{CO_2} concentrations, in which the simulations correctly predicted that a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}, as compared to \ce{[emim][NTf_2]} in an equal-mass basis.
 

### 2019-02-19 reviewer_response.tex
Alpha version for resubmission

@@
 
-Thank you for your message forwarding the reviewers’ comments on our manuscript entitled \textit{A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquid \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}.
-We have carefully addressed the comments and suggestions of the reviewers, which required us to make changes in the text.
-The most substantial revision took place in Sec.~5.3, for which we carried out additional simulations.
-In addition, we have included the full names of the ionic liquids in the abstract.
+Thank you for your message forwarding the reviewers’ comments on our manuscript ``A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquid \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}''.
+We have carefully addressed the comments and suggestions, which required us to make changes in the text.
+The most substantial revision took place in Sec.~5.3, for which we carried out additional simulations and included new figures.
+Besides, we have included the full names of the ionic liquids in the abstract.
 To facilitate your evaluation, we attached an annotated version in which all removed text has been crossed out in red and all new content is colored in blue.
@@
 
-\textbf{Answer}: The reviewer is right. We applied analytic tail corrections to the LJ interactions for all systems investigated. This information has been included in page 5 of the manuscript.
+\textbf{Answer}: The reviewer is right. We applied standard tail corrections to the LJ interactions for all systems under investigation. This information was included on page 5 of the manuscript.
 
@@
 
-\textbf{Answer}: The differences in density between our results and those reported by Koller \textit{et al.} \cite{Koller_2012}, Batista \textit{et al.} \cite{Batista_2015}, Liu \textit{et al.} \cite{Liu_2014} and Weber and Kirchner \cite{Weber_2016} are, respectively: 1 \% , 6.2 \%, 1.8 \% and 0.5 \%.
-With the exception of the force field due to Batista \textit{et al.} \cite{Batista_2015}, the discrepancies are not considerable.
-In general, we carefully followed the simulation setup reported by those authors, except for the number of ion pairs and the software package.
-For instance, Koller and co-workers \cite{Koller_2012} simulated 58 ions pairs using GROMACS, while we considered 250 ion pairs and the LAMMPS software package.
+\textbf{Answer}: The differences in density between our results and those reported by Koller \textit{et al}.
+\cite{Koller_2012}, Batista \textit{et al}.
+\cite{Batista_2015}, Liu \textit{et al}.
+\cite{Liu_2014}, and Weber and Kirchner \cite{Weber_2016} are, respectively, 1.0\% , 6.2\%, 1.8\%, and 0.5\%.
+With the exception of the force field introduced by Batista \textit{et al}. \cite{Batista_2015}, the discrepancies are small.
+In all cases, we tried to carefully follow the simulation setup reported by those authors, except for the number of ion pairs.
+For instance, Koller and co-workers \cite{Koller_2012} simulated 58 ions pairs, while we considered 250 ion pairs.
 Small differences are then expected.
@@
 
-\textbf{Answer}: In page 5 of the manuscript we specify the numerical integrators used to carry out the MD simulations.
-Considering hybrid systems of flexible and rigid molecules is straightforward in LAMMPS, since it allows to define groups of molecules and apply a different numerical integrator to each group.
+\textbf{Answer}: On page 5 of the manuscript, we specify the numerical integrators used to carry out the MD simulations.
+In fact, the software package we employed for the simulations, LAMMPS, is already prepared for dealing with hybrid systems containing flexible and rigid molecules.
+For this purpose, it allows us to define groups of atoms and apply different integrators and constraints to each group.
+When this is done, the action of a barostat will scale the positions of all atoms that pertain to flexible molecules, but it will only scale the center-of-mass positions of rigid molecules (or rigid atom groups, in general).
 
-{\color{blue}{5)It would be interesting if at least for the case of CO2 an isotherm was calculated and included in the paper.}}
+{\color{blue}{5) It would be interesting if at least for the case of CO2 an isotherm was calculated and included in the paper.}}
 
-\textbf{Answer}: We agree with the reviewer that computing an isotherm would be interesting.
-However, this computation requires to carry out extra simulations for different numbers of solute molecules, which is beyond the scope of this work.
+\textbf{Answer}: We agree with the reviewer.
+However, with the methodology we adopted, such computation would require a large number of simulations to be carried out at several pressures and several coupling parameter values for every different number of solute molecules.
+Of course, other approaches could be employed for this type of investigation, such as Grand Canonical Monte Carlo simulations, for instance.
+While we agree that including isotherms would be of interest, the effort required for doing it would be exceedingly large.
+Moreover, we believe that, without obtaining full isotherms, we were able to answer important questions regarding the physical nature of the different \ce{CO_2} solubilities in \ce{[emim][B(CN)_4]} and \ce{[emim][NTF_2]}.
+Thus, we ask both the reviewer and the editor to consider publishing our findings without adding these isotherms.
 
@@
 
-We are grateful for the comments and suggestions of the second reviewer.
+\textbf{Answer}: We sincerely thank the reviewer for the kind comments and helpful suggestions. They have all been considered and are answered below.
 
@@
 
-\textbf{Answer}: Instead of the number of runs, in page 6 we included the total simulation time for each system, since it might be a more informative measure of computational effort.
-The information about mixing rules and uncertainties calculations have been included in pages 5, 9 and 12.
+\textbf{Answer}: It is true that such information was missing and we thank the reviewer for pointing this out.
+We have included, on page 6, the total simulation time executed for each system (instead of the number of runs).
+Information about the employed mixing rules and uncertainty calculations are now included on pages 5, 9, and 12.
+Please note that these page numbers refer to the annotated version of the manuscript.
 
@@
 
-\textbf{Answer}:We haven't done a study of dynamic properties.
-We have mainly focused on predicting solvation properties given the potential of the investigated ionic liquids in separation processes for \ce{CO_2}.
+\textbf{Answer}: Unfortunately, we have not performed any study of dynamic properties.
+We have mainly focused on predicting solvation properties, given our goal of investigating differences in the ability of ionic liquids to absorb \ce{CO_2}.
+We agree, however, that being able to predict transport properties would be very important for the design of actual separation processes.
+It is, therefore, an important subject to be considered in future investigations.
 
 {\color{blue}{3.
-The results for the simulated solvation free energies of benzene, hexane, and water showed relatively large deviations from experimental data in the order of 10 \%, while the results for ethanol match.
+The results for the simulated solvation free energies of benzene, hexane, and water showed relatively large deviations from experimental data in the order of 10\%, while the results for ethanol match.
 However, for the infinite-dilution activity coefficient of these solutes in the IL [emim][B(CN)4], hexane deviates significantly stronger than benzene, ethanol, and water.
@@
 
-\textbf{Answer}: The reviewer is right and in order to analyze the strong deviation observed for hexane, we computed an experimental solvation free energy of this solute in  \ce{[emim][B(CN)_4]}, as shown in page 14.
-The results from simulation show a favorable solvation, in contradiction with the experimental data.
-That is why we emphasize in the conclusions that a future revision of the models used for the solutes is necessary.
+\textbf{Answer}: The reviewer is totally right.
+In order to analyze the strong deviation observed for hexane, we have included a new comparison of solvation free energies of this and other solutes in \ce{[emim][B(CN)_4]} computed exclusively from experimental data and computed from simulations.
+This is shown on page 14, where a new figure (Fig. 7) can be found.
+The simulation results predict a favorable solvation of hexane, which contradicts the experimental data.
+This is why we emphasize in the conclusions that a future revision of the models used for the solutes is necessary.
 
@@
 
-\textbf{Answer}: This has been acknowledged throughout the manuscript.
+\textbf{Answer}: We accepted the reviewer's suggestion and made the necessary modifications throughout the manuscript.
 

### 2019-02-19 ionic_liquids.tex
Alpha version for resubmission

@@
 \label{eq:equilibrium pressure}
-y_s \exp\left( \frac{B_s p}{R T} \right) p = c_s(p) R T \exp \left( \frac{\Delta G_\text{solv}}{R T} \right),
+y_s \exp\left( \frac{B_s p}{R T} \right) p = c_s R T \exp \left( \frac{\Delta G_\text{solv}}{R T} \right),
 \end{equation}
@@
 \end{equation}
-with the uncertainties in free energies calculated by MBAR \cite{Shirts_2008}.
+with the free-energy uncertainties computed by MBAR \cite{Shirts_2008}.
 
@@
 
-In order to obtain $\Delta G_\text{sim} (p)$ and $c_s(p)$, we carried out extra simulations at pressure values  of p = (1.722, 1.823) MPa  for \ce{CO_2}+\ce{[emim][B(CN)_4]} and at p = (4.053, 4.458) MPa for \ce{CO_2}+\ce{[emim][NTf_2]}.
-In this case, we considered a wider range of pressure, given the departure from ideal gas behavior mentioned above.
-As described in Sec.~\ref{sec:partial_pressure}, $\Delta G_\text{sim}$ and $c_s$ were interpolated to intermediate pressures by reweighting using MBAR \cite{Shirts_2008}.
-In Fig.~\ref{fig:pressure}, we show for both systems the results of $\Delta G_\text{sim}$, together with the curve of $\Delta G_\text{solv}$ defined by Eq.~\eqref{eq:equilibrium pressure}.
-Although not shown here, the changes in density are negligible: 0.05 \% and 0.07 \% for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]}, respectively.
-In addition, $\Delta G_\text{sim}$ does not vary appreciably with pressure, at least over the range of experimental data considered here. 
-This results in small corrections to the equilibrium pressures of Table~\ref{table:solv}: the intersection points are 1.807 MPa and 4.106 MPa, for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]}, respectively.
-These values did not depart considerably from the specified values, meaning that our results sustain the experimental observations.
+As one can see in Table~\ref{table:solv}, the estimated equilibrium pressure differs from the specified value for both ionic liquids.
+In order to obtain $\Delta G_\text{sim}(p)$ and $c_s(p)$ so that the proper corrections could be made, we carried out additional simulations at some nearby pressures in each case.
+Then, new results were obtained at $1.722$ and $1.823~\mathrm{MPa}$ for \ce{CO_2}+\ce{[emim][B(CN)_4]} and at $4.053$ and $4.458~\mathrm{MPa}$ for \ce{CO_2}+\ce{[emim][NTf_2]}.
+These ranges were selected after carrying out some short, exploratory simulations.
+%In this case, we considered a wider range of pressure, given the departure from ideal gas behavior mentioned above.
+As described in Sec.~\ref{sec:partial_pressure}, $\Delta G_\text{sim}$ and $c_s$ were interpolated along the whole pressure ranges by doing reweighting via MBAR \cite{Shirts_2008}.
+Each MBAR analysis involved 60 simulation samples (20 coupling parameter states at 3 distinct pressures).
+In Fig.~\ref{fig:pressure}, we show the results of $\Delta G_\text{sim}(p)$ for both systems, together with the corresponding curves of $\Delta G_\text{solv}(p)$ defined by Eq.~\eqref{eq:equilibrium pressure}.
+The observed variations in density throughout the pressure ranges (results not shown) were negligible: 0.05\% and 0.07\% for \ce{CO_2}+\ce{[emim][B(CN)_4]} and \ce{CO_2}+\ce{[emim][NTf_2]}, respectively.
+It is also clear from Fig.~\ref{fig:pressure} that $\Delta G_\text{sim}$ does not vary appreciably either.
+As a result, the corrections required for the equilibrium pressures shown in Table~\ref{table:solv} are small.
+The intersection points in the mentioned curves occur at 1.807 MPa for \ce{CO_2}+\ce{[emim][B(CN)_4]} and at 4.106 MPa \ce{CO_2}+\ce{[emim][NTf_2]}, meaning that our results corroborate the experimental observations.
 Therefore, as the pressure required to reach the same equilibrium molal concentration of \ce{CO_2} in the liquid phase is smaller for \ce{[emim][B(CN)_4]} than for \ce{[emim][NTf_2]}, our results confirm that the former is a better solvent than the latter.
@@
 Due to the availability of experimental data \cite{Yan_2010, Doma_ska_2011}, the solutes chosen for this study are benzene, hexane, cyclohexane, ethanol, and water.
-Uncertainties in activity coefficients were calculated using error propagation, such as done for $K_s$.
+Uncertainties in activity coefficients were evaluated by error propagation, such as done for Henry's law constants.
 
@@
 
-In Fig.~\ref{fig:deltag_solutes}, we show the simulated solvation free energies versus the experimental results.
-These were obtained by using $\Delta G^{0}_\text{exp}$ of Table~\ref{table:mu_solutes} and $\gamma^\infty$  from Ref.
-\cite{Doma_ska_2011} as inputs in Eq.~\eqref{eq:gamma}.
-Cyclohexane was not considered, given that $\Delta G^{0}_\text{exp}$ is not available.
-For benzene, ethanol and water the results from simulations are consistent with the negative experimental values.
-However, for hexane the simulations predict a favorable solvation, in clear contradiction with the experimental data.
-From the individual contributions of $\Delta G_\text{vdW}$ and $\Delta G_\text{Coul}$, we can conclude that the vdW contribution is largely underestimated.
-Also, in the case of hexane, one can see in Table \ref{table:gamma} that the available experimental values of $\gamma^\infty$ in \ce{[emim][B(CN)_4]} at very close temperatures ($298.15~\text{K}$ and $303~\text{K}$) differ considerably.
+In Fig.~\ref{fig:deltag_solutes}, we compare solvation free energies obtained by simulation with those computed from experimental results.
+These were obtained by using $\Delta G^{0}_\text{exp}$ of Table~\ref{table:mu_solutes} and $\gamma^\infty$ from Ref. ~\citenum{Doma_ska_2011} as inputs to Eq.~\eqref{eq:gamma}.
+Because $\Delta G^{0}_\text{exp}$ is not available for cyclohexane, such substance was not considered in the comparison.
+For benzene, ethanol, and water, the results from simulations are consistent with the negative experimental values.
+For hexane, however, the simulation prediction of a favorable solvation is in clear contradiction with the experimental data.
+From the individual contributions of $\Delta G_\text{vdW}$ and $\Delta G_\text{Coul}$, we can conclude that the van der Waals contribution is largely underestimated.
+Also, in the case of hexane, one can see in Table~\ref{table:gamma} that the available experimental values of $\gamma^\infty$ in \ce{[emim][B(CN)_4]} at very close temperatures ($298.15~\text{K}$ and $303~\text{K}$) differ considerably.
 It is, therefore, difficult to assess the reliability of our results in this case.
@@
 	\includegraphics[width=\linewidth]{delta_g_sim_exp}
-	\caption{Simulated free energy $\Delta G_\text{sim}$ versus the experimental result at $T = 298.15~\text{K}$ for the solutes hexane, benzene, ethanol and water in \ce{[emim][B(CN)_4]}.}
+	\caption{Solvation free energies at infinite dilution obtained from simulations ($\Delta G_\text{sim}$) in comparison to values computed from experimental data ($\Delta G_\text{exp}$) for the solutes hexane, benzene, ethanol, and water in \ce{[emim][B(CN)_4]}  at $T = 298.15~\text{K}$.}
 	\label{fig:deltag_solutes}
@@
 We have found that only the force field developed by Koller \textit{et al}. \cite{Koller_2012} is able to perform such task, with a small relative error of 2.8\%.
-A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in the original work, which also allows to accurately reproduce the experimental density of the pure substance.
+A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in the original work, which also allows us to accurately reproduce the experimental density of the pure substance.
 
@@
 
-The solvation free energy results suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}, despite the similarity in the Henry's law constants observed in both cases.
+The solvation free energy results at infinite dilution condition suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][NTf_2]}, despite the similarity in the Henry's law constants observed in both cases.
 This picture is further confirmed at high \ce{CO_2} concentrations, in which the simulations correctly predicted that a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}, as compared to \ce{[emim][NTf_2]} in an equal-mass basis.

### 2019-02-19 reviewer_response.tex
Resubmitted version

@@
 In this case, however, important computational details are missing in the original paper, such as the method for computing electrostatic interactions, as well as the factors for scaling the 1-4 non-bonded interactions.
-Considering these various factors, we did not focus on reproducing the results of these references, but rather to use the force field parameters reported by the corresponding authors in order to find those that best reproduce the experimental Henry constant of \ce{CO_2}.
+Considering these various factors, we did not focus on reproducing the results of these references, but rather on using the force field parameters reported therein and find those parameter sets that best reproduce the experimental Henry's law constants of \ce{CO_2}.
 

### 2019-02-19 ionic_liquids.tex
Resubmitted version

@@
 $\alpha = 0$) resulted in improved chemical potential predictions.
-That cutoff distance was also used for truncating the LJ interactions, for which we applied analytical tail corrections \cite{allen}.
-In addition, we used the Lorentz-Berthelot mixing rules to calculate the cross LJ interactions, except for the solutes modeled with the OPLS-AA force fields, which employs geometric combining rules.
+The same cutoff distance was used for truncating the LJ interactions, for which we applied analytical tail corrections \cite{allen}.
+In addition, we used the Lorentz-Berthelot mixing rule to calculate the LJ interactions of unlike atoms, except for the solutes modeled with the OPLS-AA force fields, in which geometric combining rules are employed.
 
@@
 
-In order to obtain minimum-energy conformations, we first carried out MD simulations of isolated ion pairs.
+In order to obtain minimum-energy conformations, we started by carrying out MD simulations of isolated ion pairs.
 For this, we used a Nos\'{e}-Hoover chain thermostat \cite{Martyna1992} with set-point temperature gradually changing down to nearly $0~\text{K}$.
